### 2014-06-16 draft.tex
fist commit

% vim: set sts=4 et :
\documentclass[aps,prd,reprint,nofootinbib,preprintnumbers]{revtex4}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{xcolor}

%% Shortcuts %%
\newcommand{\dd}{\text{d}}
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
\newcommand{\GeV}{\text{GeV}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\let\eps\varepsilon
\newcommand{\what}[1]{\widehat{#1}}
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
\DeclareMathOperator{\cov}{Cov}

%% Draft Macros %%
\newcommand{\todo}[1]{{\color{red}\bf ToDo: #1}}
\newcommand{\danny}[1]{{\color{purple}#1}}
\newcommand{\fred}[1]{{\color{gold!85!black}#1}}
\newcommand{\nico}[1]{{\color{green!85!black}#1}}
\newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}

\begin{document}

\allowdisplaybreaks

\preprint{SI-HEP-2014-xx}
\title{Sample Based Determination of Angular Observables}
\author{Frederik Beaujean}
\email{frederik.beaujean@lmu.de}
\affiliation{C2PAP, Universe Cluster, Ludwig-Maximilians-Universit\"at M\"unchen, Garching, Germany}
\author{Marcin Chrzaszcz}
\email{chrzaszcz.marcin@gmail.com}
\author{Nicola Serra}
\email{nicola.serra@cern.ch}
\affiliation{Physik-Institut, Universit\"at Z\"urich, Z\"urich, Switzerland}
\author{Danny van Dyk}
\email{vandyk@tp1.physik.uni-siegen.de}
\affiliation{Theoretische Physik 1, Naturwissenschaftlich-Technische Fakult\"at,
Universit\"at Siegen, Siegen, Germany}

\begin{abstract}
We study means to determine angular observables for a generic angular distribution
of either decays or scattering processes. \dots
\end{abstract}

\maketitle

\section{Introduction}
\label{sec:intro}

In this letter we study how to obtain a set of angular observables $P_i$
that arise in a generic multi-body processes without the need to carry out
an explicit fit of an angular distribution to data. Instead, we present a method
that only relies on orthogonality of angular functions, and estimation of integrals
by means of Monte Carlo techniques.\\

The initial motivation for studying what we wish to call the \emph{Method of Moments}
is the determination of angular observables in the decay rare, FCNC-mediated decay
$\bar{B}\to \bar{K}^*(\to \bar{K}\pi)\ell^+\ell^-$. However, we emphasize that
he method we describe in the remainder of this letter is applicable to arbitrary
decay or scattering processes.\\

For the purpose of this work, let $P_i$ be a set of functions of $m$ non-angular
kinematic variables $\nuvec$, $P_i \equiv P_i(\nuvec)$, with $\nuvec = (\nu_1, \dots \nu_m)$.
These include, among others, invariant masses or center of mass energies pertinent
to the respective decay or scattering processes. Let us further assume the angular
observables to be defined via a suitably factorizing probability distribution (PDF),
\begin{align}
    \label{eq:def-P}
    P(\nuvec, \thvec) = \sum_k P_i(\nuvec) \times f_i(\thvec)\,,
\end{align}
Here, the dependence on the $n$ decay angles $\thvec = (\theta_1, \dots, \theta_n)$ has been
explicitly factored out in terms of the angular functions $f_i(\thvec)$, which we assume to fulfill the
orthonormality relations
\begin{equation}
    \label{eq:def-ortho-rel}
    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^n \theta = \delta_{ij}\,.
\end{equation}
(For the purpose of this letter, however, it suffices that the system of angular
functions $f_i(\thvec)$ can be transformed into an orthonorml basis. The transformations to these
bases for a selection of decays has been written out in the appendices \ref{app:btokll} through
\ref{app:lambdabtolambdall}.)\\

For particle decays, we $P$ is expressed in terms of the fully differential decay width,
\begin{align}
    \label{eq:def-P-decay}
    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\dd^{n+m}\Gamma}{\dd \nu_1 \dots \dd \nu_m\, \dd \theta_1 \dots \theta_n}\,,
\end{align}
where $\Gamma$ is the total decay width. For a scattering process, one can similarly use
\begin{align}
    \label{eq:def-P-scattering}
    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\dd^{n+m}\sigma}{\dd \nu_1 \dots \dd \nu_m\, \dd \theta_1 \dots \theta_n}\,,
\end{align}
where the total cross section $\sigma$ is used for the normalisation. Since the determination of
the total decay width or total cross section can be quite difficult, we emphasize that different normalizations for
$P$ can be used. For instance, the total decay width (or cross section) of the process of interest can be replaced
by the corresponding quantity of a control-channel process.\\

In the remainder of this letter we discuss how to obtain the angular observables $P_i(\nuvec)$ in an experimental
setup where each recorded event is (approximately) as variate of $P$.
We lay down the groundwork in section \ref{sec:sample-based-det}. Section \ref{sec:systematics} is dedicated to
the impact of systematic effects, such as mismodelling of the underlying physics and detector acceptance
effects. Numerical studies for one uni-angular and one triple-angular distribution are provided in section
\ref{sec:numerics}. In a series of appendices we discuss the relevant orthonormal bases of angular functions
at the hand of the several rare $b$ decays.

\section{Sample Based Determination}
\label{sec:sample-based-det}

From the orthonormality relations \refeq{def-ortho-rel} follows that a single angular observable $P_i$
can be projected out of the full PDF $P$ by means of
\begin{equation}
    \label{eq:det-Pi-analytical}
    P_i(\nuvec) = \int_{\thvec = 0}^{2\pi} f_i(\thvec) P(\nuvec, \thvec) \dd^n \theta\,.
\end{equation}
In point of fact, $P_i$ is the $f_i$-moment of the PDF $P$. Additionally, Integration over the non-angular variables yields
\begin{equation}
    \langle P_i\rangle
    \equiv \int P_i(\nuvec) \dd^m \nu
    = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^n\theta\right]\dd^m \nu\,.
\end{equation}
The remainder of this section is describes the method of moments, in which we replace the
analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\

The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
$g(x)$ under the probability density $P(x)$,
\begin{equation}
    E_P[g] \equiv \int g(x) P(x) \dd x
\end{equation}
can be replaced \citeneeded by an MC estimator $\what{E_P[g]}$
\begin{equation}
    \label{eq:mc-id}
    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{N} \sum_{k=1} g(x^{(k)})\,.
\end{equation}
For the purpose of the estimation, the variates $x^{(k)}$, $k = 1, \dots, N$ must distributed under $P$,
\begin{equation}
    x^{(k)} \sim P\,.
\end{equation}
(Throughout this letter we denote all MC estimators with a wide hat.)\\

We assume, for a moment, that $P$ describes the distribution of the underlying
physical process truthfully. In that case, all events detected in an experimental setup are in fact, up to
detection efficiencies, distributed as $P$. Application of \refeq{mc-id} then yields
\begin{equation}
    \langle P_i\rangle \to \widehat{\langle P_i\rangle} = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)})\,.
\end{equation}
However, it is often of interest to obtain the $\nuvec$-integrated observables for
certain $\nuvec$ ranges, i.e. binned measurements of $\langle P_i\rangle$\footnote{%
We refer for example to the determination of the angular observables $J_i$ in $\bar{B}\to\bar{K}^*\ell^+\ell^-$
decays, see e.g. \cite{Aaij:2013iag}. For details on the relation between the $P_i$ and the angular observable $J_i$ in the
aforementioned decay, we refer to appendix \ref{app:btokstarll}.
}.
Therefore, we introduce the bin-integrated quantities
\begin{align}
    \langle P_i\rangle_{\vec{a},\vec{b}}
    & = \int_{\vec{a}}^{\vec{b}} P_i(\nuvec) \dd^m \nu\\
    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^n\theta\right]\dd^m \nu\\
    & = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec)
        \theta^{(m)}(\nuvec - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec) \dd^n\theta\right]\dd^m \nu\,.
\end{align}
Application of \refeq{mc-id} immediately yields
\begin{equation}
    \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}
    = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)}) \theta^{(m)}(\nuvec^{(k)} - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec^{(k)})\,.
\end{equation}
This basically reduces the determination of $P_i$ to a (weighted) counting experiment. As a consequence,
the statistical error on $\what{P_i}$ can be expected to follow a multivariate gaussian distribution \citeneeded.
In this case, the covariance $\cov[\what{P_i},\what{P_j}]$ is of particular interest. The latter can be replaced
by a suitable MC estimator, the sample covariance
\begin{equation}
    \cov[\what{P}_i,\what{P}_j] \to \what{\cov}[\what{P}_i, \what{P}_j]_{\vec{a},\vec{b}}
        = \frac{1}{N - 1} \sum_{k=1}^{N} \big[\hat{f}_i^{(k)} - \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\hat{f}_j^{(k)} - \widehat{\langle P_j\rangle_{\vec{a},\vec{b}}}\big]
        \theta^{(m)}(\nuvec^{(k)} - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec^{(k)})\,.
\end{equation}

\section{Sources of Systematic Uncertainties}
\label{sec:systematics}

In \refsec{sample-based-det}, we assumed that the PDF $P$ described the physical reality accurately,
and that the experiment observed each event with perfect accuracy. In order to estimate systematic
uncertainties, we lift these assumptions.

\subsection{Mismodelling due to Contributions by Higher Partial Waves}
\label{sec:systematics:partial-waves}

\danny{
So far, we assumed that our underlying physical process was accurately described by our PDF $P$.
However, in several interesting processes we might only have an approximative result for $P$.
We will now show that this is the case for the interesting class four-body decays $B\to P_1 P_2 \ell_1 \bar\ell_2$,
which includes the rare $b\to s$-mediated $B$ decay $B \to K\pi\ell^+\ell^-$ and the $V_{ub}$ suppressed decay
$B\to \pi\pi\ell^+\bar\nu_\ell$. For the sake of clarity and simplicity, we will here discuss
the application of our method to the decay $B\to \pi\pi\ell^+\bar\nu_\ell$.\\

We now face the problem that $P$ has a given dependence on the dilepton helicity angle $\theta_1$
and the azimuthal angle $\theta_3$. However, the dipion system can have an arbitrary large
total angular momentum; only the its third component is restricted to $J^{\pi\pi}_z = -1,0,+1$.
Therefore, we will restrict integration to the angles $\theta_1$ and $\theta_3$. \dots
}

\subsection{Detector Acceptance Effects and Backgrounds}
\label{sec:systematics:acceptance}

Thanks to accurate detector simulations and control studies, the experimental analyses have become
remarkably good at removing detector acceptance effects. In this section we therefore assume that
there are only a small, residual acceptance effects left that affect the events. In particular, we
assume that the latter can be modelled as a modified probability density,
\begin{equation}
    \label{eq:PDFwithDE}
    P(\nuvec,\thvec) \to P(\nuvec,\thvec) \times \Omega(\thvec),
\end{equation}
where $\Omega$ is independent of the non-angular kinematics $\nuvec$. The latter assumption is only
is invalid in general. However, if residual angular acceptance only weakly depends on $\vec{\nu}$, one
can always choose appropriate bin $\vec{\nu}$ so that $\Omega$ is approximately constant with respect
to $\vec{\nu}$. For such a case we parametrize
\begin{equation}
    \Omega_{m,l}(\thvec) = \prod_{i=1}^{m} \Big[1 + \sum_{j=1}^l \eps_i^{(j)} p_j(\cos\theta_i)\big]
\end{equation}
where $p_j(\cos\theta_i)$ denotes the $j$th Legendre polynomial. Since we only consider residual
acceptance effects, we expect $\eps_i^{(j)} \ll 1$. \footnote{\danny{what are reasonable values/upper limits on the $\eps$?}}\\

\paragraph{Uniangular Distribution}
For definiteness and clarity, we consider first an uni-angular distribution $P(\theta)$.
In this case we can parametrize the PDF $P$ as
\begin{equation}
    P(\theta) = P_1 + P_2 \cos\theta + P_2 \cos^2\theta\,,
\end{equation}
which is a parametrization that has been used in the literature for $\bar{B}\to\bar{K}\ell^+\ell^-$ decays \cite{Bobeth:2007dw}.
While this system of angular functions is not orthonormal, it can easily be orthonormalized. For the basis of angular
functions, see \refapp{btokll}.
Considering detector acceptance effects up to second order in $\cos\theta$, the function $\Omega(\vec\theta)$ reads
\begin{equation}
    \Omega_{1,2}(\theta_1) = 1 + \eps_{1}^{(1)} \cos\theta + \frac{\eps_{1}^{(2)}}{2}\big(3 \cos^2\theta - 1\big)\qquad\eps_{1}^{(i)} = \order{\eps}\,.
\end{equation}
Inclusion of $\Omega_{1,2}$ as part of the PDF as proposed in \refeq{PDFwithDE} modifies the MC estimators for the angular observables.
We find
\begin{equation}
\begin{aligned}
    \wwhat{P_1} & = \Big(1 + \frac{\eps_{1}^{(2)}}{2}\Big) \what{P_1} + \frac{9 \eps_{1}^{(2)}}{70} \what{P_3}\\
    \wwhat{P_2} & = \Big(1 - \frac{2 \eps_{1}^{(2)}}{5}\Big) \what{P_2} - \eps_{1}^{(1)} \what{P_1} - \frac{3\eps_{1}^{(1)}}{5} \what{P_3}\\
    \wwhat{P_3} & = \Big(1 - \frac{11\eps_{1}^{(2)}}{14}\Big)\what{P_3} - \frac{3\eps_{1}^{(2)}}{2} \what{P_1} - \eps_{1}^{(1)} \what{P_2}\,.
\end{aligned}
\end{equation}
Here $\what{P_i}$ denotes the uncorrected estimators, while $\wwhat{P_i}$ denotes the efficiency-corrected estimators of the angular observables.\\

\paragraph{Triangular Distribution}

\begin{table*}
    \resizebox{.99\textwidth}{!}{\ensuremath{\input{tab-btokstarll-1to6.tex}}}\\[2.5\medskipamount]
    \resizebox{.99\textwidth}{!}{\ensuremath{\input{tab-btokstarll-7to12.tex}}}\\[2.5\medskipamount]
    \resizebox{.99\textwidth}{!}{\ensuremath{\input{tab-btokstarll-13to18.tex}}}
    \caption{The matrix $N_{ij}$ that appears in \refeq{eff-corrected-est-btokstarll}. Due to spatial
        constraints, we split its display into columns $j=1s,1c,1i,2s,2c,2i$ (top),
        $j=3,4,4i,5,5i,6s$ (middle) and $j=6c,7,7i,8,8i,9$ (bottom).
        \label{tab:eff-corrected-est-btokstarll}
    }
\end{table*}

As an example for a triangular distribution we use the decay $\bar{B}\to\bar{K}^*(\to \bar{K}\pi)\ell^+\ell^-$.
A parametrization of its angular distribution can be found in \refapp{btokstarll}.\\

For this type of distribution, we expand $\Omega_3$ to linear order in $\eps$,
\begin{equation}
    \Omega_{3,2}(\theta_1,\theta_2,\theta_3) = 1 + \sum_{i=1}^3 \sum_{j=1}^2 \eps_i^{(j)} p_j(\cos\theta_i) + \order{\eps^2}\,.
\end{equation}
This leads to a matrix-valued equation that relates the effiency-corrected estimators $\wwhat{P}_i$ to the uncorrected
estimators $\what{P}_j$,
\begin{equation}
    \label{eq:eff-corrected-est-btokstarll}
    \wwhat{P}_i = \sum_{j=1\text{s},\dots\,9} \big(\delta_{ij} + N_{ij}\big) \what{P}_j\,.
\end{equation}
We provide the matrix $N$ in \reftab{eff-corrected-est-btokstarll}.\\

\paragraph{Recipe to determine the acceptance effects}

The determination of the coefficients $\eps_i^{(j)}$ that parametrize the detectory effects is generally
a difficult task. Here, we will show a systematic method to determine these coefficients. \dots

\section{Toy Studies}
\label{sec:numerics}

\todo{
\begin{itemize}
    \item Simulate this for one angle $\theta_{1}$ (similar to $B\to K \ell^+\ell^-$) with varying samples sizes.
    \item Simulate this for three angles $\theta_{1\dots 3}$ (similar to $B\to K^*(\to K \pi)\ell^+\ell^-$) with varying samples sizes.
    \item Also, check explicitly the variance and covariance of the results for all sample sizes considered.
\end{itemize}}

\section{Conclusion}

In this letter \dots
\begin{enumerate}
    \item errors on the means are in very good approximation gaussian.
    \item correlation are small and faithfully model a multivariate gaussian.
\end{enumerate}

\acknowledgments

The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).
\dots
\danny{Potential people to read the manuscript: Jochen Dingfelder (Belle-II, Bonn), Ulrik Egede (LHCb, Imperial London), Christoph Langenbruch (LHCb, Warwick), Michel De Cian (LHCb, Heidelberg).}

\appendix

\section{Application to $\bar{B}\to\bar{K}\ell^+\ell^-$}
\label{app:btokll}

The PDF for the decay $\bar{B}\to\bar{K}\ell^+\ell^-$ has been calculated for the most
complete basis of dimension-six $b\to s \ell^+\ell^-$ operators. It reads \cite{Bobeth:2007dw,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
\end{equation}
where the basis of angular functions $f_i$ reads
\begin{equation}
\begin{aligned}
    f_1 & = 1\,, &
    f_2 & = \cos\theta_1\,, &
    f_2 & = \cos^2\theta_1\,.
\end{aligned}
\end{equation}
Here we denote the dilepton mass squared as $q^2$, and the dilepton helicity angle as $\theta_1 \equiv \theta_{\ell}$. We transform the PDF from a $\cos\theta_1$-dependence
to a $\theta_1$-dependence,
\begin{equation}
    P(q^2, \theta_1) = \sum_i P_i f_i(\cos\theta_1) \sin \theta_1\,.
\end{equation}

We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_i$ in the sence that
\begin{equation}
    \int_0^\pi \dd\theta_1 \hat{f}_i(\theta_1) f_j(\theta_1) \sin\theta_1 = \delta_{ij}\,,
\end{equation}
thereby enabling us to project out exactly one of the angular
observables $P_i(q^2)$
\begin{equation}
    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = P_i(q^2)\,.
\end{equation}
The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
    \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,.
\end{aligned}
\end{equation}

\section{Application to $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ (S-wave and P-wave)}
\label{app:btokstarll}

The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
for the most general basis of dimension-six $b\to s$ operators. It reads \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{J_{i}(q^2)}{\Gamma} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
\end{equation}
where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle.
The decay width is
\begin{equation}
    \Gamma = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
\end{equation}
The angular functions read \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
\begin{aligned}
    f_{1s} & = \sin^2\theta_2 &
    f_{1c} & = \cos^2\theta_2 &
    f_{1i} & = \cos\theta_2\\
    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\phi &
    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\phi\\
    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\phi & & &
    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\phi\\
    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\phi & & &
    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\phi\\
    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\phi & & &
    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\phi\\
    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\phi & & &
    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\phi\,.
\end{aligned}
\end{equation}
(Note here the notation, where indices with an \emph{i} arise only from S-wave/P-wave interference.)
In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i P_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $P_i(q^2) = J_i(q^2) / \Gamma$.\\

We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_j$ in the sense that
\begin{equation}
    \frac{3}{8\pi}\int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) f_j(\theta_1,\theta_2,\phi) \sin\theta_1 \sin\theta_2 = \delta_{ij}\,,
\end{equation}
thereby enabling us to project out exactly one of the angular
observables $P_i(q^2)$
\begin{equation}
    \int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) P(q^2, \theta_1,\theta_2,\phi) = P_i(q^2)\,.
\end{equation}
The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_1 - 42 \cos^2\theta_1\big) + \big(  45 \sin^2\theta_1 - 30 \cos^2\theta_1\big)\cos 2\theta_2}{64} \,,\\
    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_1 + 84 \cos^2\theta_1\big) + \big( -15 \sin^2\theta_1 + 60 \cos^2\theta_1\big)\cos 2\theta_2}{32} \,,\\
    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_1 - 30 \cos^2\theta_1\big) + \big(+135 \sin^2\theta_1 - 90 \cos^2\theta_1\big)\cos 2\theta_2}{64} \,,\\
    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_1 + 60 \cos^2\theta_1\big) + \big( -45 \sin^2\theta_1 +180 \cos^2\theta_1\big)\cos 2\theta_2}{32} \,,
\end{aligned}
\end{equation}
as well as
\begin{equation}
\begin{aligned}
    \hat{f}_{1sc}& = \frac{\big(21 + 15 \cos2\theta_2\big)\cos\theta_1}{16}               \,,&
    \hat{f}_{2sc}& = \frac{\big(15 + 45 \cos2\theta_2\big)\cos\theta_1}{16}               \,,\\
    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_1 -  6 \cos^2\theta_1\big)\cos\theta_2}{4} \,,&
    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_1 + 12 \cos^2\theta_1\big)\cos\theta_2}{2} \,,\\
    \hat{f}_{3}  & = \frac{75 \sin^2\theta_1 \sin^2\theta_2 \cos2\phi}{32}                \,,&
    \hat{f}_{9}  & = \frac{75 \sin^2\theta_1 \sin^2\theta_2 \sin2\phi}{32}                \,,\\
    \hat{f}_{4}  & = \frac{75 \sin 2\theta_1 \sin 2\theta_2 \cos \phi}{32}                \,,&
    \hat{f}_{4i} & = \frac{15 \sin  \theta_1 \sin 2\theta_2 \cos \phi}{8}                 \,,\\
    \hat{f}_{5}  & = \frac{15 \sin 2\theta_1 \sin  \theta_2 \cos \phi}{8}                 \,,&
    \hat{f}_{5i} & = \frac{3  \sin  \theta_1 \sin  \theta_2 \cos \phi}{2}                 \,,\\
    \hat{f}_{7}  & = \frac{15 \sin 2\theta_1 \sin  \theta_2 \sin \phi}{8}                 \,,&
    \hat{f}_{7i} & = \frac{3  \sin  \theta_1 \sin  \theta_2 \sin \phi}{2}                 \,,\\
    \hat{f}_{8}  & = \frac{75 \sin 2\theta_1 \sin 2\theta_2 \sin \phi}{32}                \,,&
    \hat{f}_{8i} & = \frac{15 \sin  \theta_1 \sin 2\theta_2 \sin \phi}{8}                 \,.
\end{aligned}
\end{equation}

\section{Application to $\bar{B}\to P_1 P_2\ell^+\ell^-$ (all partial waves)}
\label{app:btokpill}

The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays, with $P,P_1,P_2$ pseudoscalar mesons,
and $\ell_1$, $\bar\ell_2$ charge or neutral leptons, includes decays
such as e.g. $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$.
Their PDFs can generally be written as \cite{Lee:1992ih}
\begin{equation}
    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\Gamma}\frac{\dd^5 \Gamma}{\dd q^2\,\dd k^2\, \dd\cos\theta_1\,\dd\cos\theta_2\,\dd\phi} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
\end{equation}
where
\begin{equation}
\begin{aligned}
    f_1 & = 1\,,              &
    f_2 & = \cos 2\theta_1\,, &
    f_6 & = \cos  \theta_1\,, \\
    f_3 & = \sin^2\theta_1 \cos 2\phi\,,&
    f_4 & = \sin 2\theta_1 \cos  \phi\,,&
    f_5 & = \sin  \theta_1 \cos  \phi\,,\\
    f_9 & = \sin^2\theta_1 \sin 2\phi\,.&
    f_8 & = \sin 2\theta_1 \sin  \phi\,,&
    f_7 & = \sin  \theta_1 \sin  \phi\,,
\end{aligned}
\end{equation}
Here we denote dilepton mass squared and the dilepton helicity angle as $q^2$ and $\theta_1$, while
the dimeson mass squared and the dimeson helicity angles are denoted as $k^2$ and $\theta_2$. The
azimuthal angle is denoted as $\phi$. The total decay width is
\begin{equation}
    \langle \Gamma\rangle = \int_0^\pi \dd\theta_1\,\frac{\langle 3I_1(\cos\theta_1) - I_2(\cos\theta_1)}{3}\,.
\end{equation}
As usual, we transform from a $\cos\theta_1$-dependence to a $\theta_1$-dependence.
\begin{equation}
\begin{aligned}
    P(q^2, k^2, \theta_1, \theta_2, \phi)
    & = \frac{1}{4\pi} \sum_i \frac{I(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \phi) \sin\theta_1 \sin\theta_2\\
    & \equiv \frac{1}{4\pi} \sum_i P_i(q^2, k^2, \theta_2) f_i(\theta_1, \phi) \sin\theta_2\,.
\end{aligned}
\end{equation}
where we also define $P_i(q^2, k^2, \theta_2) \equiv \theta_2 I_i(q^2, k^2, \cos\theta_2) / \Gamma$.\\

We provide a basis $\hat{f}_i$ of angular functions which is dual to the basis $f_j$ in the sense that
\begin{equation}
    \frac{1}{4\pi}\int_0^\pi \dd\theta_1 \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\phi) f_j(\theta_1,\phi) \sin\theta_1 = \delta_{ij}\,,
\end{equation}
thereby enabling us to project out exactly one of the angular
observables $P_i(q^2)$
\begin{equation}
    \int_0^\pi \dd\theta_1 \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\phi) P(q^2, k^2, \theta_1,\theta_2,\phi) = P_i(q^2, k^2, \theta_2)\,.
\end{equation}
The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{21 + 15 \cos 2\theta_1}{16}\,, &
    \hat{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
    \hat{f}_6 & = 3 \cos\theta_1                   \,, \\
    \hat{f}_3 & = \frac{15}{4}                \cos 2\phi     \,, &
    \hat{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \phi     \,, &
    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \phi     \,, \\
    \hat{f}_9 & = \frac{15}{4}                \sin 2\phi     \,, &
    \hat{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \phi     \,, &
    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \phi     \,.
\end{aligned}
\end{equation}

\section{Application to $\Lambda_b\to \Lambda(\to N \pi)\ell^+\ell^-$}
\label{app:lambdabtolambdall}

The physical PDF for the decay -- in the presence of Standard Model operator and their chirality flipped counter parts -- reads \cite{Boeer:2014xx}
\begin{equation}
    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\Gamma} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
\end{equation}
where $q^2$ denotes the dilepton mass squared, and $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
helicity angles in the dilepton and $N\pi$ systems, respectively. The basis of angular functions reads
\begin{equation}
    \begin{aligned}
% 1
        f_{1ss} & = \sin^2\theta_1 &
        f_{1cc} & = \cos^2\theta_1 &
        f_{1c}  & = \cos\theta_1\\
% 2
        f_{2ss} & = \sin^2\theta_1 \cos\theta_2 &
        f_{2cc} & = \cos^2\theta_1 \cos\theta_2 &
        f_{2c}  & = \cos\theta_1   \cos\theta_2 \\
% 3
        f_{3sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\phi &
        f_{3s}  & = \sin\theta_1              \sin\theta_2 \cos\phi \\
% 4
        f_{4sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\phi &
        f_{4s}  & = \sin\theta_1              \sin\theta_2 \sin\phi
    \end{aligned}
\end{equation}
The decay width reads $\langle\Gamma\rangle = \langle2 K_{1ss} + K_{1cc}\rangle$. In terms of the angles $\theta_1$ and $\theta_2$, instead of the cosines, the PDF reads
\begin{equation}
    P_{\Lambda_b}(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i P_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $P_i(q^2) = K_i(q^2) / \Gamma$.

We provide a dual basis $\hat{f}_i$ of the angular functions which is orthogonal to the basis $f_j$ in the sense that
\begin{equation}
    \frac{3}{8\pi}\int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) f_j(\theta_1,\theta_2,\phi) \sin\theta_1 \sin\theta_2 = \delta_{ij}\,,
\end{equation}
thereby enabling us to project out exactly one of the angular observables $P_i(q^2)$ using
\begin{equation}
    \int_0^\pi \dd \theta_1 \int_0^\pi \dd \theta_2 \int_0^{2\pi} \dd \phi P(q^2, \theta_1, \theta_2, \phi) \hat{f}_i(\theta_1, \theta_2, \phi) = P_i(q^2)\,.
\end{equation}
The dual basis reads
\begin{equation}
    \begin{aligned}
% 1
        \hat f_{1ss} & = \frac{\pi^3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) &
        \hat f_{1cc} & = \frac{\pi^3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) &
        \hat f_{1c}  & = \pi^3 \cos\theta_1\\
% 2
        \hat f_{2ss} & = \frac{3\pi^3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) \cos\theta_2 &
        \hat f_{2cc} & = \frac{3\pi^3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) \cos\theta_2 &
        \hat f_{2c}  & = 3\pi^3 \cos\theta_1   \cos\theta_2 \\
% 3
        \hat f_{3sc} & = \frac{15\pi^3}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\phi &
        \hat f_{3s}  & = \frac{3\pi^3}{2} \sin\theta_1              \sin\theta_2 \cos\phi \\
% 4
        \hat f_{4sc} & = \frac{15\pi^3}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\phi &
        \hat f_{4s}  & = \frac{3\pi^3}{2} \sin\theta_1              \sin\theta_2 \sin\phi
    \end{aligned}
\end{equation}

\bibliography{references}

\end{document}

### 2014-06-18 draft.tex
Add two comments on combining observables (across P, across q2)

@@
 \end{equation}
+We would like to emphasize that the sample covariance should rapidly converge towards the true covariance matrix.
+This will allow to construct constraints on optimized observables with correlated uncertainties 
+from the experimental constraints on the angular observables. (See \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf}
+for definitions of such optimized observables in $B\to K^*\ell^+\ell^-$ decays).
 
@@
 acceptance effects, we expect $\eps_i^{(j)} \ll 1$. \footnote{\danny{what are reasonable values/upper limits on the $\eps$?}}\\
+
+We are aware that setting a bin width that fulfills the aforementioned criterion can be at odds with
+other requirements. For instance, in exclusive $b\to s\ell^+\ell^-$ decays, the bin width for
+$\vec{\nu} = q^2$ needs to cover a sufficiently large part of the phase space beyond the open charm
+threshold. We emphasize that the outcome of an analysis as proposed here can easily combine several
+bins by means of a weighted average.\\
 

### 2014-06-21 draft.tex
Add appendix on partial wave expansion of observables

@@
 \danny{Potential people to read the manuscript: Jochen Dingfelder (Belle-II, Bonn), Ulrik Egede (LHCb, Imperial London), Christoph Langenbruch (LHCb, Warwick), Michel De Cian (LHCb, Heidelberg).}
+D.v.D would like to thank Gudrun Hiller and Martin Jung for discussing the results of \cite{Das:2014xx} prior to publication.
 
@@
 
+\section{On the Partial Wave Expansions of Interference Terms}
+\label{app:partial-waves}
+
+Let $P \equiv P(\vec{\nu},\theta)$ be an observable of only one angle $\theta$ and further non-angular variables $\vec{\nu}$. Further, let
+$P$ have an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots \hat{=} S,P,D,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
+\begin{equation}
+    P(\theta) \equiv A_1(\theta) A_2^*(\theta) \equiv \left(\sum_{l_1=0}^\infty A_1^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta)\right) \left(\sum_{l_2=0}^\infty A_1^{(l_2)} p_{l_2}^{(m_2)}(\cos\theta)\right)\,.
+\end{equation}
+Here $m_1$ and $m_2$ denote the third component of the angular momentum of the respective amplitude $A_1$ or $A_2$, and we impose $l_1 \geq l_2$.\\
+
+From positivity of the amplitudes one immediately finds
+\begin{equation}
+    \int \dd\cos\theta |A_i(\theta)|^2 = \sum_{l_i = 0}^\infty |A_i^{(l_i)}|^2 n_{l_i, m_i} < \infty\,,
+\end{equation}
+where we introduce $n_{l,m}$ via the scalar product of two associated Legendre polynomials,
+\begin{equation}
+    \label{eq:legendre-scalar-product}
+    n_{l, m} \delta_{l, l'} \equiv \int_{0}^\pi p_{l}^{(m)}(\cos\theta) p_{l'}^{(m)} (\cos\theta) \dd \cos\theta = \frac{2}{(2 l + 1)} \frac{(l + m)!}{(l - m)!} \delta_{l, l'}\,.
+\end{equation}
+Using the large-$l$ behaviour of $n_{l_i,m_i}$ one finds that with increasing $l_i$ the partial waves amplitudes must asymptotically fall off,
+\begin{equation}
+    |A_i^{(l_i)}(\cos\theta)| \Big|_{l_i \gg m_i} \sim \frac{1}{\sqrt{l_i}}\,.
+\end{equation}
+This motivates to cut-off of the partial-wave expansion at some angular momentum $L$. Will will show in the following that such a cut-off
+is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$.\\
+
+We propose the decomposition of $P$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with $m=m_1 + m_2$, and
+$l_1 - l_2 \leq j \leq l_1 + l_2$,
+\begin{equation}
+    P(\vec{\nu}, \theta) = \sum_j P_{j,m}(\vec{\nu}) p_{j}^{(m)}(\cos\theta)\,.
+\end{equation}
+This parametrization has two merits. First, we can immediately project out the angular observables $P_{j,m}$ by means of \refeq{legendre-scalar-product}:
+\begin{equation}
+    P_{j,m}(\vec{\nu}) = \frac{1}{n_{j,m}} \int_{-1}^{+1} P(\vec{\nu},\cos \theta) p_{j}^{(m)}(\cos\theta) \dd\cos\theta\,.
+\end{equation}
+Second, we can immediately express $P_{j,m}(\vec{\nu})$ in terms of the partial-wave amplitudes,
+\begin{equation}
+    \label{eq:partial-wave-observable-infinite}
+    \begin{aligned}
+        P_{j,m}(\vec{\nu})
+            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) \big(A_{2}^{(l_2)}\big)^* p_{l_2}^{(m_2)}(\cos\theta)\\
+            & = \sum_{l_1,l_2=0}^\infty A_{1}^{l_1} \big(A_{2}^{(l_2)}\big)^* \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
+    \end{aligned}
+\end{equation}
+In the last step, we use Gaunt's formula \cite{Gaunt:1929} to integrate a triple product of associated Legendre polynomials,
+\begin{equation}
+\begin{aligned}
+    T_{l_1,l_2,j}^{(m_1,m_2)}
+        & = \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) p_{l_1}^{(m_1)}(\cos\theta) p_{l_2}^{(m_2)}(\cos\theta) \dd\cos\theta\\
+        & = (-1)^{s - l_1 - m_2} \frac{2 (l_1 + m_1)! (l_2 + m_2)! (2s - 2 l_2)! s!}{(l_1 - m_1)! (s - j)! (s - l_1)! (s - l_2)! (2s + 1)!}\\
+        & \times \sum_{t=p}^q (-1)^t \frac{(j + m + t)!(l_1 + l_2 - m - t)!}{t! (j - m - t)! (l_1 - l_2 + m + t)! (l_2 - m_2 - t)!}\,,
+\end{aligned}
+\end{equation}
+where
+\begin{equation}
+\begin{aligned}
+    m & = m_1 + m_2\,, &
+    m_1 & \geq m_2\,,  \\
+    j, l_1, l_2 & \geq 0\,, &
+    m, m_1, m_2 & \geq 0\,,
+\end{aligned}
+\end{equation}
+and
+\begin{equation}
+\begin{aligned}
+    s & = \frac{j + l_1 + l_2}{2}\,, &
+    p & = \max(0, l_2 - l_1 - m)\,, &
+    q & = \min(l_1 + l_2 - m, j - m, l_2 - m_2)\,.
+\end{aligned}
+\end{equation}
+The necessary condition for $T \neq 0$ are
+\begin{equation}
+    s \in \mathbb{N}\qquad \wedge \qquad l_1 - l_2 \leq l \leq l_1 + l_2,.
+\end{equation}
+The latter condition is well known from adding angular momenta.
+
 \bibliography{references}

### 2014-06-23 draft.tex
[draft] Corrections on first page

@@
 \usepackage{graphicx}
-\usepackage{xcolor}
+\usepackage[svgnames]{xcolor}
 
@@
 \newcommand{\danny}[1]{{\color{purple}#1}}
-\newcommand{\fred}[1]{{\color{gold!85!black}#1}}
+\newcommand{\fred}[1]{{\color{brown!85!black}#1}}
 \newcommand{\nico}[1]{{\color{green!85!black}#1}}
@@
 \preprint{SI-HEP-2014-xx}
-\title{Sample Based Determination of Angular Observables}
+\title{Sample-Based Determination of Angular Observables}
 \author{Frederik Beaujean}
@@
 We study means to determine angular observables for a generic angular distribution
-of either decays or scattering processes. \dots
+of a decay or scattering process. \dots
 \end{abstract}
@@
 
-In this letter we study how to obtain a set of angular observables $P_i$
-that arise in a generic multi-body processes without the need to carry out
-an explicit fit of an angular distribution to data. Instead, we present a method
-that only relies on orthogonality of angular functions, and estimation of integrals
-by means of Monte Carlo techniques.\\
+In this letter we study how to obtain a set of angular observables
+$\{P_i\}$ that arise in a generic multi-body process without the need
+to carry out a likelihood fit of an angular distribution to the
+measured events. Instead, we present a method that only relies on
+orthogonality of angular functions, and estimation of integrals
+by means of Monte Carlo techniques. \fred{Paragraph sounds like abstract}\\
 
 The initial motivation for studying what we wish to call the \emph{Method of Moments}
-is the determination of angular observables in the decay rare, FCNC-mediated decay
+is the determination of angular observables in the rare decay FCNC-mediated decay
 $\bar{B}\to \bar{K}^*(\to \bar{K}\pi)\ell^+\ell^-$. However, we emphasize that
-he method we describe in the remainder of this letter is applicable to arbitrary
+he method we describe in the remainder of this letter is general and applies to arbitrary
 decay or scattering processes.\\
 
-For the purpose of this work, let $P_i$ be a set of functions of $m$ non-angular
-kinematic variables $\nuvec$, $P_i \equiv P_i(\nuvec)$, with $\nuvec = (\nu_1, \dots \nu_m)$.
-These include, among others, invariant masses or center of mass energies pertinent
-to the respective decay or scattering processes. Let us further assume the angular
-observables to be defined via a suitably factorizing probability distribution (PDF),
+Let $\thvec = (\theta_1, \dots \theta_n)$ denote the set of all
+angles, and let $\nuvec = (\nu_1, \dots \nu_m)$ denote the set of all
+other non-angular kinematic variables needed to fully specify the
+final state of the process under study. For example, $\nuvec$ may
+include invariant masses or center-of-mass energies. We define an
+angular observable $P_i$ as a coefficient in the probability density
+function (PDF) of the process,
 \begin{align}
     \label{eq:def-P}
-    P(\nuvec, \thvec) = \sum_k P_i(\nuvec) \times f_i(\thvec)\,,
+    P(\nuvec, \thvec) = \sum_i P_i(\nuvec) \times f_i(\thvec)\,,
 \end{align}
-Here, the dependence on the $n$ decay angles $\thvec = (\theta_1, \dots, \theta_n)$ has been
-explicitly factored out in terms of the angular functions $f_i(\thvec)$, which we assume to fulfill the
-orthonormality relations
+Here, the dependence on the $n$ decay angles $\thvec$ has been
+explicitly factored out in terms of the angular functions
+$f_i(\thvec)$, which we assume to fulfill the orthonormality relations
 \begin{equation}
@@
 \end{equation}
-(For the purpose of this letter, however, it suffices that the system of angular
-functions $f_i(\thvec)$ can be transformed into an orthonorml basis. The transformations to these
-bases for a selection of decays has been written out in the appendices \ref{app:btokll} through
+(For the purpose of this letter, however, it suffices that the system
+of angular functions $f_i(\thvec)$ can be transformed into an
+orthonormal basis. The transformation needs to be worked out on a
+case-by-case basis. For a selection of $B$ decays, the transformations
+are listed in the appendices \ref{app:btokll} through
 \ref{app:lambdabtolambdall}.)\\
 
-For particle decays, we $P$ is expressed in terms of the fully differential decay width,
+For particle decays, $P$ is generally expressed in terms of the fully differential decay width,
 \begin{align}
@@
 
-\section{Sample Based Determination}
+\section{Sample-Based Determination}
 \label{sec:sample-based-det}

### 2014-06-24 draft.tex
small update

@@
 \author{Marcin Chrzaszcz}
-\email{chrzaszcz.marcin@gmail.com}
+\email{marcin.chrzaszcz@uzh.ch}
 \author{Nicola Serra}
@@
 The determination of the coefficients $\eps_i^{(j)}$ that parametrize the detectory effects is generally
-a difficult task. Here, we will show a systematic method to determine these coefficients. \dots
+a difficult task. Here, we will show a systematic method to determine these coefficients.\\
+One starts from generating a flap phase space MonteCarlo sample.
+Simulated events are then put thought the detector simulation, and selection requirements.
+Since flap phase space ensures flat distribution of angles on the generated level, the only non zero moment is one associated to Fl.
+Measuring the moments of this MC sample leads will etc.
+Mayby this should be an appendix.
 
@@
 \dots
-\danny{Potential people to read the manuscript: Jochen Dingfelder (Belle-II, Bonn), Ulrik Egede (LHCb, Imperial London), Christoph Langenbruch (LHCb, Warwick), Michel De Cian (LHCb, Heidelberg).}
+\danny{Potential people to read the manuscript: Jochen Dingfelder (Belle-II, Bonn), Ulrik Egede (LHCb, Imperial London), Christoph Langenbruch (LHCb, Warwick), Michel De Cian (LHCb, Heidelberg), Adrian Bevan (ATLAS, Queen Mary)  }
 D.v.D would like to thank Gudrun Hiller and Martin Jung for discussing the results of \cite{Das:2014xx} prior to publication.

### 2014-06-24 draft.tex
More corrections and comments, mostly on statistics and notation

--- 2014-06-23 draft.tex
@@
 \let\eps\varepsilon
+\newcommand{\aver}[1]{\langle #1 \rangle}
 \newcommand{\what}[1]{\widehat{#1}}
@@
     \label{eq:def-P}
-    P(\nuvec, \thvec) = \sum_i P_i(\nuvec) \times f_i(\thvec)\,,
+    P(\nuvec, \thvec) = \sum_i P_i(\nuvec) \times f_i(\thvec)\,.
 \end{align}
@@
 \end{equation}
-(For the purpose of this letter, however, it suffices that the system
+For the purpose of this letter, however, it suffices that the system
 of angular functions $f_i(\thvec)$ can be transformed into an
@@
 are listed in the appendices \ref{app:btokll} through
-\ref{app:lambdabtolambdall}.)\\
+\ref{app:lambdabtolambdall}.  Note that $P_i$ is \emph{not} a PDF.  \\
 
@@
 \end{align}
-where the total cross section $\sigma$ is used for the normalisation. Since the determination of
-the total decay width or total cross section can be quite difficult, we emphasize that different normalizations for
-$P$ can be used. For instance, the total decay width (or cross section) of the process of interest can be replaced
-by the corresponding quantity of a control-channel process.\\
+where the total cross section $\sigma$ is used for the
+normalization. Since the determination of the total decay width or
+total cross section can be quite difficult, we emphasize that
+different normalizations for $P$ can be used.  For instance, the total
+decay width (or cross section) of the process of interest can be
+replaced by the corresponding quantity of a control-channel
+process.\fred{How would $P$ remain a proper probability such that
+  $\int P = 1$? You can't simply change the normalization. I propose a
+  change of notation: I find it terribly confusing that $P(\nuvec,
+  \thvec)$ is a probability but $P_i(\nuvec)$ is not. For $P_i$, later
+  on the symbols $J_i, K_i$ etc are used. We don't have to use the
+  same symbol everywhere but let's not use $P_i$}\\
 
-In the remainder of this letter we discuss how to obtain the angular observables $P_i(\nuvec)$ in an experimental
-setup where each recorded event is (approximately) as variate of $P$.
-We lay down the groundwork in section \ref{sec:sample-based-det}. Section \ref{sec:systematics} is dedicated to
-the impact of systematic effects, such as mismodelling of the underlying physics and detector acceptance
-effects. Numerical studies for one uni-angular and one triple-angular distribution are provided in section
-\ref{sec:numerics}. In a series of appendices we discuss the relevant orthonormal bases of angular functions
-at the hand of the several rare $b$ decays.
+In the remainder of this letter we discuss how to obtain the angular
+observables $P_i(\nuvec)$ in an experimental setup where each recorded
+event is (approximately) distributed according to $P$.  We establish
+the statistical basics in section \ref{sec:sample-based-det}. Section
+\ref{sec:systematics} is dedicated to the impact of systematic effects
+such as mismodeling the underlying physics or detector acceptance
+effects. Numerical studies for one uni-angular and one triple-angular
+distribution are provided in section \ref{sec:numerics}. In a series
+of appendices we provide the orthonormal bases of angular functions
+relevant to several rare $b$ decays.
 
@@
 
-From the orthonormality relations \refeq{def-ortho-rel} follows that a single angular observable $P_i$
+The orthonormality relations \refeq{def-ortho-rel} imply that a single angular observable $P_i$
 can be projected out of the full PDF $P$ by means of
@@
 \end{equation}
-In point of fact, $P_i$ is the $f_i$-moment of the PDF $P$. Additionally, Integration over the non-angular variables yields
+In point of fact, $P_i$ is the $f_i$-th moment of the PDF $P$\fred{This
+  notation is uncommon. Is that how we \emph{define} the $f_i$-th
+  moment?}. Additionally, integration over the non-angular variables
+yields
 \begin{equation}
@@
 \end{equation}
-The remainder of this section is describes the method of moments, in which we replace the
+The remainder of this section  describes the method of moments, in which we replace the
 analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\
@@
 \end{equation}
-can be replaced \citeneeded by an MC estimator $\what{E_P[g]}$
+can be approximated \citeneeded\fred{Robert, Casella} by an MC estimator $\what{E_P[g]}$
 \begin{equation}
     \label{eq:mc-id}
-    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{N} \sum_{k=1} g(x^{(k)})\,.
+    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{N} \sum_{k=1} g(x^{(k)})
 \end{equation}
-For the purpose of the estimation, the variates $x^{(k)}$, $k = 1, \dots, N$ must distributed under $P$,
+due to the strong law of large numbers for $N \to \infty$ assuming
+that the variates $x^{(k)}$, $k = 1, \dots, N$ are distributed as
+$P$; i.e.,
 \begin{equation}
@@
 \end{equation}
-(Throughout this letter we denote all MC estimators with a wide hat.)\\
+Throughout this letter we denote all MC estimators with a wide hat.\\
 
@@
 physical process truthfully. In that case, all events detected in an experimental setup are in fact, up to
-detection efficiencies, distributed as $P$. Application of \refeq{mc-id} then yields
+detection efficiencies, distributed as $P$. \fred{Paragraph is redundant an can be omitted.}
+
+Application of \refeq{mc-id} then yields \fred{notation is very confusing $P_i$ for $x^{(k)} \sim P$}
 \begin{equation}
@@
 \end{equation}
-However, it is often of interest to obtain the $\nuvec$-integrated observables for
-certain $\nuvec$ ranges, i.e. binned measurements of $\langle P_i\rangle$\footnote{%
-We refer for example to the determination of the angular observables $J_i$ in $\bar{B}\to\bar{K}^*\ell^+\ell^-$
-decays, see e.g. \cite{Aaij:2013iag}. For details on the relation between the $P_i$ and the angular observable $J_i$ in the
-aforementioned decay, we refer to appendix \ref{app:btokstarll}.
-}.
-Therefore, we introduce the bin-integrated quantities
+It is often of interest to obtain the $\nuvec$- observables integrated
+over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
+P_i\rangle$\footnote{% We refer for example to the determination of
+  the angular observables $J_i$ in $\bar{B}\to\bar{K}^*\ell^+\ell^-$
+  decays, see e.g. \cite{Aaij:2013iag}. For details on the relation
+  between the $P_i$ and the angular observable $J_i$ in the
+  aforementioned decay, we refer to appendix \ref{app:btokstarll}.  }.
+Therefore, we introduce the bin-integrated quantity
 \begin{align}
@@
     & = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec)
-        \theta^{(m)}(\nuvec - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec) \dd^n\theta\right]\dd^m \nu\,.
+        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
+        %% \theta^{(m)}(\nuvec - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec)
+        \dd^n\theta\right]\dd^m \nu\,,
 \end{align}
+where the argument of the indicator function $ \mathbf{1}(\vec{a} \le
+\nuvec \le \vec{b})$ is to be interpreted componentwise.
 Application of \refeq{mc-id} immediately yields
 \begin{equation}
+    \label{bin-importance}
     \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}
-    = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)}) \theta^{(m)}(\nuvec^{(k)} - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec^{(k)})\,.
+    = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
-This basically reduces the determination of $P_i$ to a (weighted) counting experiment. As a consequence,
-the statistical error on $\what{P_i}$ can be expected to follow a multivariate gaussian distribution \citeneeded.
-In this case, the covariance $\cov[\what{P_i},\what{P_j}]$ is of particular interest. The latter can be replaced
-by a suitable MC estimator, the sample covariance
+This basically reduces the estimation of
+$\aver{P_i}_{\vec{a},\vec{b}}$ to a (weighted) counting experiment. In
+the limit $N \to \infty$, the random vector $( \dots,
+\aver{P_i}_{\vec{a},\vec{b}}, \dots)$ follows a multivariate Gaussian
+distribution \citeneeded\fred{Why?  multivariate in $\widehat{P_i}$?}
+with a mean vector estimated by \refeq{bin-importance} and covariance
+estimated as
 \begin{equation}
-    \cov[\what{P}_i,\what{P}_j] \to \what{\cov}[\what{P}_i, \what{P}_j]_{\vec{a},\vec{b}}
-        = \frac{1}{N - 1} \sum_{k=1}^{N} \big[\hat{f}_i^{(k)} - \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\hat{f}_j^{(k)} - \widehat{\langle P_j\rangle_{\vec{a},\vec{b}}}\big]
-        \theta^{(m)}(\nuvec^{(k)} - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec^{(k)})\,.
+    \cov[\aver{P_i},\aver{P_j}]_{\vec{a},\vec{b}} \to \what{\cov}[\aver{P}_i, \aver{P}_j]_{\vec{a},\vec{b}}
+        = \frac{1}{N - 1} \sum_{k=1}^{N} \big[{f}_i(x^{(k)}) - \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[f_j(x^{(k)}) - \widehat{\langle P_j\rangle_{\vec{a},\vec{b}}}\big]
+        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
-We would like to emphasize that the sample covariance should rapidly converge towards the true covariance matrix.
+We would like to emphasize that the sample covariance should rapidly \fred{So what value of $N$ is close enought to $\infty$?} converge towards the true covariance matrix.
 This will allow to construct constraints on optimized observables with correlated uncertainties
@@
 
-In \refsec{sample-based-det}, we assumed that the PDF $P$ described the physical reality accurately,
-and that the experiment observed each event with perfect accuracy. In order to estimate systematic
+In \refsec{sample-based-det}, we assume that the PDF $P$ describe the physical reality accurately,
+and that the experiment observes each event with perfect accuracy. In order to estimate systematic
 uncertainties, we lift these assumptions.
 
-\subsection{Mismodelling due to Contributions by Higher Partial Waves}
+\subsection{Mismodeling due to Contributions by Higher Partial Waves}
 \label{sec:systematics:partial-waves}
+
+\fred{Paragraph is very specific to one physics case. Needs a drawing}
 
@@
 
+\fred{If this is to be general, should explain what we mean by
+  acceptance. Isn't it that experiments just model the detector well?
+  The P. to observe an event in $\nuvec, \thvec$ might be very
+  different from the P. to create an event in $\nuvec, \thvec$. All
+  that's needed is a full forward model. I'm not sure that in
+  \refeq{eq:PDFwithDE} we still have a normalized probability. Am I
+  right to say that detector effects can be very much localized and
+  nondifferentiable? Like some wires are inactive, or the region close
+  to the beam has zero acceptance. In the latter case, modeling
+  residual acceptance effects with smooth Legendre polynomials seems a
+  bad idea.}
+
 Thanks to accurate detector simulations and control studies, the experimental analyses have become
@@
 there are only a small, residual acceptance effects left that affect the events. In particular, we
-assume that the latter can be modelled as a modified probability density,
+assume that the latter can be modeled as a modified probability density,
 \begin{equation}
@@
     \item Also, check explicitly the variance and covariance of the results for all sample sizes considered.
+    \item compare robustness to likelihood fit when fit doesn't
+      converge. Why exactly doesn't it converge? What if physics model
+      wrong, say some angular terms are missing.
 \end{itemize}}
@@
     \item errors on the means are in very good approximation gaussian.
-    \item correlation are small and faithfully model a multivariate gaussian.
+    \item correlation are small and faithfully model a multivariate gaussian. \fred{$\Rightarrow$ easy transfer of knowledge to theory fits}
 \end{enumerate}
@@
 Here we denote the dilepton mass squared as $q^2$, and the dilepton helicity angle as $\theta_1 \equiv \theta_{\ell}$. We transform the PDF from a $\cos\theta_1$-dependence
-to a $\theta_1$-dependence,
+to a $\theta_1$-dependence \fred{why? Formula easier? Where is the ``-'' sign from the Jacobian $\partial_{\theta} \cos \theta = - \sin \theta$ },
 \begin{equation}
@@
 
-We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_i$ in the sence that
+We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_i$ in the sense that \fred{What are the upper limits?
+$\pi$ or $2 \pi$?
+Not consistent with section I and II.
+I think it would be fair to talk about the dual basis already there.}
 \begin{equation}

### 2014-06-24 draft.tex
Tweak app E a little bit

--- 2014-06-24 draft.tex
@@
 
-\section{On the Partial Wave Expansions of Interference Terms}
+\section{On the Partial Wave Expansions of Angular Observables}
 \label{app:partial-waves}
@@
 \begin{equation}
-    P(\theta) \equiv A_1(\theta) A_2^*(\theta) \equiv \left(\sum_{l_1=0}^\infty A_1^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta)\right) \left(\sum_{l_2=0}^\infty A_1^{(l_2)} p_{l_2}^{(m_2)}(\cos\theta)\right)\,.
+    \label{eq:def-partial-wave-observable}
+    P(\theta) \equiv F\big(A_1(\theta) A_2^*(\theta)\big) \equiv \left(\sum_{l_1=0}^\infty A_1^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta)\right) \left(\sum_{l_2=0}^\infty A_1^{(l_2)} p_{l_2}^{(m_2)}(\cos\theta)\right)\,,\qquad F=\Re{},\Im{}\,.
 \end{equation}
-Here $m_1$ and $m_2$ denote the third component of the angular momentum of the respective amplitude $A_1$ or $A_2$, and we impose $l_1 \geq l_2$.\\
+Here $m_1$ and $m_2$ denote the third component of the angular momentum of the respective amplitude $A_1$ or $A_2$, and we impose $m_1 \geq m_2$.\\
 
@@
 \end{equation}
-Using the large-$l$ behaviour of $n_{l_i,m_i}$ one finds that with increasing $l_i$ the partial waves amplitudes must asymptotically fall off,
+Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial waves amplitudes must asymptotically fall off,
 \begin{equation}
@@
 \end{equation}
-This motivates to cut-off of the partial-wave expansion at some angular momentum $L$. Will will show in the following that such a cut-off
-is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$.\\
+This motivates to cut the partial-wave expansion off at some angular momentum $L$.\\
 
-We propose the decomposition of $P$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with $m=m_1 + m_2$, and
-$l_1 - l_2 \leq j \leq l_1 + l_2$,
+Will will show in the following that such a cut off
+is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$.
+Since this expansion implies a well-defined total angular momentum for each observables, one ensures that the observables can in fact be disentangled experimentally.\\
+
+We propose the decomposition of $P$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with total angular momentum $j$ and its third component $m=m_1 + m_2$.
 \begin{equation}
@@
         P_{j,m}(\vec{\nu})
-            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) \big(A_{2}^{(l_2)}\big)^* p_{l_2}^{(m_2)}(\cos\theta)\\
-            & = \sum_{l_1,l_2=0}^\infty A_{1}^{l_1} \big(A_{2}^{(l_2)}\big)^* \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
+            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left(A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) \big(A_{2}^{(l_2)}\big)^*\right) p_{l_2}^{(m_2)}(\cos\theta)\\
+            & = \sum_{l_1,l_2=0}^\infty F\left(A_{1}^{l_1} \big(A_{2}^{(l_2)}\big)^*\right) \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
     \end{aligned}
@@
 \begin{equation}
+    \label{eq:angular-momentum-addition}
     s \in \mathbb{N}\qquad \wedge \qquad l_1 - l_2 \leq l \leq l_1 + l_2,.
 \end{equation}
-The latter condition is well known from adding angular momenta.
+The latter condition is well known from adding angular momenta. Note, however, that
+the sum in \refeq{def-partial-wave-observable} goes to infinitely high angular momenta $l_1$ and $l_2$. As a consequence
+of this and of \refeq{angular-momentum-addition}, the angular observables $P_{j,m}$
+consist of sums with infinite terms. It is then up to theoretical analyses to
+estimate or calculate the impact of individual contributions, with or without the cut off $L$.
+For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014}.
 

### 2014-06-24 draft.tex
Work on section III.A

@@
 
-\danny{
 So far, we assumed that our underlying physical process was accurately described by our PDF $P$.
 However, in several interesting processes we might only have an approximative result for $P$.
-We will now show that this is the case for the interesting class four-body decays $B\to P_1 P_2 \ell_1 \bar\ell_2$,
+We will now show that this is the case for the interesting class of four-body decays $B\to P_1 P_2 \ell_1 \bar\ell_2$,
 which includes the rare $b\to s$-mediated $B$ decay $B \to K\pi\ell^+\ell^-$ and the $V_{ub}$ suppressed decay
-$B\to \pi\pi\ell^+\bar\nu_\ell$. For the sake of clarity and simplicity, we will here discuss
-the application of our method to the decay $B\to \pi\pi\ell^+\bar\nu_\ell$.\\
+$B\to \pi\pi\ell^+\bar\nu_\ell$. For both examples the PDF $P$ is known in the small-width approximation
+and when assuming a pure $P$-wave, resonant final state. An extension to $S-P$ interference has been
+studied for $B\to K\pi\ell^+\ell^-$ \cite{Blake:2012xx,Becirevic:2011xx} and for $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$
+\cite{Faller:2013xx}.
 
-We now face the problem that $P$ has a given dependence on the dilepton helicity angle $\theta_1$
-and the azimuthal angle $\theta_3$. However, the dipion system can have an arbitrary large
-total angular momentum; only the its third component is restricted to $J^{\pi\pi}_z = -1,0,+1$.
-Therefore, we will restrict integration to the angles $\theta_1$ and $\theta_3$. \dots
-}
+For this class of decays, we face the problem that $P$ has a given dependence on the dilepton helicity angle $\theta_1$
+and the azimuthal angle $\theta_3$. (See also \refapp{btokpill} for details on the angular distribution.)
+However, on the level of decay amplitudes the dimeson system can have an arbitrary
+large total angular momentum; only the third component of its angular momentum is restricted to $J^{\pi\pi}_z = -1,0,+1$.\\
+
+We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(m)}$
+with respect to the remaining angle $\theta_2$. Using the observables $P_k(\vec{\nu}=(q^2, k^2))$ as defined in \refapp{}
+the expansion reads
+\begin{equation}
+    P_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{j,m}} P_{k,j}(\vec{\nu}) p_{j}^{(m)}(\cos\theta_2)\sin\theta_2\,,
+\end{equation}
+where $m=0$ for $n=1,2,6$ and $m=1$ for $n=3,4,5,7,8,9$. The angular observables defined as coefficients of this expansion
+have the merit of a well-defined total angular momentum, and thus can be disentangled (see \refapp{partial-waves} for
+a derivation). As a consequence of the orthogonality of the Legendre polynomials, mismodelling or lack of modelling of higher
+partial-wave observables \emph{does not affect} the method of moments as given in the previous section.
+Unfortunately, this benefit on the experimental side is accompanied with a theoretical draw back. Each observable
+$P_{k,j}(\vec{\nu})$ consists of an infinite sum of bilinear of partial-wave amplitudes. It remains for theoretical
+analyses to estimate or calculate the impact of partial waves beyond the P wave \cite{Das:2014}.\\
+
+We wish to emphasize, however, that detector acceptance effects systematically affect the expansion for any basis
+of angular functions. The means to cope with this problem are discussed in the following subsection.
 
@@
 \begin{equation}
-    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\Gamma}\frac{\dd^5 \Gamma}{\dd q^2\,\dd k^2\, \dd\cos\theta_1\,\dd\cos\theta_2\,\dd\phi} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
+    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\langle \Gamma\rangle}\frac{\dd^5 \Gamma}{\dd q^2\,\dd k^2\, \dd\cos\theta_1\,\dd\cos\theta_2\,\dd\phi} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
 \end{equation}
@@
 \begin{equation}
-    \langle \Gamma\rangle = \int_0^\pi \dd\theta_1\,\frac{\langle 3I_1(\cos\theta_1) - I_2(\cos\theta_1)}{3}\,.
+    \langle \Gamma\rangle = \int_0^\pi \dd\theta_1\,\dd q^2\,\dd k^2\,\sin\theta_2 \frac{3I_1(q^2, k^2, \cos\theta_2) - I_2(q^2, k^2, \cos\theta_2)}{3}\,.
 \end{equation}
@@
     & = \frac{1}{4\pi} \sum_i \frac{I(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \phi) \sin\theta_1 \sin\theta_2\\
-    & \equiv \frac{1}{4\pi} \sum_i P_i(q^2, k^2, \theta_2) f_i(\theta_1, \phi) \sin\theta_2\,.
+    & \equiv \frac{1}{4\pi} \sum_i P_i(q^2, k^2, \theta_2) f_i(\theta_1, \phi)\,.
 \end{aligned}
 \end{equation}
-where we also define $P_i(q^2, k^2, \theta_2) \equiv \theta_2 I_i(q^2, k^2, \cos\theta_2) / \Gamma$.\\
+where we also define $P_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / \Gamma$.\\
 
@@
 thereby enabling us to project out exactly one of the angular
-observables $P_i(q^2)$
+observables $P_i(q^2, k^2, \theta_2)$
 \begin{equation}

### 2014-06-24 draft.tex
Move first paragraph of Intro to Abstract

@@
 \begin{abstract}
-We study means to determine angular observables for a generic angular distribution
-of a decay or scattering process. \dots
+In this letter we study how to obtain a set of angular observables
+$\{P_i\}$ that arise in a generic multi-body process without the need
+to carry out a likelihood fit of an angular distribution to the
+measured events. Instead, we present a method that only relies on
+orthogonality of angular functions, and estimation of integrals
+by means of Monte Carlo techniques.
 \end{abstract}
@@
 \label{sec:intro}
-
-In this letter we study how to obtain a set of angular observables
-$\{P_i\}$ that arise in a generic multi-body process without the need
-to carry out a likelihood fit of an angular distribution to the
-measured events. Instead, we present a method that only relies on
-orthogonality of angular functions, and estimation of integrals
-by means of Monte Carlo techniques. \fred{Paragraph sounds like abstract}\\
 

### 2014-06-24 draft.tex
Slight change of notation in Secs I and II wrt indices

@@
 
-Let $\thvec = (\theta_1, \dots \theta_n)$ denote the set of all
-angles, and let $\nuvec = (\nu_1, \dots \nu_m)$ denote the set of all
+Let $\thvec = (\theta_1, \dots \theta_N)$ denote the set of all
+angles, and let $\nuvec = (\nu_1, \dots \nu_M)$ denote the set of all
 other non-angular kinematic variables needed to fully specify the
@@
     \label{eq:def-ortho-rel}
-    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^n \theta = \delta_{ij}\,.
+    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^N \theta = \delta_{ij}\,.
 \end{equation}
@@
     \label{eq:def-P-decay}
-    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\dd^{n+m}\Gamma}{\dd \nu_1 \dots \dd \nu_m\, \dd \theta_1 \dots \theta_n}\,,
+    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\dd^{N+M}\Gamma}{\dd \nu_1 \dots \dd \nu_M\, \dd \theta_1 \dots \theta_N}\,,
 \end{align}
@@
     \label{eq:def-P-scattering}
-    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\dd^{n+m}\sigma}{\dd \nu_1 \dots \dd \nu_m\, \dd \theta_1 \dots \theta_n}\,,
+    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\dd^{N+M}\sigma}{\dd \nu_1 \dots \dd \nu_M\, \dd \theta_1 \dots \theta_N}\,,
 \end{align}
@@
     \label{eq:det-Pi-analytical}
-    P_i(\nuvec) = \int_{\thvec = 0}^{2\pi} f_i(\thvec) P(\nuvec, \thvec) \dd^n \theta\,.
+    P_i(\nuvec) = \int_{\thvec = 0}^{2\pi} f_i(\thvec) P(\nuvec, \thvec) \dd^N \theta\,.
 \end{equation}
@@
     \langle P_i\rangle
-    \equiv \int P_i(\nuvec) \dd^m \nu
-    = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^n\theta\right]\dd^m \nu\,.
+    \equiv \int P_i(\nuvec) \dd^M \nu
+    = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\,.
 \end{equation}
@@
     \label{eq:mc-id}
-    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{N} \sum_{k=1} g(x^{(k)})
+    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1} g(x^{(k)})
 \end{equation}
-due to the strong law of large numbers for $N \to \infty$ assuming
-that the variates $x^{(k)}$, $k = 1, \dots, N$ are distributed as
+due to the strong law of large numbers for $K \to \infty$ assuming
+that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
 $P$; i.e.,
@@
 \begin{equation}
-    \langle P_i\rangle \to \widehat{\langle P_i\rangle} = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)})\,.
+    \langle P_i\rangle \to \widehat{\langle P_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} f_i(x^{(k)})\,.
 \end{equation}
@@
 over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
-P_i\rangle$\footnote{% We refer for example to the determination of
-  the angular observables $J_i$ in $\bar{B}\to\bar{K}^*\ell^+\ell^-$
-  decays, see e.g. \cite{Aaij:2013iag}. For details on the relation
-  between the $P_i$ and the angular observable $J_i$ in the
-  aforementioned decay, we refer to appendix \ref{app:btokstarll}.  }.
+P_i\rangle$
 Therefore, we introduce the bin-integrated quantity
@@
     \langle P_i\rangle_{\vec{a},\vec{b}}
-    & = \int_{\vec{a}}^{\vec{b}} P_i(\nuvec) \dd^m \nu\\
-    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^n\theta\right]\dd^m \nu\\
+    & = \int_{\vec{a}}^{\vec{b}} P_i(\nuvec) \dd^M \nu\\
+    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\\
     & = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec)
@@
     \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}
-    = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
+    = \frac{1}{N} \sum_{k=1}^{K} f_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
@@
     \cov[\aver{P_i},\aver{P_j}]_{\vec{a},\vec{b}} \to \what{\cov}[\aver{P}_i, \aver{P}_j]_{\vec{a},\vec{b}}
-        = \frac{1}{N - 1} \sum_{k=1}^{N} \big[{f}_i(x^{(k)}) - \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[f_j(x^{(k)}) - \widehat{\langle P_j\rangle_{\vec{a},\vec{b}}}\big]
+        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[{f}_i(x^{(k)}) - \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[f_j(x^{(k)}) - \widehat{\langle P_j\rangle_{\vec{a},\vec{b}}}\big]
         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
-We would like to emphasize that the sample covariance should rapidly \fred{So what value of $N$ is close enought to $\infty$?} converge towards the true covariance matrix.
+We would like to emphasize that the sample covariance should rapidly \fred{So what value of $K$ is close enought to $\infty$?} converge towards the true covariance matrix.
 This will allow to construct constraints on optimized observables with correlated uncertainties

### 2014-06-24 draft.tex
Add and use reference MCSM-2004
Overlooked some indices in Secs. I and II
Fix references and some statements in Sec. III.A

@@
 \end{equation}
-can be approximated \citeneeded\fred{Robert, Casella} by an MC estimator $\what{E_P[g]}$
+can be approximated \cite{MCSM-2004} by an MC estimator $\what{E_P[g]}$
 \begin{equation}
@@
         %% \theta^{(m)}(\nuvec - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec)
-        \dd^n\theta\right]\dd^m \nu\,,
+        \dd^N\theta\right]\dd^M \nu\,,
 \end{align}
@@
     \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}
-    = \frac{1}{N} \sum_{k=1}^{K} f_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
+    = \frac{1}{K} \sum_{k=1}^{K} f_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
@@
 and when assuming a pure $P$-wave, resonant final state. An extension to $S-P$ interference has been
-studied for $B\to K\pi\ell^+\ell^-$ \cite{Blake:2012xx,Becirevic:2011xx} and for $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$
-\cite{Faller:2013xx}.
+studied for $B\to K\pi\ell^+\ell^-$ \cite{Blake:2012mb,Becirevic:2011bp} and for $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$
+\cite{Faller:2013dwa}.
 
@@
 We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(m)}$
-with respect to the remaining angle $\theta_2$. Using the observables $P_k(\vec{\nu}=(q^2, k^2))$ as defined in \refapp{}
+with respect to the remaining angle $\theta_2$. Using the observables $P_k(\vec{\nu}=(q^2, k^2))$ as defined in \refapp{partial-waves}
 the expansion reads
@@
 where $m=0$ for $n=1,2,6$ and $m=1$ for $n=3,4,5,7,8,9$. The angular observables defined as coefficients of this expansion
-have the merit of a well-defined total angular momentum, and thus can be disentangled (see \refapp{partial-waves} for
+have the merit of a well-defined total angular momentum, and thus can be disentangled for
 a derivation). As a consequence of the orthogonality of the Legendre polynomials, mismodelling or lack of modelling of higher
@@
 $P_{k,j}(\vec{\nu})$ consists of an infinite sum of bilinear of partial-wave amplitudes. It remains for theoretical
-analyses to estimate or calculate the impact of partial waves beyond the P wave \cite{Das:2014}.\\
+analyses to estimate or calculate the impact of partial waves beyond the S and P wave contributions.
+(For $B\to K\pi\ell^+\ell^-$ an initial study has been carried out for contributions up to the D wave \cite{Das:2014}).\\
 

### 2014-06-24 draft.tex
started writing the unfolding matrix

@@
 \usepackage[svgnames]{xcolor}
-
+\usepackage{hepparticles}
+\usepackage{hepnicenames}
+\usepackage{hepunits}
 %% Shortcuts %%
@@
 \renewcommand{\theta}{\vartheta}
-\newcommand{\GeV}{\text{GeV}}
+%\newcommand{\GeV}{\text{GeV}}
 \newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
@@
 \author{Marcin Chrzaszcz}
-\email{marcin.chrzaszcz@uzh.ch}
+\email{mchrzasz@cern.ch}
 \author{Nicola Serra}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+
+\section{Systematic way for determining the acceptance matrix for }
+
+In this section we will give a systematic description on how to obtain unfolding matrix based on MC sample.
+We start by generating so called flat phase space.
+In this MC all simulated angular distributions of $\cos \theta_l$, $\cos \theta_k$ and $\phi$ are flat.
+Assuming the massless limit, and not scalars the PDF has only 9 parameters: $F_l$, and $S_{3,4,5,6s,7,8,9}$:
+\begin{multline}
+\dfrac{d^4\Gamma}{ \Gamma dq^2 dcos\theta_k dcos\theta_l d\phi}=\dfrac{9}{32\pi}( \dfrac{3}{4} (1-F_l) \sin^2 \theta_k + F_l\cos^2 \theta_k + ( \dfrac{1}{4}(1-Fl)\sin^2 \theta_k \\ -  F_l\cos^2) cos 2\theta_l  + S_3 \sin^2 \theta_k \sin^2 \theta_l \cos2\phi + S_4 \sin2 \theta_k \sin \theta_l \cos\phi +\\ S_5 \sin2 \theta_k \sin \theta_l \cos \phi +  (S_{6s} \sin^2 \theta_k) \cos \theta_l + \\ S_7 \sin 2\theta_k \sin \theta_l \sin \phi +  S_8 \sin 2 \theta_k \sin 2 \theta_l \sin phi + S_9 sin^2 \theta_k \sin^2 \theta_l \sin 2 \phi)
+\end{multline}
+From theory it is easy to compute that only Fl will have a non zero moment equal to $\dfrac{2}{3}$.
+Next we apply the detector simulation and selection as done on real data.
+Then we can measure again all 9 moments which we put in a vector $\overrightarrow{v}$.
+The first column of an unfolding matrix $M_{unfold}$ will be then equal to $\dfrac{3}{2} \overrightarrow{v}$.
+Next we can weight selected events accordingly to $f_{s_3}$.
+From theory one can calculate that only moment corresponding to $S_3$ will be non zero and equal to $\dfrac{32}{225} S3$.
+Measuring the moments on weighted events and punting them in a vector: $\overrightarrow{v_2}$ leads to second column of unfolding matrix equal the $\dfrac{225}{32} \overrightarrow{v_2}$.
+Repeating this procedure for all moments will lead to full determination of the unfolding matrix.
+We provide reader the explicit calculation of the normalization factors for the moments vectors:
+\begin{equation}
+\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{S_{3,4,8,9}}*f_{S_{3,4,8,9}}= \dfrac{32}{225} ,
+\end{equation}
+
+\begin{equation}
+\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{S_{5,6,7}}*f_{S_{5,6,7}}= \dfrac{8}{45} ,
+\end{equation}
+\begin{equation}
+\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{F_l}= \dfrac{2}{3} 
+\end{equation}
+
 \bibliography{references}

### 2014-06-25 draft.tex
Comments and corrections on appendices

@@
 Not consistent with section I and II.
-I think it would be fair to talk about the dual basis already there.}
+I think it would be fair to talk about the dual basis already there.
+Do we set $f=0$ on $[\pi, 2 \pi]$?}
 \begin{equation}
@@
 The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
-for the most general basis of dimension-six $b\to s$ operators. It reads \cite{Blake:2012mb,Bobeth:2012vn}
+for the most general basis of dimension-six $b\to s$ operators. It reads \cite{Blake:2012mb,Bobeth:2012vn}\fred{In the theory convention. Now we use $J_i$ instead of $P_i$.}
 \begin{equation}
@@
 \end{equation}
-where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle.
+where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle.\fred{$\phi$ not explained}
 The decay width is
@@
 \end{equation}
-(Note here the notation, where indices with an \emph{i} arise only from S-wave/P-wave interference.)
-In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
+We indicate contributions from the interference of S waves and P waves by an index \emph{i}. In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
 \begin{equation}
@@
 
-The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays, with $P,P_1,P_2$ pseudoscalar mesons,
-and $\ell_1$, $\bar\ell_2$ charge or neutral leptons, includes decays
-such as e.g. $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$.
+The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays, where $P,P_1$, and $P_2$ are pseudoscalar mesons,
+and $\ell_1$ and $\bar\ell_2$ are charged or neutral leptons, includes decays
+such as $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$. \fred{If this appendix includes the previous one, how come there are less angular functions here?}
 Their PDFs can generally be written as \cite{Lee:1992ih}
@@
 where $q^2$ denotes the dilepton mass squared, and $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
-helicity angles in the dilepton and $N\pi$ systems, respectively. The basis of angular functions reads
+helicity angles in the dilepton and $N\pi$ systems, respectively. The basis of angular functions reads \fred{cite Danny's upcoming paper}
 \begin{equation}

### 2014-07-03 draft.tex
nothing
added toy chapter

@@
 \usepackage{hepunits}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{epstopdf}
 %% Shortcuts %%
@@
 \dfrac{d^4\Gamma}{ \Gamma dq^2 dcos\theta_k dcos\theta_l d\phi}=\dfrac{9}{32\pi}( \dfrac{3}{4} (1-F_l) \sin^2 \theta_k + F_l\cos^2 \theta_k + ( \dfrac{1}{4}(1-Fl)\sin^2 \theta_k \\ -  F_l\cos^2) cos 2\theta_l  + S_3 \sin^2 \theta_k \sin^2 \theta_l \cos2\phi + S_4 \sin2 \theta_k \sin \theta_l \cos\phi +\\ S_5 \sin2 \theta_k \sin \theta_l \cos \phi +  (S_{6s} \sin^2 \theta_k) \cos \theta_l + \\ S_7 \sin 2\theta_k \sin \theta_l \sin \phi +  S_8 \sin 2 \theta_k \sin 2 \theta_l \sin phi + S_9 sin^2 \theta_k \sin^2 \theta_l \sin 2 \phi)
+\label{PDF}
 \end{multline}
@@
 
+\section{Toy MC studies}
+
+We present a sensitivity study based on toy MC.
+Events were generated accordingly to \ref{PDF} for Standard Model expectation values corresponding to different $q^2$ bins and different number of events.
+In all studied cases we have not observed any biases in pull distribution.
+\begin{figure}[h]
+        \centering
+        \begin{subfigure}[b]{0.45\textwidth}
+                \includegraphics[width=0.8\textwidth]{figs/Q2_5_6_S5.png}
+               % \caption{Uncertainty on $S_5$}
+                 \end{subfigure}
+        \begin{subfigure}[b]{0.45\textwidth}
+                \includegraphics[width=0.8\textwidth]{figs/Q2_5_6_S7.png}
+              %\caption{Uncertainty on $S_7$}
+                 \end{subfigure}
+       \caption{Uncertainty on PDF parameters as a function of number of events. Red curve represents a fit to $f(x)=\dfrac{\alpha}{\sqrt{x}}$ function.}
+        \label{errors}
+\end{figure}\\
+The errors as a function of number of signal events are given in~\ref{errors}.
+As can be see errors follow strictly the $\sqrt{n}$ law.
+We performed also the fit to the same toys.
+For low number of events we observed significant biases.
+For the high number of signal events we observed  errors coming from fit to be $5-15\%$ smaller then  the ones obtained by method of moments.
+
 \bibliography{references}

### 2014-07-09 draft.tex
Major update, as discussed with Fred

--- 2014-06-25 draft.tex
@@
 \newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
+\newcommand{\ie}{\textit{i.e.}}
 \newcommand{\nuvec}{\vec{\nu}}
@@
 \newcommand{\aver}[1]{\langle #1 \rangle}
-\newcommand{\what}[1]{\widehat{#1}}
+\newcommand{\est}[1]{\widehat{#1}}
 \newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
 \DeclareMathOperator{\cov}{Cov}
+%\DeclareMathOperator{\skew}{Skew}
+\DeclareMathOperator{\kurt}{Kurt}
 
@@
 
+\captionsetup{compatibility=false}
+
 \begin{document}
@@
 
-\preprint{SI-HEP-2014-xx}
-\title{Sample-Based Determination of Angular Observables}
+\preprint{SI-HEP-2014-17}
+\title{Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays}
 \author{Frederik Beaujean}
@@
 orthogonality of angular functions, and estimation of integrals
-by means of Monte Carlo techniques.
+by means of Monte Carlo techniques. Beyond providing estimators
+for central values and uncertainties, we provide means to determine
+the correlation between all angular observables. We show that detector
+acceptance effects can be accounted for in the analysis.
 \end{abstract}
@@
 $\bar{B}\to \bar{K}^*(\to \bar{K}\pi)\ell^+\ell^-$. However, we emphasize that
-he method we describe in the remainder of this letter is general and applies to arbitrary
-decay or scattering processes.\\
+the method we describe in this letter is general, and it applies to arbitrary
+decay or scattering processes. We find a previous work \cite{Dighe:1998vk}
+advocates this method chiefly for the determination of angular observables in non-leptonic
+$B$ decays, but also mentions the applicability to semileptonic decays. We improve
+upon this previous work by studying correlations between the angular observables,
+and sources of systematic uncertainties. Moreover, we will show that the method
+at hand has two benefits over the usual approach based on likelihood fits.
+\begin{enumerate}
+    \item Likelihood fits do not always converge. \fred{Why? Mismodelling? Expand!}
+    \item Using the method at hand, the joint probability distribution of the
+        angular observables converges towards a multivariate normal distribution.
+        This allows easy transfer of information from the experiment to interest
+        theorists.
+\end{enumerate}
 
-Let $\thvec = (\theta_1, \dots \theta_N)$ denote the set of all
+We continue with basic definitions that pertain to angular observables, and our
+results in the subsequent sections. Let $\thvec = (\theta_1, \dots \theta_N)$ denote the set of all
 angles, and let $\nuvec = (\nu_1, \dots \nu_M)$ denote the set of all
@@
 include invariant masses or center-of-mass energies. We define an
-angular observable $P_i$ as a coefficient in the probability density
-function (PDF) of the process,
+angular observable $S_i$ as a coefficient in the probability density
+function (PDF) of the process by means of
 \begin{align}
     \label{eq:def-P}
-    P(\nuvec, \thvec) = \sum_i P_i(\nuvec) \times f_i(\thvec)\,.
+    P(\nuvec, \thvec) \equiv \sum_i S_i(\nuvec) \times f_i(\thvec)\,.
 \end{align}
@@
     \label{eq:def-ortho-rel}
-    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^N \theta = \delta_{ij}\,.
+    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^N \theta = \delta_{ij}\,,
 \end{equation}
+with $\Omega$ representing the full angular phase space relevant to the process.
 For the purpose of this letter, however, it suffices that the system
@@
 orthonormal basis. The transformation needs to be worked out on a
-case-by-case basis. For a selection of $B$ decays, the transformations
-are listed in the appendices \ref{app:btokll} through
-\ref{app:lambdabtolambdall}.  Note that $P_i$ is \emph{not} a PDF.  \\
+case-by-case basis. For a selection of $B$ decays which we consider the most interesting
+we list the transformations in a series of appendices \ref{app:btokll} through
+\ref{app:lambdabtolambdall}.\\
 
@@
 replaced by the corresponding quantity of a control-channel
-process.\fred{How would $P$ remain a proper probability such that
-  $\int P = 1$? You can't simply change the normalization. I propose a
-  change of notation: I find it terribly confusing that $P(\nuvec,
-  \thvec)$ is a probability but $P_i(\nuvec)$ is not. For $P_i$, later
-  on the symbols $J_i, K_i$ etc are used. We don't have to use the
-  same symbol everywhere but let's not use $P_i$}\\
+process. This change of normalization is equivalent to a linear rescaling of
+the angular observables $\lbrace S_i\rbrace$; thus ratios or similar suitable combinations
+of the angular observables are invariant.\\
 
 In the remainder of this letter we discuss how to obtain the angular
-observables $P_i(\nuvec)$ in an experimental setup where each recorded
+observables $S_i(\nuvec)$ in an experimental setup where each recorded
 event is (approximately) distributed according to $P$.  We establish
@@
 
-The orthonormality relations \refeq{def-ortho-rel} imply that a single angular observable $P_i$
+The orthonormality relations \refeq{def-ortho-rel} imply that a single angular observable $S_i$
 can be projected out of the full PDF $P$ by means of
@@
     \label{eq:det-Pi-analytical}
-    P_i(\nuvec) = \int_{\thvec = 0}^{2\pi} f_i(\thvec) P(\nuvec, \thvec) \dd^N \theta\,.
+    S_i(\nuvec) = \int_{\Omega} \hat{f}_i(\thvec) P(\nuvec, \thvec) \dd^N \theta\,.
 \end{equation}
-In point of fact, $P_i$ is the $f_i$-th moment of the PDF $P$\fred{This
-  notation is uncommon. Is that how we \emph{define} the $f_i$-th
-  moment?}. Additionally, integration over the non-angular variables
-yields
+where $\lbrace \hat{f}_i \rbrace$ denotes a \emph{dual basis} of angular function. In all generality
+the bases $\lbrace f_i \rbrace$ and $\lbrace \hat{f}_i \rbrace$ are not identical. This is the
+case for our selection of applications in appendices \ref{app:btokll} through \ref{app:lambdabtolambdall}.\\
+
+It is sensible to refer to the angular observable $S_i$ as the \emph{$\hat{f}_i$-moment} of the PDF $P$.
+We emphasize that a relation of type \refeq{det-Pi-analytical} holds for any combination of
+scalar product and orthonormal basis of angular functions $\lbrace f_i \rbrace$; \ie, there is no unique
+basis of angular functions. For the proof we refer to ref. \cite{Dighe:1998vk}.\\
+In addition, integration over the non-angular variables yields
 \begin{equation}
-    \langle P_i\rangle
-    \equiv \int P_i(\nuvec) \dd^M \nu
-    = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\,.
+    \langle S_i\rangle
+    \equiv \int S_i(\nuvec) \dd^M \nu
+    = \int \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\,.
 \end{equation}
@@
 \end{equation}
-can be approximated \cite{MCSM-2004} by an MC estimator $\what{E_P[g]}$
+can be approximated \cite{MCSM-2004} by an MC estimator $\est{E_P[g]}$
 \begin{equation}
@@
 
-We assume, for a moment, that $P$ describes the distribution of the underlying
-physical process truthfully. In that case, all events detected in an experimental setup are in fact, up to
-detection efficiencies, distributed as $P$. \fred{Paragraph is redundant an can be omitted.}
-
-Application of \refeq{mc-id} then yields \fred{notation is very confusing $P_i$ for $x^{(k)} \sim P$}
+Application of \refeq{mc-id} then yields
 \begin{equation}
-    \langle P_i\rangle \to \widehat{\langle P_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} f_i(x^{(k)})\,.
+    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})\,.
 \end{equation}
@@
 over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
-P_i\rangle$
+S_i\rangle$.
 Therefore, we introduce the bin-integrated quantity
 \begin{align}
-    \langle P_i\rangle_{\vec{a},\vec{b}}
-    & = \int_{\vec{a}}^{\vec{b}} P_i(\nuvec) \dd^M \nu\\
-    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\\
-    & = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec)
+    \langle S_i\rangle_{\vec{a},\vec{b}}
+    & = \int_{\vec{a}}^{\vec{b}} S_i(\nuvec) \dd^M \nu\\
+    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\\
+    & = \int \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec)
         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
-        %% \theta^{(m)}(\nuvec - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec)
         \dd^N\theta\right]\dd^M \nu\,,
@@
 \begin{equation}
-    \label{bin-importance}
-    \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}
-    = \frac{1}{K} \sum_{k=1}^{K} f_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
+    \label{eq:bin-importance}
+    \widehat{\langle S_i\rangle_{\vec{a},\vec{b}}}
+    = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
 This basically reduces the estimation of
-$\aver{P_i}_{\vec{a},\vec{b}}$ to a (weighted) counting experiment. In
+$\aver{S_i}_{\vec{a},\vec{b}}$ to a (weighted) counting experiment. In
 the limit $N \to \infty$, the random vector $( \dots,
-\aver{P_i}_{\vec{a},\vec{b}}, \dots)$ follows a multivariate Gaussian
-distribution \citeneeded\fred{Why?  multivariate in $\widehat{P_i}$?}
-with a mean vector estimated by \refeq{bin-importance} and covariance
+\aver{S_i}_{\vec{a},\vec{b}}, \dots)$ follows a multivariate Gaussian
+distribution \citeneeded\fred{Robert,Casella?}
+with the mean vector estimated by \refeq{bin-importance}, and the covariance
 estimated as
 \begin{equation}
-    \cov[\aver{P_i},\aver{P_j}]_{\vec{a},\vec{b}} \to \what{\cov}[\aver{P}_i, \aver{P}_j]_{\vec{a},\vec{b}}
-        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[{f}_i(x^{(k)}) - \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[f_j(x^{(k)}) - \widehat{\langle P_j\rangle_{\vec{a},\vec{b}}}\big]
+    \cov[\aver{S_i},\aver{S_j}]_{\vec{a},\vec{b}} \to \est{\cov}[\aver{S}_i, \aver{S}_j]_{\vec{a},\vec{b}}
+        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\hat{f}_i(x^{(k)}) - \est{\langle S_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\hat{f}_j(x^{(k)}) - \widehat{\langle S_j\rangle_{\vec{a},\vec{b}}}\big]
         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
-We would like to emphasize that the sample covariance should rapidly \fred{So what value of $K$ is close enought to $\infty$?} converge towards the true covariance matrix.
-This will allow to construct constraints on optimized observables with correlated uncertainties
-from the experimental constraints on the angular observables. (See \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf}
-for definitions of such optimized observables in $B\to K^*\ell^+\ell^-$ decays).
+We would like to emphasize that the sample covariance should rapidly converge towards the true covariance matrix.
+We propose to declare convergence once estimators for skewness and kurtosis are sufficiently small,
+\begin{equation}
+    \est{\operatorname{Skew}}[\aver{S_i},\aver{S_j}] \ll 1\,\,\text{ and }\,\,\est{\kurt}[\aver{S_i},\aver{S_j}] \ll 1\,.
+\end{equation}
+
+The convergence towards a normal distribution for the results allows to transfer correlation information to interested
+theorists. In particular, this will allow to constrict predictive distributions of optimized observables.
+(See e.g. \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf}
+for definitions of such optimized observables in $B\to K^*\ell^+\ell^-$ decays, \cite{Faller:2013dwa} for application to
+the decay $B\to \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$).
 
@@
 
-In \refsec{sample-based-det}, we assume that the PDF $P$ describe the physical reality accurately,
+In \refsec{sample-based-det}, we assume that the PDF $P$ describe the underlying physics accurately,
 and that the experiment observes each event with perfect accuracy. In order to estimate systematic
@@
 However, in several interesting processes we might only have an approximative result for $P$.
-We will now show that this is the case for the interesting class of four-body decays $B\to P_1 P_2 \ell_1 \bar\ell_2$,
-which includes the rare $b\to s$-mediated $B$ decay $B \to K\pi\ell^+\ell^-$ and the $V_{ub}$ suppressed decay
-$B\to \pi\pi\ell^+\bar\nu_\ell$. For both examples the PDF $P$ is known in the small-width approximation
-and when assuming a pure $P$-wave, resonant final state. An extension to $S-P$ interference has been
-studied for $B\to K\pi\ell^+\ell^-$ \cite{Blake:2012mb,Becirevic:2011bp} and for $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$
-\cite{Faller:2013dwa}.
+In this section, we take the interesting class of four-body decays $B\to P_1 P_2 \ell_1 \bar\ell_2$
+as an example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B \to K\pi\ell^+\ell^-$, and
+the $V_{ub}$ suppressed decay $B\to \pi\pi\ell^+\bar\nu_\ell$. For both examples the PDF $P$ is known in
+the small-width approximation and when assuming a pure $P$-wave, resonant final state. An extension to
+$S-P$ interference has been studied for $B\to K\pi\ell^+\ell^-$ \cite{Blake:2012mb,Becirevic:2011bp},
+and for $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$ \cite{Faller:2013dwa}. For a first study of $S$, $P$
+and $D$ interference, see \cite{Das:2014sra}}.%
+The PDFs for these decays are usually expressed in terms of one or a few partial waves
+of the dimeson system. However, the angular momentum of the dimeson system is unbounded from above.
+\\
 
-For this class of decays, we face the problem that $P$ has a given dependence on the dilepton helicity angle $\theta_1$
-and the azimuthal angle $\theta_3$. (See also \refapp{btokpill} for details on the angular distribution.)
-However, on the level of decay amplitudes the dimeson system can have an arbitrary
-large total angular momentum; only the third component of its angular momentum is restricted to $J^{\pi\pi}_z = -1,0,+1$.\\
+For the selected class of decays, we face the problem that $P$ has a given dependence on the dilepton
+helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokpill} for details
+on the angular distribution.) However, on the level of decay amplitudes the dimeson system can have an arbitrary
+large total angular momentum $j$; only its third component is restricted to $m = -1,0,+1$.\\
 
-We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(m)}$
-with respect to the remaining angle $\theta_2$. Using the observables $P_k(\vec{\nu}=(q^2, k^2))$ as defined in \refapp{partial-waves}
-the expansion reads
+We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(|m|)}$
+with respect to the remaining angle $\theta_2$. Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
+and as defined in \refapp{partial-waves}, the expansion reads
 \begin{equation}
-    P_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{j,m}} P_{k,j}(\vec{\nu}) p_{j}^{(m)}(\cos\theta_2)\sin\theta_2\,,
+    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{j,|m|}} S_{k,j}(\vec{\nu}) p_{j}^{(|m|)}(\cos\theta_2)\sin\theta_2\,,
 \end{equation}
-where $m=0$ for $n=1,2,6$ and $m=1$ for $n=3,4,5,7,8,9$. The angular observables defined as coefficients of this expansion
-have the merit of a well-defined total angular momentum, and thus can be disentangled for
-a derivation). As a consequence of the orthogonality of the Legendre polynomials, mismodelling or lack of modelling of higher
-partial-wave observables \emph{does not affect} the method of moments as given in the previous section.
+where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}, and we have
+\begin{equation}
+    |m| = \begin{cases}
+        0\,, & k = 1,2,6\,\\
+        1\,, & k = 3,4,5,7,8,9\,,
+    \end{cases}\,.
+\end{equation}
+The angular observables $S_{k,j}$ defined as coefficients of this expansion
+have the merit of a well-defined total angular momentum, and thus are physically discriminable.
+As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
+partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section.\\
+
 Unfortunately, this benefit on the experimental side is accompanied with a theoretical draw back. Each observable
-$P_{k,j}(\vec{\nu})$ consists of an infinite sum of bilinear of partial-wave amplitudes. It remains for theoretical
+$S_{k,j}(\vec{\nu})$ consists of an infinite sum of bilinear of partial-wave amplitudes. It remains for theoretical
 analyses to estimate or calculate the impact of partial waves beyond the S and P wave contributions.
-(For $B\to K\pi\ell^+\ell^-$ an initial study has been carried out for contributions up to the D wave \cite{Das:2014}).\\
+(For $B\to K\pi\ell^+\ell^-$ a first study has been carried out where contributions up to the D wave are studied \cite{Das:2014sra}).\\
 
@@
 
-\subsection{Detector Acceptance Effects and Backgrounds}
+\subsection{Detector Acceptance Effects}
 \label{sec:systematics:acceptance}
 
-\fred{If this is to be general, should explain what we mean by
-  acceptance. Isn't it that experiments just model the detector well?
-  The P. to observe an event in $\nuvec, \thvec$ might be very
-  different from the P. to create an event in $\nuvec, \thvec$. All
-  that's needed is a full forward model. I'm not sure that in
-  \refeq{eq:PDFwithDE} we still have a normalized probability. Am I
-  right to say that detector effects can be very much localized and
-  nondifferentiable? Like some wires are inactive, or the region close
-  to the beam has zero acceptance. In the latter case, modeling
-  residual acceptance effects with smooth Legendre polynomials seems a
-  bad idea.}
-
+\fred{Comment that in this section $\vec\nu$ and $\vec\theta$ are used after ``correction'' has been applied.}
+\danny{Rethink order of this section.}
 Thanks to accurate detector simulations and control studies, the experimental analyses have become
@@
 \begin{equation}
-    P(\theta) = P_1 + P_2 \cos\theta + P_2 \cos^2\theta\,,
+    P(\theta) = S_1 + S_2 \cos\theta + S_2 \cos^2\theta\,,
 \end{equation}
@@
 \begin{aligned}
-    \wwhat{P_1} & = \Big(1 + \frac{\eps_{1}^{(2)}}{2}\Big) \what{P_1} + \frac{9 \eps_{1}^{(2)}}{70} \what{P_3}\\
-    \wwhat{P_2} & = \Big(1 - \frac{2 \eps_{1}^{(2)}}{5}\Big) \what{P_2} - \eps_{1}^{(1)} \what{P_1} - \frac{3\eps_{1}^{(1)}}{5} \what{P_3}\\
-    \wwhat{P_3} & = \Big(1 - \frac{11\eps_{1}^{(2)}}{14}\Big)\what{P_3} - \frac{3\eps_{1}^{(2)}}{2} \what{P_1} - \eps_{1}^{(1)} \what{P_2}\,.
+    \wwhat{S_1} & = \Big(1 + \frac{\eps_{1}^{(2)}}{2}\Big) \est{S_1} + \frac{9 \eps_{1}^{(2)}}{70} \est{S_3}\\
+    \wwhat{S_2} & = \Big(1 - \frac{2 \eps_{1}^{(2)}}{5}\Big) \est{S_2} - \eps_{1}^{(1)} \est{S_1} - \frac{3\eps_{1}^{(1)}}{5} \est{P_3}\\
+    \wwhat{S_3} & = \Big(1 - \frac{11\eps_{1}^{(2)}}{14}\Big)\est{S_3} - \frac{3\eps_{1}^{(2)}}{2} \est{S_1} - \eps_{1}^{(1)} \est{P_2}\,.
 \end{aligned}
 \end{equation}
-Here $\what{P_i}$ denotes the uncorrected estimators, while $\wwhat{P_i}$ denotes the efficiency-corrected estimators of the angular observables.\\
+Here $\lbrace \est{S_i}\rbrace$ are the uncorrected estimators, while $\lbrace \wwhat{S_i}\rbrace$ denote the
+acceptance-corrected estimators of the angular observables.\\
 
@@
 \end{equation}
-This leads to a matrix-valued equation that relates the effiency-corrected estimators $\wwhat{P}_i$ to the uncorrected
-estimators $\what{P}_j$,
+This leads to a matrix-valued equation that relates the effiency-corrected estimators $\wwhat{S}_i$ to the uncorrected
+estimators $\est{S}_j$,
 \begin{equation}
     \label{eq:eff-corrected-est-btokstarll}
-    \wwhat{P}_i = \sum_{j=1\text{s},\dots\,9} \big(\delta_{ij} + N_{ij}\big) \what{P}_j\,.
+    \wwhat{S}_i = \sum_{j=1\text{s},\dots\,9} \big(\delta_{ij} + N_{ij}\big) \est{S}_j\,.
 \end{equation}
@@
 
-The determination of the coefficients $\eps_i^{(j)}$ that parametrize the detectory effects is generally
-a difficult task. Here, we will show a systematic method to determine these coefficients.\\
-One starts from generating a flap phase space MonteCarlo sample.
-Simulated events are then put thought the detector simulation, and selection requirements.
-Since flap phase space ensures flat distribution of angles on the generated level, the only non zero moment is one associated to Fl.
-Measuring the moments of this MC sample leads will etc.
-Mayby this should be an appendix.
+The determination of detector acceptance is generally a difficult task. Here, we will show a systematic
+method to its effects.\\
+
+As previous, we use a PDF $P$ decomposed into $N$ angular observables $S_k$. We denote the estimator of the observable
+$S_k$ as $\est{S_k}$, which is affected by the detector acceptance. We assume now that the acceptance-corrected estimator
+$\wwhat{S_k}$ is a linear combination of the uncorrected estimators $\lbrace \est{S_k}\rbrace$,
+\begin{equation}
+    \label{eq:linear-assumption}
+    \wwhat{S_k} = \sum_j M_{kj} \est{S}_j\,.
+\end{equation}
+The coefficients $M_{kj}$ can now be systematically determined from MC studies of the detector geometry.
+\begin{enumerate}
+    \item In step $i$, let $S_i = 1$, and $S_{k\neq i} = 0$.
+    \item Simulate events from the PDF, and adjust each event based on the detector geometry. This allows
+        to compute $\est{S_j^{(i)}}$ from the simulation.
+    \item Solve the system of linear equations
+        \begin{equation}
+        \begin{aligned}
+            1 & = \sum_j M_{ij}^{(i)} \est{S_j^{(i)}}\,,\\
+            0 & = \sum_j M_{kj}^{(i)} \est{S_j^{(i)}}\,,\qquad\forall k \neq i\,.
+        \end{aligned}
+        \end{equation}
+        This allows the dermination of those coefficients $M_{kj}^{(i)}$ for which $\est{S_j^{(i)}} \neq 0$.
+    \item If $i < N$ advance $i$ by one and go to step 1
+\end{enumerate}
+We can now check if the assumption \refeq{linear-assumption} is valid, by checking that
+$M_{kj}^{(i)} = M_{kj}^{(i')}$ for all $i$, $i'$.
 
@@
 
-\todo{
+In order to study the performance of the proposed method, we simulate measurements for one uni-angular
+and one tri-angular decay distribution for various numbers of events. As inputs we use the SM predictions
+for the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to K\pi)\ell^+\ell^-$, respectively. We cover the
+$q^2$ ranges $1\GeV^2$ to $6\GeV^2$, and $15\GeV^2$ to to the respective kinematic endpoint, with two
+bin widths: $1\GeV^2$ and $0.5\GeV^2$. This is to ensure that a wide spectrum of possible values for
+the angular observables. We find:
 \begin{itemize}
-    \item Simulate this for one angle $\theta_{1}$ (similar to $B\to K \ell^+\ell^-$) with varying samples sizes.
-    \item Simulate this for three angles $\theta_{1\dots 3}$ (similar to $B\to K^*(\to K \pi)\ell^+\ell^-$) with varying samples sizes.
-    \item Also, check explicitly the variance and covariance of the results for all sample sizes considered.
-    \item compare robustness to likelihood fit when fit doesn't
+    \item In all studied cases we observed not a single bias in the pull distribution of the observable.
+    \item The error $\sigma_k(N)$ of an angular observable $S_k$, evaluate for $N$ events is very well
+        fitted by
+        \begin{equation}
+            \sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}
+        \end{equation}
+        with $\sigma_k(1) = \order{1}$. \todo{Check this!}
+    \item \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of $N$.}
+    \item \todo{Perform Mardia's Skewness and Kurtosis tests.}
+    \item \dots
+\end{itemize}
+We find that all of the above results show consistenly convergence of the distribution for the angular observables
+towards a multivariate normal distribution.
+
+\begin{figure}[t]
+        \centering
+        \begin{subfigure}[b]{0.45\textwidth}
+                \includegraphics[width=0.8\textwidth]{figs/Q2_5_6_S5.png}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.45\textwidth}
+                \includegraphics[width=0.8\textwidth]{figs/Q2_5_6_S7.png}
+        \end{subfigure}
+        \caption{Uncertainty of the angular observables $S_5$ and $S_7$, extracted from simulated events of the decay $B\to K^*\ell^+\ell^-$
+        and as a function of the number of simulated events $N$. The red curve represents a fit to the function $\sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}$.}
+        \label{fig:errors}
+\end{figure}
+
+We used the simulated events and fitted a likelihood function to them.
+\begin{itemize}
+    \item For a small number of simulated events, \danny{$N=?$}, we observe a significant bias in the pull distributions.
+    \item For a large number of simulated events, \danny{$N=?$}, the uncertainty of the angular observables is
+        smaller compared to the results of the method of moments.
+\end{itemize}
+\todo{compare robustness to likelihood fit when fit doesn't
 converge. Why exactly doesn't it converge? What if physics model
-      wrong, say some angular terms are missing.
-\end{itemize}}
+wrong, say some angular terms are missing.}
 
@@
 \danny{Potential people to read the manuscript: Jochen Dingfelder (Belle-II, Bonn), Ulrik Egede (LHCb, Imperial London), Christoph Langenbruch (LHCb, Warwick), Michel De Cian (LHCb, Heidelberg), Adrian Bevan (ATLAS, Queen Mary)  }
-D.v.D would like to thank Gudrun Hiller and Martin Jung for discussing the results of \cite{Das:2014xx} prior to publication.
+D.v.D would like to thank Gudrun Hiller and Martin Jung for discussing the results of \cite{Das:2014sra} prior to publication.
 
@@
 \end{equation}
-where the basis of angular functions $f_i$ reads
+where the basis of angular functions $\lbrace f_i\rbrace$ reads
 \begin{equation}
@@
 Here we denote the dilepton mass squared as $q^2$, and the dilepton helicity angle as $\theta_1 \equiv \theta_{\ell}$. We transform the PDF from a $\cos\theta_1$-dependence
-to a $\theta_1$-dependence \fred{why? Formula easier? Where is the ``-'' sign from the Jacobian $\partial_{\theta} \cos \theta = - \sin \theta$ },
+to a $\theta_1$-dependence,
 \begin{equation}
@@
 \end{equation}
+where we define $P_{\lbrace 1,2,3\rbrace} \equiv \lbrace a, b, c\rbrace / \Gamma$.\\
 
-We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_i$ in the sense that \fred{What are the upper limits?
-$\pi$ or $2 \pi$?
-Not consistent with section I and II.
-I think it would be fair to talk about the dual basis already there.
-Do we set $f=0$ on $[\pi, 2 \pi]$?}
-\begin{equation}
-    \int_0^\pi \dd\theta_1 \hat{f}_i(\theta_1) f_j(\theta_1) \sin\theta_1 = \delta_{ij}\,,
-\end{equation}
-thereby enabling us to project out exactly one of the angular
-observables $P_i(q^2)$
-\begin{equation}
-    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = P_i(q^2)\,.
-\end{equation}
-The dual basis reads
+The dual basis $\lbrace \hat{f}_i\rbrace$ reads
 \begin{equation}
@@
     \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
-    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,.
+    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,,
 \end{aligned}
+\end{equation}
+such that 
+\begin{equation}
+    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
 \end{equation}
@@
 The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
-for the most general basis of dimension-six $b\to s$ operators. It reads \cite{Blake:2012mb,Bobeth:2012vn}\fred{In the theory convention. Now we use $J_i$ instead of $P_i$.}
+for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
 \begin{equation}
-    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{J_{i}(q^2)}{\Gamma} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
+    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{J_{i}(q^2)}{\dd\Gamma/\dd q^2} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
 \end{equation}
-where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle.\fred{$\phi$ not explained}
-The decay width is
+where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
+The $q^2$-differential decay width reads
 \begin{equation}
-    \Gamma = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
+    \frac{\dd\Gamma}{\dd q^2} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
 \end{equation}
@@
 \begin{equation}
-    P(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i P_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
+    P(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
 \end{equation}
-where we also define $P_i(q^2) = J_i(q^2) / \Gamma$.\\
+where we also define $S_i(q^2) = J_i(q^2) / (\dd\Gamma/\dd q^2)$.\\
 
-We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_j$ in the sense that
-\begin{equation}
-    \frac{3}{8\pi}\int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) f_j(\theta_1,\theta_2,\phi) \sin\theta_1 \sin\theta_2 = \delta_{ij}\,,
-\end{equation}
-thereby enabling us to project out exactly one of the angular
-observables $P_i(q^2)$
-\begin{equation}
-    \int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) P(q^2, \theta_1,\theta_2,\phi) = P_i(q^2)\,.
-\end{equation}
 The dual basis reads
@@
 \end{aligned}
+\end{equation}
+such that 
+\begin{equation}
+    \int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) P(q^2, \theta_1,\theta_2,\phi) = S_i(q^2)\,.
 \end{equation}
@@
 estimate or calculate the impact of individual contributions, with or without the cut off $L$.
-For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014}.
+For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
 

### 2014-07-09 draft.tex
Make appendices more consistent

@@
 and $\ell_1$ and $\bar\ell_2$ are charged or neutral leptons, includes decays
-such as $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$. \fred{If this appendix includes the previous one, how come there are less angular functions here?}
+such as $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$.
 Their PDFs can generally be written as \cite{Lee:1992ih}
@@
     & = \frac{1}{4\pi} \sum_i \frac{I(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \phi) \sin\theta_1 \sin\theta_2\\
-    & \equiv \frac{1}{4\pi} \sum_i P_i(q^2, k^2, \theta_2) f_i(\theta_1, \phi)\,.
+    & \equiv \frac{1}{4\pi} \sum_i S_i(q^2, k^2, \theta_2) f_i(\theta_1, \phi)\,.
 \end{aligned}
 \end{equation}
-where we also define $P_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / \Gamma$.\\
+where we also define $S_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / (\dd\Gamma/\dd q^2)$.\\
 
-We provide a basis $\hat{f}_i$ of angular functions which is dual to the basis $f_j$ in the sense that
-\begin{equation}
-    \frac{1}{4\pi}\int_0^\pi \dd\theta_1 \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\phi) f_j(\theta_1,\phi) \sin\theta_1 = \delta_{ij}\,,
-\end{equation}
-thereby enabling us to project out exactly one of the angular
-observables $P_i(q^2, k^2, \theta_2)$
-\begin{equation}
-    \int_0^\pi \dd\theta_1 \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\phi) P(q^2, k^2, \theta_1,\theta_2,\phi) = P_i(q^2, k^2, \theta_2)\,.
-\end{equation}
 The dual basis reads
@@
 \end{equation}
+such that
+\begin{equation}
+    \int_0^\pi \dd\theta_1 \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\phi) P(q^2, k^2, \theta_1,\theta_2,\phi) = S_i(q^2, k^2, \theta_2)\,.
+\end{equation}
 
@@
 \begin{equation}
-    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\Gamma} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
+    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\dd \Gamma/\dd q^2} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
 \end{equation}
-where $q^2$ denotes the dilepton mass squared, and $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
-helicity angles in the dilepton and $N\pi$ systems, respectively. The basis of angular functions reads \fred{cite Danny's upcoming paper}
+where $q^2$ denotes the dilepton mass squared, $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
+helicity angles in the dilepton and $N\pi$ systems, respectively, and $\theta_3 = \phi$ denotes the azimuthal angle.
+The basis of angular functions reads \cite{Boeer:2014xx}
 \begin{equation}
@@
 \end{equation}
-The decay width reads $\langle\Gamma\rangle = \langle2 K_{1ss} + K_{1cc}\rangle$. In terms of the angles $\theta_1$ and $\theta_2$, instead of the cosines, the PDF reads
+The decay width reads
 \begin{equation}
-    P_{\Lambda_b}(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i P_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
+    \frac{\dd \Gamma}{\dd q^2} = 2 K_{1ss} + K_{1cc}
 \end{equation}
-where we also define $P_i(q^2) = K_i(q^2) / \Gamma$.
+In terms of the angles $\theta_1$ and $\theta_2$, instead of the cosines, the PDF reads
+\begin{equation}
+    P_{\Lambda_b}(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
+\end{equation}
+where we also define $S_i(q^2) = K_i(q^2) / (\dd\Gamma/\dd q^2)$.\\
 
-We provide a dual basis $\hat{f}_i$ of the angular functions which is orthogonal to the basis $f_j$ in the sense that
-\begin{equation}
-    \frac{3}{8\pi}\int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) f_j(\theta_1,\theta_2,\phi) \sin\theta_1 \sin\theta_2 = \delta_{ij}\,,
-\end{equation}
-thereby enabling us to project out exactly one of the angular observables $P_i(q^2)$ using
-\begin{equation}
-    \int_0^\pi \dd \theta_1 \int_0^\pi \dd \theta_2 \int_0^{2\pi} \dd \phi P(q^2, \theta_1, \theta_2, \phi) \hat{f}_i(\theta_1, \theta_2, \phi) = P_i(q^2)\,.
-\end{equation}
 The dual basis reads
@@
     \end{aligned}
+\end{equation}
+such that
+\begin{equation}
+    \int_0^\pi \dd \theta_1 \int_0^\pi \dd \theta_2 \int_0^{2\pi} \dd \phi P(q^2, \theta_1, \theta_2, \phi) \hat{f}_i(\theta_1, \theta_2, \phi) = S_i(q^2)\,.
 \end{equation}

### 2014-07-16 draft.tex
Rework secion on detector acceptance effects

@@
 
+\paragraph{Recipe to determine the acceptance effects}
+
+The determination of detector acceptance is generally a difficult task. Here, we will show a systematic
+method to estimate its effects based on both the method of moments, and MC simulations of the detector.\\
+
+As previous, we use a PDF $P$ decomposed into $N$ angular observables $\lbrace S_k\rbrace$,
+\begin{equation}
+    P \equiv P(\vec\nu,\vec\theta | \lbrace S_k \rbrace)\,.
+\end{equation}
+We denote the estimator of an
+observable $S_k$ as $\est{S_k}$, which is affected by the detector acceptance. We assume now that there is a linear relation
+between the true angular observables $\lbrace S_k^\text{true}\rbrace$, and the estimators $\lbrace \est{S_k}\rbrace$,
+\begin{equation}
+    \label{eq:linear-assumption}
+    \est{S_i} = \sum_{i = 1}^N M_{i j} S_j^\text{true}\,.
+\end{equation}
+In that case, the matrix $M_{ij}$ can be fully determined through the following steps.
+\begin{enumerate}
+    \item For a fixed $j$, let $S_j^\text{true} = 1$, and $S_k^\text{true} = 0\,\forall k\neq j$.
+    \item Draw simulated events $\lbrace x_t^{(k)}\rbrace = \lbrace(\vec{\nu}^{(k)}_t,\vec\theta^{(k)}_t)\rbrace$ (dubbed ``true'') from the PDF $P_j$,
+        \begin{equation}
+            P_j \equiv P(\vec\nu,\vec\theta | \lbrace S_j = 1, S_{k\neq j} = 0\rbrace)\,.
+        \end{equation}
+    \item Use the true events as input for the MC simulation of the detector, in order to obtain the detector
+        events $\lbrace x^{(k)}_d\rbrace = \lbrace(\vec{\nu}^{(k)}_d,\vec\theta^{(k)}_d)\rbrace$.
+    \item Use the method of moments to determine the uncorrected observables $\lbrace \est{S_k} \rbrace$, based on the detector
+        events $\lbrace x^{(k)}_d\rbrace$.
+    \item By virtue of \refeq{linear-assumption} and step 1, the $j$-th column of $M$ has been determined via
+        \begin{equation}
+            M_{ij} = \est{S_i}\,.
+        \end{equation}
+    \item Repeat the above steps for all values of $j$ to determine all columns of $M$.
+\end{enumerate}
+
+It remains to invert the relation \refeq{linear-assumption}, so that one can determine the unfolded
+angular observables $\lbrace \wwhat{S_k}\rbrace$ as
+\begin{equation}
+    \wwhat{S_i} = \left(M^{-1}\right)_{ij} \est{S_j}\,.
+\end{equation}
+
+We emphasize that this methods hinges on the assumption in \refeq{linear-assumption}, which might not be fulfilled in general.
+In particular, if detector effects are small, of it they can be reduced through other means, our approach is expected to work.
+The effects can be considered small if
+\begin{equation}
+    ||M - \mathbf{1}||_2 \ll N\,.
+\end{equation}
+Here $||\cdot||_2$ denotes the Frobenius norm.
+
+\danny{$@$Marcin: How well does this work? Is \refeq{linear-assumption} fulfilled in your cases?}
+
+\vspace{\bigskipamount}
+\hrule
+\danny{Should we remove the remainder of this section?}
 \fred{Comment that in this section $\vec\nu$ and $\vec\theta$ are used after ``correction'' has been applied.}
-\danny{Rethink order of this section.}
 Thanks to accurate detector simulations and control studies, the experimental analyses have become
@@
 We provide the matrix $N$ in \reftab{eff-corrected-est-btokstarll}.\\
-
-\paragraph{Recipe to determine the acceptance effects}
-
-The determination of detector acceptance is generally a difficult task. Here, we will show a systematic
-method to its effects.\\
-
-As previous, we use a PDF $P$ decomposed into $N$ angular observables $S_k$. We denote the estimator of the observable
-$S_k$ as $\est{S_k}$, which is affected by the detector acceptance. We assume now that the acceptance-corrected estimator
-$\wwhat{S_k}$ is a linear combination of the uncorrected estimators $\lbrace \est{S_k}\rbrace$,
-\begin{equation}
-    \label{eq:linear-assumption}
-    \wwhat{S_k} = \sum_j M_{kj} \est{S}_j\,.
-\end{equation}
-The coefficients $M_{kj}$ can now be systematically determined from MC studies of the detector geometry.
-\begin{enumerate}
-    \item In step $i$, let $S_i = 1$, and $S_{k\neq i} = 0$.
-    \item Simulate events from the PDF, and adjust each event based on the detector geometry. This allows
-        to compute $\est{S_j^{(i)}}$ from the simulation.
-    \item Solve the system of linear equations
-        \begin{equation}
-        \begin{aligned}
-            1 & = \sum_j M_{ij}^{(i)} \est{S_j^{(i)}}\,,\\
-            0 & = \sum_j M_{kj}^{(i)} \est{S_j^{(i)}}\,,\qquad\forall k \neq i\,.
-        \end{aligned}
-        \end{equation}
-        This allows the dermination of those coefficients $M_{kj}^{(i)}$ for which $\est{S_j^{(i)}} \neq 0$.
-    \item If $i < N$ advance $i$ by one and go to step 1
-\end{enumerate}
-We can now check if the assumption \refeq{linear-assumption} is valid, by checking that
-$M_{kj}^{(i)} = M_{kj}^{(i')}$ for all $i$, $i'$.
+\hrule
 

### 2014-07-17 draft.tex
Add par. and comments to detector effects

@@
 
-The determination of detector acceptance is generally a difficult task. Here, we will show a systematic
-method to estimate its effects based on both the method of moments, and MC simulations of the detector.\\
+The determination of detector acceptance is generally a difficult
+task. Here, we will show a systematic method to estimate its effects
+based on both the method of moments, and MC simulations of the
+detector.
 
-As previous, we use a PDF $P$ decomposed into $N$ angular observables $\lbrace S_k\rbrace$,
+\fred{In the ideal case, one would have an explicit probabilistic
+  model of the detector acceptance effects and could thus write down
+  the full forward model of the measured events arise. In practice,
+  this would require much more CPU time than available, and one is
+  therefore forced to simplify the model. The standard approach is to
+  generate \emph{true} particle events $\lbrace x_t^{(k)}\rbrace =
+  \lbrace(\vec{\nu}^{(k)}_t,\vec\theta^{(k)}_t)\rbrace$ from a PDF
+  assumed to describe the bare physical process, and to propagate
+  those particles through a detailed simulation of the detector. The
+  observable traces that the particles leave in the detector are fed
+  into reconstruction algorithms resulting in the \emph{detector}
+  events $\lbrace x^{(k)}_d\rbrace = \lbrace(\vec{\nu}^{(k)}_d,
+  \vec\theta^{(k)}_d)\rbrace$.
+
+[Where does the reconstruction uncertainty enter? Below we just
+  account for systematic shifts but our estimate of the uncertainty of
+  one $S_k$ would be only the statistical uncertainty from the finite
+  sample size. How about the extra correlation between different $S_k$
+  that is induced?] }\\
+
+As before, we assume a PDF $P$ can be decomposed into $N$ parts with angular observables $\lbrace S_k\rbrace$,
 \begin{equation}
@@
 between the true angular observables $\lbrace S_k^\text{true}\rbrace$, and the estimators $\lbrace \est{S_k}\rbrace$,
+\fred{Do we need $S_k^\text{true}$? Isn't it just $S_k$?}
 \begin{equation}
@@
         \end{equation}
+        \fred{I wonder if a small sample size also leads to artificial
+          nonzero off-diagonal elements of $M$}
     \item Repeat the above steps for all values of $j$ to determine all columns of $M$.

### 2014-07-17 draft.tex
Update to Sec. III

@@
 between the true angular observables $\lbrace S_k^\text{true}\rbrace$, and the estimators $\lbrace \est{S_k}\rbrace$,
-\fred{Do we need $S_k^\text{true}$? Isn't it just $S_k$?}
 \begin{equation}
@@
 \end{equation}
+This assumption is based on a smooth angular acceptance function. While this will not be true for the laboratory frame,
+smoothness may be recovered in boosted frame, e.g. the rest frame of the decaying particle.
 In that case, the matrix $M_{ij}$ can be fully determined through the following steps.
@@
 
-We emphasize that this methods hinges on the assumption in \refeq{linear-assumption}, which might not be fulfilled in general.
-In particular, if detector effects are small, of it they can be reduced through other means, our approach is expected to work.
-The effects can be considered small if
+We emphasize that this methods hinges on the assumption in \refeq{linear-assumption}, We thus suggest to explicitly
+test the assumption. One way of testing involves repeating the previous procedure
+with $S_j^\text{true} = 1/x$. If the lineary assumption holds, one should find
 \begin{equation}
-    ||M - \mathbf{1}||_2 \ll N\,.
+    M_{ij} = x \est{S_i}\,,
 \end{equation}
-Here $||\cdot||_2$ denotes the Frobenius norm.
-
-\danny{$@$Marcin: How well does this work? Is \refeq{linear-assumption} fulfilled in your cases?}
-
-\vspace{\bigskipamount}
-\hrule
-\danny{Should we remove the remainder of this section?}
-\fred{Comment that in this section $\vec\nu$ and $\vec\theta$ are used after ``correction'' has been applied.}
-Thanks to accurate detector simulations and control studies, the experimental analyses have become
-remarkably good at removing detector acceptance effects. In this section we therefore assume that
-there are only a small, residual acceptance effects left that affect the events. In particular, we
-assume that the latter can be modeled as a modified probability density,
-\begin{equation}
-    \label{eq:PDFwithDE}
-    P(\nuvec,\thvec) \to P(\nuvec,\thvec) \times \Omega(\thvec),
-\end{equation}
-where $\Omega$ is independent of the non-angular kinematics $\nuvec$. The latter assumption is only
-is invalid in general. However, if residual angular acceptance only weakly depends on $\vec{\nu}$, one
-can always choose appropriate bin $\vec{\nu}$ so that $\Omega$ is approximately constant with respect
-to $\vec{\nu}$. For such a case we parametrize
-\begin{equation}
-    \Omega_{m,l}(\thvec) = \prod_{i=1}^{m} \Big[1 + \sum_{j=1}^l \eps_i^{(j)} p_j(\cos\theta_i)\big]
-\end{equation}
-where $p_j(\cos\theta_i)$ denotes the $j$th Legendre polynomial. Since we only consider residual
-acceptance effects, we expect $\eps_i^{(j)} \ll 1$. \footnote{\danny{what are reasonable values/upper limits on the $\eps$?}}\\
-
-We are aware that setting a bin width that fulfills the aforementioned criterion can be at odds with
-other requirements. For instance, in exclusive $b\to s\ell^+\ell^-$ decays, the bin width for
-$\vec{\nu} = q^2$ needs to cover a sufficiently large part of the phase space beyond the open charm
-threshold. We emphasize that the outcome of an analysis as proposed here can easily combine several
-bins by means of a weighted average.\\
-
-\paragraph{Uniangular Distribution}
-For definiteness and clarity, we consider first an uni-angular distribution $P(\theta)$.
-In this case we can parametrize the PDF $P$ as
-\begin{equation}
-    P(\theta) = S_1 + S_2 \cos\theta + S_2 \cos^2\theta\,,
-\end{equation}
-which is a parametrization that has been used in the literature for $\bar{B}\to\bar{K}\ell^+\ell^-$ decays \cite{Bobeth:2007dw}.
-While this system of angular functions is not orthonormal, it can easily be orthonormalized. For the basis of angular
-functions, see \refapp{btokll}.
-Considering detector acceptance effects up to second order in $\cos\theta$, the function $\Omega(\vec\theta)$ reads
-\begin{equation}
-    \Omega_{1,2}(\theta_1) = 1 + \eps_{1}^{(1)} \cos\theta + \frac{\eps_{1}^{(2)}}{2}\big(3 \cos^2\theta - 1\big)\qquad\eps_{1}^{(i)} = \order{\eps}\,.
-\end{equation}
-Inclusion of $\Omega_{1,2}$ as part of the PDF as proposed in \refeq{PDFwithDE} modifies the MC estimators for the angular observables.
-We find
-\begin{equation}
-\begin{aligned}
-    \wwhat{S_1} & = \Big(1 + \frac{\eps_{1}^{(2)}}{2}\Big) \est{S_1} + \frac{9 \eps_{1}^{(2)}}{70} \est{S_3}\\
-    \wwhat{S_2} & = \Big(1 - \frac{2 \eps_{1}^{(2)}}{5}\Big) \est{S_2} - \eps_{1}^{(1)} \est{S_1} - \frac{3\eps_{1}^{(1)}}{5} \est{P_3}\\
-    \wwhat{S_3} & = \Big(1 - \frac{11\eps_{1}^{(2)}}{14}\Big)\est{S_3} - \frac{3\eps_{1}^{(2)}}{2} \est{S_1} - \eps_{1}^{(1)} \est{P_2}\,.
-\end{aligned}
-\end{equation}
-Here $\lbrace \est{S_i}\rbrace$ are the uncorrected estimators, while $\lbrace \wwhat{S_i}\rbrace$ denote the
-acceptance-corrected estimators of the angular observables.\\
-
-\paragraph{Triangular Distribution}
-
-\begin{table*}
-    \resizebox{.99\textwidth}{!}{\ensuremath{\input{tab-btokstarll-1to6.tex}}}\\[2.5\medskipamount]
-    \resizebox{.99\textwidth}{!}{\ensuremath{\input{tab-btokstarll-7to12.tex}}}\\[2.5\medskipamount]
-    \resizebox{.99\textwidth}{!}{\ensuremath{\input{tab-btokstarll-13to18.tex}}}
-    \caption{The matrix $N_{ij}$ that appears in \refeq{eff-corrected-est-btokstarll}. Due to spatial
-        constraints, we split its display into columns $j=1s,1c,1i,2s,2c,2i$ (top),
-        $j=3,4,4i,5,5i,6s$ (middle) and $j=6c,7,7i,8,8i,9$ (bottom).
-        \label{tab:eff-corrected-est-btokstarll}
-    }
-\end{table*}
-
-As an example for a triangular distribution we use the decay $\bar{B}\to\bar{K}^*(\to \bar{K}\pi)\ell^+\ell^-$.
-A parametrization of its angular distribution can be found in \refapp{btokstarll}.\\
-
-For this type of distribution, we expand $\Omega_3$ to linear order in $\eps$,
-\begin{equation}
-    \Omega_{3,2}(\theta_1,\theta_2,\theta_3) = 1 + \sum_{i=1}^3 \sum_{j=1}^2 \eps_i^{(j)} p_j(\cos\theta_i) + \order{\eps^2}\,.
-\end{equation}
-This leads to a matrix-valued equation that relates the effiency-corrected estimators $\wwhat{S}_i$ to the uncorrected
-estimators $\est{S}_j$,
-\begin{equation}
-    \label{eq:eff-corrected-est-btokstarll}
-    \wwhat{S}_i = \sum_{j=1\text{s},\dots\,9} \big(\delta_{ij} + N_{ij}\big) \est{S}_j\,.
-\end{equation}
-We provide the matrix $N$ in \reftab{eff-corrected-est-btokstarll}.\\
-\hrule
+for arbitrary values of $x > 1$.
 

### 2014-07-17 draft.tex
Remove App. F

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
-
-\section{Systematic way for determining the acceptance matrix for }
-
-In this section we will give a systematic description on how to obtain unfolding matrix based on MC sample.
-We start by generating so called flat phase space.
-In this MC all simulated angular distributions of $\cos \theta_l$, $\cos \theta_k$ and $\phi$ are flat.
-Assuming the massless limit, and not scalars the PDF has only 9 parameters: $F_l$, and $S_{3,4,5,6s,7,8,9}$:
-\begin{multline}
-\dfrac{d^4\Gamma}{ \Gamma dq^2 dcos\theta_k dcos\theta_l d\phi}=\dfrac{9}{32\pi}( \dfrac{3}{4} (1-F_l) \sin^2 \theta_k + F_l\cos^2 \theta_k + ( \dfrac{1}{4}(1-Fl)\sin^2 \theta_k \\ -  F_l\cos^2) cos 2\theta_l  + S_3 \sin^2 \theta_k \sin^2 \theta_l \cos2\phi + S_4 \sin2 \theta_k \sin \theta_l \cos\phi +\\ S_5 \sin2 \theta_k \sin \theta_l \cos \phi +  (S_{6s} \sin^2 \theta_k) \cos \theta_l + \\ S_7 \sin 2\theta_k \sin \theta_l \sin \phi +  S_8 \sin 2 \theta_k \sin 2 \theta_l \sin phi + S_9 sin^2 \theta_k \sin^2 \theta_l \sin 2 \phi)
-\label{PDF}
-\end{multline}
-From theory it is easy to compute that only Fl will have a non zero moment equal to $\dfrac{2}{3}$.
-Next we apply the detector simulation and selection as done on real data.
-Then we can measure again all 9 moments which we put in a vector $\overrightarrow{v}$.
-The first column of an unfolding matrix $M_{unfold}$ will be then equal to $\dfrac{3}{2} \overrightarrow{v}$.
-Next we can weight selected events accordingly to $f_{s_3}$.
-From theory one can calculate that only moment corresponding to $S_3$ will be non zero and equal to $\dfrac{32}{225} S3$.
-Measuring the moments on weighted events and punting them in a vector: $\overrightarrow{v_2}$ leads to second column of unfolding matrix equal the $\dfrac{225}{32} \overrightarrow{v_2}$.
-Repeating this procedure for all moments will lead to full determination of the unfolding matrix.
-We provide reader the explicit calculation of the normalization factors for the moments vectors:
-\begin{equation}
-\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{S_{3,4,8,9}}*f_{S_{3,4,8,9}}= \dfrac{32}{225} ,
-\end{equation}
-
-\begin{equation}
-\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{S_{5,6,7}}*f_{S_{5,6,7}}= \dfrac{8}{45} ,
-\end{equation}
-\begin{equation}
-\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{F_l}= \dfrac{2}{3}
-\end{equation}
-
 \bibliography{references}

### 2014-07-18 draft.tex
[app. B] remarking while checking the calculation

@@
 
-The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
-for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
+The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and
+including P-wave contributions -- has been calculated for the most
+general basis of dimension-six $b\to s$ operators. \fred{In
+  \cite{Bobeth:2012vn} below (A.1), it says that the S wave is assumed
+  to be removed.} It reads, expressed in terms of the angular
+observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
 \begin{equation}
@@
 \end{equation}
-where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
+where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$\fred{In \cite{Bobeth:2012vn} it is called $\theta_{K}$} is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
 The $q^2$-differential decay width reads
@@
 \end{equation}
-The angular functions read \cite{Blake:2012mb,Bobeth:2012vn}
+The angular functions read \cite{Blake:2012mb,Bobeth:2012vn} \fred{I can't find $f_{1i}$ in either paper}
 \begin{equation}
@@
 \end{equation}
-as well as
+as well as \fred{Now it is $\hat{f}_{1sc}$ instead of $\hat{f}_{1i}$}
 \begin{equation}

### 2014-07-20 draft.tex
App. B: theta_1 <-> theta_2, and address Freds comments

--- 2014-07-17 draft.tex
@@
 \begin{equation}
-    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{J_{i}(q^2)}{\dd\Gamma/\dd q^2} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
+    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \theta_3} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\dd\Gamma/\dd q^2} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
 \end{equation}
-where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
+where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
 The $q^2$-differential decay width reads
@@
 \end{equation}
-The angular functions read \cite{Blake:2012mb,Bobeth:2012vn}
+The angular functions\footnote{%
+    We consistently use the label "$i$" to denote angular function and observables that arise
+    from interference between S-wave and P-wave amplitudes. Our convention is related to the convention
+    of \cite{Bobeth:2012vn} through $f_{1i} \leftrightarrow f_{1sc}$, $f_{2i} \leftrightarrow f_{2sc}$.
+} read \cite{Blake:2012mb,Bobeth:2012vn}
 \begin{equation}
@@
     f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
-    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\phi &
-    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\phi\\
-    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\phi & & &
-    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\phi\\
-    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\phi & & &
-    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\phi\\
+    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\theta_3 &
+    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
+    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 & & &
+    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\theta_3\\
+    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\theta_3 & & &
+    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\theta_3\\
     f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
     f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
-    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\phi & & &
-    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\phi\\
-    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\phi & & &
-    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\phi\,.
+    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\theta_3 & & &
+    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\theta_3\\
+    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\theta_3 & & &
+    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\,.
 \end{aligned}
@@
 \begin{equation}
-    P(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
+    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
 \end{equation}
-where we also define $S_i(q^2) = J_i(q^2) / (\dd\Gamma/\dd q^2)$.\\
+where we also define $S_k(q^2) \equiv J_k(q^2) / (\dd\Gamma/\dd q^2)$.\\
 
@@
 \begin{aligned}
-    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_1 - 42 \cos^2\theta_1\big) + \big(  45 \sin^2\theta_1 - 30 \cos^2\theta_1\big)\cos 2\theta_2}{64} \,,\\
-    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_1 + 84 \cos^2\theta_1\big) + \big( -15 \sin^2\theta_1 + 60 \cos^2\theta_1\big)\cos 2\theta_2}{32} \,,\\
-    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_1 - 30 \cos^2\theta_1\big) + \big(+135 \sin^2\theta_1 - 90 \cos^2\theta_1\big)\cos 2\theta_2}{64} \,,\\
-    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_1 + 60 \cos^2\theta_1\big) + \big( -45 \sin^2\theta_1 +180 \cos^2\theta_1\big)\cos 2\theta_2}{32} \,,
+    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_2 - 42 \cos^2\theta_2\big) + \big(  45 \sin^2\theta_2 - 30 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
+    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_2 + 84 \cos^2\theta_2\big) + \big( -15 \sin^2\theta_2 + 60 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,\\
+    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_2 - 30 \cos^2\theta_2\big) + \big(+135 \sin^2\theta_2 - 90 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
+    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_2 + 60 \cos^2\theta_2\big) + \big( -45 \sin^2\theta_2 +180 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,
 \end{aligned}
@@
 \begin{aligned}
-    \hat{f}_{1sc}& = \frac{\big(21 + 15 \cos2\theta_2\big)\cos\theta_1}{16}               \,,&
-    \hat{f}_{2sc}& = \frac{\big(15 + 45 \cos2\theta_2\big)\cos\theta_1}{16}               \,,\\
-    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_1 -  6 \cos^2\theta_1\big)\cos\theta_2}{4} \,,&
-    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_1 + 12 \cos^2\theta_1\big)\cos\theta_2}{2} \,,\\
-    \hat{f}_{3}  & = \frac{75 \sin^2\theta_1 \sin^2\theta_2 \cos2\phi}{32}                \,,&
-    \hat{f}_{9}  & = \frac{75 \sin^2\theta_1 \sin^2\theta_2 \sin2\phi}{32}                \,,\\
-    \hat{f}_{4}  & = \frac{75 \sin 2\theta_1 \sin 2\theta_2 \cos \phi}{32}                \,,&
-    \hat{f}_{4i} & = \frac{15 \sin  \theta_1 \sin 2\theta_2 \cos \phi}{8}                 \,,\\
-    \hat{f}_{5}  & = \frac{15 \sin 2\theta_1 \sin  \theta_2 \cos \phi}{8}                 \,,&
-    \hat{f}_{5i} & = \frac{3  \sin  \theta_1 \sin  \theta_2 \cos \phi}{2}                 \,,\\
-    \hat{f}_{7}  & = \frac{15 \sin 2\theta_1 \sin  \theta_2 \sin \phi}{8}                 \,,&
-    \hat{f}_{7i} & = \frac{3  \sin  \theta_1 \sin  \theta_2 \sin \phi}{2}                 \,,\\
-    \hat{f}_{8}  & = \frac{75 \sin 2\theta_1 \sin 2\theta_2 \sin \phi}{32}                \,,&
-    \hat{f}_{8i} & = \frac{15 \sin  \theta_1 \sin 2\theta_2 \sin \phi}{8}                 \,.
+    \hat{f}_{1i} & = \frac{\big(21 + 15 \cos1\theta_2\big)\cos\theta_2}{16}               \,,&
+    \hat{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
+    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
+    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
+    \hat{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,&
+    \hat{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,,\\
+    \hat{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
+    \hat{f}_{4i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \cos \theta_3}{8}                 \,,\\
+    \hat{f}_{5}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \cos \theta_3}{8}                 \,,&
+    \hat{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
+    \hat{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
+    \hat{f}_{7i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \sin \theta_3}{2}                 \,,\\
+    \hat{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
+    \hat{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,.
 \end{aligned}
@@
 \begin{equation}
-    \int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) P(q^2, \theta_1,\theta_2,\phi) = S_i(q^2)\,.
+    \int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \theta_3 \hat{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
 \end{equation}

### 2014-07-20 draft.tex
Fix some typoes in App. E, add a few remarks

@@
 %% Shortcuts %%
-\newcommand{\dd}{\text{d}}
+\newcommand{\dd}{\text{d}\!}
 \newcommand{\refapp}[1]{app.~(\ref{app:#1})}
@@
 
-Let $P \equiv P(\vec{\nu},\theta)$ be an observable of only one angle $\theta$ and further non-angular variables $\vec{\nu}$. Further, let
-$P$ have an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots \hat{=} S,P,D,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
+Let $S \equiv S(\vec{\nu},\theta)$ be an observable of only one angle $\theta$ and further non-angular variables $\vec{\nu}$. Further, let
+$S$ have an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D of the underlying amplitudes $A_1$ and $A_2$,
 \begin{equation}
     \label{eq:def-partial-wave-observable}
-    P(\theta) \equiv F\big(A_1(\theta) A_2^*(\theta)\big) \equiv \left(\sum_{l_1=0}^\infty A_1^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta)\right) \left(\sum_{l_2=0}^\infty A_1^{(l_2)} p_{l_2}^{(m_2)}(\cos\theta)\right)\,,\qquad F=\Re{},\Im{}\,.
+    S(\theta) \equiv F\left[A_1(\theta) A_2^*(\theta)\right] \equiv F\left[\left(\sum_{l_1=0}^\infty A_1^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta)\right) \left(\sum_{l_2=0}^\infty A_2^{*(l_2)} p_{l_2}^{(m_2)}(\cos\theta)\right)\right]\,,
 \end{equation}
+where $F = \text{Re},\text{Im}$ denotes taking either the real or the imaginary part.
 Here $m_1$ and $m_2$ denote the third component of the angular momentum of the respective amplitude $A_1$ or $A_2$, and we impose $m_1 \geq m_2$.\\
@@
 Will will show in the following that such a cut off
-is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$.
-Since this expansion implies a well-defined total angular momentum for each observables, one ensures that the observables can in fact be disentangled experimentally.\\
+is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$. Since this expansion implies
+a well-defined total angular momentum for each observable, one ensures that the observables can in fact be disentangled experimentally.\\
 
-We propose the decomposition of $P$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with total angular momentum $j$ and its third component $m=m_1 + m_2$.
+We propose the decomposition of $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with total angular momentum $j$ and its third component $m=m_1 + m_2$.
 \begin{equation}
-    P(\vec{\nu}, \theta) = \sum_j P_{j,m}(\vec{\nu}) p_{j}^{(m)}(\cos\theta)\,.
+    S(\vec{\nu}, \theta) = \sum_j S_{j,m}(\vec{\nu}) p_{j}^{(m)}(\cos\theta)\,.
 \end{equation}
-This parametrization has two merits. First, we can immediately project out the angular observables $P_{j,m}$ by means of \refeq{legendre-scalar-product}:
+This parametrization has two merits. First, we can immediately project out the angular observables $S_{j,m}$ by means of \refeq{legendre-scalar-product}:
 \begin{equation}
-    P_{j,m}(\vec{\nu}) = \frac{1}{n_{j,m}} \int_{-1}^{+1} P(\vec{\nu},\cos \theta) p_{j}^{(m)}(\cos\theta) \dd\cos\theta\,.
+    S_{j,m}(\vec{\nu}) = \frac{1}{n_{j,m}} \int_{-1}^{+1} S(\vec{\nu},\cos \theta) p_{j}^{(m)}(\cos\theta)\,\dd\cos\theta\,.
 \end{equation}
-Second, we can immediately express $P_{j,m}(\vec{\nu})$ in terms of the partial-wave amplitudes,
+Second, we can immediately express $S_{j,m}(\vec{\nu})$ in terms of the partial-wave amplitudes,
 \begin{equation}
@@
     \begin{aligned}
-        P_{j,m}(\vec{\nu})
-            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left(A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) \big(A_{2}^{(l_2)}\big)^*\right) p_{l_2}^{(m_2)}(\cos\theta)\\
-            & = \sum_{l_1,l_2=0}^\infty F\left(A_{1}^{l_1} \big(A_{2}^{(l_2)}\big)^*\right) \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
+        S_{j,m}(\vec{\nu})
+            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) A_{2}^{*(l_2)}p_{l_2}^{(m_2)}(\cos\theta)\right]\\
+            & = \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} A_{2}^{*(l_2)}\right] \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
     \end{aligned}
@@
     T_{l_1,l_2,j}^{(m_1,m_2)}
-        & = \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) p_{l_1}^{(m_1)}(\cos\theta) p_{l_2}^{(m_2)}(\cos\theta) \dd\cos\theta\\
+        & = \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) p_{l_1}^{(m_1)}(\cos\theta) p_{l_2}^{(m_2)}(\cos\theta)\,\dd\cos\theta\\
         & = (-1)^{s - l_1 - m_2} \frac{2 (l_1 + m_1)! (l_2 + m_2)! (2s - 2 l_2)! s!}{(l_1 - m_1)! (s - j)! (s - l_1)! (s - l_2)! (2s + 1)!}\\
@@
 For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
+We close by remarking that for any angular momentum cut-off $\ell < L$, one can find an upper limit for the squared sum
+of all remaining partial waves through the inclusive decay; i.e. schematically
+\begin{equation}
+    \sum_{i=1}^2 \sum_{l=L}^\infty |A_i^{(l)}|^2 \leq \frac{\dd^{1 + \dim\vec\nu} \Gamma_\text{incl}}{\dd \cos\theta\, \dd\,\vec\nu}\,.
+\end{equation}
 

### 2014-07-24 draft.tex
Add sketch of decay topology for section III.A
[notation, appendix] Check and comment on appendices C-E, change symbol of differential

@@
 %% Shortcuts %%
-\newcommand{\dd}{\text{d}\!}
+\newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
 \newcommand{\refapp}[1]{app.~(\ref{app:#1})}
@@
     \label{eq:def-ortho-rel}
-    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^N \theta = \delta_{ij}\,,
+    \int_\Omega \rmdx{^N \theta} f_i(\thvec) f_j(\thvec)  = \delta_{ij}\,,
 \end{equation}
@@
     \label{eq:def-P-decay}
-    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\dd^{N+M}\Gamma}{\dd \nu_1 \dots \dd \nu_M\, \dd \theta_1 \dots \theta_N}\,,
+    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\rmdx{^{N+M}\Gamma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
 \end{align}
@@
     \label{eq:def-P-scattering}
-    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\dd^{N+M}\sigma}{\dd \nu_1 \dots \dd \nu_M\, \dd \theta_1 \dots \theta_N}\,,
+    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\rmdx{^{N+M}\sigma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
 \end{align}
@@
     \label{eq:det-Pi-analytical}
-    S_i(\nuvec) = \int_{\Omega} \hat{f}_i(\thvec) P(\nuvec, \thvec) \dd^N \theta\,.
+    S_i(\nuvec) = \int_{\Omega} \rmdx{^N \theta} \hat{f}_i(\thvec) P(\nuvec, \thvec)\,.
 \end{equation}
@@
     \langle S_i\rangle
-    \equiv \int S_i(\nuvec) \dd^M \nu
-    = \int \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\,.
+    \equiv \int \rmdx{^M \nu} S_i(\nuvec)
+    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta}\hat{f}_i(\thvec) P(\nuvec,\thvec) \right].
 \end{equation}
@@
 \begin{equation}
-    E_P[g] \equiv \int g(x) P(x) \dd x
+    E_P[g] \equiv \int \rmdx{x} g(x) P(x)
 \end{equation}
@@
     \langle S_i\rangle_{\vec{a},\vec{b}}
-    & = \int_{\vec{a}}^{\vec{b}} S_i(\nuvec) \dd^M \nu\\
-    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\\
-    & = \int \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec)
+    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
+    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)  \right]\\
+    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)
         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
-        \dd^N\theta\right]\dd^M \nu\,,
+        \right],
 \end{align}
@@
 
-\fred{Paragraph is very specific to one physics case. Needs a drawing}
+\begin{figure}
+    \includegraphics[width=.6\textwidth]{fig-topology.pdf}
+    \caption{Decay topology for decays $B\to P_1 P_2 \ell_1 \bar\ell_2$. \label{fig:topology}}
+\end{figure}
 
@@
 \begin{equation}
-    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
+    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1}} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
 \end{equation}
@@
 \begin{equation}
-    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
+    \int_0^\pi \rmdx{\theta_1} \hat{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
 \end{equation}
@@
 
-The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
+The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ --- up to and including P-wave contributions --- has been calculated
 for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
 \begin{equation}
-    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \theta_3} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\dd\Gamma/\dd q^2} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
+    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
 \end{equation}
@@
 \begin{equation}
-    \frac{\dd\Gamma}{\dd q^2} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
+    \frac{\rmdx{\Gamma}}{\rmdx{q^2}} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
 \end{equation}
@@
     f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\theta_3 &
-    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
-    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 & & &
+    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 &
     f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\theta_3\\
@@
     f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\theta_3 & & &
-    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\,.
+    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\\
+    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
 \end{aligned}
@@
 \end{equation}
-where we also define $S_k(q^2) \equiv J_k(q^2) / (\dd\Gamma/\dd q^2)$.\\
+where we also define $S_k(q^2) \equiv J_k(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\
 
@@
     \hat{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
-    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
-    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
-    \hat{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,&
-    \hat{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,,\\
+    \hat{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,& &\\
     \hat{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
@@
     \hat{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
+    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
+    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
     \hat{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
@@
     \hat{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
-    \hat{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,.
+    \hat{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,,\\
+    \hat{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,.\\
 \end{aligned}
@@
 \begin{equation}
-    \int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \theta_3 \hat{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
+    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} \hat{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
 \end{equation}
@@
 
-The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays, where $P,P_1$, and $P_2$ are pseudoscalar mesons,
+The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays \fred{title has $\bar{B}$ instead of $P$}, where $P,P_1$, and $P_2$ are pseudoscalar mesons,
 and $\ell_1$ and $\bar\ell_2$ are charged or neutral leptons, includes decays
 such as $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$.
-Their PDFs can generally be written as \cite{Lee:1992ih}
+Their decay PDFs can generally be written as \cite{Lee:1992ih}
 \begin{equation}
-    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\langle \Gamma\rangle}\frac{\dd^5 \Gamma}{\dd q^2\,\dd k^2\, \dd\cos\theta_1\,\dd\cos\theta_2\,\dd\phi} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
+    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\langle \Gamma\rangle}\frac{\rmdx{^5 \Gamma}}{\rmdx{q^2} \rmdx{k^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
 \end{equation}
-where
+\fred{rather use index $k$ as in previous appendix} where
 \begin{equation}
@@
     f_2 & = \cos 2\theta_1\,, &
+    f_3 & = \sin^2\theta_1 \cos 2\phi\,,\\
+    f_4 & = \sin 2\theta_1 \cos  \phi\,,&
+    f_5 & = \sin  \theta_1 \cos  \phi\,,&
     f_6 & = \cos  \theta_1\,, \\
-    f_3 & = \sin^2\theta_1 \cos 2\phi\,,&
-    f_4 & = \sin 2\theta_1 \cos  \phi\,,&
-    f_5 & = \sin  \theta_1 \cos  \phi\,,\\
-    f_9 & = \sin^2\theta_1 \sin 2\phi\,.&
+    f_7 & = \sin  \theta_1 \sin  \phi\,,&
     f_8 & = \sin 2\theta_1 \sin  \phi\,,&
-    f_7 & = \sin  \theta_1 \sin  \phi\,,
+    f_9 & = \sin^2\theta_1 \sin 2\phi\,.\\
 \end{aligned}
@@
 the dimeson mass squared and the dimeson helicity angles are denoted as $k^2$ and $\theta_2$. The
-azimuthal angle is denoted as $\phi$. The total decay width is
+azimuthal angle is denoted as $\phi$. \fred{Danny changed $\phi$ to $\theta_3$ in previous appendix. Here, too?}
+The total decay width is \fred{integrand independent of $\theta_1$? I guess you want to integrate over $\theta_2$}
 \begin{equation}
-    \langle \Gamma\rangle = \int_0^\pi \dd\theta_1\,\dd q^2\,\dd k^2\,\sin\theta_2 \frac{3I_1(q^2, k^2, \cos\theta_2) - I_2(q^2, k^2, \cos\theta_2)}{3}\,.
+    \langle \Gamma\rangle = \int_0^\pi \rmdx{\theta_1} \rmdx{q^2} \rmdx{k^2} \sin\theta_2 \frac{3I_1(q^2, k^2, \cos\theta_2) - I_2(q^2, k^2, \cos\theta_2)}{3}\,.
 \end{equation}
@@
 \end{equation}
-where we also define $S_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / (\dd\Gamma/\dd q^2)$.\\
+where we also define $S_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.
+\fred{$\sin\theta_1$ missing after $f_i$? Why $\rmdx{\Gamma} /\, \rmdx{q^2}$ and not just $\Gamma$ in definition?}\\
 
@@
     \hat{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
-    \hat{f}_6 & = 3 \cos\theta_1                   \,, \\
-    \hat{f}_3 & = \frac{15}{4}                \cos 2\phi     \,, &
+    \hat{f}_3 & = \frac{15}{4}                \cos 2\phi     \,,\\
     \hat{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \phi     \,, &
-    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \phi     \,, \\
-    \hat{f}_9 & = \frac{15}{4}                \sin 2\phi     \,, &
+    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \phi     \,, &
+    \hat{f}_6 & = 3 \cos\theta_1                   \,,\\
+    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \phi     \,, &
     \hat{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \phi     \,, &
-    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \phi     \,.
+    \hat{f}_9 & = \frac{15}{4}                \sin 2\phi     \,.\\
 \end{aligned}
 \end{equation}
+\fred{$\hat{f}_3$ and $\hat{f}_9$ need factor $\frac{4}{5}$}
 such that
 \begin{equation}
-    \int_0^\pi \dd\theta_1 \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\phi) P(q^2, k^2, \theta_1,\theta_2,\phi) = S_i(q^2, k^2, \theta_2)\,.
+    \int_0^\pi \rmdx{\theta_1} \int_0^{2\pi} \rmdx{\phi} \hat{f}_i(\theta_1,\phi) P(q^2, k^2, \theta_1,\theta_2,\phi) = S_i(q^2, k^2, \theta_2)\,.
 \end{equation}
@@
 
-The physical PDF for the decay -- in the presence of Standard Model operator and their chirality flipped counter parts -- reads \cite{Boeer:2014xx}
+The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts -- reads \cite{Boeer:2014xx}
 \begin{equation}
-    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\dd \Gamma/\dd q^2} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
+    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
 \end{equation}
 where $q^2$ denotes the dilepton mass squared, $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
-helicity angles in the dilepton and $N\pi$ systems, respectively, and $\theta_3 = \phi$ denotes the azimuthal angle.
+helicity angles in the dilepton and
+$N\pi$ systems, respectively, and $\theta_3 = \phi$ \fred{Then use $\theta_3$ below and not $\phi$} denotes the azimuthal angle.
 The basis of angular functions reads \cite{Boeer:2014xx}
@@
 \begin{equation}
-    \frac{\dd \Gamma}{\dd q^2} = 2 K_{1ss} + K_{1cc}
+    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}
 \end{equation}
@@
 \end{equation}
-where we also define $S_i(q^2) = K_i(q^2) / (\dd\Gamma/\dd q^2)$.\\
+where we also define $S_i(q^2) = K_i(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\
 
@@
 \end{equation}
-such that
+such that \fred{Works out only if $\pi^3$ dropped everywhere, and $\hat f_{2cc} \to 2 \hat f_{2cc}$}
 \begin{equation}
-    \int_0^\pi \dd \theta_1 \int_0^\pi \dd \theta_2 \int_0^{2\pi} \dd \phi P(q^2, \theta_1, \theta_2, \phi) \hat{f}_i(\theta_1, \theta_2, \phi) = S_i(q^2)\,.
+    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\phi} P(q^2, \theta_1, \theta_2, \phi) \hat{f}_i(\theta_1, \theta_2, \phi) = S_i(q^2)\,.
 \end{equation}
 
-\section{On the Partial Wave Expansions of Angular Observables}
+\section{On the Partial-Wave Expansions of Angular Observables}
 \label{app:partial-waves}
@@
 Let $S \equiv S(\vec{\nu},\theta)$ be an observable of only one angle $\theta$ and further non-angular variables $\vec{\nu}$. Further, let
-$S$ have an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D of the underlying amplitudes $A_1$ and $A_2$,
+$S$ have an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
 \begin{equation}
@@
 \end{equation}
-where $F = \text{Re},\text{Im}$ denotes taking either the real or the imaginary part.
-Here $m_1$ and $m_2$ denote the third component of the angular momentum of the respective amplitude $A_1$ or $A_2$, and we impose $m_1 \geq m_2$.\\
+where $F \in \{\text{Re},\text{Im}\}$ denotes taking either the real
+or the imaginary part. \fred{Now $\nuvec$ gone}
+$p_{l}^{(m)}$ is an \emph{associated Legendre} polynomial and $m_i$ is the third component of the angular momentum of the amplitude $A_i$, and we impose $m_1 \geq m_2$.\\
 
-From positivity of the amplitudes one immediately finds
+From the positivity of amplitudes, one immediately finds
 \begin{equation}
-    \int \dd\cos\theta |A_i(\theta)|^2 = \sum_{l_i = 0}^\infty |A_i^{(l_i)}|^2 n_{l_i, m_i} < \infty\,,
+    \int \rmdx{\cos\theta}  \, |A_i(\theta)|^2 = \sum_{l_i = 0}^\infty |A_i^{(l_i)}|^2 n_{l_i, m_i} < \infty\,,
 \end{equation}
@@
     \label{eq:legendre-scalar-product}
-    n_{l, m} \delta_{l, l'} \equiv \int_{0}^\pi p_{l}^{(m)}(\cos\theta) p_{l'}^{(m)} (\cos\theta) \dd \cos\theta = \frac{2}{(2 l + 1)} \frac{(l + m)!}{(l - m)!} \delta_{l, l'}\,.
+    n_{l, m} \delta_{l, l'} \equiv \int_{-1}^1 \rmdx{\cos\theta} p_{l}^{(m)}(\cos\theta) p_{l'}^{(m)} (\cos\theta)  = \frac{2}{(2 l + 1)} \frac{(l + m)!}{(l - m)!} \delta_{l, l'}\,.
 \end{equation}
-Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial waves amplitudes must asymptotically fall off,
+Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial-wave amplitudes must asymptotically fall off as
 \begin{equation}
@@
 is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$. Since this expansion implies
-a well-defined total angular momentum for each observable, one ensures that the observables can in fact be disentangled experimentally.\\
+a well defined total angular momentum for each observable, one ensures that the observables can in fact be disentangled experimentally.\\
 
@@
 \begin{equation}
-    S_{j,m}(\vec{\nu}) = \frac{1}{n_{j,m}} \int_{-1}^{+1} S(\vec{\nu},\cos \theta) p_{j}^{(m)}(\cos\theta)\,\dd\cos\theta\,.
+    S_{j,m}(\vec{\nu}) = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} S(\vec{\nu},\cos \theta) p_{j}^{(m)}(\cos\theta)\,.
 \end{equation}
-Second, we can immediately express $S_{j,m}(\vec{\nu})$ in terms of the partial-wave amplitudes,
+Second, we can immediately express $S_{j,m}(\vec{\nu})$ in terms of
+the partial-wave amplitudes, \fred{We may exchage the integral and the
+  series because each element of the series is a product of
+  polynomials on the compact support [-1,1], and thus each integral is
+  absolutely convergent}
 \begin{equation}
@@
         S_{j,m}(\vec{\nu})
-            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) A_{2}^{*(l_2)}p_{l_2}^{(m_2)}(\cos\theta)\right]\\
+            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) A_{2}^{*(l_2)}p_{l_2}^{(m_2)}(\cos\theta)\right]\\
             & = \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} A_{2}^{*(l_2)}\right] \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
@@
     T_{l_1,l_2,j}^{(m_1,m_2)}
-        & = \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) p_{l_1}^{(m_1)}(\cos\theta) p_{l_2}^{(m_2)}(\cos\theta)\,\dd\cos\theta\\
+        & = \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) p_{l_1}^{(m_1)}(\cos\theta) p_{l_2}^{(m_2)}(\cos\theta)\\
         & = (-1)^{s - l_1 - m_2} \frac{2 (l_1 + m_1)! (l_2 + m_2)! (2s - 2 l_2)! s!}{(l_1 - m_1)! (s - j)! (s - l_1)! (s - l_2)! (2s + 1)!}\\
@@
 \end{equation}
-The necessary condition for $T \neq 0$ are
+The necessary conditions for $T \neq 0$ are
 \begin{equation}
@@
 of this and of \refeq{angular-momentum-addition}, the angular observables $P_{j,m}$
-consist of sums with infinite terms. It is then up to theoretical analyses to
+consist of sums with infinitely many terms. It is then up to theoretical analyses to
 estimate or calculate the impact of individual contributions, with or without the cut off $L$.
 For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
-We close by remarking that for any angular momentum cut-off $\ell < L$, one can find an upper limit for the squared sum
-of all remaining partial waves through the inclusive decay; i.e. schematically
+We close by remarking that for any angular-momentum cut off $\ell < L$\fred{Do you mean $L < \infty$? Don't use $\ell$ again}, one can find an upper limit for the squared sum
+of all remaining partial waves through the inclusive decay; i.e., schematically
 \begin{equation}
-    \sum_{i=1}^2 \sum_{l=L}^\infty |A_i^{(l)}|^2 \leq \frac{\dd^{1 + \dim\vec\nu} \Gamma_\text{incl}}{\dd \cos\theta\, \dd\,\vec\nu}\,.
+    \sum_{i=1}^2 \sum_{l=L}^\infty |A_i^{(l)}|^2 \leq \frac{\rmdx{^{1 + \dim\vec\nu}} \Gamma_\text{incl}}{\rmdx{\cos\theta} \rmdx{\vec\nu}}\,.
 \end{equation}

### 2014-07-24 draft.tex
Fix typo in the abstract

@@
 In this letter we study how to obtain a set of angular observables
-$\{P_i\}$ that arise in a generic multi-body process without the need
+$\{S_i\}$ that arise in a generic multi-body process without the need
 to carry out a likelihood fit of an angular distribution to the

### 2014-07-25 draft.tex
Fix issues in Apps. C and D found by Fred

@@
 
-The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays \fred{title has $\bar{B}$ instead of $P$}, where $P,P_1$, and $P_2$ are pseudoscalar mesons,
+The class of semileptonic $\bar{B}\to P_1 P_2 \ell_1\bar\ell_2$ decays, where $P_1$, and $P_2$ are pseudoscalar mesons,
 and $\ell_1$ and $\bar\ell_2$ are charged or neutral leptons, includes decays
@@
 \begin{equation}
-    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\langle \Gamma\rangle}\frac{\rmdx{^5 \Gamma}}{\rmdx{q^2} \rmdx{k^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
+    P(q^2, p^2, \cos\theta_1, \cos \theta_2, \theta_3) = \frac{1}{\langle \Gamma\rangle}\frac{\rmdx{^5 \Gamma}}{\rmdx{q^2} \rmdx{p^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_k(\cos\theta_1,\phi)\,,
 \end{equation}
-\fred{rather use index $k$ as in previous appendix} where
+where
 \begin{equation}
@@
 Here we denote dilepton mass squared and the dilepton helicity angle as $q^2$ and $\theta_1$, while
-the dimeson mass squared and the dimeson helicity angles are denoted as $k^2$ and $\theta_2$. The
-azimuthal angle is denoted as $\phi$. \fred{Danny changed $\phi$ to $\theta_3$ in previous appendix. Here, too?}
-The total decay width is \fred{integrand independent of $\theta_1$? I guess you want to integrate over $\theta_2$}
+the dimeson mass squared and the dimeson helicity angles are denoted as $p^2$ and $\theta_2$. The
+azimuthal angle is denoted as $\theta_3$.
+The total decay width is
 \begin{equation}
-    \langle \Gamma\rangle = \int_0^\pi \rmdx{\theta_1} \rmdx{q^2} \rmdx{k^2} \sin\theta_2 \frac{3I_1(q^2, k^2, \cos\theta_2) - I_2(q^2, k^2, \cos\theta_2)}{3}\,.
+    \langle \Gamma\rangle = \int_0^\pi \rmdx{\theta_2} \rmdx{q^2} \rmdx{p^2} \sin\theta_2 \frac{3I_1(q^2, p^2, \cos\theta_2) - I_2(q^2, p^2, \cos\theta_2)}{3}\,.
 \end{equation}
-As usual, we transform from a $\cos\theta_1$-dependence to a $\theta_1$-dependence.
+As previous, we transform from a $\cos\theta_2$-dependence to a $\theta_2$-dependence.
 \begin{equation}
 \begin{aligned}
-    P(q^2, k^2, \theta_1, \theta_2, \phi)
-    & = \frac{1}{4\pi} \sum_i \frac{I(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \phi) \sin\theta_1 \sin\theta_2\\
-    & \equiv \frac{1}{4\pi} \sum_i S_i(q^2, k^2, \theta_2) f_i(\theta_1, \phi)\,.
+    P(q^2, p^2, \theta_1, \theta_2, \theta_3)
+    & = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \theta_3) \sin\theta_1 \sin\theta_2\\
+    & \equiv \frac{1}{4\pi} \sum_k S_k(q^2, p^2, \theta_2) f_k(\theta_1, \theta_3) \sin\theta_1\,.
 \end{aligned}
 \end{equation}
-where we also define $S_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.
-\fred{$\sin\theta_1$ missing after $f_i$? Why $\rmdx{\Gamma} /\, \rmdx{q^2}$ and not just $\Gamma$ in definition?}\\
+where we also define $S_k(q^2, p^2, \theta_2) \equiv \sin\theta_2 I_k(q^2, p^2, \cos\theta_2) / \langle \Gamma\rangle$.\\
 
@@
     \hat{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
-    \hat{f}_3 & = \frac{15}{4}                \cos 2\phi     \,,\\
+    \hat{f}_3 & = \frac{15}{4} \sin^2\theta_1 \cos 2\phi     \,,\\
     \hat{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \phi     \,, &
@@
     \hat{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \phi     \,, &
-    \hat{f}_9 & = \frac{15}{4}                \sin 2\phi     \,.\\
+    \hat{f}_9 & = \frac{15}{4} \sin^2\theta_1 \sin 2\phi     \,.\\
 \end{aligned}
 \end{equation}
-\fred{$\hat{f}_3$ and $\hat{f}_9$ need factor $\frac{4}{5}$}
 such that
@@
 \begin{equation}
-    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
+    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
 \end{equation}
@@
 helicity angles in the dilepton and
-$N\pi$ systems, respectively, and $\theta_3 = \phi$ \fred{Then use $\theta_3$ below and not $\phi$} denotes the azimuthal angle.
+$N\pi$ systems, respectively, and $\theta_3 = \phi$ denotes the azimuthal angle.
 The basis of angular functions reads \cite{Boeer:2014xx}
@@
 % 3
-        f_{3sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\phi &
-        f_{3s}  & = \sin\theta_1              \sin\theta_2 \cos\phi \\
+        f_{3sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\theta_3 &
+        f_{3s}  & = \sin\theta_1              \sin\theta_2 \cos\theta_3 \\
 % 4
-        f_{4sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\phi &
-        f_{4s}  & = \sin\theta_1              \sin\theta_2 \sin\phi
+        f_{4sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\theta_3 &
+        f_{4s}  & = \sin\theta_1              \sin\theta_2 \sin\theta_3
     \end{aligned}
@@
 \begin{equation}
-    P_{\Lambda_b}(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
+    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \theta_3) \sin\theta_1 \sin\theta_2\,,
 \end{equation}
-where we also define $S_i(q^2) = K_i(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\
+where we also define $S_i(q^2) \equiv K_i(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\
 
@@
 % 1
-        \hat f_{1ss} & = \frac{\pi^3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) &
-        \hat f_{1cc} & = \frac{\pi^3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) &
-        \hat f_{1c}  & = \pi^3 \cos\theta_1\\
+        \hat f_{1ss} & = \frac{1}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) &
+        \hat f_{1cc} & = \frac{1}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) &
+        \hat f_{1c}  & = \cos\theta_1\\
 % 2
-        \hat f_{2ss} & = \frac{3\pi^3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) \cos\theta_2 &
-        \hat f_{2cc} & = \frac{3\pi^3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) \cos\theta_2 &
-        \hat f_{2c}  & = 3\pi^3 \cos\theta_1   \cos\theta_2 \\
+        \hat f_{2ss} & = \frac{3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) \cos\theta_2 &
+        \hat f_{2cc} & = \frac{3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) \cos\theta_2 &
+        \hat f_{2c}  & = 3 \cos\theta_1   \cos\theta_2 \\
 % 3
-        \hat f_{3sc} & = \frac{15\pi^3}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\phi &
-        \hat f_{3s}  & = \frac{3\pi^3}{2} \sin\theta_1              \sin\theta_2 \cos\phi \\
+        \hat f_{3sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\phi &
+        \hat f_{3s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \cos\phi \\
 % 4
-        \hat f_{4sc} & = \frac{15\pi^3}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\phi &
-        \hat f_{4s}  & = \frac{3\pi^3}{2} \sin\theta_1              \sin\theta_2 \sin\phi
+        \hat f_{4sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\phi &
+        \hat f_{4s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \sin\phi
     \end{aligned}
 \end{equation}
-such that \fred{Works out only if $\pi^3$ dropped everywhere, and $\hat f_{2cc} \to 2 \hat f_{2cc}$}
+such that
 \begin{equation}

### 2014-07-25 draft.tex
[appendix B-D] \phi -> \theta_3

@@
 \label{app:btokstarll}
-
 The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ --- up to and including P-wave contributions --- has been calculated
@@
 \begin{equation}
-    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
+    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \theta_3) \sin\theta_1 \sin\theta_2\,,
 \end{equation}
@@
 \begin{equation}
-    P(q^2, p^2, \cos\theta_1, \cos \theta_2, \theta_3) = \frac{1}{\langle \Gamma\rangle}\frac{\rmdx{^5 \Gamma}}{\rmdx{q^2} \rmdx{p^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_k(\cos\theta_1,\phi)\,,
+    P(q^2, p^2, \cos\theta_1, \cos \theta_2, \theta_3) = \frac{1}{\langle \Gamma\rangle}\frac{\rmdx{^5 \Gamma}}{\rmdx{q^2} \rmdx{p^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_k(\cos\theta_1,\theta_3)\,,
 \end{equation}
@@
     f_2 & = \cos 2\theta_1\,, &
-    f_3 & = \sin^2\theta_1 \cos 2\phi\,,\\
-    f_4 & = \sin 2\theta_1 \cos  \phi\,,&
-    f_5 & = \sin  \theta_1 \cos  \phi\,,&
+    f_3 & = \sin^2\theta_1 \cos 2\theta_3\,,\\
+    f_4 & = \sin 2\theta_1 \cos  \theta_3\,,&
+    f_5 & = \sin  \theta_1 \cos  \theta_3\,,&
     f_6 & = \cos  \theta_1\,, \\
-    f_7 & = \sin  \theta_1 \sin  \phi\,,&
-    f_8 & = \sin 2\theta_1 \sin  \phi\,,&
-    f_9 & = \sin^2\theta_1 \sin 2\phi\,.\\
+    f_7 & = \sin  \theta_1 \sin  \theta_3\,,&
+    f_8 & = \sin 2\theta_1 \sin  \theta_3\,,&
+    f_9 & = \sin^2\theta_1 \sin 2\theta_3\,.\\
 \end{aligned}
@@
     \hat{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
-    \hat{f}_3 & = \frac{15}{4} \sin^2\theta_1 \cos 2\phi     \,,\\
-    \hat{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \phi     \,, &
-    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \phi     \,, &
+    \hat{f}_3 & = \frac{15}{4} \sin^2\theta_1 \cos 2\theta_3     \,,\\
+    \hat{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \theta_3     \,, &
+    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \theta_3     \,, &
     \hat{f}_6 & = 3 \cos\theta_1                   \,,\\
-    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \phi     \,, &
-    \hat{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \phi     \,, &
-    \hat{f}_9 & = \frac{15}{4} \sin^2\theta_1 \sin 2\phi     \,.\\
+    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \theta_3     \,, &
+    \hat{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \theta_3     \,, &
+    \hat{f}_9 & = \frac{15}{4} \sin^2\theta_1 \sin 2\theta_3     \,.\\
 \end{aligned}
@@
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^{2\pi} \rmdx{\phi} \hat{f}_i(\theta_1,\phi) P(q^2, k^2, \theta_1,\theta_2,\phi) = S_i(q^2, k^2, \theta_2)\,.
+    \int_0^\pi \rmdx{\theta_1} \int_0^{2\pi} \rmdx{\theta_3} \hat{f}_i(\theta_1,\theta_3) P(q^2, k^2, \theta_1,\theta_2,\theta_3) = S_i(q^2, k^2, \theta_2)\,.
 \end{equation}
@@
 \begin{equation}
-    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
+    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
 \end{equation}
@@
 % 3
-        \hat f_{3sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\phi &
-        \hat f_{3s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \cos\phi \\
+        \hat f_{3sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\theta_3 &
+        \hat f_{3s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \cos\theta_3 \\
 % 4
-        \hat f_{4sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\phi &
-        \hat f_{4s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \sin\phi
+        \hat f_{4sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\theta_3 &
+        \hat f_{4s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \sin\theta_3
     \end{aligned}
@@
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\phi} P(q^2, \theta_1, \theta_2, \phi) \hat{f}_i(\theta_1, \theta_2, \phi) = S_i(q^2)\,.
+    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} P(q^2, \theta_1, \theta_2, \theta_3) \hat{f}_i(\theta_1, \theta_2, \theta_3) = S_i(q^2)\,.
 \end{equation}

### 2014-07-27 draft.tex
technical commit

--- 2014-07-24 draft.tex
@@
 %% Shortcuts %%
-\newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
+\newcommand{\dd}{\text{d}}
 \newcommand{\refapp}[1]{app.~(\ref{app:#1})}
@@
 In this letter we study how to obtain a set of angular observables
-$\{S_i\}$ that arise in a generic multi-body process without the need
+$\{P_i\}$ that arise in a generic multi-body process without the need
 to carry out a likelihood fit of an angular distribution to the
@@
     \label{eq:def-ortho-rel}
-    \int_\Omega \rmdx{^N \theta} f_i(\thvec) f_j(\thvec)  = \delta_{ij}\,,
+    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^N \theta = \delta_{ij}\,,
 \end{equation}
@@
     \label{eq:def-P-decay}
-    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\rmdx{^{N+M}\Gamma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
+    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\dd^{N+M}\Gamma}{\dd \nu_1 \dots \dd \nu_M\, \dd \theta_1 \dots \theta_N}\,,
 \end{align}
@@
     \label{eq:def-P-scattering}
-    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\rmdx{^{N+M}\sigma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
+    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\dd^{N+M}\sigma}{\dd \nu_1 \dots \dd \nu_M\, \dd \theta_1 \dots \theta_N}\,,
 \end{align}
@@
     \label{eq:det-Pi-analytical}
-    S_i(\nuvec) = \int_{\Omega} \rmdx{^N \theta} \hat{f}_i(\thvec) P(\nuvec, \thvec)\,.
+    S_i(\nuvec) = \int_{\Omega} \hat{f}_i(\thvec) P(\nuvec, \thvec) \dd^N \theta\,.
 \end{equation}
@@
     \langle S_i\rangle
-    \equiv \int \rmdx{^M \nu} S_i(\nuvec)
-    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta}\hat{f}_i(\thvec) P(\nuvec,\thvec) \right].
+    \equiv \int S_i(\nuvec) \dd^M \nu
+    = \int \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\,.
 \end{equation}
@@
 \begin{equation}
-    E_P[g] \equiv \int \rmdx{x} g(x) P(x)
+    E_P[g] \equiv \int g(x) P(x) \dd x
 \end{equation}
@@
     \langle S_i\rangle_{\vec{a},\vec{b}}
-    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
-    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)  \right]\\
-    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)
+    & = \int_{\vec{a}}^{\vec{b}} S_i(\nuvec) \dd^M \nu\\
+    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\\
+    & = \int \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec)
         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
-        \right],
+        \dd^N\theta\right]\dd^M \nu\,,
 \end{align}
@@
 
-\begin{figure}
-    \includegraphics[width=.6\textwidth]{fig-topology.pdf}
-    \caption{Decay topology for decays $B\to P_1 P_2 \ell_1 \bar\ell_2$. \label{fig:topology}}
-\end{figure}
+\fred{Paragraph is very specific to one physics case. Needs a drawing}
 
@@
 \end{equation}
-This assumption is based on a smooth angular acceptance function. While this will not be true for the laboratory frame,
-smoothness may be recovered in boosted frame, e.g. the rest frame of the decaying particle.
 In that case, the matrix $M_{ij}$ can be fully determined through the following steps.
@@
 
-We emphasize that this methods hinges on the assumption in \refeq{linear-assumption}, We thus suggest to explicitly
-test the assumption. One way of testing involves repeating the previous procedure
-with $S_j^\text{true} = 1/x$. If the lineary assumption holds, one should find
+We emphasize that this methods hinges on the assumption in \refeq{linear-assumption}, which might not be fulfilled in general.
+In particular, if detector effects are small, of it they can be reduced through other means, our approach is expected to work.
+The effects can be considered small if
 \begin{equation}
-    M_{ij} = x \est{S_i}\,,
+    ||M - \mathbf{1}||_2 \ll N\,.
 \end{equation}
-for arbitrary values of $x > 1$.
+Here $||\cdot||_2$ denotes the Frobenius norm.
+
+\danny{$@$Marcin: How well does this work? Is \refeq{linear-assumption} fulfilled in your cases?}
+
+\vspace{\bigskipamount}
+\hrule
+\danny{Should we remove the remainder of this section?}
+\fred{Comment that in this section $\vec\nu$ and $\vec\theta$ are used after ``correction'' has been applied.}
+Thanks to accurate detector simulations and control studies, the experimental analyses have become
+remarkably good at removing detector acceptance effects. In this section we therefore assume that
+there are only a small, residual acceptance effects left that affect the events. In particular, we
+assume that the latter can be modeled as a modified probability density,
+\begin{equation}
+    \label{eq:PDFwithDE}
+    P(\nuvec,\thvec) \to P(\nuvec,\thvec) \times \Omega(\thvec),
+\end{equation}
+where $\Omega$ is independent of the non-angular kinematics $\nuvec$. The latter assumption is only
+is invalid in general. However, if residual angular acceptance only weakly depends on $\vec{\nu}$, one
+can always choose appropriate bin $\vec{\nu}$ so that $\Omega$ is approximately constant with respect
+to $\vec{\nu}$. For such a case we parametrize
+\begin{equation}
+    \Omega_{m,l}(\thvec) = \prod_{i=1}^{m} \Big[1 + \sum_{j=1}^l \eps_i^{(j)} p_j(\cos\theta_i)\big]
+\end{equation}
+where $p_j(\cos\theta_i)$ denotes the $j$th Legendre polynomial. Since we only consider residual
+acceptance effects, we expect $\eps_i^{(j)} \ll 1$. \footnote{\danny{what are reasonable values/upper limits on the $\eps$?}}\\
+
+We are aware that setting a bin width that fulfills the aforementioned criterion can be at odds with
+other requirements. For instance, in exclusive $b\to s\ell^+\ell^-$ decays, the bin width for
+$\vec{\nu} = q^2$ needs to cover a sufficiently large part of the phase space beyond the open charm
+threshold. We emphasize that the outcome of an analysis as proposed here can easily combine several
+bins by means of a weighted average.\\
+
+\paragraph{Uniangular Distribution}
+For definiteness and clarity, we consider first an uni-angular distribution $P(\theta)$.
+In this case we can parametrize the PDF $P$ as
+\begin{equation}
+    P(\theta) = S_1 + S_2 \cos\theta + S_2 \cos^2\theta\,,
+\end{equation}
+which is a parametrization that has been used in the literature for $\bar{B}\to\bar{K}\ell^+\ell^-$ decays \cite{Bobeth:2007dw}.
+While this system of angular functions is not orthonormal, it can easily be orthonormalized. For the basis of angular
+functions, see \refapp{btokll}.
+Considering detector acceptance effects up to second order in $\cos\theta$, the function $\Omega(\vec\theta)$ reads
+\begin{equation}
+    \Omega_{1,2}(\theta_1) = 1 + \eps_{1}^{(1)} \cos\theta + \frac{\eps_{1}^{(2)}}{2}\big(3 \cos^2\theta - 1\big)\qquad\eps_{1}^{(i)} = \order{\eps}\,.
+\end{equation}
+Inclusion of $\Omega_{1,2}$ as part of the PDF as proposed in \refeq{PDFwithDE} modifies the MC estimators for the angular observables.
+We find
+\begin{equation}
+\begin{aligned}
+    \wwhat{S_1} & = \Big(1 + \frac{\eps_{1}^{(2)}}{2}\Big) \est{S_1} + \frac{9 \eps_{1}^{(2)}}{70} \est{S_3}\\
+    \wwhat{S_2} & = \Big(1 - \frac{2 \eps_{1}^{(2)}}{5}\Big) \est{S_2} - \eps_{1}^{(1)} \est{S_1} - \frac{3\eps_{1}^{(1)}}{5} \est{P_3}\\
+    \wwhat{S_3} & = \Big(1 - \frac{11\eps_{1}^{(2)}}{14}\Big)\est{S_3} - \frac{3\eps_{1}^{(2)}}{2} \est{S_1} - \eps_{1}^{(1)} \est{P_2}\,.
+\end{aligned}
+\end{equation}
+Here $\lbrace \est{S_i}\rbrace$ are the uncorrected estimators, while $\lbrace \wwhat{S_i}\rbrace$ denote the
+acceptance-corrected estimators of the angular observables.\\
+
+\paragraph{Triangular Distribution}
+
+\begin{table*}
+    \resizebox{.99\textwidth}{!}{\ensuremath{\input{tab-btokstarll-1to6.tex}}}\\[2.5\medskipamount]
+    \resizebox{.99\textwidth}{!}{\ensuremath{\input{tab-btokstarll-7to12.tex}}}\\[2.5\medskipamount]
+    \resizebox{.99\textwidth}{!}{\ensuremath{\input{tab-btokstarll-13to18.tex}}}
+    \caption{The matrix $N_{ij}$ that appears in \refeq{eff-corrected-est-btokstarll}. Due to spatial
+        constraints, we split its display into columns $j=1s,1c,1i,2s,2c,2i$ (top),
+        $j=3,4,4i,5,5i,6s$ (middle) and $j=6c,7,7i,8,8i,9$ (bottom).
+        \label{tab:eff-corrected-est-btokstarll}
+    }
+\end{table*}
+
+As an example for a triangular distribution we use the decay $\bar{B}\to\bar{K}^*(\to \bar{K}\pi)\ell^+\ell^-$.
+A parametrization of its angular distribution can be found in \refapp{btokstarll}.\\
+
+For this type of distribution, we expand $\Omega_3$ to linear order in $\eps$,
+\begin{equation}
+    \Omega_{3,2}(\theta_1,\theta_2,\theta_3) = 1 + \sum_{i=1}^3 \sum_{j=1}^2 \eps_i^{(j)} p_j(\cos\theta_i) + \order{\eps^2}\,.
+\end{equation}
+This leads to a matrix-valued equation that relates the effiency-corrected estimators $\wwhat{S}_i$ to the uncorrected
+estimators $\est{S}_j$,
+\begin{equation}
+    \label{eq:eff-corrected-est-btokstarll}
+    \wwhat{S}_i = \sum_{j=1\text{s},\dots\,9} \big(\delta_{ij} + N_{ij}\big) \est{S}_j\,.
+\end{equation}
+We provide the matrix $N$ in \reftab{eff-corrected-est-btokstarll}.\\
+\hrule
 
@@
         \end{subfigure}
-        \caption{Uncertainty of the angular observables $S_5$ and $S_7$, extracted from simulated events of the decay $B\to K^*\ell^+\ell^-$
-        and as a function of the number of simulated events $N$. The red curve represents a fit to the function $\sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}$.}
+        \caption{Uncertainty of the angular observables $S_5$ and $S_7$, extracted from simulated events of the decay $B\to K^*\ell^+\ell^-$ and as a function of the number of simulated events $N$.
+The red curve represents a fit to the function $\sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}$.}
         \label{fig:errors}
@@
 \begin{equation}
-    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1}} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
+    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
 \end{equation}
@@
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \hat{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
+    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
 \end{equation}
@@
 
-The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ --- up to and including P-wave contributions --- has been calculated
+The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
 for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
 \begin{equation}
-    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
+    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{J_{i}(q^2)}{\dd\Gamma/\dd q^2} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
 \end{equation}
-where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
+where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
 The $q^2$-differential decay width reads
 \begin{equation}
-    \frac{\rmdx{\Gamma}}{\rmdx{q^2}} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
+    \frac{\dd\Gamma}{\dd q^2} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
 \end{equation}
-The angular functions\footnote{%
-    We consistently use the label "$i$" to denote angular function and observables that arise
-    from interference between S-wave and P-wave amplitudes. Our convention is related to the convention
-    of \cite{Bobeth:2012vn} through $f_{1i} \leftrightarrow f_{1sc}$, $f_{2i} \leftrightarrow f_{2sc}$.
-} read \cite{Blake:2012mb,Bobeth:2012vn}
+The angular functions read \cite{Blake:2012mb,Bobeth:2012vn}
 \begin{equation}
@@
     f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
-    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\theta_3 &
-    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 &
-    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\theta_3\\
-    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\theta_3 & & &
-    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\theta_3\\
+    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\phi &
+    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\phi\\
+    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\phi & & &
+    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\phi\\
+    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\phi & & &
+    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\phi\\
     f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
     f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
-    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\theta_3 & & &
-    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\theta_3\\
-    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\theta_3 & & &
-    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\\
-    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
+    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\phi & & &
+    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\phi\\
+    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\phi & & &
+    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\phi\,.
 \end{aligned}
@@
 \begin{equation}
-    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
+    P(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
 \end{equation}
-where we also define $S_k(q^2) \equiv J_k(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\
+where we also define $S_i(q^2) = J_i(q^2) / (\dd\Gamma/\dd q^2)$.\\
 
@@
 \begin{aligned}
-    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_2 - 42 \cos^2\theta_2\big) + \big(  45 \sin^2\theta_2 - 30 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
-    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_2 + 84 \cos^2\theta_2\big) + \big( -15 \sin^2\theta_2 + 60 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,\\
-    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_2 - 30 \cos^2\theta_2\big) + \big(+135 \sin^2\theta_2 - 90 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
-    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_2 + 60 \cos^2\theta_2\big) + \big( -45 \sin^2\theta_2 +180 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,
+    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_1 - 42 \cos^2\theta_1\big) + \big(  45 \sin^2\theta_1 - 30 \cos^2\theta_1\big)\cos 2\theta_2}{64} \,,\\
+    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_1 + 84 \cos^2\theta_1\big) + \big( -15 \sin^2\theta_1 + 60 \cos^2\theta_1\big)\cos 2\theta_2}{32} \,,\\
+    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_1 - 30 \cos^2\theta_1\big) + \big(+135 \sin^2\theta_1 - 90 \cos^2\theta_1\big)\cos 2\theta_2}{64} \,,\\
+    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_1 + 60 \cos^2\theta_1\big) + \big( -45 \sin^2\theta_1 +180 \cos^2\theta_1\big)\cos 2\theta_2}{32} \,,
 \end{aligned}
@@
 \begin{aligned}
-    \hat{f}_{1i} & = \frac{\big(21 + 15 \cos1\theta_2\big)\cos\theta_2}{16}               \,,&
-    \hat{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
-    \hat{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,& &\\
-    \hat{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
-    \hat{f}_{4i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \cos \theta_3}{8}                 \,,\\
-    \hat{f}_{5}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \cos \theta_3}{8}                 \,,&
-    \hat{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
-    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
-    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
-    \hat{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
-    \hat{f}_{7i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \sin \theta_3}{2}                 \,,\\
-    \hat{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
-    \hat{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,,\\
-    \hat{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,.\\
+    \hat{f}_{1sc}& = \frac{\big(21 + 15 \cos2\theta_2\big)\cos\theta_1}{16}               \,,&
+    \hat{f}_{2sc}& = \frac{\big(15 + 45 \cos2\theta_2\big)\cos\theta_1}{16}               \,,\\
+    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_1 -  6 \cos^2\theta_1\big)\cos\theta_2}{4} \,,&
+    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_1 + 12 \cos^2\theta_1\big)\cos\theta_2}{2} \,,\\
+    \hat{f}_{3}  & = \frac{75 \sin^2\theta_1 \sin^2\theta_2 \cos2\phi}{32}                \,,&
+    \hat{f}_{9}  & = \frac{75 \sin^2\theta_1 \sin^2\theta_2 \sin2\phi}{32}                \,,\\
+    \hat{f}_{4}  & = \frac{75 \sin 2\theta_1 \sin 2\theta_2 \cos \phi}{32}                \,,&
+    \hat{f}_{4i} & = \frac{15 \sin  \theta_1 \sin 2\theta_2 \cos \phi}{8}                 \,,\\
+    \hat{f}_{5}  & = \frac{15 \sin 2\theta_1 \sin  \theta_2 \cos \phi}{8}                 \,,&
+    \hat{f}_{5i} & = \frac{3  \sin  \theta_1 \sin  \theta_2 \cos \phi}{2}                 \,,\\
+    \hat{f}_{7}  & = \frac{15 \sin 2\theta_1 \sin  \theta_2 \sin \phi}{8}                 \,,&
+    \hat{f}_{7i} & = \frac{3  \sin  \theta_1 \sin  \theta_2 \sin \phi}{2}                 \,,\\
+    \hat{f}_{8}  & = \frac{75 \sin 2\theta_1 \sin 2\theta_2 \sin \phi}{32}                \,,&
+    \hat{f}_{8i} & = \frac{15 \sin  \theta_1 \sin 2\theta_2 \sin \phi}{8}                 \,.
 \end{aligned}
@@
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} \hat{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
+    \int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) P(q^2, \theta_1,\theta_2,\phi) = S_i(q^2)\,.
 \end{equation}
@@
 
-The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays \fred{title has $\bar{B}$ instead of $P$}, where $P,P_1$, and $P_2$ are pseudoscalar mesons,
+The class of $P\to P_1 P_2 \ell_1\bar\ell_2$ decays, where $P,P_1$, and $P_2$ are pseudoscalar mesons,
 and $\ell_1$ and $\bar\ell_2$ are charged or neutral leptons, includes decays
 such as $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$.
-Their decay PDFs can generally be written as \cite{Lee:1992ih}
+Their PDFs can generally be written as \cite{Lee:1992ih}
 \begin{equation}
-    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\langle \Gamma\rangle}\frac{\rmdx{^5 \Gamma}}{\rmdx{q^2} \rmdx{k^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
+    P(q^2, k^2, \cos\theta_1, \cos \theta_2, \phi) = \frac{1}{\langle \Gamma\rangle}\frac{\dd^5 \Gamma}{\dd q^2\,\dd k^2\, \dd\cos\theta_1\,\dd\cos\theta_2\,\dd\phi} = \frac{1}{4\pi} \sum_i \frac{I_i(q^2, k^2, \cos\theta_2)}{\Gamma} f_i(\cos\theta_1,\phi)\,,
 \end{equation}
-\fred{rather use index $k$ as in previous appendix} where
+where
 \begin{equation}
@@
     f_2 & = \cos 2\theta_1\,, &
-    f_3 & = \sin^2\theta_1 \cos 2\phi\,,\\
+    f_6 & = \cos  \theta_1\,, \\
+    f_3 & = \sin^2\theta_1 \cos 2\phi\,,&
     f_4 & = \sin 2\theta_1 \cos  \phi\,,&
-    f_5 & = \sin  \theta_1 \cos  \phi\,,&
-    f_6 & = \cos  \theta_1\,, \\
-    f_7 & = \sin  \theta_1 \sin  \phi\,,&
+    f_5 & = \sin  \theta_1 \cos  \phi\,,\\
+    f_9 & = \sin^2\theta_1 \sin 2\phi\,.&
     f_8 & = \sin 2\theta_1 \sin  \phi\,,&
-    f_9 & = \sin^2\theta_1 \sin 2\phi\,.\\
+    f_7 & = \sin  \theta_1 \sin  \phi\,,
 \end{aligned}
@@
 the dimeson mass squared and the dimeson helicity angles are denoted as $k^2$ and $\theta_2$. The
-azimuthal angle is denoted as $\phi$. \fred{Danny changed $\phi$ to $\theta_3$ in previous appendix. Here, too?}
-The total decay width is \fred{integrand independent of $\theta_1$? I guess you want to integrate over $\theta_2$}
+azimuthal angle is denoted as $\phi$. The total decay width is
 \begin{equation}
-    \langle \Gamma\rangle = \int_0^\pi \rmdx{\theta_1} \rmdx{q^2} \rmdx{k^2} \sin\theta_2 \frac{3I_1(q^2, k^2, \cos\theta_2) - I_2(q^2, k^2, \cos\theta_2)}{3}\,.
+    \langle \Gamma\rangle = \int_0^\pi \dd\theta_1\,\dd q^2\,\dd k^2\,\sin\theta_2 \frac{3I_1(q^2, k^2, \cos\theta_2) - I_2(q^2, k^2, \cos\theta_2)}{3}\,.
 \end{equation}
@@
 \end{equation}
-where we also define $S_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.
-\fred{$\sin\theta_1$ missing after $f_i$? Why $\rmdx{\Gamma} /\, \rmdx{q^2}$ and not just $\Gamma$ in definition?}\\
+where we also define $S_i(q^2, k^2, \theta_2) \equiv \sin\theta_2 I_i(q^2, k^2, \cos\theta_2) / (\dd\Gamma/\dd q^2)$.\\
 
@@
     \hat{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
-    \hat{f}_3 & = \frac{15}{4}                \cos 2\phi     \,,\\
+    \hat{f}_6 & = 3 \cos\theta_1                   \,, \\
+    \hat{f}_3 & = \frac{15}{4}                \cos 2\phi     \,, &
     \hat{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \phi     \,, &
-    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \phi     \,, &
-    \hat{f}_6 & = 3 \cos\theta_1                   \,,\\
-    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \phi     \,, &
+    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \phi     \,, \\
+    \hat{f}_9 & = \frac{15}{4}                \sin 2\phi     \,, &
     \hat{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \phi     \,, &
-    \hat{f}_9 & = \frac{15}{4}                \sin 2\phi     \,.\\
+    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \phi     \,.
 \end{aligned}
 \end{equation}
-\fred{$\hat{f}_3$ and $\hat{f}_9$ need factor $\frac{4}{5}$}
 such that
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^{2\pi} \rmdx{\phi} \hat{f}_i(\theta_1,\phi) P(q^2, k^2, \theta_1,\theta_2,\phi) = S_i(q^2, k^2, \theta_2)\,.
+    \int_0^\pi \dd\theta_1 \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\phi) P(q^2, k^2, \theta_1,\theta_2,\phi) = S_i(q^2, k^2, \theta_2)\,.
 \end{equation}
@@
 
-The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts -- reads \cite{Boeer:2014xx}
+The physical PDF for the decay -- in the presence of Standard Model operator and their chirality flipped counter parts -- reads \cite{Boeer:2014xx}
 \begin{equation}
-    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
+    P_{\Lambda_b}(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\dd \Gamma/\dd q^2} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
 \end{equation}
 where $q^2$ denotes the dilepton mass squared, $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
-helicity angles in the dilepton and
-$N\pi$ systems, respectively, and $\theta_3 = \phi$ \fred{Then use $\theta_3$ below and not $\phi$} denotes the azimuthal angle.
+helicity angles in the dilepton and $N\pi$ systems, respectively, and $\theta_3 = \phi$ denotes the azimuthal angle.
 The basis of angular functions reads \cite{Boeer:2014xx}
@@
 \begin{equation}
-    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}
+    \frac{\dd \Gamma}{\dd q^2} = 2 K_{1ss} + K_{1cc}
 \end{equation}
@@
 \end{equation}
-where we also define $S_i(q^2) = K_i(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\
+where we also define $S_i(q^2) = K_i(q^2) / (\dd\Gamma/\dd q^2)$.\\
 
@@
 \end{equation}
-such that \fred{Works out only if $\pi^3$ dropped everywhere, and $\hat f_{2cc} \to 2 \hat f_{2cc}$}
+such that
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\phi} P(q^2, \theta_1, \theta_2, \phi) \hat{f}_i(\theta_1, \theta_2, \phi) = S_i(q^2)\,.
+    \int_0^\pi \dd \theta_1 \int_0^\pi \dd \theta_2 \int_0^{2\pi} \dd \phi P(q^2, \theta_1, \theta_2, \phi) \hat{f}_i(\theta_1, \theta_2, \phi) = S_i(q^2)\,.
 \end{equation}
 
-\section{On the Partial-Wave Expansions of Angular Observables}
+\section{On the Partial Wave Expansions of Angular Observables}
 \label{app:partial-waves}
 
-Let $S \equiv S(\vec{\nu},\theta)$ be an observable of only one angle $\theta$ and further non-angular variables $\vec{\nu}$. Further, let
-$S$ have an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
+Let $P \equiv P(\vec{\nu},\theta)$ be an observable of only one angle $\theta$ and further non-angular variables $\vec{\nu}$. Further, let
+$P$ have an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots \hat{=} S,P,D,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
 \begin{equation}
     \label{eq:def-partial-wave-observable}
-    S(\theta) \equiv F\left[A_1(\theta) A_2^*(\theta)\right] \equiv F\left[\left(\sum_{l_1=0}^\infty A_1^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta)\right) \left(\sum_{l_2=0}^\infty A_2^{*(l_2)} p_{l_2}^{(m_2)}(\cos\theta)\right)\right]\,,
+    P(\theta) \equiv F\big(A_1(\theta) A_2^*(\theta)\big) \equiv \left(\sum_{l_1=0}^\infty A_1^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta)\right) \left(\sum_{l_2=0}^\infty A_1^{(l_2)} p_{l_2}^{(m_2)}(\cos\theta)\right)\,,\qquad F=\Re{},\Im{}\,.
 \end{equation}
-where $F \in \{\text{Re},\text{Im}\}$ denotes taking either the real
-or the imaginary part. \fred{Now $\nuvec$ gone}
-$p_{l}^{(m)}$ is an \emph{associated Legendre} polynomial and $m_i$ is the third component of the angular momentum of the amplitude $A_i$, and we impose $m_1 \geq m_2$.\\
+Here $m_1$ and $m_2$ denote the third component of the angular momentum of the respective amplitude $A_1$ or $A_2$, and we impose $m_1 \geq m_2$.\\
 
-From the positivity of amplitudes, one immediately finds
+From positivity of the amplitudes one immediately finds
 \begin{equation}
-    \int \rmdx{\cos\theta}  \, |A_i(\theta)|^2 = \sum_{l_i = 0}^\infty |A_i^{(l_i)}|^2 n_{l_i, m_i} < \infty\,,
+    \int \dd\cos\theta |A_i(\theta)|^2 = \sum_{l_i = 0}^\infty |A_i^{(l_i)}|^2 n_{l_i, m_i} < \infty\,,
 \end{equation}
@@
     \label{eq:legendre-scalar-product}
-    n_{l, m} \delta_{l, l'} \equiv \int_{-1}^1 \rmdx{\cos\theta} p_{l}^{(m)}(\cos\theta) p_{l'}^{(m)} (\cos\theta)  = \frac{2}{(2 l + 1)} \frac{(l + m)!}{(l - m)!} \delta_{l, l'}\,.
+    n_{l, m} \delta_{l, l'} \equiv \int_{0}^\pi p_{l}^{(m)}(\cos\theta) p_{l'}^{(m)} (\cos\theta) \dd \cos\theta = \frac{2}{(2 l + 1)} \frac{(l + m)!}{(l - m)!} \delta_{l, l'}\,.
 \end{equation}
-Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial-wave amplitudes must asymptotically fall off as
+Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial waves amplitudes must asymptotically fall off,
 \begin{equation}
@@
 Will will show in the following that such a cut off
-is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$. Since this expansion implies
-a well defined total angular momentum for each observable, one ensures that the observables can in fact be disentangled experimentally.\\
+is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$.
+Since this expansion implies a well-defined total angular momentum for each observables, one ensures that the observables can in fact be disentangled experimentally.\\
 
-We propose the decomposition of $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with total angular momentum $j$ and its third component $m=m_1 + m_2$.
+We propose the decomposition of $P$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with total angular momentum $j$ and its third component $m=m_1 + m_2$.
 \begin{equation}
-    S(\vec{\nu}, \theta) = \sum_j S_{j,m}(\vec{\nu}) p_{j}^{(m)}(\cos\theta)\,.
+    P(\vec{\nu}, \theta) = \sum_j P_{j,m}(\vec{\nu}) p_{j}^{(m)}(\cos\theta)\,.
 \end{equation}
-This parametrization has two merits. First, we can immediately project out the angular observables $S_{j,m}$ by means of \refeq{legendre-scalar-product}:
+This parametrization has two merits. First, we can immediately project out the angular observables $P_{j,m}$ by means of \refeq{legendre-scalar-product}:
 \begin{equation}
-    S_{j,m}(\vec{\nu}) = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} S(\vec{\nu},\cos \theta) p_{j}^{(m)}(\cos\theta)\,.
+    P_{j,m}(\vec{\nu}) = \frac{1}{n_{j,m}} \int_{-1}^{+1} P(\vec{\nu},\cos \theta) p_{j}^{(m)}(\cos\theta) \dd\cos\theta\,.
 \end{equation}
-Second, we can immediately express $S_{j,m}(\vec{\nu})$ in terms of
-the partial-wave amplitudes, \fred{We may exchage the integral and the
-  series because each element of the series is a product of
-  polynomials on the compact support [-1,1], and thus each integral is
-  absolutely convergent}
+Second, we can immediately express $P_{j,m}(\vec{\nu})$ in terms of the partial-wave amplitudes,
 \begin{equation}
@@
     \begin{aligned}
-        S_{j,m}(\vec{\nu})
-            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) A_{2}^{*(l_2)}p_{l_2}^{(m_2)}(\cos\theta)\right]\\
-            & = \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} A_{2}^{*(l_2)}\right] \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
+        P_{j,m}(\vec{\nu})
+            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left(A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) \big(A_{2}^{(l_2)}\big)^*\right) p_{l_2}^{(m_2)}(\cos\theta)\\
+            & = \sum_{l_1,l_2=0}^\infty F\left(A_{1}^{l_1} \big(A_{2}^{(l_2)}\big)^*\right) \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
     \end{aligned}
@@
     T_{l_1,l_2,j}^{(m_1,m_2)}
-        & = \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) p_{l_1}^{(m_1)}(\cos\theta) p_{l_2}^{(m_2)}(\cos\theta)\\
+        & = \int_{-1}^{+1} p_{j}^{(m_1 + m_2)}(\cos\theta) p_{l_1}^{(m_1)}(\cos\theta) p_{l_2}^{(m_2)}(\cos\theta) \dd\cos\theta\\
         & = (-1)^{s - l_1 - m_2} \frac{2 (l_1 + m_1)! (l_2 + m_2)! (2s - 2 l_2)! s!}{(l_1 - m_1)! (s - j)! (s - l_1)! (s - l_2)! (2s + 1)!}\\
@@
 \end{equation}
-The necessary conditions for $T \neq 0$ are
+The necessary condition for $T \neq 0$ are
 \begin{equation}
@@
 of this and of \refeq{angular-momentum-addition}, the angular observables $P_{j,m}$
-consist of sums with infinitely many terms. It is then up to theoretical analyses to
+consist of sums with infinite terms. It is then up to theoretical analyses to
 estimate or calculate the impact of individual contributions, with or without the cut off $L$.
 For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
-We close by remarking that for any angular-momentum cut off $\ell < L$\fred{Do you mean $L < \infty$? Don't use $\ell$ again}, one can find an upper limit for the squared sum
-of all remaining partial waves through the inclusive decay; i.e., schematically
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+
+\section{Systematic way for determining the acceptance matrix for }
+
+In this section we will give a systematic description on how to obtain unfolding matrix based on MC sample.
+We start by generating so called flat phase space.
+In this MC all simulated angular distributions of $\cos \theta_l$, $\cos \theta_k$ and $\phi$ are flat.
+Assuming the massless limit, and not scalars the PDF has only 9 parameters: $F_l$, and $S_{3,4,5,6s,7,8,9}$:
+\begin{multline}
+\dfrac{d^4\Gamma}{ \Gamma dq^2 dcos\theta_k dcos\theta_l d\phi}=\dfrac{9}{32\pi}( \dfrac{3}{4} (1-F_l) \sin^2 \theta_k + F_l\cos^2 \theta_k + ( \dfrac{1}{4}(1-Fl)\sin^2 \theta_k \\ -  F_l\cos^2) cos 2\theta_l  + S_3 \sin^2 \theta_k \sin^2 \theta_l \cos2\phi + S_4 \sin2 \theta_k \sin \theta_l \cos\phi +\\ S_5 \sin2 \theta_k \sin \theta_l \cos \phi +  (S_{6s} \sin^2 \theta_k) \cos \theta_l + \\ S_7 \sin 2\theta_k \sin \theta_l \sin \phi +  S_8 \sin 2 \theta_k \sin 2 \theta_l \sin phi + S_9 sin^2 \theta_k \sin^2 \theta_l \sin 2 \phi)
+\label{PDF}
+\end{multline}
+From theory it is easy to compute that only Fl will have a non zero moment equal to $\dfrac{2}{3}$.
+Next we apply the detector simulation and selection as done on real data.
+Then we can measure again all 9 moments which we put in a vector $\overrightarrow{v}$.
+The first column of an unfolding matrix $M_{unfold}$ will be then equal to $\dfrac{3}{2} \overrightarrow{v}$.
+Next we can weight selected events accordingly to $f_{s_3}$.
+From theory one can calculate that only moment corresponding to $S_3$ will be non zero and equal to $\dfrac{32}{225} S3$.
+Measuring the moments on weighted events and punting them in a vector: $\overrightarrow{v_2}$ leads to second column of unfolding matrix equal the $\dfrac{225}{32} \overrightarrow{v_2}$.
+Repeating this procedure for all moments will lead to full determination of the unfolding matrix.
+We provide reader the explicit calculation of the normalization factors for the moments vectors:
 \begin{equation}
-    \sum_{i=1}^2 \sum_{l=L}^\infty |A_i^{(l)}|^2 \leq \frac{\rmdx{^{1 + \dim\vec\nu}} \Gamma_\text{incl}}{\rmdx{\cos\theta} \rmdx{\vec\nu}}\,.
+\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{S_{3,4,8,9}}*f_{S_{3,4,8,9}}= \dfrac{32}{225} ,
+\end{equation}
+
+\begin{equation}
+\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{S_{5,6,7}}*f_{S_{5,6,7}}= \dfrac{8}{45} ,
+\end{equation}
+\begin{equation}
+\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{F_l}= \dfrac{2}{3}
 \end{equation}

### 2014-07-28 draft.tex
confirming O(1)
Fix some of the issues in App. E found by Fred

--- 2014-07-25 draft.tex
@@
         \end{equation}
-        with $\sigma_k(1) = \order{1}$. \todo{Check this!}
+        with $\sigma_k(1) = \order{1}$. 
     \item \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of $N$.}
@@
 \end{equation}
+(Here and in the next step we may exchage the integral and the
+series because each element of the series is a product of
+polynomials on the compact support [-1,1], and thus each integral
+is absolutely convergent).
 Second, we can immediately express $S_{j,m}(\vec{\nu})$ in terms of
-the partial-wave amplitudes, \fred{We may exchage the integral and the
-  series because each element of the series is a product of
-  polynomials on the compact support [-1,1], and thus each integral is
-  absolutely convergent}
+the partial-wave amplitudes,
 \begin{equation}
@@
 \end{equation}
+
 In the last step, we use Gaunt's formula \cite{Gaunt:1929} to integrate a triple product of associated Legendre polynomials,
@@
 For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
-We close by remarking that for any angular-momentum cut off $\ell < L$\fred{Do you mean $L < \infty$? Don't use $\ell$ again}, one can find an upper limit for the squared sum
+We close by remarking that for any angular-momentum cut off $l < L$\fred{Do you mean $L < \infty$?}, one can find an upper limit for the squared sum
 of all remaining partial waves through the inclusive decay; i.e., schematically

### 2014-08-04 draft.tex
Set utf encoding to spell Marcin's last name
[intro] Start work

@@
 \documentclass[aps,prd,reprint,nofootinbib,preprintnumbers]{revtex4}
+
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
 
@@
 \affiliation{C2PAP, Universe Cluster, Ludwig-Maximilians-Universit\"at M\"unchen, Garching, Germany}
-\author{Marcin Chrzaszcz}
+\author{Marcin Chrz\k{a}szcz}
 \email{mchrzasz@cern.ch}
@@
 explicitly factored out in terms of the angular functions
-$f_i(\thvec)$, which we assume to fulfill the orthonormality relations
+$\{f_i(\thvec)\}$, which we assume to fulfill the orthonormality relations
 \begin{equation}
@@
 For the purpose of this letter, however, it suffices that the system
-of angular functions $f_i(\thvec)$ can be transformed into an
+of angular functions $\{f_i(\thvec)\}$ can be transformed into an
 orthonormal basis. The transformation needs to be worked out on a
@@
 
-In the remainder of this letter we discuss how to obtain the angular
-observables $S_i(\nuvec)$ in an experimental setup where each recorded
+% Our method is closely related to Pearson's method of moments
+% \citeneeded{}. One draws samples from a PDF $P(x | \nuvec)$ that
+% depends on parameters $\nuvec$. Then one approximates the population
+% (central) moments $x^k$ by the sample moments
+Our method is an extension of the classical method of moments with
+orthogonal functions~\cite{James:2006zz}.
+
+In the remainder of this letter we discuss how to obtain an angular
+observable $S_i(\nuvec)$ in an experimental setup where each recorded
 event is (approximately) distributed according to $P$.  We establish
@@
 \label{app:btokstarll}
+
 The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ --- up to and including P-wave contributions --- has been calculated

### 2014-08-04 draft.tex
[sec. I,II] Connect to moments literature, compare likelihood and moments methods

@@
 \usepackage{epstopdf}
+
 %% Shortcuts %%
-\newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
+\newcommand{\aver}[1]{\langle #1 \rangle}
+\newcommand{\dual}[1]{\tilde{#1}}
+\newcommand{\est}[1]{\widehat{#1}}
+\newcommand{\ie}{\textit{i.e.}}
+\newcommand{\nuvec}{\vec{\nu}}
+\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
 \newcommand{\refapp}[1]{app.~(\ref{app:#1})}
@@
 \newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
-\newcommand{\ie}{\textit{i.e.}}
-\newcommand{\nuvec}{\vec{\nu}}
+\newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
 \newcommand{\thvec}{\vec{\vartheta}}
@@
 \renewcommand{\theta}{\vartheta}
-%\newcommand{\GeV}{\text{GeV}}
-\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
 \let\eps\varepsilon
-\newcommand{\aver}[1]{\langle #1 \rangle}
-\newcommand{\est}[1]{\widehat{#1}}
 \newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
+
 \DeclareMathOperator{\cov}{Cov}
@@
 explicitly factored out in terms of the angular functions
-$\{f_i(\thvec)\}$, which we assume to fulfill the orthonormality relations
+$\{f_i(\thvec)\}$. We assume there exists a dual basis of functions
+$\{\dual{f}_i(\thvec)\}$ such that the orthonormality relations
 \begin{equation}
     \label{eq:def-ortho-rel}
-    \int_\Omega \rmdx{^N \theta} f_i(\thvec) f_j(\thvec)  = \delta_{ij}\,,
+    \int_\Omega \rmdx{^N \theta} \dual{f}_i(\thvec) f_j(\thvec)  = \delta_{ij}
 \end{equation}
-with $\Omega$ representing the full angular phase space relevant to the process.
-For the purpose of this letter, however, it suffices that the system
-of angular functions $\{f_i(\thvec)\}$ can be transformed into an
-orthonormal basis. The transformation needs to be worked out on a
-case-by-case basis. For a selection of $B$ decays which we consider the most interesting
-we list the transformations in a series of appendices \ref{app:btokll} through
-\ref{app:lambdabtolambdall}.\\
-
-For particle decays, $P$ is generally expressed in terms of the fully differential decay width,
+hold with $\Omega$ representing the full angular phase space relevant
+to the process.  For particle decays, $P$ is generally expressed in
+terms of the fully differential decay width,
 \begin{align}
@@
 Our method is an extension of the classical method of moments with
-orthogonal functions~\cite{James:2006zz}.
+orthogonal functions~\cite[sec. 8.2]{James:2006zz}. The only difference
+is that conventionally the angular functions are assumed
+\emph{self-dual}, $\dual{f}_i = f_i$. However, it suffices that the
+system of angular functions $\{f_i(\thvec)\}$ \emph{can} be transformed into
+an orthonormal basis. It turns out to be much more convenient to work
+in the basis natural to each process but the statistical properties
+are equivalent for both approaches provided that one replace $f_i \to
+\dual{f}_i$ appropriately. Using the ansatz
+\begin{equation}
+  \label{eq:dual-ansatz}
+  \dual{f}_i = \sum_{j} a_{ij} f_j \,,
+\end{equation}
+the dual basis needs to be worked out case by case through solving the
+linear system of equations (\ref{eq:def-ortho-rel}). For a selection
+of hadron decays with a $b$ quark in the initial state and two leptons
+in the final state, we list the dual bases in a series of appendices
+\ref{app:btokll} through \ref{app:lambdabtolambdall}. Note that a
+similar analysis was done in~\cite{Dighe:1998vk} for the decays $B \to
+J/\psi \phi$ and $B \to J/\psi K^{*}$.
 
@@
     \label{eq:det-Pi-analytical}
-    S_i(\nuvec) = \int_{\Omega} \rmdx{^N \theta} \hat{f}_i(\thvec) P(\nuvec, \thvec)\,.
+    S_i(\nuvec) = \int_{\Omega} \rmdx{^N \theta}  P(\nuvec, \thvec) \dual{f}_i(\thvec)\,.
 \end{equation}
-where $\lbrace \hat{f}_i \rbrace$ denotes a \emph{dual basis} of angular function. In all generality
-the bases $\lbrace f_i \rbrace$ and $\lbrace \hat{f}_i \rbrace$ are not identical. This is the
+where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular functions. In general, $\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$. This is the
 case for our selection of applications in appendices \ref{app:btokll} through \ref{app:lambdabtolambdall}.\\
 
-It is sensible to refer to the angular observable $S_i$ as the \emph{$\hat{f}_i$-moment} of the PDF $P$.
+It is sensible to refer to the angular observable $S_i$ as the \emph{$f_i$-moment} of the PDF $P$.
 We emphasize that a relation of type \refeq{det-Pi-analytical} holds for any combination of
@@
     \equiv \int \rmdx{^M \nu} S_i(\nuvec)
-    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta}\hat{f}_i(\thvec) P(\nuvec,\thvec) \right].
+    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta} P(\nuvec,\thvec) \dual{f}_i(\thvec) \right].
 \end{equation}
@@
 \begin{equation}
-    E_P[g] \equiv \int \rmdx{x} g(x) P(x)
+    E_P[g] \equiv \int \rmdx{x} P(x) g(x)
 \end{equation}
-can be approximated \cite{MCSM-2004} by an MC estimator $\est{E_P[g]}$
+can be approximated \cite{MCSM-2004} by the consistent and unbiased
+estimator $\est{E_P[g]}$~\cite[sec. 8.2]{James:2006zz}
 \begin{equation}
     \label{eq:mc-id}
-    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1} g(x^{(k)})
+    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1}^K g(x^{(k)}) \,,\,    x^{(k)} \sim P
 \end{equation}
@@
 that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
-$P$; i.e.,
-\begin{equation}
-    x^{(k)} \sim P\,.
-\end{equation}
+$P$.
 Throughout this letter we denote all MC estimators with a wide hat.\\
@@
 \begin{equation}
-    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})\,.
+    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})\,.
 \end{equation}
@@
     & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
-    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)  \right]\\
-    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)
+    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} P(\nuvec,\thvec) \dual{f}_i(\thvec)  \right]\\
+    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta}  P(\nuvec,\thvec) \dual{f}_i(\thvec)
         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
@@
     \widehat{\langle S_i\rangle_{\vec{a},\vec{b}}}
-    = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
+    = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
-This basically reduces the estimation of
-$\aver{S_i}_{\vec{a},\vec{b}}$ to a (weighted) counting experiment. In
-the limit $N \to \infty$, the random vector $( \dots,
-\aver{S_i}_{\vec{a},\vec{b}}, \dots)$ follows a multivariate Gaussian
-distribution \citeneeded\fred{Robert,Casella?}
-with the mean vector estimated by \refeq{bin-importance}, and the covariance
+This reduces the estimation of $\aver{S_i}_{\vec{a},\vec{b}}$ to a
+(weighted) counting experiment. In the limit $N \to \infty$, the
+central limit theorem (CLT) implies that the random vector
+\begin{equation}
+  \label{eq:angular-obs-vec}
+  \widehat{\vec{S}_{\vec{a},\vec{b}}} \equiv (\aver{S_1}_{\vec{a},\vec{b}}\,, \dots, \aver{S_i}_{\vec{a},\vec{b}}\,,
+  \dots)
+\end{equation}
+ follows a multivariate Gaussian distribution whose mean vector
+is approximated by \refeq{bin-importance} and whose covariance is
 estimated as
@@
     \cov[\aver{S_i},\aver{S_j}]_{\vec{a},\vec{b}} \to \est{\cov}[\aver{S}_i, \aver{S}_j]_{\vec{a},\vec{b}}
-        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\hat{f}_i(x^{(k)}) - \est{\langle S_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\hat{f}_j(x^{(k)}) - \widehat{\langle S_j\rangle_{\vec{a},\vec{b}}}\big]
+        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\dual{f}_i(x^{(k)}) - \est{\langle S_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\dual{f}_j(x^{(k)}) - \widehat{\langle S_j\rangle_{\vec{a},\vec{b}}}\big]
         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
-We would like to emphasize that the sample covariance should rapidly converge towards the true covariance matrix.
-We propose to declare convergence once estimators for skewness and kurtosis are sufficiently small,
+In our physics applications, the parameter space is compact and each
+$\dual{f}_i$ is bounded. Hence the requisites for the most basic
+version of the CLT to hold --- finite mean and covariance of
+$\dual{f}_i$ --- are automatically satisfied.  We would like to
+emphasize that the sample covariance should \fred{``Should'' as in it
+  does in practice? Reference toy studies below} rapidly converge
+towards the true covariance matrix.  We propose to declare convergence
+\fred{I'd prefer: check that skewness and kurtosis are sufficiently
+  small} once estimators for skewness and kurtosis are sufficiently
+small,
 \begin{equation}
@@
 
-The convergence towards a normal distribution for the results allows to transfer correlation information to interested
-theorists. In particular, this will allow to constrict predictive distributions of optimized observables.
-(See e.g. \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf}
-for definitions of such optimized observables in $B\to K^*\ell^+\ell^-$ decays, \cite{Faller:2013dwa} for application to
-the decay $B\to \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$).
+Compared to the usual maximum-likelihood approach, we find for the method of moments:
+\begin{enumerate}
+\item The angular observable $\aver{S_i}$ can be determined
+  independently of any other observable $\aver{S_j}$. It is therefore
+  much more robust to physics assumptions needed to define the full
+  likelihood. In particular, this means one does not have to be
+  specific regarding the form of new-physics contributions.
+\item It is superior for a small number of samples $N$. Likelihood
+  fits tend to be numerically unstable if lots of parameters need to
+  be estimated from sparse data. This is more severe if the mode of
+  the likelihood is near the boundary of the physically allowed
+  region.\fred{Is there some LHCb note we could cite?} In many of the
+  decays of interest, there are only say dozens of events recorded.
+\item The estimate is unbiased for any $N$. In contrast, the
+  maximum-likelihood estimate has a bias of order
+  $1/N$~\cite{Cox:1968}. In practice, one should keep in mind the
+  bias-variance trade-off: it is a well known phenomenon that removing
+  the bias usually leads to an increase in variance of the sampling
+  distribution of the estimator~\cite[sec. 7.3]{James:2006zz}. From a
+  Bayesian decision-theory point of view, both contribute similarly to
+  the expected loss associated with deciding on just one value of the
+  unknown parameter. It is therefore highly questionable to reduce
+  only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
+  the results discussed below in \refsec{numerics}, the likelihood
+  fits --- if they converge --- produce uncertainties (10--15)\%
+  smaller than those from the method of moments.
+\item The approximate normal distribution allows easier and more
+  correct transfer of the information in the data to interested
+  theorists for more accurate fits of standard-model and new-physics
+  parameters \citeneeded\fred{Our fits and others'?} or for more precise predictions of
+  optimized observables; e.g.,
+  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
+    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
+  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
+  \cite{Faller:2013dwa} for application to the decay $B\to
+  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
+  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
+  likelihood also approaches a multivariate Gaussian as $N \to
+  \infty$, the two methods differ in their utility as input for
+  theorists if $\widehat{\vec{S}_{\vec{a},\vec{b}}}$ is not well
+  inside the physical region. For example, suppose there are two
+  angular observables that are constrained to a triangular region by
+  phase-space or unitarity arguments as \fred{Could add a sketch. It
+    is supposed to resemble $A_{\text{FB}},F_L$ for $B \to K^* \ell \ell$.}
+  \begin{equation}
+    \label{eq:constr-ex}
+    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
+  \end{equation}
+  It may (and often does) happen in practice that
+  $\widehat{\vec{S}_{\vec{a},\vec{b}}}$ is close or even outside the
+  allowed region such that a significant part of the probability mass
+  of $\vec{S}$ covers unphysical values. In a Bayesian fit, one would
+  take $\mathcal{N}(\vec{S} | \widehat{\vec{S}_{\vec{a},\vec{b}}},
+  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
+  simply set a uniform prior on the triangle defined by
+  \refeq{constr-ex} to have a well defined problem. This could be
+  trivially combined with other independent information in a global
+  fit. For a likelihood fit, the constraint needs to be built in by
+  the experiment into the analysis of the actual events and the
+  resulting likelihood as a function of $\vec{S}$ is distinctly not
+  Gaussian. Since experimental collaborations as a whole tend to favor
+  data-privacy over accurate use of their results in theorist's
+  analyses, the multivariate likelihood is kept secret, and cannot be
+  recovered from the numerical value of $\vec{S}$ and the standard
+  errors reported in written publications. The theorist then usually
+  includes the results as independent measurements with a Gaussian
+  distribution and disregards the constraint altogether. This last
+  situation is undesirable for both experimentalists and theorists.
+\end{enumerate}
 
@@
 
-The dual basis $\lbrace \hat{f}_i\rbrace$ reads
+The dual basis $\lbrace \dual{f}_i\rbrace$ reads
 \begin{equation}
 \begin{aligned}
-    \hat{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
-    \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
-    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,,
+    \dual{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
+    \dual{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
+    \dual{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,,
 \end{aligned}
@@
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \hat{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
+    \int_0^\pi \rmdx{\theta_1} \dual{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
 \end{equation}
@@
 \begin{aligned}
-    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_2 - 42 \cos^2\theta_2\big) + \big(  45 \sin^2\theta_2 - 30 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
-    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_2 + 84 \cos^2\theta_2\big) + \big( -15 \sin^2\theta_2 + 60 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,\\
-    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_2 - 30 \cos^2\theta_2\big) + \big(+135 \sin^2\theta_2 - 90 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
-    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_2 + 60 \cos^2\theta_2\big) + \big( -45 \sin^2\theta_2 +180 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,
+    \dual{f}_{1s} & = \frac{\big( 63 \sin^2\theta_2 - 42 \cos^2\theta_2\big) + \big(  45 \sin^2\theta_2 - 30 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
+    \dual{f}_{1c} & = \frac{\big(-21 \sin^2\theta_2 + 84 \cos^2\theta_2\big) + \big( -15 \sin^2\theta_2 + 60 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,\\
+    \dual{f}_{2s} & = \frac{\big( 45 \sin^2\theta_2 - 30 \cos^2\theta_2\big) + \big(+135 \sin^2\theta_2 - 90 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
+    \dual{f}_{2c} & = \frac{\big(-15 \sin^2\theta_2 + 60 \cos^2\theta_2\big) + \big( -45 \sin^2\theta_2 +180 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,
 \end{aligned}
@@
 \begin{aligned}
-    \hat{f}_{1i} & = \frac{\big(21 + 15 \cos1\theta_2\big)\cos\theta_2}{16}               \,,&
-    \hat{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
-    \hat{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,& &\\
-    \hat{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
-    \hat{f}_{4i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \cos \theta_3}{8}                 \,,\\
-    \hat{f}_{5}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \cos \theta_3}{8}                 \,,&
-    \hat{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
-    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
-    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
-    \hat{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
-    \hat{f}_{7i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \sin \theta_3}{2}                 \,,\\
-    \hat{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
-    \hat{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,,\\
-    \hat{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,.\\
+    \dual{f}_{1i} & = \frac{\big(21 + 15 \cos1\theta_2\big)\cos\theta_2}{16}               \,,&
+    \dual{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
+    \dual{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,& &\\
+    \dual{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
+    \dual{f}_{4i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \cos \theta_3}{8}                 \,,\\
+    \dual{f}_{5}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \cos \theta_3}{8}                 \,,&
+    \dual{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
+    \dual{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
+    \dual{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
+    \dual{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
+    \dual{f}_{7i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \sin \theta_3}{2}                 \,,\\
+    \dual{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
+    \dual{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,,\\
+    \dual{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,.\\
 \end{aligned}
@@
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} \hat{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
+    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} \dual{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
 \end{equation}
@@
 \begin{aligned}
-    \hat{f}_1 & = \frac{21 + 15 \cos 2\theta_1}{16}\,, &
-    \hat{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
-    \hat{f}_3 & = \frac{15}{4} \sin^2\theta_1 \cos 2\theta_3     \,,\\
-    \hat{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \theta_3     \,, &
-    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \theta_3     \,, &
-    \hat{f}_6 & = 3 \cos\theta_1                   \,,\\
-    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \theta_3     \,, &
-    \hat{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \theta_3     \,, &
-    \hat{f}_9 & = \frac{15}{4} \sin^2\theta_1 \sin 2\theta_3     \,.\\
+    \dual{f}_1 & = \frac{21 + 15 \cos 2\theta_1}{16}\,, &
+    \dual{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
+    \dual{f}_3 & = \frac{15}{4} \sin^2\theta_1 \cos 2\theta_3     \,,\\
+    \dual{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \theta_3     \,, &
+    \dual{f}_5 & = 3            \sin  \theta_1 \cos  \theta_3     \,, &
+    \dual{f}_6 & = 3 \cos\theta_1                   \,,\\
+    \dual{f}_7 & = 3            \sin  \theta_1 \sin  \theta_3     \,, &
+    \dual{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \theta_3     \,, &
+    \dual{f}_9 & = \frac{15}{4} \sin^2\theta_1 \sin 2\theta_3     \,.\\
 \end{aligned}
@@
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^{2\pi} \rmdx{\theta_3} \hat{f}_i(\theta_1,\theta_3) P(q^2, k^2, \theta_1,\theta_2,\theta_3) = S_i(q^2, k^2, \theta_2)\,.
+    \int_0^\pi \rmdx{\theta_1} \int_0^{2\pi} \rmdx{\theta_3} \dual{f}_i(\theta_1,\theta_3) P(q^2, k^2, \theta_1,\theta_2,\theta_3) = S_i(q^2, k^2, \theta_2)\,.
 \end{equation}
@@
 % 1
-        \hat f_{1ss} & = \frac{1}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) &
-        \hat f_{1cc} & = \frac{1}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) &
-        \hat f_{1c}  & = \cos\theta_1\\
+        \dual f_{1ss} & = \frac{1}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) &
+        \dual f_{1cc} & = \frac{1}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) &
+        \dual f_{1c}  & = \cos\theta_1\\
 % 2
-        \hat f_{2ss} & = \frac{3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) \cos\theta_2 &
-        \hat f_{2cc} & = \frac{3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) \cos\theta_2 &
-        \hat f_{2c}  & = 3 \cos\theta_1   \cos\theta_2 \\
+        \dual f_{2ss} & = \frac{3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) \cos\theta_2 &
+        \dual f_{2cc} & = \frac{3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) \cos\theta_2 &
+        \dual f_{2c}  & = 3 \cos\theta_1   \cos\theta_2 \\
 % 3
-        \hat f_{3sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\theta_3 &
-        \hat f_{3s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \cos\theta_3 \\
+        \dual f_{3sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\theta_3 &
+        \dual f_{3s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \cos\theta_3 \\
 % 4
-        \hat f_{4sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\theta_3 &
-        \hat f_{4s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \sin\theta_3
+        \dual f_{4sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\theta_3 &
+        \dual f_{4s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \sin\theta_3
     \end{aligned}
@@
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} P(q^2, \theta_1, \theta_2, \theta_3) \hat{f}_i(\theta_1, \theta_2, \theta_3) = S_i(q^2)\,.
+    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} P(q^2, \theta_1, \theta_2, \theta_3) \dual{f}_i(\theta_1, \theta_2, \theta_3) = S_i(q^2)\,.
 \end{equation}

### 2014-08-04 draft.tex
More work on sec. IV, comments on Fred's points

@@
 \usepackage{graphicx}
-\usepackage{caption}
-\usepackage{subcaption}
 \usepackage{epstopdf}
@@
 \newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
+\newcommand{\reffig}[1]{fig.~(\ref{fig:#1})}
 \newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
@@
 \newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}
-
-\captionsetup{compatibility=false}
 
@@
 and sources of systematic uncertainties. Moreover, we will show that the method
-at hand has two benefits over the usual approach based on likelihood fits.
+at hand has two benefits over the usual approach based on likelihood fits. To wit:
 \begin{enumerate}
-    \item Likelihood fits do not always converge. \fred{Why? Mismodelling? Expand!}
-    \item Using the method at hand, the joint probability distribution of the
+    \item Likelihood fits have convergence problems for a small number of
+        events, and can require reparametrizations and/or approximations
+        for a successful fit to the signal PDF, see e.g. \cite{Egede:2008uy}.
+        The method of moments has no such convergence problems.
+    \item The results of likelihood fits suffer from systematic uncertainties
+        and systematic bias (see e.g. \cite{Egede:2008uy}), especially in but not limited
+        to cases in which the PDFs do not faithfully model the underlying physics. We will
+        show that the method of moments does not suffer a very particular type of
+        mismodelling that arises from introducing a cutoff in a partial wave expansion.
+    \item Using the method of moments, the joint probability distribution of the
         angular observables converges towards a multivariate normal distribution.
-        This allows easy transfer of information from the experiment to interest
-        theorists.
+        This allows an easy transfer of correlation information from the experiments to
+        interested theorists.
 \end{enumerate}
@@
 \end{equation}
-due to the strong law of large numbers for $K \to \infty$ assuming
+due to the strong law of large numbers for $K \to \infty$, assuming
 that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
@@
 small,
+
 \begin{equation}
-    \est{\operatorname{Skew}}[\aver{S_i},\aver{S_j}] \ll 1\,\,\text{ and }\,\,\est{\kurt}[\aver{S_i},\aver{S_j}] \ll 1\,.
+    \est{\operatorname{Skew}}[\aver{S_i},\aver{S_j}] \leq B_S\,\,\text{ and }\,\,\est{\kurt}[\aver{S_i},\aver{S_j}] \leq B_K\,.
 \end{equation}
+where the limits $B_S$ and $B_K$ should be determined from process-specific, dedicated toy studies.\\
 
@@
   situation is undesirable for both experimentalists and theorists.
+  \danny{Two comments:
+      \begin{itemize}
+      \item We should tune down the ``data privacy'' line of thought. LHCb
+      actively works on providing the full likelihood to theorists.
+      Rather, we should emphasize that providing the likelihood
+      as obtained from the ML-fit is technically much harder (think: profile likelihood,
+      since the theorists are not interested in control channels, \dots)
+      \item The constraints as described here are \emph{theoretical}
+      in nature! If one changes the PDF (e.g. in $B\to K^*\ell^+\ell^-$,
+      higher partial waves will have an impact on the shape of the
+      \emph{physical region}. Thus, imposing these constraints should
+      not be done on the side of the experiment.
+      \end{itemize}
+  }
 \end{enumerate}
@@
 However, in several interesting processes we might only have an approximative result for $P$.
-In this section, we take the interesting class of four-body decays $B\to P_1 P_2 \ell_1 \bar\ell_2$
-as an example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B \to K\pi\ell^+\ell^-$, and
+In this section we focus on one particular class of mismodelling of the signal PDF: the angular
+momentum-cutoff in partial wave expansions. This mismodelling potentially affects a large
+number of decays and scattering processes. For the sake of clarity we take the interesting class
+of four-body decays $B\to P_1 P_2 \ell_1 \bar\ell_2$ as an example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B \to K\pi\ell^+\ell^-$, and
 the $V_{ub}$ suppressed decay $B\to \pi\pi\ell^+\bar\nu_\ell$. For both examples the PDF $P$ is known in
@@
 and for $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$ \cite{Faller:2013dwa}. For a first study of $S$, $P$
-and $D$ interference, see \cite{Das:2014sra}}.%
-The PDFs for these decays are usually expressed in terms of one or a few partial waves
-of the dimeson system. However, the angular momentum of the dimeson system is unbounded from above.
-\\
+and $D$ interference, see \cite{Das:2014sra}}.\\
 
-For the selected class of decays, we face the problem that $P$ has a given dependence on the dilepton
+Within existing analyses, the PDFs for these decays are usually expressed in terms of one or a few
+partial waves of the dimeson system. However, the angular momentum of the dimeson system is unbounded
+from above, and gives rise to an infinite set of angular observables.\\
+
+For the selected class of decays, we can describe that problem as follows: The PDF $P$ has a fixed dependence on the dilepton
 helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokpill} for details
-on the angular distribution.) However, on the level of decay amplitudes the dimeson system can have an arbitrary
-large total angular momentum $j$; only its third component is restricted to $m = -1,0,+1$.\\
-
+on the angular distribution.) However, on the level of decay amplitudes the dimeson system can have an arbitrarily
+large total angular momentum $j$; only its third component is restricted to $m = -1,0,+1$.
 We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(|m|)}$
@@
 \end{equation}
-where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}, and we have
+where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
+example we have (cf. also \refapp{btokpill})
 \begin{equation}
@@
 \end{equation}
-The angular observables $S_{k,j}$ defined as coefficients of this expansion
+The angular observables $S_{k,j}$ defined as coefficients of this expansion in Legendre polynomials
 have the merit of a well-defined total angular momentum, and thus are physically discriminable.
 As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
-partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section.\\
+partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. To wit,
+ignoring further (orthogonal) terms in the PDF cannot affect the mean vector $(\dots, S_k, \dots)$ nor its variance.\\
 
@@
 We wish to emphasize, however, that detector acceptance effects systematically affect the expansion for any basis
-of angular functions. The means to cope with this problem are discussed in the following subsection.
+of angular functions, including the one suggested in this section. The means to cope with this problem are discussed
+in the following subsection.
 
-\subsection{Detector Acceptance Effects}
+\subsection{Recipe for the Determination of Detector Acceptance Effects}
 \label{sec:systematics:acceptance}
 
-\paragraph{Recipe to determine the acceptance effects}
-
-The determination of detector acceptance is generally a difficult
+The determination of a detector's angular acceptance is generally a difficult
 task. Here, we will show a systematic method to estimate its effects
 based on both the method of moments, and MC simulations of the
-detector.
+detector.\\
 
-\fred{In the ideal case, one would have an explicit probabilistic
+In the ideal case, one would have an explicit probabilistic
 model of the detector acceptance effects and could thus write down
-  the full forward model of the measured events arise. In practice,
+the full forward model from which the measured events arise. In practice,
 this would require much more CPU time than available, and one is
@@
 events $\lbrace x^{(k)}_d\rbrace = \lbrace(\vec{\nu}^{(k)}_d,
-  \vec\theta^{(k)}_d)\rbrace$.
+\vec\theta^{(k)}_d)\rbrace$.\\
 
-[Where does the reconstruction uncertainty enter? Below we just
-  account for systematic shifts but our estimate of the uncertainty of
-  one $S_k$ would be only the statistical uncertainty from the finite
-  sample size. How about the extra correlation between different $S_k$
-  that is induced?] }\\
-
-As before, we assume a PDF $P$ can be decomposed into $N$ parts with angular observables $\lbrace S_k\rbrace$,
+As before, we assume the PDF $P$ can be decomposed into $N$ parts with angular observables $\lbrace S_k\rbrace$,
 \begin{equation}
@@
     \label{eq:linear-assumption}
-    \est{S_i} = \sum_{i = 1}^N M_{i j} S_j^\text{true}\,.
+    \est{S_i} = \sum_{j = 1}^N M_{i j} S_j^\text{true}\,.
 \end{equation}
 This assumption is based on a smooth angular acceptance function. While this will not be true for the laboratory frame,
-smoothness may be recovered in boosted frame, e.g. the rest frame of the decaying particle.
+smoothness may be recovered in a boosted frame, e.g. the rest frame of the decaying particle.
 In that case, the matrix $M_{ij}$ can be fully determined through the following steps.
@@
     \item For a fixed $j$, let $S_j^\text{true} = 1$, and $S_k^\text{true} = 0\,\forall k\neq j$.
-    \item Draw simulated events $\lbrace x_t^{(k)}\rbrace = \lbrace(\vec{\nu}^{(k)}_t,\vec\theta^{(k)}_t)\rbrace$ (dubbed ``true'') from the PDF $P_j$,
+    \item Draw simulated events $\lbrace x_t^{(k)}\rbrace = \lbrace(\vec{\nu}^{(k)}_t,\vec\theta^{(k)}_t)\rbrace$ from the PDF $P_j$,
         \begin{equation}
@@
         events $\lbrace x^{(k)}_d\rbrace = \lbrace(\vec{\nu}^{(k)}_d,\vec\theta^{(k)}_d)\rbrace$.
-    \item Use the method of moments to determine the uncorrected observables $\lbrace \est{S_k} \rbrace$, based on the detector
-        events $\lbrace x^{(k)}_d\rbrace$.
+    \item Determine the uncorrected observables $\lbrace \est{S_k} \rbrace$ based on the detector
+        events $\lbrace x^{(k)}_d\rbrace$. For all intents and purposes, automation of this step is only feasible
+        with to the method of moments, since it does not suffer form convergence problems.
     \item By virtue of \refeq{linear-assumption} and step 1, the $j$-th column of $M$ has been determined via
@@
         \end{equation}
-        \fred{I wonder if a small sample size also leads to artificial
-          nonzero off-diagonal elements of $M$}
     \item Repeat the above steps for all values of $j$ to determine all columns of $M$.
@@
 
-We emphasize that this methods hinges on the assumption in \refeq{linear-assumption}, We thus suggest to explicitly
-test the assumption. One way of testing involves repeating the previous procedure
-with $S_j^\text{true} = 1/x$. If the lineary assumption holds, one should find
+We emphasize that this methods hinges on the assumption in \refeq{linear-assumption}; we thus suggest to explicitly
+test the linearity. One way of testing involves repeating the previous procedure
+with $S_j^\text{true} = 1/z$, $z > 0$. If the linearity assumption holds, one should find
 \begin{equation}
-    M_{ij} = x \est{S_i}\,,
+    M_{ij}(z) = z \est{S_i}\,,
 \end{equation}
-for arbitrary values of $x > 1$.
+for a fixed value of $j$.
 
@@
 bin widths: $1\GeV^2$ and $0.5\GeV^2$. This is to ensure that a wide spectrum of possible values for
-the angular observables. We find:
+the angular observables.\\
+
+Our finding can be summarized as follows:
 \begin{itemize}
     \item In all studied cases we observed not a single bias in the pull distribution of the observable.
-    \item The error $\sigma_k(N)$ of an angular observable $S_k$, evaluate for $N$ events is very well
-        fitted by
+        All pull distributions can successfully be fitted to a gaussian distribution. As an example, we
+        show the pull distributions for the observables $S_5$ and $S_7$ for a SM-like $B\to K^*\ell^+\ell^-$
+        decays in \reffig{pulls}.
+    \item We study the absolute uncertainty $\sigma_k(N)$ with respect to the angular observable $S_k$
+        as a function of the number of simulated events $N$. As expected for a multivariate gaussian
+        distribution, we find that the absolute uncertainty is well fitted by
         \begin{equation}
@@
         \end{equation}
-        with $\sigma_k(1) = \order{1}$.
+        with $\sigma_k(1) = \order{1}$, regardless of the size of $S_k$. The latter can best be shown
+        for the uncertainties of two exampular observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
+        for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
+    \item For all toy studies, we produce plots of their Skewness and their Kurtosis as functions of
+        $N$. We find in all cases that the distributions agree. 
     \item \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of $N$.}
-    \item \todo{Perform Mardia's Skewness and Kurtosis tests.}
     \item \dots
@@
         \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-                \includegraphics[width=0.8\textwidth]{figs/Q2_5_6_S5.png}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
-                \includegraphics[width=0.8\textwidth]{figs/Q2_5_6_S7.png}
-        \end{subfigure}
+            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S5_200.png}
+            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
+        \caption{Pull distribution for the angular observables $S_5$ and $S_7$, extracted from $200$ simulated events of the decay $B\to K^*\ell^+\ell^-$.
+The red curve represents a fit to a gaussian distribution.}
+        \label{fig:pulls}
+\end{figure}
+
+\begin{figure}[t]
+        \centering
+            \includegraphics[width=0.45\textwidth]{figs/error-Q2_5_6_S5.png}
+            \includegraphics[width=0.45\textwidth]{figs/error-Q2_5_6_S7.png}
         \caption{Uncertainty of the angular observables $S_5$ and $S_7$, extracted from simulated events of the decay $B\to K^*\ell^+\ell^-$ and as a function of the number of simulated events $N$.

### 2014-08-11 draft.tex
Polish stats section

@@
 \let\eps\varepsilon
+\newcommand{\vecest}[1]{\widehat{\vec{#1}}}
 \newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
@@
     \item Using the method of moments, the joint probability distribution of the
-        angular observables converges towards a multivariate normal distribution.
+        angular observables converges towards a multivariate Gaussian distribution.
         This allows an easy transfer of correlation information from the experiments to
@@
 
-It is sensible to refer to the angular observable $S_i$ as the \emph{$f_i$-moment} of the PDF $P$.
-We emphasize that a relation of type \refeq{det-Pi-analytical} holds for any combination of
-scalar product and orthonormal basis of angular functions $\lbrace f_i \rbrace$; \ie, there is no unique
+It is sensible to refer to the angular observable $S_i$ as the
+\emph{$f_i$-moment} of the PDF $P$.  We emphasize that a relation of
+type \refeq{det-Pi-analytical} holds for any combination of a density
+written as in \refeq{def-P} and an orthonormal basis of angular
+functions $\lbrace f_i \rbrace$; \ie, there is no unique
 basis of angular functions. For the proof we refer to ref. \cite{Dighe:1998vk}.\\
-In addition, integration over the non-angular variables yields
+
+Integration over the non-angular variables yields
 \begin{equation}
@@
 \begin{equation}
-    E_P[g] \equiv \int \rmdx{x} P(x) g(x)
+    E_P[g] \equiv \int \rmdx{x} P(x) g(x),
 \end{equation}
@@
 \end{equation}
-It is often of interest to obtain the $\nuvec$- observables integrated
-over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
-S_i\rangle$.
-Therefore, we introduce the bin-integrated quantity
+It is often of interest to obtain observables integrated over certain
+bins of $\nuvec$. We define
 \begin{align}
     \langle S_i\rangle_{\vec{a},\vec{b}}
-    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
+    & \equiv \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
     & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} P(\nuvec,\thvec) \dual{f}_i(\thvec)  \right]\\
@@
 \end{equation}
-This reduces the estimation of $\aver{S_i}_{\vec{a},\vec{b}}$ to a
-(weighted) counting experiment. In the limit $N \to \infty$, the
+For notational simplicity, let us forget about the $\nuvec$
+integration and consider only $S_i$. In the limit $K \to \infty$, the
 central limit theorem (CLT) implies that the random vector
@@
   \label{eq:angular-obs-vec}
-  \widehat{\vec{S}_{\vec{a},\vec{b}}} \equiv (\aver{S_1}_{\vec{a},\vec{b}}\,, \dots, \aver{S_i}_{\vec{a},\vec{b}}\,,
+  \vecest{S} \equiv (S_1, \dots, S_i\,,
   \dots)
 \end{equation}
- follows a multivariate Gaussian distribution whose mean vector
-is approximated by \refeq{bin-importance} and whose covariance is
-estimated as
+follows a multivariate Gaussian distribution $\mathcal{N}( \vec{S},
+\widehat{\Sigma})$ centered on the true value $\vec{S}$ with a
+covariance estimated as
 \begin{equation}
-    \cov[\aver{S_i},\aver{S_j}]_{\vec{a},\vec{b}} \to \est{\cov}[\aver{S}_i, \aver{S}_j]_{\vec{a},\vec{b}}
-        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\dual{f}_i(x^{(k)}) - \est{\langle S_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\dual{f}_j(x^{(k)}) - \widehat{\langle S_j\rangle_{\vec{a},\vec{b}}}\big]
-        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
+    \cov[S_i,S_j] \to \est{\cov}[{S}_i, {S}_j]
+        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\dual{f}_i(x^{(k)}) - \est{ S_i}\big]\,\big[\dual{f}_j(x^{(k)}) - \widehat{ S_j}\big]\,.
 \end{equation}
@@
 \begin{equation}
-    \est{\operatorname{Skew}}[\aver{S_i},\aver{S_j}] \leq B_S\,\,\text{ and }\,\,\est{\kurt}[\aver{S_i},\aver{S_j}] \leq B_K\,.
+    \est{\operatorname{Skew}}[S_i,S_j] \leq B_S\,\,\text{ and }\,\,\est{\kurt}[S_i,S_j] \leq B_K\,.
 \end{equation}
-where the limits $B_S$ and $B_K$ should be determined from process-specific, dedicated toy studies.\\
+where the limits $B_S$ and $B_K$ should be determined from process-specific dedicated toy studies.\\
 
@@
 \begin{enumerate}
-\item The angular observable $\aver{S_i}$ can be determined
-  independently of any other observable $\aver{S_j}$. It is therefore
+  \item The angular observable ${S_i}$ can be determined
+  independently of any other observable ${S_j}$. It is therefore
   much more robust to physics assumptions needed to define the full
   likelihood. In particular, this means one does not have to be
-  specific regarding the form of new-physics contributions.
+  specific regarding the form of new-physics contributions; in fact,
+  one does not even need to be able to explicitly formulate the
+  likelihood at all.
 \item It is superior for a small number of samples $N$. Likelihood
@@
   smaller than those from the method of moments.
-\item The approximate normal distribution allows easier and more
-  correct transfer of the information in the data to interested
-  theorists for more accurate fits of standard-model and new-physics
-  parameters \citeneeded\fred{Our fits and others'?} or for more precise predictions of
-  optimized observables; e.g.,
+  \item The approximate multivariate Gaussian distribution of $\vecest{S}$
+  allows easier and more correct transfer of the information in the
+  data to interested theorists for more accurate fits of
+  standard-model and new-physics parameters \citeneeded\fred{Our fits
+    and others'?} or for more precise predictions of optimized
+  observables; e.g.,
   \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
@@
   in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
-  likelihood also approaches a multivariate Gaussian as $N \to
+  likelihood also approaches a multivariate Gaussian as $K \to
   \infty$, the two methods differ in their utility as input for
-  theorists if $\widehat{\vec{S}_{\vec{a},\vec{b}}}$ is not well
+  theorists if $\widehat{\vec{S}}$ is not well
   inside the physical region. For example, suppose there are two
@@
   phase-space or unitarity arguments as \fred{Could add a sketch. It
-    is supposed to resemble $A_{\text{FB}},F_L$ for $B \to K^* \ell \ell$.}
+    is supposed to resemble $A_{\text{FB}},F_L$ for $B \to K^* \ell
+    \ell$.}
   \begin{equation}
@@
   \end{equation}
-  It may (and often does) happen in practice that
-  $\widehat{\vec{S}_{\vec{a},\vec{b}}}$ is close or even outside the
-  allowed region such that a significant part of the probability mass
-  of $\vec{S}$ covers unphysical values. In a Bayesian fit, one would
-  take $\mathcal{N}(\vec{S} | \widehat{\vec{S}_{\vec{a},\vec{b}}},
+  It may (and often does) happen in practice that $\widehat{\vec{S}}$
+  is close or even outside the allowed region such that a significant
+  part of the probability mass covers unphysical values. In a Bayesian
+  fit, one would take $\mathcal{N}(\vecest{S} | \vec{S},
   \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
-  simply set a uniform prior on the triangle defined by
-  \refeq{constr-ex} to have a well defined problem. This could be
-  trivially combined with other independent information in a global
-  fit. For a likelihood fit, the constraint needs to be built in by
-  the experiment into the analysis of the actual events and the
+  simply set a uniform prior on the triangle in the $\vec{S}$ plane
+  defined by \refeq{constr-ex} to have a well defined problem. This
+  could be trivially combined with other independent information in a
+  global fit. Someone with a different physics model might have to
+  consider a
+  different physical region, and could incorporate it just as easily.\\
+
+  For a likelihood fit, the constraint needs to be part of the
+  analysis performed by the experimental collaboration, and the
   resulting likelihood as a function of $\vec{S}$ is distinctly not
-  Gaussian. Since experimental collaborations as a whole tend to favor
-  data-privacy over accurate use of their results in theorist's
-  analyses, the multivariate likelihood is kept secret, and cannot be
-  recovered from the numerical value of $\vec{S}$ and the standard
-  errors reported in written publications. The theorist then usually
-  includes the results as independent measurements with a Gaussian
-  distribution and disregards the constraint altogether. This last
-  situation is undesirable for both experimentalists and theorists.
-  \danny{Two comments:
-      \begin{itemize}
-      \item We should tune down the ``data privacy'' line of thought. LHCb
-      actively works on providing the full likelihood to theorists.
-      Rather, we should emphasize that providing the likelihood
-      as obtained from the ML-fit is technically much harder (think: profile likelihood,
-      since the theorists are not interested in control channels, \dots)
-      \item The constraints as described here are \emph{theoretical}
-      in nature! If one changes the PDF (e.g. in $B\to K^*\ell^+\ell^-$,
-      higher partial waves will have an impact on the shape of the
-      \emph{physical region}. Thus, imposing these constraints should
-      not be done on the side of the experiment.
-      \end{itemize}
-  }
+  Gaussian.  For experimentalists, communicating such a result has
+  proved to be challenging due to technical reasons (data formats,
+  size etc.) and the fear that theorists misinterprete the many
+  nuisance parameters (from control channels, detector calibrations
+  etc.) that are also part of the likelihood. This leads to the
+  undesirable situation that that only the mode and standard errors
+  are reported, and theorists often include the results as independent
+  measurements with a Gaussian distribution and disregard the boundary
+  problem altogether.
+
 \end{enumerate}
@@
 
+\fred{$N$ used for the symbol $K$ of section I and II}
 Our finding can be summarized as follows:
@@
 We find that all of the above results show consistenly convergence of the distribution for the angular observables
-towards a multivariate normal distribution.
+towards a multivariate Gaussian distribution.
 

### 2014-08-27 draft.tex
Address issue pointed out by one of Nico's postdocs
More work on Sec IV and a first attempt at writing a conclusion

@@
 \begin{equation}
-    \wwhat{S_i} = \left(M^{-1}\right)_{ij} \est{S_j}\,.
+    \wwhat{S_i} = \danny{N_\eps} \left(M^{-1}\right)_{ij} \est{S_j}\,.
 \end{equation}
+\danny{Here $N_\eps$ is a normalization factor based on the detector acceptance function $\eps$. It emerges
+    since the product $P(x) \eps(x)$ is not a PDF; it is not normalized appropriately\footnote{We thank
+    X.X\danny{Marcin: Please insert whathisname} for pointing this out.}. We can determine $N_\eps$ by
+    imposing
+    \begin{gather}
+        1 \equiv \int \rmdx{x} P(x | \lbrace \wwhat{S}_k\rbrace) = N_\eps \sum_{k,j} \left(M^{-1}\right)_{kj} \est{S_j}\int \rmdx{x} f_k(x)\,,\\
+        \Rightarrow N_\eps \equiv \frac{1}{\sum_{k,j} \left(M^{-1}\right)_{kj} \est{S_j} \int \rmdx{x} f_k(x)}\,.
+    \end{gather}
+}
 
-We emphasize that this methods hinges on the assumption in \refeq{linear-assumption}; we thus suggest to explicitly
+We emphasize that this method hinges on the assumption in \refeq{linear-assumption}\danny{which is well motivated:
+the PDF is a linear combination of the basis functions $f_i$, and the moments are therefore a linear
+functional of said basis functions. Nevertheless,}
+we thus suggest to explicitly
 test the linearity. One way of testing involves repeating the previous procedure
@@
 for a fixed value of $j$.
+
+\danny{In order to better understand the detector aceptance effects, we propose two steps. For the sake of
+    clarity of our argument, we assume in the following that the PDF $P$ is expanded in products of
+    appropriately chosen Legendre polynomials to some multi-index order $\vec{l}_P^{(0)}$. Similarly,
+    moments and detector effects are nominally determined up to some order $\vec{l}_M^{(0)}$, with
+    $\vec{l}_M^{(0)} \leq \vec{l}_P^{(0)}$. Here and in the following all comparisons are to be read
+    for each compoenent.\\
+    For the first step, we remind that the unfolding matrix $M$ depends implicitly on the physical
+    PDF $P$. We therefore recommend variation of the order of the expansion of $P$ to $\vec{l}_P \geq \vec{l}_P^{(0)}$
+    component-wise. This way one can estimate the mixing of PDF terms of order $\vec{l}_P$ into moments of order $\vec{l}_M^{(0)}$
+    or lower.\\
+    In a second step, we assume using the nominal expansion of the PDF up to order $\vec{l}_P^{(0)}$.
+    With moments of order $\vec{l}_M \geq \vec{l}_M^{(0)}$ one can therefore find the impact of the
+    acceptance effects on the mixing of moments of order $\vec{l}_M^{(0})$ and below
+    into moments beyond the order of the PDF.
+    Our recommendation is not illustrated at the hand of numerical examples, which would necessitate
+    access to realistic detector models. The latter are not available to persons outside the
+    respective collaborations. The proposed studies are therefore beyond the scope of this work.
+}
 
@@
         decays in \reffig{pulls}.
-    \item We study the absolute uncertainty $\sigma_k(N)$ with respect to the angular observable $S_k$
-        as a function of the number of simulated events $N$. As expected for a multivariate gaussian
+    \item We study the absolute uncertainty $\sigma_k(K)$ with respect to the angular observable $S_k$
+        as a function of the number of simulated events $K$. As expected for a multivariate gaussian
         distribution, we find that the absolute uncertainty is well fitted by
@@
         \end{equation}
-        with $\sigma_k(1) = \order{1}$, regardless of the size of $S_k$. The latter can best be shown
+        with $\sigma_k(1) = \order{1}$, regardless of the absolute size of $S_k$. The latter can best be shown
         for the uncertainties of two exampular observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
         for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
-    \item For all toy studies, we produce plots of their Skewness and their Kurtosis as functions of
-        $N$. We find in all cases that the distributions agree.
-    \item \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of $N$.}
-    \item \dots
+    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
+        $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
+        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $K$.}
 \end{itemize}
-We find that all of the above results show consistenly convergence of the distribution for the angular observables
-towards a multivariate Gaussian distribution.
+We find that all of the above results show consistently that the joint distrbution of the angular observables
+converges towards a multivariate Gaussian distribution. We propose to describe the resulting distribution as
+a multivariate Gauss when skewness and kurtosis are small enough. The precise targets for these quantities
+are subject to the details of the physical analysis, and therefore outside the scope of our work.
 
@@
 
+{\textbf{[dvd: can the following be removed?]}
 We used the simulated events and fitted a likelihood function to them.
@@
 converge. Why exactly doesn't it converge? What if physics model
-wrong, say some angular terms are missing.}
+wrong, say some angular terms are missing.}}
 
@@
 
-In this letter \dots
-\begin{enumerate}
-    \item errors on the means are in very good approximation gaussian.
-    \item correlation are small and faithfully model a multivariate gaussian. \fred{$\Rightarrow$ easy transfer of knowledge to theory fits}
-\end{enumerate}
+We have carried out a combined analytical and numerical study of the method of moments; a method for
+the extraction of angular observales from the angular distribution of a generic multi-body process.
+We have studied the performance of the method of moments using pseudo data derived from the SM
+predctions for one uniangular decay ($B\to K\ell^+\ell^-$) and one triangular decay ($B\to K^*\ell^+\ell^-$).
+From this, we find rapid convergence of the joint likelihood of the angular observables towards a multivariate Gaussian.
+We draw the conclusion that this method exhibits several benefits in the determination of angular observables when
+compared with a maximum-likelihood fit.\\
+
+First, we find no bias in the determinations of the angular observables even for a small number of events.
+However, this comes at the expense of a slight increase of the order of $10\%$ for the statistical uncertainty
+on the mean.
+Second, in the absence of acceptance effects, a determination using the method of moments is correct and unbiased
+even when not all aspects of the physical distribution are modelled. This is explicitl shown for the case of
+higher partial waveds in multibody final states.
+Third, we develop a systematic method for the dertermination of detector acceptance effects that lead to
+dilution and mixing of the angular observables. We present a way to calculate the necessary unfolding matrix,
+which is only computationally feasible when using the method of moments.\\
+Fourth, the fact that the joint distribution of the results is Gaussian allows for an easy transfer of correlation
+information to theory analyses.
+Last but not least, the resulting distribution arises without additional constraints necessary for the convergence
+of some maximum-likelihood fits. Therefore the results can be directly combined with similarly-obtained results from
+a different experiment, without the need to remove the constraints of measurements that stem from different experiments.\\
+
+In conclusion, we argue that the method of moments is a competetive alternative to maximum-likelihood fits as long
+as angular distributions are involved. We wish to raise the interesting prospect of extending this very method to
+applications with non-angular orthogonal bases for the PDF.
 
@@
 The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).
-\dots
+We would like to thank Ulrik Egede and Konstantinos Petridis for insightful discussions.
 \danny{Potential people to read the manuscript: Jochen Dingfelder (Belle-II, Bonn), Ulrik Egede (LHCb, Imperial London), Christoph Langenbruch (LHCb, Warwick), Michel De Cian (LHCb, Heidelberg), Adrian Bevan (ATLAS, Queen Mary)  }

### 2014-08-27 draft.tex
Some followup on Sec. IV

@@
     since the product $P(x) \eps(x)$ is not a PDF; it is not normalized appropriately\footnote{We thank
-    X.X\danny{Marcin: Please insert whathisname} for pointing this out.}. We can determine $N_\eps$ by
+    X.X\danny{Marcin: Please insert whatshisname} for pointing this out.}. We can determine $N_\eps$ by
     imposing
@@
 
-\fred{$N$ used for the symbol $K$ of section I and II}
 Our finding can be summarized as follows:
@@
         \begin{equation}
-            \sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}
+            \label{eq:unc-on-mean}
+            \sigma_k(K) = \frac{\sigma_k(1)}{\sqrt{K}}
         \end{equation}
@@
             \includegraphics[width=0.45\textwidth]{figs/error-Q2_5_6_S7.png}
-        \caption{Uncertainty of the angular observables $S_5$ and $S_7$, extracted from simulated events of the decay $B\to K^*\ell^+\ell^-$ and as a function of the number of simulated events $N$.
-The red curve represents a fit to the function $\sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}$.}
+            \caption{Uncertainty of the angular observables $S_5$ and $S_7$, extracted from simulated events of the decay $B\to K^*\ell^+\ell^-$ and as a function of the number of simulated events $K$.
+The red curve represents a fit to the function given in \refeq{unc-on-mean}.}
         \label{fig:errors}
@@
 
-{\textbf{[dvd: can the following be removed?]}
+\hrulefill\\
+{\textbf{\color{red}[dvd: can the following be removed?]}
 We used the simulated events and fitted a likelihood function to them.
 \begin{itemize}
-    \item For a small number of simulated events, \danny{$N=?$}, we observe a significant bias in the pull distributions.
-    \item For a large number of simulated events, \danny{$N=?$}, the uncertainty of the angular observables is
+    \item For a small number of simulated events, \danny{$K=?$}, we observe a significant bias in the pull distributions.
+    \item For a large number of simulated events, \danny{$K=?$}, the uncertainty of the angular observables is
         smaller compared to the results of the method of moments.
 \end{itemize}
-\todo{compare robustness to likelihood fit when fit doesn't
+todo: compare robustness to likelihood fit when fit doesn't
 converge. Why exactly doesn't it converge? What if physics model
-wrong, say some angular terms are missing.}}
+wrong, say some angular terms are missing.}
+\hrulefill
 

### 2014-10-20 draft.tex
[draft] Some comments and notes

@@
 \usepackage{hepunits}
+\usepackage{hyperref}
 \usepackage{graphicx}
@@
 \end{equation}
-The remainder of this section describes the method of moments, in which we replace the
-analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\
-
-The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
-$g(x)$ under the probability density $P(x)$,
+The remainder of this section describes the method of moments, in
+which we replace the analytical integration by Monte Carlo (MC)
+estimates.  The central tenet of MC integration is the fact that the
+expectation value $E_P[g]$ of some function $g(x)$ under the
+probability density $P(x)$,
 \begin{equation}
@@
 \end{equation}
-can be approximated \cite{MCSM-2004} by the consistent and unbiased
+can be approximated by the consistent and unbiased
 estimator $\est{E_P[g]}$~\cite[sec. 8.2]{James:2006zz}
@@
 due to the strong law of large numbers for $K \to \infty$, assuming
-that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
+that the variates $x^{(k)}$, $k = 1, \dots, K$, are distributed as
 $P$.
@@
 follows a multivariate Gaussian distribution $\mathcal{N}( \vec{S},
-\widehat{\Sigma})$ centered on the true value $\vec{S}$ with a
-covariance estimated as
+\widehat{\Sigma})$ centered on the true value $\vec{S}$ with the
+covariance $\widehat{\Sigma}_{ij}$ estimated as
 \begin{equation}
@@
   measurements with a Gaussian distribution and disregard the boundary
-  problem altogether.
+  problem as well as correlations altogether.
 
@@
 
-In \refsec{sample-based-det}, we assume that the PDF $P$ describe the underlying physics accurately,
+In \refsec{sample-based-det}, we assume that the PDF $P$ describes the underlying physics accurately,
 and that the experiment observes each event with perfect accuracy. In order to estimate systematic
@@
     \includegraphics[width=.6\textwidth]{fig-topology.pdf}
-    \caption{Decay topology for decays $B\to P_1 P_2 \ell_1 \bar\ell_2$. \label{fig:topology}}
+    \caption{Decay topology for decays $B\to P_1 P_2 \ell_1 \bar\ell_2$. \label{fig:topology}\fred{We should use the same symbol $\theta$ as in text}}
 \end{figure}
 
-So far, we assumed that our underlying physical process was accurately described by our PDF $P$.
-However, in several interesting processes we might only have an approximative result for $P$.
-In this section we focus on one particular class of mismodelling of the signal PDF: the angular
-momentum-cutoff in partial wave expansions. This mismodelling potentially affects a large
-number of decays and scattering processes. For the sake of clarity we take the interesting class
-of four-body decays $B\to P_1 P_2 \ell_1 \bar\ell_2$ as an example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B \to K\pi\ell^+\ell^-$, and
-the $V_{ub}$ suppressed decay $B\to \pi\pi\ell^+\bar\nu_\ell$. For both examples the PDF $P$ is known in
-the small-width approximation and when assuming a pure $P$-wave, resonant final state. An extension to
-$S-P$ interference has been studied for $B\to K\pi\ell^+\ell^-$ \cite{Blake:2012mb,Becirevic:2011bp},
-and for $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$ \cite{Faller:2013dwa}. For a first study of $S$, $P$
+In several interesting processes we might only have an approximate
+result for $P$.  In this section, we focus on one particular class of
+mismodelling of the signal PDF: the angular momentum-cutoff in partial
+wave expansions. This mismodelling potentially affects a large number
+of decays and scattering processes. For the sake of clarity we take
+the interesting class of four-body decays $B\to P_1 P_2 \ell_1
+\bar\ell_2$ \fred{How general is this? The plot implies that the
+  dimeson and the dilepton do not have a common vertex. But this
+  requires an intermediate state, e.g., $K^{*}$}as an
+example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B
+  \to K\pi\ell^+\ell^-$, and the $V_{ub}$ suppressed decay $B\to
+  \pi\pi\ell^+\bar\nu_\ell$. For both examples the PDF $P$ is known in
+  the small-width approximation and when assuming a pure $P$-wave,
+  resonant final state. An extension to $S-P$ interference has been
+  studied for $B\to K\pi\ell^+\ell^-$
+  \cite{Blake:2012mb,Becirevic:2011bp}, and for $\bar{B}\to
+  \pi\pi\ell^-\bar\nu_\ell$ \cite{Faller:2013dwa}. For a first study
+  of $S$, $P$
   and $D$ interference, see \cite{Das:2014sra}}.\\
 
-Within existing analyses, the PDFs for these decays are usually expressed in terms of one or a few
+Within existing analyses, the PDFs of these decays are usually expressed in terms of one or a few
 partial waves of the dimeson system. However, the angular momentum of the dimeson system is unbounded
@@
 helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokpill} for details
-on the angular distribution.) However, on the level of decay amplitudes the dimeson system can have an arbitrarily
-large total angular momentum $j$; only its third component is restricted to $m = -1,0,+1$.
+on the angular distribution.) However, at the level of decay amplitudes the dimeson system can have an arbitrarily
+large total angular momentum $j$; only its third component is restricted to $m = -1,0,+1$. \fred{check}
 We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(|m|)}$
 with respect to the remaining angle $\theta_2$. Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
-and as defined in \refapp{partial-waves}, the expansion reads
+and as defined in \refapp{partial-waves} \fred{A lot of mixing between appendices C and E}, the expansion reads
 \begin{equation}
@@
 The angular observables $S_{k,j}$ defined as coefficients of this expansion in Legendre polynomials
-have the merit of a well-defined total angular momentum, and thus are physically discriminable.
+have the merit of a well defined total angular momentum, and thus are physically discriminable.
 As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
 partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. To wit,
-ignoring further (orthogonal) terms in the PDF cannot affect the mean vector $(\dots, S_k, \dots)$ nor its variance.\\
+ignoring further (orthogonal) terms in the PDF cannot affect the mean vector $(\dots, S_k, \dots)$ nor its variance. \fred{yes!}\\
 
 Unfortunately, this benefit on the experimental side is accompanied with a theoretical draw back. Each observable
-$S_{k,j}(\vec{\nu})$ consists of an infinite sum of bilinear of partial-wave amplitudes. It remains for theoretical
+$S_{k,j}(\vec{\nu})$ consists of an infinite sum of bilinears of partial-wave amplitudes. It remains for theoretical
 analyses to estimate or calculate the impact of partial waves beyond the S and P wave contributions.
@@
 task. Here, we will show a systematic method to estimate its effects
-based on both the method of moments, and MC simulations of the
+based on both the method of moments and MC simulations of the
 detector.\\
 
-In the ideal case, one would have an explicit probabilistic
-model of the detector acceptance effects and could thus write down
-the full forward model from which the measured events arise. In practice,
-this would require much more CPU time than available, and one is
-therefore forced to simplify the model. The standard approach is to
-generate \emph{true} particle events $\lbrace x_t^{(k)}\rbrace =
+In the ideal case, one would have an explicit probabilistic model of
+the detector acceptance effects and could thus write down the full
+forward model from which the measured events arise. In practice, this
+would require much more CPU time than available, and one is therefore
+forced to simplify the model. The standard approach is to generate
+\emph{true} particle events $\lbrace x_t^{(k)}\rbrace =
 \lbrace(\vec{\nu}^{(k)}_t,\vec\theta^{(k)}_t)\rbrace$ from a PDF
-assumed to describe the bare physical process, and to propagate
-those particles through a detailed simulation of the detector. The
+assumed to describe the bare physical process, and to propagate those
+particles through a detailed simulation of the detector. The
 observable traces that the particles leave in the detector are fed
-into reconstruction algorithms resulting in the \emph{detector}
-events $\lbrace x^{(k)}_d\rbrace = \lbrace(\vec{\nu}^{(k)}_d,
-\vec\theta^{(k)}_d)\rbrace$.\\
+into reconstruction algorithms resulting in the \emph{detector} events
+$\lbrace x^{(k)}_d\rbrace = \lbrace(\vec{\nu}^{(k)}_d,
+\vec\theta^{(k)}_d)\rbrace$.\fred{What about uncertainty in $\vec{\nu}, \vec{\theta}$? How does it enter the experimental likelihood? And how our method?}\\
 
@@
 observable $S_k$ as $\est{S_k}$, which is affected by the detector acceptance. We assume now that there is a linear relation
-between the true angular observables $\lbrace S_k^\text{true}\rbrace$, and the estimators $\lbrace \est{S_k}\rbrace$,
+between the true angular observables $\lbrace S_k^\text{true}\rbrace$, and the estimators $\lbrace \est{S_k}\rbrace$, \fred{We don't need the $^{\text true}$.}
 \begin{equation}
@@
         with $\sigma_k(1) = \order{1}$, regardless of the absolute size of $S_k$. The latter can best be shown
-        for the uncertainties of two exampular observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
+        for the example of uncertainties of two observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
         for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
@@
 
-The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts -- reads \cite{Boeer:2014xx}
+The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts --- reads \cite{Boeer:2014xx}
 \begin{equation}
@@
 
-Let $S \equiv S(\vec{\nu},\theta)$ be an observable of only one angle $\theta$ and further non-angular variables $\vec{\nu}$. Further, let
+Let $S \equiv S(\vec{\nu},\theta)$ be an observable of only one angle $\theta$ and further non-angular variables $\vec{\nu}$.
+\fred{This is confusing: in the intro, we define $S$ as independent of any angle.} \fred{What about two angles?
+More amplitudes seem trivial, one would just have more $S_i$} Further, let
 $S$ have an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
@@
 \end{equation}
-Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial-wave amplitudes must asymptotically fall off as
+Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial-wave amplitudes must asymptotically fall off as \fred{Let's say why. Unitarity?}
 \begin{equation}

### 2014-10-20 draft.tex
[draft] Add some more questions

@@
 \end{equation}
-This assumption is based on a smooth angular acceptance function. While this will not be true for the laboratory frame,
-smoothness may be recovered in a boosted frame, e.g. the rest frame of the decaying particle.
-In that case, the matrix $M_{ij}$ can be fully determined through the following steps.
+This assumption is based on a smooth angular acceptance
+function. \fred{Check the LHCb \href{http://inspirehep.net/record/1287929}{paper} on $B \to K \ell \ell$: their
+  acceptance (fig. 1) is not smooth due to a cut!} \fred{I don't understand. Need a derivation of why this hinges on smoothness} While this will not be true for
+the laboratory frame, smoothness may be recovered in a boosted frame,
+e.g. the rest frame of the decaying particle.  In that case, the
+matrix $M_{ij}$ can be fully determined through the following steps.
 \begin{enumerate}
-    \item For a fixed $j$, let $S_j^\text{true} = 1$, and $S_k^\text{true} = 0\,\forall k\neq j$.
-    \item Draw simulated events $\lbrace x_t^{(k)}\rbrace = \lbrace(\vec{\nu}^{(k)}_t,\vec\theta^{(k)}_t)\rbrace$ from the PDF $P_j$,
+    \item For fixed $j$, let $S_j^\text{true} = 1$, and $S_k^\text{true} = 0\,\forall k\neq j$.
+    \item Draw simulated events $\lbrace x_t^{(k)}\rbrace =
+      \lbrace(\vec{\nu}^{(k)}_t,\vec\theta^{(k)}_t)\rbrace$ \fred{don't use $k$ as superscript and subscript} from the PDF $P_j$,
       \begin{equation}
+        \label{eq:single-comp}
             P_j \equiv P(\vec\nu,\vec\theta | \lbrace S_j = 1, S_{k\neq j} = 0\rbrace)\,.
         \end{equation}
-    \item Use the true events as input for the MC simulation of the detector, in order to obtain the detector
+    \item Use the true events as input for the MC simulation of the detector in order to obtain the detector
         events $\lbrace x^{(k)}_d\rbrace = \lbrace(\vec{\nu}^{(k)}_d,\vec\theta^{(k)}_d)\rbrace$.
@@
 \end{equation}
-for a fixed value of $j$.
+for a fixed value of $j$. \fred{This is useless. \refeq{single-comp}
+  says: draw from a single component $f_j$. This $f_j$ defines the
+  distribution, and whatever factor you put in front of it, you get
+  the same distribution of events.}
 
@@
 \end{equation}
-We indicate contributions from the interference of S waves and P waves by an index \emph{i}. In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
+In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
 \begin{equation}

### 2014-10-21 draft.tex
[draft] some more comments and questions

@@
 \end{equation}
+\fred{since when is $S_k a fct. of \cos \theta_2$?}
 where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
@@
   \end{equation}
-\danny{Here $N_\eps$ is a normalization factor based on the detector acceptance function $\eps$. It emerges
-    since the product $P(x) \eps(x)$ is not a PDF; it is not normalized appropriately\footnote{We thank
-    X.X\danny{Marcin: Please insert whatshisname} for pointing this out.}. We can determine $N_\eps$ by
-    imposing
+  \fred{What happens to the uncertainties? Unfolding is used in many
+    places, so there are elaborate recipes. Should we assume the same
+    uncertainties as before? Since it is linear, rescaling should be sufficient. Or compute covariance directly for transformed observables} \danny{Here $N_\eps$ is a normalization factor
+    based on the detector acceptance function $\eps$. It emerges since
+    the product $P(x) \eps(x)$ is not a PDF; it is not normalized
+    appropriately\footnote{We thank X.X\danny{Marcin: Please insert
+        whatshisname} for pointing this out.}. We can determine
+    $N_\eps$ by imposing
     \begin{gather}
@@
     With moments of order $\vec{l}_M \geq \vec{l}_M^{(0)}$ one can therefore find the impact of the
-    acceptance effects on the mixing of moments of order $\vec{l}_M^{(0})$ and below
+    acceptance effects on the mixing of moments of order $\vec{l}_M^{(0)}$ and below
     into moments beyond the order of the PDF.
@@
 
+\fred{I'm puzzled. If you can do the calculation to some order
+  $\vec{l}_P$, why would you use a lower order for the actual result?
+  I.e., if you have the NNLO results, why would you limit yourself to
+  NLO?}
+
 \section{Toy Studies}
@@
 
-In order to study the performance of the proposed method, we simulate measurements for one uni-angular
-and one tri-angular decay distribution for various numbers of events. As inputs we use the SM predictions
-for the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to K\pi)\ell^+\ell^-$, respectively. We cover the
-$q^2$ ranges $1\GeV^2$ to $6\GeV^2$, and $15\GeV^2$ to to the respective kinematic endpoint, with two
-bin widths: $1\GeV^2$ and $0.5\GeV^2$. This is to ensure that a wide spectrum of possible values for
+In order to study the performance of the proposed method, we simulate
+measurements for one uni-angular and one tri-angular decay
+distribution for various numbers of events. As inputs we use the SM
+predictions for the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to
+K\pi)\ell^+\ell^-$, respectively. We cover the $q^2$ ranges $1 \GeV^2$
+to $6 \GeV^2$, and $15 \GeV^2$ to the respective kinematic endpoint,
+with two bin widths: $1\GeV^2$ and $0.5\GeV^2$. This is to ensure that
+a wide spectrum of possible values for
 the angular observables.\\
@@
 \begin{itemize}
-    \item In all studied cases we observed not a single bias in the pull distribution of the observable.
+    \item In all studied cases we observed not a single bias in the pull \fred{should define pull} distribution of the observable.
         All pull distributions can successfully be fitted to a gaussian distribution. As an example, we

### 2014-10-22 acceptance.py
Add acceptance.py to verify mathematica results in python

@@ -1,0 +1,348 @@
+'''Check the efficiency correction for the method of moments.
+
+The considered decays is like B -> K ll. Write PDF as sum over Legendre polynomials.
+
+1. Draw samples from a uniform distribution of \cos \theta, and compute integrals, then reweight by P * eps
+2. Draw from P * eps using MCMC from pypmc
+
+Both methods give similar estimates of the angular
+observables. Amazingly: 1. much simpler to implement, and yields the
+true values up to machine precision every time. How?!
+
+3. Plot the regions
+4. Optimize using nlopt
+
+'''
+from __future__ import division, print_function
+
+# import nlopt
+import numpy as np
+from numpy.polynomial.legendre import Legendre
+import pypmc
+from matplotlib import pyplot as plt
+from scipy.integrate import quad
+
+# np.random.seed(123465123)
+
+# define a proposal
+prop_dof   = 5.
+prop_sigma = np.array([[3]])
+prop = pypmc.density.student_t.LocalStudentT(prop_sigma, prop_dof)
+
+class BtoKll:
+    '''Differential decay rate of B -> K ll for fixed q^2.'''
+    def __init__(self, eps=2/3*np.array([0.6, 0.05, -0.55])):
+        '''eps: coefficients of Legendre polynomials of acceptance. Make sure it integrates to less than one.'''
+        self._accept = Legendre(eps)
+        # first 0.5 is fixed by normalization!
+        self._S = np.zeros(3)
+        self._S[0] = 0.5
+
+    def differential_rate(self, S, x):
+        # x = np.cos(theta)
+        x = np.asarray(x)
+
+        # first coefficient fixed
+        self._S[1:] = S[:]
+        P = Legendre(self._S)(x)
+
+        # A_FB, F_H = S[0], S[1]
+        # # Eq. (1) in arXiv:1403.8045v2
+        # P = 0.75 * (1. - F_H) * (1 - x**2) + 0.5 * F_H + A_FB * x
+        # ensure positive decay rate
+        if (P <= 0.0).any():
+            return -np.inf
+        return np.log(P).sum()
+
+    # def prior(self, S):
+    #     A_FB, F_H = S[0], S[1]
+    #     if abs(A_FB) > +1:
+    #         return -np.inf
+    #     if F_H < 0. or F_H > 3.:
+    #         return -np.inf
+    #     if abs(A_FB) > F_H / 2:
[…]

### 2014-10-28 draft.tex
Rewrite recipe to determine acceptance effects

@@
 an orthonormal basis. It turns out to be much more convenient to work
-in the basis natural to each process but the statistical properties
+in the basis of Legendre polynomials but the statistical properties
 are equivalent for both approaches provided that one replace $f_i \to
@@
 
-The determination of a detector's angular acceptance is generally a difficult
-task. Here, we will show a systematic method to estimate its effects
-based on both the method of moments and MC simulations of the
-detector.\\
-
-In the ideal case, one would have an explicit probabilistic model of
+The determination of a detector's performance to detect signal events
+with accurate determination of the event's angles is generally a difficult
+task. In the ideal case, one would have an explicit probabilistic model of
 the detector acceptance effects and could thus write down the full
@@
 forced to simplify the model. The standard approach is to generate
-\emph{true} particle events $\lbrace x_t^{(k)}\rbrace =
-\lbrace(\vec{\nu}^{(k)}_t,\vec\theta^{(k)}_t)\rbrace$ from a PDF
+the \emph{true} particle events $\lbrace x_\text{t}^{(n)}\rbrace =
+\lbrace(\vec{\nu}^{(n)}_\text{t},\vec\theta^{(n)}_\text{t})\rbrace$, $n=1,\dots,N_\text{t}$, from a PDF
 assumed to describe the bare physical process, and to propagate those
-particles through a detailed simulation of the detector. The
-observable traces that the particles leave in the detector are fed
+particles through a detailed simulation of the detector.
+The observable traces that the particles leave in the detector are fed
 into reconstruction algorithms resulting in the \emph{detector} events
-$\lbrace x^{(k)}_d\rbrace = \lbrace(\vec{\nu}^{(k)}_d,
-\vec\theta^{(k)}_d)\rbrace$.\fred{What about uncertainty in $\vec{\nu}, \vec{\theta}$? How does it enter the experimental likelihood? And how our method?}\\
+$\lbrace x^{(n)}_\text{d}\rbrace = \lbrace(\vec{\nu}^{(n)}_\text{d},
+\vec\theta^{(n)}_\text{d})\rbrace$, $n=1,\dots,N_\text{d}$.
+Most generally, the detected events $\lbrace x_\text{d}^{(k)}\rbrace$
+are distributed as $P_\text{d}$,
+\begin{equation}
+    P_\text{d}(x_\text{d}) = \int P_\text{t}(x_\text{t}) E(x_\text{d}, x_\text{t}) \rmdx{x_\text{t}}\,.
+\end{equation}
+Here $P$ is the probability distribution of the true events, and the kernel $E(x_\text{d}, x_\text{t})$
+parametrizes acceptance and resolution
+effects. Note that $P_\text{d}$ is \emph{not} a PDF, since it is not normalized,
+\begin{equation}
+    \int P_\text{d}(x) \rmdx{x} \neq 1\,.
+\end{equation}
+For the sake of clarity, we will restrict ourselves
+to pure acceptance effects and suppress resolution effects in the remainder of this section; i.e.,
+\begin{equation}
+    E(x_\text{d}, x_\text{t}) \equiv \eps(x_\text{t}) \delta(x_\text{d}, x_\text{t})\,.
+\end{equation}
+We will refer to $\eps$ as the \emph{detector acceptance} function. In what follows,
+we propose a systematic methods to unfold all effects of $\eps$ through MC simulations
+and the method of moments.\\
 
-As before, we assume the PDF $P$ can be decomposed into $N$ parts with angular observables $\lbrace S_k\rbrace$,
+We will now proceed with the explicit usage of a uniangular PDF with $x = \cos\theta$.\footnote{%
+    The generalization of this section to multiangular PDFs is straighforward. It can be achieved
+    by promoting $x$ to a vector, promoting the Legendre polynomials to products of independent polynomials
+    and the indices $i,j,k,m$ to multi-indices.
+}
+Let us define the PDF in terms of the Legendre polymials (i.e., $f_k(x) \equiv P_k(x)$),
 \begin{equation}
-    P \equiv P(\vec\nu,\vec\theta | \lbrace S_k \rbrace)\,.
+    P(x) \equiv \sum_k S_k f_k(x),
 \end{equation}
-We denote the estimator of an
-observable $S_k$ as $\est{S_k}$, which is affected by the detector acceptance. We assume now that there is a linear relation
-between the true angular observables $\lbrace S_k^\text{true}\rbrace$, and the estimators $\lbrace \est{S_k}\rbrace$, \fred{We don't need the $^{\text true}$.}
+where $k = 0, 1, \dots$ denotes the total angular momentum of the observables.
+From the normalization of the PDF then follows $S_0 = 1/2$. From positivity of $P$ one
+obtains $|S_k| \leq 1/2$ for angular momentum $k > 0$. More stringent relations between the
+$S_k$ might hold, but are beyond the scope of this work. For latter use, we define
+$\vec{S}^{(m)}_k \equiv 1/2 (\delta_{k,0} + \delta_{k,m})$, and we emphasize that
 \begin{equation}
-    \label{eq:linear-assumption}
-    \est{S_i} = \sum_{j = 1}^N M_{i j} S_j^\text{true}\,.
+    P^{(m)}(x) \equiv P(x | \lbrace S^{(m)}_k \rbrace)
 \end{equation}
-This assumption is based on a smooth angular acceptance
-function. \fred{Check the LHCb \href{http://inspirehep.net/record/1287929}{paper} on $B \to K \ell \ell$: their
-  acceptance (fig. 1) is not smooth due to a cut!} \fred{I don't understand. Need a derivation of why this hinges on smoothness} While this will not be true for
-the laboratory frame, smoothness may be recovered in a boosted frame,
-e.g. the rest frame of the decaying particle.  In that case, the
-matrix $M_{ij}$ can be fully determined through the following steps.
-\begin{enumerate}
-    \item For fixed $j$, let $S_j^\text{true} = 1$, and $S_k^\text{true} = 0\,\forall k\neq j$.
-    \item Draw simulated events $\lbrace x_t^{(k)}\rbrace =
-      \lbrace(\vec{\nu}^{(k)}_t,\vec\theta^{(k)}_t)\rbrace$ \fred{don't use $k$ as superscript and subscript} from the PDF $P_j$,
+is a PDF. The dual basis of angular functions follows then from the normalization
+and orthogonality of the Legendre polynomials, and one therefore has
 \begin{equation}
-        \label{eq:single-comp}
-            P_j \equiv P(\vec\nu,\vec\theta | \lbrace S_j = 1, S_{k\neq j} = 0\rbrace)\,.
+    \tilde{f}_k(x) = \frac{2 k + 1}{2} f_k(x),\qquad \int_{-1}^{+1} \tilde{f}_k(x) f_l(x) \rmdx{x} = \delta_{k,l}\,.
 \end{equation}
-    \item Use the true events as input for the MC simulation of the detector in order to obtain the detector
-        events $\lbrace x^{(k)}_d\rbrace = \lbrace(\vec{\nu}^{(k)}_d,\vec\theta^{(k)}_d)\rbrace$.
-    \item Determine the uncorrected observables $\lbrace \est{S_k} \rbrace$ based on the detector
-        events $\lbrace x^{(k)}_d\rbrace$. For all intents and purposes, automation of this step is only feasible
-        with to the method of moments, since it does not suffer form convergence problems.
-    \item By virtue of \refeq{linear-assumption} and step 1, the $j$-th column of $M$ has been determined via
+
+We now define the \emph{simulated raw} moments $\lbrace Q_{i}^{(m)}\rbrace$,
 \begin{equation}
-            M_{ij} = \est{S_i}\,.
+    Q_i^{(m)} \equiv \int_{-1}^{+1} \tilde{f}_i(x) P^{(m)}(x) \eps(x) \rmdx{x} = \frac{1}{2} \int_{-1}^{+1} \tilde{f}_i(x) \big[f_0(x) + f_m(x)\big] \eps(x) \rmdx{x}\,,
 \end{equation}
-    \item Repeat the above steps for all values of $j$ to determine all columns of $M$.
-\end{enumerate}
+which are instrumental to our recipe.
+MC estimators for these simulated moments can be constructed from specifically crafted detector events $x_\text{d}^{(n,m)}$, $n = 1, \dots, N_\text{d}^{(m)}$, where
+\begin{equation}
+    x_\text{d}^{(n,m)} \sim P_\eps^{(m)} \equiv \frac{P^{(m)} \eps}{R^{(m)}}\,.
+\end{equation}
+Here the normalization $R^{(m)}$ is chosen such that $\int P_\eps^{(m)}(x) \rmdx{x} = 1$.
+We emphasize that $R^{(m)}$ can estimated as $\est{R}^{(m)} = N_\text{d}^{(m)} / N_\text{t}$, where $N_\text{t}$ corresponds to the number of simulated true events.
+The estimators then read
+\begin{equation}
+    \est{Q}_i^{(m)} \equiv \est{R}^{(m)} \frac{1}{N_\text{d}} \sum_n^{N_\text{d}} \tilde{f}_i(x_\text{d}^{(n,m)})
+\end{equation}
 
-It remains to invert the relation \refeq{linear-assumption}, so that one can determine the unfolded
-angular observables $\lbrace \wwhat{S_k}\rbrace$ as
+Linearity of the integral over $x$ and convergence of the expansion of $P_\eps^{(m)}$ in terms Legendre polynomials ensures that
 \begin{equation}
-    \wwhat{S_i} = \danny{N_\eps} \left(M^{-1}\right)_{ij} \est{S_j}\,.
+    Q_i^{(m)} = \sum_j M_{ij} S_j^{(m)}\,.
 \end{equation}
-  \fred{What happens to the uncertainties? Unfolding is used in many
-    places, so there are elaborate recipes. Should we assume the same
-    uncertainties as before? Since it is linear, rescaling should be sufficient. Or compute covariance directly for transformed observables} \danny{Here $N_\eps$ is a normalization factor
-    based on the detector acceptance function $\eps$. It emerges since
-    the product $P(x) \eps(x)$ is not a PDF; it is not normalized
-    appropriately\footnote{We thank X.X\danny{Marcin: Please insert
-        whatshisname} for pointing this out.}. We can determine
-    $N_\eps$ by imposing
-    \begin{gather}
-        1 \equiv \int \rmdx{x} P(x | \lbrace \wwhat{S}_k\rbrace) = N_\eps \sum_{k,j} \left(M^{-1}\right)_{kj} \est{S_j}\int \rmdx{x} f_k(x)\,,\\
-        \Rightarrow N_\eps \equiv \frac{1}{\sum_{k,j} \left(M^{-1}\right)_{kj} \est{S_j} \int \rmdx{x} f_k(x)}\,.
-    \end{gather}
-}
+We call the matrix $M_{ij}$ the \emph{unfolding matrix}, which is specific to our decay at hand. Given our definition of
+$S_k^{(m)}$ it can easily be calculated as
+\begin{equation}
+    M_{ij} = \begin{cases}
+        2 Q_i^{(0)}                          & j = 0\,,\\
+        2\left(Q_i^{(j)} - Q_i^{(0)}\right)  & j \neq 0\,,\\
+    \end{cases}
+\end{equation}
+and its MC estimator $\est{M}_{ij}$  can be obtained through the replacements $Q_i^{(m)} \to \est{Q}_i^{(m)}$.\\
 
-We emphasize that this method hinges on the assumption in \refeq{linear-assumption}\danny{which is well motivated:
-the PDF is a linear combination of the basis functions $f_i$, and the moments are therefore a linear
-functional of said basis functions. Nevertheless,}
-we thus suggest to explicitly
-test the linearity. One way of testing involves repeating the previous procedure
-with $S_j^\text{true} = 1/z$, $z > 0$. If the linearity assumption holds, one should find
+In order to finally extract the angular observables from data, we use the \emph{measured raw moments}. Their MC estimator
+$\lbrace \est{Q}_i\rbrace$ -- based on the \emph{detected events} $x^{(n)}$, $n=1,\dots,N$ -- reads
 \begin{equation}
-    M_{ij}(z) = z \est{S_i}\,,
+    \est{Q}_i \equiv R \frac{1}{N} \sum_n^N \tilde{f}_i(x^{(n)})\,.
 \end{equation}
-for a fixed value of $j$. \fred{This is useless. \refeq{single-comp}
-  says: draw from a single component $f_j$. This $f_j$ defines the
-  distribution, and whatever factor you put in front of it, you get
-  the same distribution of events.}
+Here $R \equiv \int P(x) \eps(x)$ is an a priori unknown normalization that also occurs in the determination of the branching
+ratio of the specific decay. We then obtain MC estimators of the angular observables via
+\begin{equation}
+    \est{S}_i \equiv \sum_{i} \left(\hat{M}^{-1}\right)_{ij} \est{Q}_j\,.
+\end{equation}
+The precise value of $R$ depends on the a priori unknown angular observables $\lbrace S_i\rbrace$.
+However, ratios and other suitable combinations of the estimators $\lbrace \est{S}_i\rbrace$ are independent
+of $R$.
 
-\danny{In order to better understand the detector aceptance effects, we propose two steps. For the sake of
-    clarity of our argument, we assume in the following that the PDF $P$ is expanded in products of
-    appropriately chosen Legendre polynomials to some multi-index order $\vec{l}_P^{(0)}$. Similarly,
-    moments and detector effects are nominally determined up to some order $\vec{l}_M^{(0)}$, with
-    $\vec{l}_M^{(0)} \leq \vec{l}_P^{(0)}$. Here and in the following all comparisons are to be read
-    for each compoenent.\\
-    For the first step, we remind that the unfolding matrix $M$ depends implicitly on the physical
-    PDF $P$. We therefore recommend variation of the order of the expansion of $P$ to $\vec{l}_P \geq \vec{l}_P^{(0)}$
-    component-wise. This way one can estimate the mixing of PDF terms of order $\vec{l}_P$ into moments of order $\vec{l}_M^{(0)}$
-    or lower.\\
-    In a second step, we assume using the nominal expansion of the PDF up to order $\vec{l}_P^{(0)}$.
-    With moments of order $\vec{l}_M \geq \vec{l}_M^{(0)}$ one can therefore find the impact of the
-    acceptance effects on the mixing of moments of order $\vec{l}_M^{(0)}$ and below
-    into moments beyond the order of the PDF.
-    Our recommendation is not illustrated at the hand of numerical examples, which would necessitate
-    access to realistic detector models. The latter are not available to persons outside the
-    respective collaborations. The proposed studies are therefore beyond the scope of this work.
-}
-
-\fred{I'm puzzled. If you can do the calculation to some order
-  $\vec{l}_P$, why would you use a lower order for the actual result?
-  I.e., if you have the NNLO results, why would you limit yourself to
-  NLO?}
+\todo{size of $M$ in relation to the maximum angular momentum of $\eps$}
 
@@
 \begin{equation}
-    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1}} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
+    P(q^2, \cos\theta_1)
+        = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^2\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1}}
+        = \frac{a(q^2)}{\rmdx{\Gamma}/\rmdx{q^2}} + \frac{b(q^2)}{\rmdx{\Gamma}/\rmdx{q^2}} \cos\theta_1 + \frac{c(q^2)}{\rmdx{\Gamma}/\rmdx{q^2}} \cos^2\theta_1
+        = \sum_i S_i p_i(\cos\theta_1)\,,
 \end{equation}
-where the basis of angular functions $\lbrace f_i\rbrace$ reads
+with the conventional observables $a(q^2)$ through $c(q^2)$, and $\rmdx{\Gamma}/\rmdx{q^2} = 2a + 2/3 c$. We conveniently use the Legendre polynomials
+$p_i(x)$, $i=0,1,2$,
 \begin{equation}
 \begin{aligned}
-    f_1 & = 1\,, &
-    f_2 & = \cos\theta_1\,, &
-    f_2 & = \cos^2\theta_1\,.
+    p_0(x) & = 1\,, &
+    p_1(x) & = x\,, &
+    p_2(x) & = \frac{1}{2} (3x^2 - 1)\,,
 \end{aligned}
 \end{equation}
-Here we denote the dilepton mass squared as $q^2$, and the dilepton helicity angle as $\theta_1 \equiv \theta_{\ell}$. We transform the PDF from a $\cos\theta_1$-dependence
-to a $\theta_1$-dependence,
-\begin{equation}
-    P(q^2, \theta_1) = \sum_i P_i f_i(\cos\theta_1) \sin \theta_1\,.
-\end{equation}
-where we define $P_{\lbrace 1,2,3\rbrace} \equiv \lbrace a, b, c\rbrace / \Gamma$.\\
-
-The dual basis $\lbrace \dual{f}_i\rbrace$ reads
+as our basis of angular functions. Our basis of angular observables then
+translates to the conventional basis as
 \begin{equation}
 \begin{aligned}
-    \dual{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
-    \dual{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
-    \dual{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,,
+    S_0 & = \frac{1}{2}\,, &
+    S_1 & = \frac{b}{\Gamma}\,, &
+    S_2 & = \frac{2c}{3\Gamma}\,.
 \end{aligned}
 \end{equation}
+In this case, the dual basis is simply given by $\tilde{p}_i(x) = (2 i + 1)/2 p_i(x)$
 such that
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \dual{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
+    \int_0^\pi \rmdx{\theta_1} \dual{p}_i(\cos\theta_1) P(q^2, \cos\theta_1)\sin\theta_1 = S_i(q^2)\,.
 \end{equation}
@@
 \label{app:btokstarll}
+
+\todo{rewrite to use Legendre polynomials}
 
@@
 
+\todo{rewrite to use Legendre polynomials}
+
 The class of semileptonic $\bar{B}\to P_1 P_2 \ell_1\bar\ell_2$ decays, where $P_1$, and $P_2$ are pseudoscalar mesons,
@@
 \label{app:lambdabtolambdall}
+
+\todo{rewrite to use Legendre polynomials}
 

### 2014-11-17 draft.tex
Convert appendix D to legendre basis

@@
 
-\todo{rewrite to use Legendre polynomials}
-
 The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts --- reads \cite{Boeer:2014xx}
 \begin{equation}
-    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
+    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \sum_i S_i f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
 \end{equation}
@@
 $N\pi$ systems, respectively, and $\theta_3 = \phi$ denotes the azimuthal angle.
-The basis of angular functions reads \cite{Boeer:2014xx}
+The index $i$ should be interpreted as a multi-index, $i \equiv (l_1, l_2, m)$,
+where $0 \leq l_1 \leq 2$ and $0 \leq l_2 \leq 1$ denote the total angular momentum in the
+dilepton and the $N\pi$ system, respectively, and $-1 \leq m \leq 1$
+is the third component of either of the angular momenta.
+Our choice of an orthonormal basis and its dual reads
 \begin{equation}
 \begin{aligned}
-% 1
-        f_{1ss} & = \sin^2\theta_1 &
-        f_{1cc} & = \cos^2\theta_1 &
-        f_{1c}  & = \cos\theta_1\\
-% 2
-        f_{2ss} & = \sin^2\theta_1 \cos\theta_2 &
-        f_{2cc} & = \cos^2\theta_1 \cos\theta_2 &
-        f_{2c}  & = \cos\theta_1   \cos\theta_2 \\
-% 3
-        f_{3sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\theta_3 &
-        f_{3s}  & = \sin\theta_1              \sin\theta_2 \cos\theta_3 \\
-% 4
-        f_{4sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\theta_3 &
-        f_{4s}  & = \sin\theta_1              \sin\theta_2 \sin\theta_3
+    f_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
+    & = \frac{1}{8\pi} \sqrt{\frac{(l_1 - |m|)!\,(l_2 - |m|)!}{(l_1 + |m|)!\,(l_2 + |m|)!}} p_{l_1}^{|m|}(\cos\theta_1) p_{l_2}^{|m|}(\cos\theta_2)\\
+    & \times \begin{cases}
+            \cos(|m|\theta_3) & m > 0\\
+            \sin(|m|\theta_3) & m < 0\\
+            1                 & m = 0
+        \end{cases}\,,\\
+    \tilde{f}_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
+    & = (2l_1 + 1)(2l_2 + 1)\sqrt{\frac{(l_1 - m)!\,(l_2 - m)!}{(l_1 + m)!\,(l_2 + m)!}} p_{l_1}^m(\cos\theta_1) p_{l_2}^m(\cos\theta_2)\\
+    & \times \begin{cases}
+            2 \cos(|m|\theta_3) & m > 0\\
+            2 \sin(|m|\theta_3) & m < 0\\
+            1                   & m = 0
+        \end{cases}\,.\\
 \end{aligned}
 \end{equation}
-The decay width reads
-\begin{equation}
-    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}
-\end{equation}
-In terms of the angles $\theta_1$ and $\theta_2$, instead of the cosines, the PDF reads
-\begin{equation}
-    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \theta_3) \sin\theta_1 \sin\theta_2\,,
-\end{equation}
-where we also define $S_i(q^2) \equiv K_i(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\
-
-The dual basis reads
+The correspondence between out choice of angular observables in the angular momentum basis, and the angular
+observables as defined in reference \cite{Boeer:2014xx} reads
 \begin{equation}
 \begin{aligned}
-% 1
-        \dual f_{1ss} & = \frac{1}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) &
-        \dual f_{1cc} & = \frac{1}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) &
-        \dual f_{1c}  & = \cos\theta_1\\
-% 2
-        \dual f_{2ss} & = \frac{3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) \cos\theta_2 &
-        \dual f_{2cc} & = \frac{3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) \cos\theta_2 &
-        \dual f_{2c}  & = 3 \cos\theta_1   \cos\theta_2 \\
-% 3
-        \dual f_{3sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\theta_3 &
-        \dual f_{3s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \cos\theta_3 \\
-% 4
-        \dual f_{4sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\theta_3 &
-        \dual f_{4s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \sin\theta_3
+    S_{0, 0,  0} & = 1\,,                                                             &
+    S_{1, 0,  0} & = \frac{3 K_{1c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
+    S_{2, 0,  0} & = \frac{2(K_{1cc} - K_{1ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
+    S_{0, 1,  0} & = \frac{K_{2cc} + 2 K_{2ss}}{\rmdx\Gamma/\rmdx{q^2}}\,,            &
+    S_{1, 1,  0} & = \frac{3 K_{2c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
+    S_{2, 1,  0} & = \frac{2(K_{2cc} - K_{2ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
+                 &                                                                    &
+    S_{1, 1, -1} & = \frac{6 K_{4s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
+    S_{2, 1, -1} & = \frac{2 \sqrt{3} K_{4sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,             \\
+                 &                                                                    &
+    S_{1, 1, +1} & = \frac{6 K_{3s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
+    S_{2, 1, +1} & = \frac{2 \sqrt{3} K_{3sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,
 \end{aligned}
 \end{equation}
-such that
+where the decay width is
 \begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} P(q^2, \theta_1, \theta_2, \theta_3) \dual{f}_i(\theta_1, \theta_2, \theta_3) = S_i(q^2)\,.
+    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}\,.
+\end{equation}
+
+The dual basis is chosen such that
+\begin{equation}
+    \int_{-1}^{+1} \rmdx{\cos \theta_1} \int_{-1}^{+1} \rmdx{\cos \theta_2} \int_0^{2\pi} \rmdx{\theta_3} P(q^2, \cos \theta_1, \cos \theta_2, \theta_3) \dual{f}_i(\cos \theta_1, \cos \theta_2, \theta_3) = S_i(q^2)\,.
 \end{equation}

### 2015-01-14 acceptance.py
Rewrite python script for acceptance, discuss with Fred

@@ -1,348 +1,274 @@
-'''Check the efficiency correction for the method of moments.
-
-The considered decays is like B -> K ll. Write PDF as sum over Legendre polynomials.
-
-1. Draw samples from a uniform distribution of \cos \theta, and compute integrals, then reweight by P * eps
-2. Draw from P * eps using MCMC from pypmc
-
-Both methods give similar estimates of the angular
-observables. Amazingly: 1. much simpler to implement, and yields the
-true values up to machine precision every time. How?!
-
-3. Plot the regions
-4. Optimize using nlopt
-
-'''
-from __future__ import division, print_function
-
-# import nlopt
 import numpy as np
+import numpy.matlib as matlib
 from numpy.polynomial.legendre import Legendre
+
 import pypmc
+
 from matplotlib import pyplot as plt
-from scipy.integrate import quad
 
-# np.random.seed(123465123)
+import scipy as sp
+import scipy.integrate as integrate
 
-# define a proposal
-prop_dof   = 5.
-prop_sigma = np.array([[3]])
-prop = pypmc.density.student_t.LocalStudentT(prop_sigma, prop_dof)
+import sys
 
-class BtoKll:
-    '''Differential decay rate of B -> K ll for fixed q^2.'''
-    def __init__(self, eps=2/3*np.array([0.6, 0.05, -0.55])):
-        '''eps: coefficients of Legendre polynomials of acceptance. Make sure it integrates to less than one.'''
-        self._accept = Legendre(eps)
-        # first 0.5 is fixed by normalization!
-        self._S = np.zeros(3)
-        self._S[0] = 0.5
+class Process:
+    def dim(self):
+        '''
+        Return the number of kinematic variables
+        '''
+        raise NotImplementedError()
 
-    def differential_rate(self, S, x):
-        # x = np.cos(theta)
-        x = np.asarray(x)
+    def pdf(self, x):
+        '''
+        Evaluate the PDF
+        S: array of angular observables
+        x: array of angular variables
+        '''
+        raise NotImplementedError()
 
-        # first coefficient fixed
-        self._S[1:] = S[:]
-        P = Legendre(self._S)(x)
+    def log_pdf(self, x):
+        '''
+        Evaluate the natural logarithm of the PDF
+        '''
+        return np.log(self.pdf(x))
 
-        # A_FB, F_H = S[0], S[1]
[…]

### 2015-01-14 acceptance.py
[acceptance] Change parameters for run on c2pap

@@ -197,7 +197,8 @@ def unfolding_matrix(_process, acceptance, components, chunks, chunk_size):
             samples = sampler.draw(log_target, start=process.start(), indicator=indicator, chunks=chunks, chunk_size=chunk_size)
             for i in range(components):
                 estimator = 0
-                for x in samples:
+                # discard burn-in of 2000 samples
+                for x in samples[2000:]:
                     estimator += process.dual_component(i, x)
                 estimator *= Rm / len(samples)
 
@@ -217,8 +218,8 @@ def flat_acceptance_btokll_matrix():
     print("Flat acceptance in B->Kll")
     acceptance = lambda x: 1.
     samples = []
-    for i in range(10):
-        M = unfolding_matrix("B->Kll", acceptance, components=3, chunks=100, chunk_size=500)
+    for i in range(1):
+        M = unfolding_matrix("B->Kll", acceptance, components=3, chunks=2000, chunk_size=500)
         output = []
         for n in M.flatten():
             output.append("%4.4f" % n)
@@ -271,4 +272,3 @@ try:
     f()
 except KeyError:
     print("Unknown command '%s'" % sys.argv[1])
-

### 2015-01-15 acceptance.py
Update acceptance.py with working Lambda_b -> Lambda ll

@@ -1,3 +1,4 @@
+#!/usr/bin/python
 import numpy as np
 import numpy.matlib as matlib
 from numpy.polynomial.legendre import Legendre
@@ -8,6 +9,7 @@ from matplotlib import pyplot as plt
 
 import scipy as sp
 import scipy.integrate as integrate
+from scipy.misc import factorial
 
 import sys
 
@@ -55,10 +57,20 @@ class Process:
     def integrate(self, function):
         raise NotImplementedError()
 
+    def test(self):
+        for i in range(self.number_of_components()):
+            for j in range(self.number_of_components()):
+                integrand = lambda x: self.dual_component(i, x) * self.component(j, x)
+                print("test: i=%d, j=%d, result=%f" % (i, j, self.integrate(integrand)))
+
 
 class BToKDilepton(Process):
     def __init__(self, S):
         self.S = S
+
+    @staticmethod
+    def make(S):
+        return BToKDilepton(S)
 
     def dim(self):
         return 1
@@ -96,61 +108,103 @@ class BToKDilepton(Process):
         plt.savefig('samples-btokll-%s.pdf' % name)
 
 
-#class LambdaBToLambdaDilepton(Process):
-#    momenta = [
-#        (0, 0,  0),
-#        (1, 0,  0),
-#        (2, 0,  0),
-#        (0, 1,  0),
-#        (1, 1,  0),
-#        (2, 1,  0),
-#        (1, 1, -1),
-#        (2, 1, -1),
-#        (1, 1, +1),
-#        (2, 1, +1)
-#    ]
-#
-#    def __init__(self, S):
-#        self.S = S
-#
-#    def dim(self):
-#        return 3
-#
-#    def pdf(self, x):
-#        result = 0
-#        for i in [0, 1, 2]:
-#            result += self.S[i] * self.component(i, x)
-#        return result
-#
-#    def number_of_components(self):
-#        return 3
-#
-#    def component(self, i, x):
-#        c_th_1 = x[0]
-#        c_th_2 = x[1]
-#        th_3 = x[2]
-#        (l1, l2, m) = self.momenta[i]
-#
-#        result = 0
-#        if m == 0:
-#            result = 1.
-#        elif m > 0:
-#            result = np.cos(th_3)
-#        elif m < 0:
-#            result = np.sin(th_3)
-#
-#        m = abs(m)
-#
[…]

### 2015-01-15 draft.tex
Update draft and dual-basis.nb

@@
   region.\fred{Is there some LHCb note we could cite?} In many of the
-  decays of interest, there are only say dozens of events recorded.
+  decays of interest, there are only say dozens\todo{check!} of events recorded.
 \item The estimate is unbiased for any $N$. In contrast, the
@@
 on the angular distribution.) However, at the level of decay amplitudes the dimeson system can have an arbitrarily
-large total angular momentum $j$; only its third component is restricted to $m = -1,0,+1$. \fred{check}
+large total angular momentum $j$; only its third component is restricted to $m = -1,0,+1$.
+It is then usual to compute the angular distribution explicitly in terms of $\theta_1$ and $\theta_3$, but leave
+the angular observables dependent on the remaining helicity angle $\theta_2$.
 We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(|m|)}$
@@
 \end{equation}
-\fred{since when is $S_k a fct. of \cos \theta_2$?}
 where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
@@
 
-\todo{size of $M$ in relation to the maximum angular momentum of $\eps$}
+It remains to be emphasized that the dimensionality of the raw angular observables is not completely
+fixed by the number of angular momentum configurations of the process at hand. Let us revisit the
+decay $B\to K\ell^+\ell^-$, with only one angle,  to clear this up. For $B\to K\ell^+\ell^-$, the
+total angular momentum associated the dilepton pair can, at the level of observables, be either $0$,
+$1$ or $2$. We assume now that the acceptance function $\eps$ can be conveniently expanded in terms
+of Legendre polynomials up to maximal angular momentum $L$. From angular momentum conservation
+follows immediately that $\dim Q = L + 2$, and thus the unfolding matrix $M$ will be of
+dimension $L + 2 \times L + 2$. (For a multiangular distribution the maximum angular momentum
+has to be determined in the same way for each angle.)
+Since the $\eps$ depends highly on the nature of the particle detector at hand, it remains for
+the experimental collaborations to determine the maximum order of such an expansion.
 
@@
 First, we find no bias in the determinations of the angular observables even for a small number of events.
-However, this comes at the expense of a slight increase of the order of $10\%$ for the statistical uncertainty
+However, this comes at the expense of a slight increase of the order of $10\%$\todo{check!} for the statistical uncertainty
 on the mean.
@@
 
-\section{Application to $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ (S-wave and P-wave)}
-\label{app:btokstarll}
-
-\todo{rewrite to use Legendre polynomials}
-
-The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ --- up to and including P-wave contributions --- has been calculated
-for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
-\begin{equation}
-    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
-\end{equation}
-where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
-The $q^2$-differential decay width reads
-\begin{equation}
-    \frac{\rmdx{\Gamma}}{\rmdx{q^2}} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
-\end{equation}
-The angular functions\footnote{%
-    We consistently use the label "$i$" to denote angular function and observables that arise
-    from interference between S-wave and P-wave amplitudes. Our convention is related to the convention
-    of \cite{Bobeth:2012vn} through $f_{1i} \leftrightarrow f_{1sc}$, $f_{2i} \leftrightarrow f_{2sc}$.
-} read \cite{Blake:2012mb,Bobeth:2012vn}
-\begin{equation}
-\begin{aligned}
-    f_{1s} & = \sin^2\theta_2 &
-    f_{1c} & = \cos^2\theta_2 &
-    f_{1i} & = \cos\theta_2\\
-    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
-    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
-    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
-    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\theta_3 &
-    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 &
-    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\theta_3\\
-    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\theta_3 & & &
-    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\theta_3\\
-    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
-    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
-    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\theta_3 & & &
-    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\theta_3\\
-    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\theta_3 & & &
-    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\\
-    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
-\end{aligned}
-\end{equation}
-In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
-\begin{equation}
-    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \theta_3) \sin\theta_1 \sin\theta_2\,,
-\end{equation}
-where we also define $S_k(q^2) \equiv J_k(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\
-
-The dual basis reads
-\begin{equation}
-\begin{aligned}
-    \dual{f}_{1s} & = \frac{\big( 63 \sin^2\theta_2 - 42 \cos^2\theta_2\big) + \big(  45 \sin^2\theta_2 - 30 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
-    \dual{f}_{1c} & = \frac{\big(-21 \sin^2\theta_2 + 84 \cos^2\theta_2\big) + \big( -15 \sin^2\theta_2 + 60 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,\\
-    \dual{f}_{2s} & = \frac{\big( 45 \sin^2\theta_2 - 30 \cos^2\theta_2\big) + \big(+135 \sin^2\theta_2 - 90 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
-    \dual{f}_{2c} & = \frac{\big(-15 \sin^2\theta_2 + 60 \cos^2\theta_2\big) + \big( -45 \sin^2\theta_2 +180 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,
-\end{aligned}
-\end{equation}
-as well as
-\begin{equation}
-\begin{aligned}
-    \dual{f}_{1i} & = \frac{\big(21 + 15 \cos1\theta_2\big)\cos\theta_2}{16}               \,,&
-    \dual{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
-    \dual{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,& &\\
-    \dual{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
-    \dual{f}_{4i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \cos \theta_3}{8}                 \,,\\
-    \dual{f}_{5}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \cos \theta_3}{8}                 \,,&
-    \dual{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
-    \dual{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
-    \dual{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
-    \dual{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
-    \dual{f}_{7i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \sin \theta_3}{2}                 \,,\\
-    \dual{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
-    \dual{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,,\\
-    \dual{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,.\\
-\end{aligned}
-\end{equation}
-such that
-\begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} \dual{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
-\end{equation}
-
-\section{Application to $\bar{B}\to P_1 P_2\ell^+\ell^-$ (all partial waves)}
-\label{app:btokpill}
-
-\todo{rewrite to use Legendre polynomials}
-
-The class of semileptonic $\bar{B}\to P_1 P_2 \ell_1\bar\ell_2$ decays, where $P_1$, and $P_2$ are pseudoscalar mesons,
-and $\ell_1$ and $\bar\ell_2$ are charged or neutral leptons, includes decays
-such as $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$.
-Their decay PDFs can generally be written as \cite{Lee:1992ih}
-\begin{equation}
-    P(q^2, p^2, \cos\theta_1, \cos \theta_2, \theta_3) = \frac{1}{\langle \Gamma\rangle}\frac{\rmdx{^5 \Gamma}}{\rmdx{q^2} \rmdx{p^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_k(\cos\theta_1,\theta_3)\,,
-\end{equation}
-where
-\begin{equation}
-\begin{aligned}
-    f_1 & = 1\,,              &
-    f_2 & = \cos 2\theta_1\,, &
-    f_3 & = \sin^2\theta_1 \cos 2\theta_3\,,\\
-    f_4 & = \sin 2\theta_1 \cos  \theta_3\,,&
-    f_5 & = \sin  \theta_1 \cos  \theta_3\,,&
-    f_6 & = \cos  \theta_1\,, \\
-    f_7 & = \sin  \theta_1 \sin  \theta_3\,,&
-    f_8 & = \sin 2\theta_1 \sin  \theta_3\,,&
-    f_9 & = \sin^2\theta_1 \sin 2\theta_3\,.\\
-\end{aligned}
-\end{equation}
-Here we denote dilepton mass squared and the dilepton helicity angle as $q^2$ and $\theta_1$, while
-the dimeson mass squared and the dimeson helicity angles are denoted as $p^2$ and $\theta_2$. The
-azimuthal angle is denoted as $\theta_3$.
-The total decay width is
-\begin{equation}
-    \langle \Gamma\rangle = \int_0^\pi \rmdx{\theta_2} \rmdx{q^2} \rmdx{p^2} \sin\theta_2 \frac{3I_1(q^2, p^2, \cos\theta_2) - I_2(q^2, p^2, \cos\theta_2)}{3}\,.
-\end{equation}
-As previous, we transform from a $\cos\theta_2$-dependence to a $\theta_2$-dependence.
-\begin{equation}
-\begin{aligned}
-    P(q^2, p^2, \theta_1, \theta_2, \theta_3)
-    & = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \theta_3) \sin\theta_1 \sin\theta_2\\
-    & \equiv \frac{1}{4\pi} \sum_k S_k(q^2, p^2, \theta_2) f_k(\theta_1, \theta_3) \sin\theta_1\,.
-\end{aligned}
-\end{equation}
-where we also define $S_k(q^2, p^2, \theta_2) \equiv \sin\theta_2 I_k(q^2, p^2, \cos\theta_2) / \langle \Gamma\rangle$.\\
-
-The dual basis reads
-\begin{equation}
-\begin{aligned}
-    \dual{f}_1 & = \frac{21 + 15 \cos 2\theta_1}{16}\,, &
-    \dual{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
-    \dual{f}_3 & = \frac{15}{4} \sin^2\theta_1 \cos 2\theta_3     \,,\\
-    \dual{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \theta_3     \,, &
-    \dual{f}_5 & = 3            \sin  \theta_1 \cos  \theta_3     \,, &
-    \dual{f}_6 & = 3 \cos\theta_1                   \,,\\
-    \dual{f}_7 & = 3            \sin  \theta_1 \sin  \theta_3     \,, &
-    \dual{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \theta_3     \,, &
-    \dual{f}_9 & = \frac{15}{4} \sin^2\theta_1 \sin 2\theta_3     \,.\\
-\end{aligned}
-\end{equation}
-such that
-\begin{equation}
-    \int_0^\pi \rmdx{\theta_1} \int_0^{2\pi} \rmdx{\theta_3} \dual{f}_i(\theta_1,\theta_3) P(q^2, k^2, \theta_1,\theta_2,\theta_3) = S_i(q^2, k^2, \theta_2)\,.
-\end{equation}
-
 \section{Application to $\Lambda_b\to \Lambda(\to N \pi)\ell^+\ell^-$}
@@
 \begin{equation}
+\label{eq:lambdab:bases}
 \begin{aligned}
     f_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
-    & = \frac{1}{8\pi} \sqrt{\frac{(l_1 - |m|)!\,(l_2 - |m|)!}{(l_1 + |m|)!\,(l_2 + |m|)!}} p_{l_1}^{|m|}(\cos\theta_1) p_{l_2}^{|m|}(\cos\theta_2)\\
+    & = \sqrt{\frac{(l_1 - |m|)!\,(l_2 - |m|)!}{(l_1 + |m|)!\,(l_2 + |m|)!}} p_{l_1}^{|m|}(\cos\theta_1) p_{l_2}^{|m|}(\cos\theta_2)\\
     & \times \begin{cases}
@@
     \tilde{f}_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
-    & = (2l_1 + 1)(2l_2 + 1)\sqrt{\frac{(l_1 - m)!\,(l_2 - m)!}{(l_1 + m)!\,(l_2 + m)!}} p_{l_1}^m(\cos\theta_1) p_{l_2}^m(\cos\theta_2)\\
+    & = \frac{(2l_1 + 1)(2l_2 + 1)}{8\pi}\sqrt{\frac{(l_1 - m)!\,(l_2 - m)!}{(l_1 + m)!\,(l_2 + m)!}} p_{l_1}^m(\cos\theta_1) p_{l_2}^m(\cos\theta_2)\\
     & \times \begin{cases}
@@
 \begin{aligned}
-    S_{0, 0,  0} & = 1\,,                                                             &
-    S_{1, 0,  0} & = \frac{3 K_{1c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
-    S_{2, 0,  0} & = \frac{2(K_{1cc} - K_{1ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
-    S_{0, 1,  0} & = \frac{K_{2cc} + 2 K_{2ss}}{\rmdx\Gamma/\rmdx{q^2}}\,,            &
-    S_{1, 1,  0} & = \frac{3 K_{2c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
-    S_{2, 1,  0} & = \frac{2(K_{2cc} - K_{2ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
+    8\pi S_{0, 0,  0} & = 1\,,                                                             &
+    8\pi S_{1, 0,  0} & = \frac{3 K_{1c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
+    8\pi S_{2, 0,  0} & = \frac{2(K_{1cc} - K_{1ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
+    8\pi S_{0, 1,  0} & = \frac{K_{2cc} + 2 K_{2ss}}{\rmdx\Gamma/\rmdx{q^2}}\,,            &
+    8\pi S_{1, 1,  0} & = \frac{3 K_{2c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
+    8\pi S_{2, 1,  0} & = \frac{2(K_{2cc} - K_{2ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
                  &                                                                    &
-    S_{1, 1, -1} & = \frac{6 K_{4s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
-    S_{2, 1, -1} & = \frac{2 \sqrt{3} K_{4sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,             \\
+    8\pi S_{1, 1, -1} & = \frac{6 K_{4s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
+    8\pi S_{2, 1, -1} & = \frac{2 \sqrt{3} K_{4sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,             \\
                  &                                                                    &
-    S_{1, 1, +1} & = \frac{6 K_{3s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
-    S_{2, 1, +1} & = \frac{2 \sqrt{3} K_{3sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,
+    8\pi S_{1, 1, +1} & = \frac{6 K_{3s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
+    8\pi S_{2, 1, +1} & = \frac{2 \sqrt{3} K_{3sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,
 \end{aligned}
@@
 
+For the purpose of unfolding acceptance effects as laid down in \refsec{systematics:acceptance}, it is instrumental
+to know that $f_{0,0,0} \equiv 1$, and that $\max_{\cos\theta_1,\cos\theta_2,\phi} |f_{l_1, l_2, m}| < 1$.
+The recipe's generating PDFs are therefore
+\begin{equation}
+    P(x|\lbrace S_i^{(j)}\rbrace)\,,\quad\text{with}\quad S_i^{(j)} = \frac{1}{8\pi}\left(\delta_{i,(0,0,0)} + \delta_{i,j}\right)\,,
+\end{equation}
+where $j$ ís now also a multi-index representing $j \equiv (\tilde l_1, \tilde l_2, \tilde m)$.
+
+\section{Application to $\bar{B}\to\bar{K}\pi\ell^+\ell^-$}
+\label{app:btokstarll}
+
+The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ --- up to and including P-wave contributions --- has been calculated
+for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
+\begin{equation}
+    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}}
+    = \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
+\end{equation}
+where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle; $\theta_2 \equiv \theta_{K}$ is the $\bar{K}\pi$ helicity angle; $\theta_3 \equiv \phi$ is the azimuthal angle;
+and $q^2$ is the square of the dilepton mass. The $q^2$-differential decay width reads
+\begin{equation}
+    \frac{\rmdx{\Gamma}}{\rmdx{q^2}} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
+\end{equation}
+It is convenient to define the basis of angular functions and its dual in terms of
+associated Legendre polynomials $p_l^m(x)$. The index $i$ should thus be interpreted as a multi-index
+, $i \equiv (l_1, l_2, m)$, where $0 \leq l_1 \leq 2$ and $0 \leq l_2 \leq 2$ denote the total angular
+momentum in the dilepton and the $K\pi$ system, respectively, and $-2 \leq m \leq 2$
+is the third component of either of the angular momenta.
+We use the same bases of angular functions as given in \refeq{lambdab:bases} for the decay $\Lambda_b\to \Lambda\ell^+\ell^-$.
+In that case, the angular observables correspond to the usual choice of observables via
+\begin{equation}
+\begin{aligned}
+    8\pi S_{0, 0,  0} & = 1\,,                                                                             &
+    8\pi S_{0, 1,  0} & = \frac{3 J_{1i} - J_{2i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                            &
+    8\pi S_{0, 2,  0} & = \frac{6 (J_{1c} - J_{1s}) - 2(J_{2c} - J_{2s})}{3\rmdx{\Gamma}/\rmdx{q^2}}\,,
+\end{aligned}
+\end{equation}
+and
+\begin{equation}
+\begin{aligned}
+%
+                      &                                                                                    &
+    8\pi S_{1, 1, -1} & = \frac{6 J_{7i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                     &
+    8\pi S_{1, 2, -1} & = \frac{4 \sqrt{3} J_{7}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                             \\
+%
+    8\pi S_{1, 0,  0} & = \frac{J_{6c} + 2 J_{6s}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                            &
+    8\pi S_{1, 1,  0} & = 0\,,                                                                             &
+    8\pi S_{1, 2,  0} & = \frac{2(J_{6c} - J_{6s})}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                           \\
+%
+                      &                                                                                    &
+    8\pi S_{1, 1, +1} & = \frac{6 J_{5i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                     &
+    8\pi S_{1, 2, +1} & = \frac{4 \sqrt{3} J_{5i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,
+\end{aligned}
+\end{equation}
+and
+\begin{equation}
+\begin{aligned}
+%
+                 &                                                                                    &
+                 &                                                                                    &
+    8\pi S_{2, 2, -2} & = \frac{8 J_9}{\rmdx{\Gamma}/\rmdx{q^2}}                                           \\
+%
+                 &                                                                                    &
+    8\pi S_{1, 2, -1} & = \frac{6 J_{?}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                      &
+    8\pi S_{1, 2, -1} & = \frac{4 \sqrt{3} J_{?}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                             \\
+%
+    8\pi S_{2, 0,  0} & = \frac{4 (J_{2c} + 2 J_{2s})}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                        &
+    8\pi S_{2, 1,  0} & = \frac{4 J_{2i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                     &
+    8\pi S_{2, 2,  0} & = \frac{8 (J_{2c} - J_{2s})}{3 \rmdx{\Gamma}/\rmdx{q^2}}\,,                        \\
+\end{aligned}
+\end{equation}
+
+As before, for the purpose of unfolding acceptance effects as laid down in \refsec{systematics:acceptance}, it is instrumental
+to know that $f_{0,0,0} \equiv 1$, and that $\max_{\cos\theta_1,\cos\theta_2,\phi} |f_{l_1, l_2, m}| \leq 1$.
+The recipe's generating PDFs are therefore
+\begin{equation}
+    P(x|\lbrace S_k^{(j)}\rbrace)\,,\quad\text{with}\quad S_k^{(j)} = \frac{1}{8\pi}\left(\delta_{k,0} + \delta_{k,j}\right)\,,
+\end{equation}
+where also $j$ is now a multi-index representing $j \sim (l_1, l_2, m)$.
+
 \section{On the Partial-Wave Expansions of Angular Observables}
@@
 
-Let $S \equiv S(\vec{\nu},\theta)$ be an observable of only one angle $\theta$ and further non-angular variables $\vec{\nu}$.
-\fred{This is confusing: in the intro, we define $S$ as independent of any angle.} \fred{What about two angles?
-More amplitudes seem trivial, one would just have more $S_i$} Further, let
-$S$ have an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
+Let us assume that the angular decomposition has been achieved for some
+PDF $P$ for all except one angle $\theta$. We now focus on only of the resulting
+observables $S(\theta) \equiv S(\vec{\nu},\theta)$. The dependence on the non-angular
+variables will be dropped in the following. \danny{Fred: is this less confusing now?}
+Further, let $S$ have an expansion in terms of partial waves
+$l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
 \begin{equation}
@@
 where $F \in \{\text{Re},\text{Im}\}$ denotes taking either the real
-or the imaginary part. \fred{Now $\nuvec$ gone}
-$p_{l}^{(m)}$ is an \emph{associated Legendre} polynomial and $m_i$ is the third component of the angular momentum of the amplitude $A_i$, and we impose $m_1 \geq m_2$.\\
+or the imaginary part.
+Here $p_{l}^{(m)}$ denotes an \emph{associated Legendre} polynomial and $m_i$ is the third component of the angular momentum of the amplitude $A_i$, and we impose $m_1 \geq m_2$.\\
 
@@
 \end{equation}
-Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial-wave amplitudes must asymptotically fall off as \fred{Let's say why. Unitarity?}
+Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial-wave amplitudes must asymptotically fall off as \fred{Let's say why.
+Unitarity?} \danny{Finiteness of observables, so yes: unitarity!}
 \begin{equation}
@@
 \end{equation}
-This motivates to cut the partial-wave expansion off at some angular momentum $L$.\\
+This motivates to cut off the partial-wave expansion at some arbitrary angular momentum $L$.\\
 
@@
 \begin{equation}
-    S(\vec{\nu}, \theta) = \sum_j S_{j,m}(\vec{\nu}) p_{j}^{(m)}(\cos\theta)\,.
+    S(\theta) = \sum_j S_{j,m} p_{j}^{(m)}(\cos\theta)\,.
 \end{equation}
@@
 \begin{equation}
-    S_{j,m}(\vec{\nu}) = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} S(\vec{\nu},\cos \theta) p_{j}^{(m)}(\cos\theta)\,.
+    S_{j,m} = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} S(\theta) p_{j}^{(m)}(\cos\theta)\,.
 \end{equation}
-(Here and in the next step we may exchage the integral and the
+(Here and in the next step we may exchange the integral and the
 series because each element of the series is a product of
@@
 is absolutely convergent).
-Second, we can immediately express $S_{j,m}(\vec{\nu})$ in terms of
+Second, we can immediately express $S_{j,m}$ in terms of
 the partial-wave amplitudes,
@@
     \begin{aligned}
-        S_{j,m}(\vec{\nu})
+        S_{j,m}
             & = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) A_{2}^{*(l_2)}p_{l_2}^{(m_2)}(\cos\theta)\right]\\
@@
 \end{equation}
-The latter condition is well known from adding angular momenta. Note, however, that
+The latter condition is well known from the addition rules of angular momenta. Note, however, that
 the sum in \refeq{def-partial-wave-observable} goes to infinitely high angular momenta $l_1$ and $l_2$. As a consequence

### 2015-01-20 draft.tex
Update draft, acceptance.py, and references

@@
   data to interested theorists for more accurate fits of
-  standard-model and new-physics parameters \citeneeded\fred{Our fits
-    and others'?} or for more precise predictions of optimized
-  observables; e.g.,
+  standard-model and new-physics parameters \cite{Altmannshofer:2013foa,
+    Descotes-Genon:2013wba,Bobeth:2013soa},
+  or for more precise predictions of optimized observables; e.g.,
   \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
@@
 \end{equation}
-Here $P$ is the probability distribution of the true events, and the kernel $E(x_\text{d}, x_\text{t})$
+Here $P_\text{t}$ is the probability distribution of the true events, and the kernel $E(x_\text{d}, x_\text{t})$
 parametrizes acceptance and resolution
@@
     by promoting $x$ to a vector, promoting the Legendre polynomials to products of independent polynomials
-    and the indices $i,j,k,m$ to multi-indices.
+    or spherical harmonics, and promoting the indices $i,j,k,m$ to multi-indices.
 }
@@
 
+The accuracy of the unfolding process as outlined above critically depends on both the accuracy
+of the detector simulation, as well as the uncertainties induced by the MC estimates. While
+considerations of any detector simulation is beyond the scope of this work, we can, however,
+comment on the MC-induced uncertainties. As usual, one needs to find a balance between
+compute time and accuarcy. We find for a uniangular distribution and a total of $6\cdot 10^6$ MC
+samples (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$) that the error on the mean is
+smaller than $6\cdot 10^{-4}$. Let us conclude this section by commenting that the unfolding
+matrix is universal in a sense. Specifically, it can be reused in analyses with a similar underlying decay.
+Therefore, computing resources spent on improving its accuracy are therefore not wasted.
+
 \section{Toy Studies}
@@
 
-In order to study the performance of the proposed method, we simulate
-measurements for one uni-angular and one tri-angular decay
-distribution for various numbers of events. As inputs we use the SM
-predictions for the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to
-K\pi)\ell^+\ell^-$, respectively. We cover the $q^2$ ranges $1 \GeV^2$
-to $6 \GeV^2$, and $15 \GeV^2$ to the respective kinematic endpoint,
-with two bin widths: $1\GeV^2$ and $0.5\GeV^2$. This is to ensure that
-a wide spectrum of possible values for
-the angular observables.\\
+We now study the performance of the proposed method. In order to do so, we simulate
+individual events for two separate physical processes: one uni-angular, and one tri-angular decay
+distribution. We repeats theses analysis for varying sample sizes, ranging from
+$50$ to $500$ events. Our toy analysis base on SM predictions for angular observables
+in the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to K\pi)\ell^+\ell^-$, respectively.
+In order to faithfully investigate the performance of the method of moments, we repeats our
+numerical studies for several bin sizes in the kinematic range $1 \GeV^2 \leq q^2 \leq 6\GeV^2$,
+as well as $15 \GeV^2 \leq q^2 \leq q^2_\text{max}$. Here, the bin size is chosen either
+as $1\GeV^2$ or $0.5\GeV^2$. This setup is meant to ensure that a wide spectrum of possible
+values for the angular observables is investigated.\\
 
@@
 \begin{itemize}
-    \item In all studied cases we observed not a single bias in the pull \fred{should define pull} distribution of the observable.
-        All pull distributions can successfully be fitted to a gaussian distribution. As an example, we
-        show the pull distributions for the observables $S_5$ and $S_7$ for a SM-like $B\to K^*\ell^+\ell^-$
-        decays in \reffig{pulls}.
+    \item In all studied cases we observed not a single bias in the distribution of the $\mathrm{pull}$
+        of any observables $S$,
+        \begin{equation}
+            \mathrm{pull_i} \equiv \frac{\est{S} - S}{\est{\sigma}_S}\,.
+        \end{equation}
+        Here $S$ refers to the true (input) value for the angular observables, $\est{S}$ refers to the
+        MC estimate, and $\est{\sigma} \equiv \sqrt{\est{\Sigma}}$ refers to an estimator of the
+        variance of the measurement. All pull distributions obtained in our studies can be successfully
+        fitted to a gaussian distribution. Due to the large number of studied distributions, we have
+        to restrict ourselved to a subset. In our opinion the pull distributions for the observables
+        $S_5 \simeq 27\%$ and $S_7 \simeq 2\%$, which are obtained from SM-like $B\to K^*\ell^+\ell^-$
+        decays, are good examples. We show their respective pull distributions for \danny{$XXX$} toy studies
+        of $200$ events per study in \reffig{pulls}.
     \item We study the absolute uncertainty $\sigma_k(K)$ with respect to the angular observable $S_k$
@@
 \end{itemize}
-We find that all of the above results show consistently that the joint distrbution of the angular observables
-converges towards a multivariate Gaussian distribution. We propose to describe the resulting distribution as
-a multivariate Gauss when skewness and kurtosis are small enough. The precise targets for these quantities
-are subject to the details of the physical analysis, and therefore outside the scope of our work.
+All results of our toy studies, as summarised above, show consistently that the joint distribution of the angular
+observables converges towards a multivariate Gaussian distribution. We therefore propose to describe the
+resulting distribution as a multivariate Gauss when skewness and kurtosis fall below a given threshold.
+The precise target threshold for skewness and kurtosis are subject to the details of the underlying physical analysis, and reside therefore outside the scope of this work.
 
@@
 \end{figure}
-
-\hrulefill\\
-{\textbf{\color{red}[dvd: can the following be removed?]}
-We used the simulated events and fitted a likelihood function to them.
-\begin{itemize}
-    \item For a small number of simulated events, \danny{$K=?$}, we observe a significant bias in the pull distributions.
-    \item For a large number of simulated events, \danny{$K=?$}, the uncertainty of the angular observables is
-        smaller compared to the results of the method of moments.
-\end{itemize}
-todo: compare robustness to likelihood fit when fit doesn't
-converge. Why exactly doesn't it converge? What if physics model
-wrong, say some angular terms are missing.}
-\hrulefill
 
@@
 Let us assume that the angular decomposition has been achieved for some
-PDF $P$ for all except one angle $\theta$. We now focus on only of the resulting
-observables $S(\theta) \equiv S(\vec{\nu},\theta)$. The dependence on the non-angular
-variables will be dropped in the following. \danny{Fred: is this less confusing now?}
+PDF $P$ for all angles except one, which we label $\theta$. We now focus on only of of the resulting
+observables, which we label $S(\theta) \equiv S(\vec{\nu},\theta)$. The dependence on the non-angular
+variables will be suppressed in the following. \danny{Fred: is this less confusing now?}
 Further, let $S$ have an expansion in terms of partial waves
@@
 For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
-We close by remarking that for any angular-momentum cut off $l < L$\fred{Do you mean $L < \infty$?}, one can find an upper limit for the squared sum
-of all remaining partial waves through the inclusive decay; i.e., schematically
-\begin{equation}
-    \sum_{i=1}^2 \sum_{l=L}^\infty |A_i^{(l)}|^2 \leq \frac{\rmdx{^{1 + \dim\vec\nu}} \Gamma_\text{incl}}{\rmdx{\cos\theta} \rmdx{\vec\nu}}\,.
-\end{equation}
+We close by remarking that for any angular-momentum cut off $l < L$\fred{Do you mean $L < \infty$?}, one can find an upper limit for the squared sum of all remaining partial waves through a comparison with the inclusive decay
+width.
 

### 2015-01-20 acceptance.py

@@ -259,7 +259,7 @@ def unfolding_matrix(_process, acceptance, components, chunks, chunk_size, ovalu
             for i in range(components):
                 estimator = 0
                 # discard burn-in of 2000 samples
-                for x in samples[2000:]:
+                for x in samples:
                     estimator += process.dual_component(i, x)
                 estimator *= Rm / len(samples)
 
@@ -280,12 +280,14 @@ def flat_acceptance_btokll_matrix():
     print("Flat acceptance in B->Kll")
     acceptance = lambda x: 1.
     samples = []
-    for i in range(1):
-        M = unfolding_matrix("B->Kll", acceptance, components=3, chunks=2000, chunk_size=500, ovalue=0.5)
+    for i in range(20):
+        chunks=100
+        chunk_size=750
+        M = unfolding_matrix("B->Kll", acceptance, components=3, chunks=chunks, chunk_size=chunk_size, ovalue=0.5)
         output = []
         for n in M.flatten():
             output.append("%4.4f" % n)
-        print "{ " + ", ".join(output) + " },"
+        print "{ %s }, (* samples=%d *)" % (", ".join(output), chunks * chunk_size)
 
 #      b. generic acceptance "B->Kll"
 def generic_acceptance_btokll_matrix():
@@ -295,11 +297,13 @@ def generic_acceptance_btokll_matrix():
     acceptance = lambda x: Legendre(acceptance_coeffs)(x[0])
     samples = []
     for i in range(1):
-        M = unfolding_matrix("B->Kll", acceptance, components=components, chunks=100, chunk_size=500, ovalue=0.5)
+        chunks=2000
+        chunk_size=500
+        M = unfolding_matrix("B->Kll", acceptance, components=components, chunks=chunks, chunk_size=chunk_size, ovalue=0.5)
         output = []
         for n in M.flatten():
             output.append("%4.4f" % n)
-        print "{ " + ", ".join(output) + " },"
+        print "{ %s }, (* samples=%d *)" % (", ".join(output), chunks * chunk_size)
 
 #      c. flat acceptance "Lambda_b->Lambdall"
 def flat_acceptance_lambdabtolambdall_matrix():

### 2015-01-22 draft.tex
[draft] corrections on intro

@@
 
-The initial motivation for studying what we wish to call the \emph{Method of Moments}
-is the determination of angular observables in the rare decay FCNC-mediated decay
-$\bar{B}\to \bar{K}^*(\to \bar{K}\pi)\ell^+\ell^-$. However, we emphasize that
-the method we describe in this letter is general, and it applies to arbitrary
-decay or scattering processes. We find a previous work \cite{Dighe:1998vk}
-advocates this method chiefly for the determination of angular observables in non-leptonic
-$B$ decays, but also mentions the applicability to semileptonic decays. We improve
-upon this previous work by studying correlations between the angular observables,
-and sources of systematic uncertainties. Moreover, we will show that the method
-at hand has two benefits over the usual approach based on likelihood fits. To wit:
+The initial motivation for studying what we wish to call the
+\emph{method of moments} is the determination of angular observables
+in the rare decay FCNC-mediated decay $\bar{B}\to \bar{K}^*(\to
+\bar{K}\pi)\ell^+\ell^-$. However, we emphasize that the method we
+describe in this letter is general, and it applies to arbitrary decay
+or scattering processes. We find a previous work \cite{Dighe:1998vk}
+advocates this method chiefly for the determination of angular
+observables in non-leptonic $B$ decays, but also mentions the
+applicability to semileptonic decays. We improve upon this previous
+work by studying correlations \fred{really? because of higher $l$}
+between the angular observables, and by showing explicitly how to
+incorporate uncertainties due to acceptance effects. Moreover, we show
+that the method of moments has two major advantages over the usual
+approach based on likelihood fits:
 \begin{enumerate}
@@
 The determination of a detector's performance to detect signal events
-with accurate determination of the event's angles is generally a difficult
-task. In the ideal case, one would have an explicit probabilistic model of
-the detector acceptance effects and could thus write down the full
-forward model from which the measured events arise. In practice, this
-would require much more CPU time than available, and one is therefore
-forced to simplify the model. The standard approach is to generate
-the \emph{true} particle events $\lbrace x_\text{t}^{(n)}\rbrace =
-\lbrace(\vec{\nu}^{(n)}_\text{t},\vec\theta^{(n)}_\text{t})\rbrace$, $n=1,\dots,N_\text{t}$, from a PDF
-assumed to describe the bare physical process, and to propagate those
-particles through a detailed simulation of the detector.
-The observable traces that the particles leave in the detector are fed
-into reconstruction algorithms resulting in the \emph{detector} events
-$\lbrace x^{(n)}_\text{d}\rbrace = \lbrace(\vec{\nu}^{(n)}_\text{d},
-\vec\theta^{(n)}_\text{d})\rbrace$, $n=1,\dots,N_\text{d}$.
-Most generally, the detected events $\lbrace x_\text{d}^{(k)}\rbrace$
-are distributed as $P_\text{d}$,
+with accurate determination of the event's angles is generally a
+difficult task. In the ideal case, one would have an explicit
+probabilistic model of the detector acceptance effects and could thus
+write down the full forward model from which the measured events
+arise. In practice, this would require much more CPU time than
+available, and one is therefore forced to simplify the model. The
+standard approach is to generate the \emph{true} particle events
+$\lbrace x_\text{t}^{(n)}\rbrace =
+\lbrace(\vec{\nu}^{(n)}_\text{t},\vec\theta^{(n)}_\text{t})\rbrace$,
+$n=1,\dots,N_\text{t}$, from a PDF assumed to describe the bare
+physical process, and to propagate those particles through a detailed
+simulation of the detector.  The observable traces that the particles
+leave in the detector are fed into reconstruction algorithms resulting
+in the \emph{detector} events $\lbrace x^{(n)}_\text{d}\rbrace =
+\lbrace(\vec{\nu}^{(n)}_\text{d}, \vec\theta^{(n)}_\text{d})\rbrace$,
+$n=1,\dots,N_\text{d}$.  In general, the distribution of the detected
+events is
 \begin{equation}
-    P_\text{d}(x_\text{d}) = \int P_\text{t}(x_\text{t}) E(x_\text{d}, x_\text{t}) \rmdx{x_\text{t}}\,.
+    P_\text{d}(x_\text{d}) = \int P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}}\,.
 \end{equation}
-Here $P_\text{t}$ is the probability distribution of the true events, and the kernel $E(x_\text{d}, x_\text{t})$
-parametrizes acceptance and resolution
-effects. Note that $P_\text{d}$ is \emph{not} a PDF, since it is not normalized,
+Here $P_\text{t}$ is the probability distribution of the true events,
+and the kernel $E(x_\text{d}| x_\text{t})$ parametrizes acceptance and
+resolution effects. Note that $P_\text{d}$ is \emph{not} a PDF, since
+it is not normalized,
 \begin{equation}

### 2015-01-22 draft.tex
Corrections after discussion with Fred

@@
 For the selected class of decays, we can describe that problem as follows: The PDF $P$ has a fixed dependence on the dilepton
-helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokpill} for details
+helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokstarll} for details
 on the angular distribution.) However, at the level of decay amplitudes the dimeson system can have an arbitrarily
-large total angular momentum $j$; only its third component is restricted to $m = -1,0,+1$.
+large total angular momentum $j$; only its third component is restricted to $j_z = -1,0,+1$.
 It is then usual to compute the angular distribution explicitly in terms of $\theta_1$ and $\theta_3$, but leave
@@
 where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
-example we have (cf. also \refapp{btokpill})
+example we have (cf. also \refapp{btokstarll} and \cite{Lee:1992ih})
 \begin{equation}
     |m| = \begin{cases}
-        0\,, & k = 1,2,6\,\\
-        1\,, & k = 3,4,5,7,8,9\,,
+        0\,, & k = 1,2,6\,,\\
+        1\,, & k = 4,5,7,8\,,\\
+        m\,, & k = 3,9
     \end{cases}\,.
@@
 \begin{equation}
+    \label{eq:estS}
     \est{S}_i \equiv \sum_{i} \left(\hat{M}^{-1}\right)_{ij} \est{Q}_j\,.
@@
 However, ratios and other suitable combinations of the estimators $\lbrace \est{S}_i\rbrace$ are independent
-of $R$.
+of $R$. Conversely, $R$ can be extracted from the self-consistency condition\footnote{This condition
+is process dependent; see \refeq{recipe:lambdabtolambdall} and \refeq{recipe:btokstarll}.}
+$\hat{S}_0 = \frac{1}{2}$. Since $R$ is relevant in the determination of the branching ratio, it is therefore useful
+to carry out that determination and the extraction of the angular observables in a combined analysis.
 
-It remains to be emphasized that the dimensionality of the raw angular observables is not completely
-fixed by the number of angular momentum configurations of the process at hand. Let us revisit the
-decay $B\to K\ell^+\ell^-$, with only one angle,  to clear this up. For $B\to K\ell^+\ell^-$, the
-total angular momentum associated the dilepton pair can, at the level of observables, be either $0$,
-$1$ or $2$. We assume now that the acceptance function $\eps$ can be conveniently expanded in terms
-of Legendre polynomials up to maximal angular momentum $L$. From angular momentum conservation
-follows immediately that $\dim Q = L + 2$, and thus the unfolding matrix $M$ will be of
-dimension $L + 2 \times L + 2$. (For a multiangular distribution the maximum angular momentum
-has to be determined in the same way for each angle.)
-Since the $\eps$ depends highly on the nature of the particle detector at hand, it remains for
+\danny{
+We note that the set $\lbrace \est{S}_k\rbrace$ as determined from \refeq{estS} does not fully correspond to the
+set $\lbrace S_k\rbrace$ for an arbitrary $\eps$. Taking again the decay $B\to K\ell^+\ell^-$
+as an example, we have $\dim S = 3$. Assuming an expansion of the detector acceptance $\eps$
+in terms of Legendre polynomial up to order $L$, we obtain $\dim \est{Q} = \dim \est{S} = \dim S + L$.
+The MC estimators then have the following structure:
+\begin{equation}
+    \lbrace \est{S}_k \rbrace = \lbrace \underbrace{\est{S}_0, \dots, \est{S}_{\dim S}}_\text{physical}, \underbrace{\est{S}_{\dim S + 1}, \dots, \est{S}_{\dim Q}}_\text{``superfluous''}\rbrace\,.
+\end{equation}
+The method is consistent as long as the MC estimators for the ``superfluous'' observables with indices $\dim S + 1$ to $\dim Q$
+are compatible with zero. \footnote{This holds only for the physical model of uniangular decay distributions. For some decays, these superfluous observables
+correspond to higher partial waves that have been suppressed in the physical model; see \refapp{btokstarll} for such a case.}
+Since $L$ depends on the construction of the particle detector at hand, it remains for
 the experimental collaborations to determine the maximum order of such an expansion.
+}
 
@@
     8\pi S_{0, 0,  0} & = 1\,,                                                             &
+    8\pi S_{0, 1,  0} & = \frac{K_{2cc} + 2 K_{2ss}}{\rmdx\Gamma/\rmdx{q^2}}\,,
+\end{aligned}
+\end{equation}
+and
+\begin{equation}
+\begin{aligned}
+%
+                      &                                                                    &
+    8\pi S_{1, 1, -1} & = \frac{6 K_{4s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       \\
+%
     8\pi S_{1, 0,  0} & = \frac{3 K_{1c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
-    8\pi S_{2, 0,  0} & = \frac{2(K_{1cc} - K_{1ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
-    8\pi S_{0, 1,  0} & = \frac{K_{2cc} + 2 K_{2ss}}{\rmdx\Gamma/\rmdx{q^2}}\,,            &
-    8\pi S_{1, 1,  0} & = \frac{3 K_{2c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
+    8\pi S_{1, 1,  0} & = \frac{3 K_{2c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       \\
+%
+                      &                                                                    &
+    8\pi S_{1, 1, +1} & = \frac{6 K_{3s}}{\rmdx\Gamma/\rmdx{q^2}}\,,
+\end{aligned}
+\end{equation}
+and
+\begin{equation}
+\begin{aligned}
+%
+                      &                                                                    &
+    8\pi S_{2, 1, -1} & = \frac{2 \sqrt{3} K_{4sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,             \\
+%
+    8\pi S_{2, 0,  0} & = \frac{2(K_{1cc} - K_{1ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           &
     8\pi S_{2, 1,  0} & = \frac{2(K_{2cc} - K_{2ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
+%
                       &                                                                    &
-    8\pi S_{1, 1, -1} & = \frac{6 K_{4s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
-    8\pi S_{2, 1, -1} & = \frac{2 \sqrt{3} K_{4sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,             \\
-                 &                                                                    &
-    8\pi S_{1, 1, +1} & = \frac{6 K_{3s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
     8\pi S_{2, 1, +1} & = \frac{2 \sqrt{3} K_{3sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,
@@
 \begin{equation}
-    P(x|\lbrace S_i^{(j)}\rbrace)\,,\quad\text{with}\quad S_i^{(j)} = \frac{1}{8\pi}\left(\delta_{i,(0,0,0)} + \delta_{i,j}\right)\,,
+    \label{eq:recipe:lambdabtolambdall}
+    P(x|\lbrace S_i^{(j)}\rbrace)\,,\quad\text{with}\quad S_i^{(j)} = \frac{1}{8\pi}
+        \begin{cases}
+            \delta_{i,(0,0,0)}                  & j = (0, 0, 0)\\
+            \delta_{i,(0,0,0)}  + \delta_{i,j}  & j \neq (0, 0, 0)
+        \end{cases}
 \end{equation}
-where $j$ ís now also a multi-index representing $j \equiv (\tilde l_1, \tilde l_2, \tilde m)$.
+where $j$ is now also a multi-index representing $j \equiv (\tilde l_1, \tilde l_2, \tilde m)$.
 
@@
     8\pi S_{1, 1, +1} & = \frac{6 J_{5i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                     &
-    8\pi S_{1, 2, +1} & = \frac{4 \sqrt{3} J_{5i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,
+    8\pi S_{1, 2, +1} & = \frac{4 \sqrt{3} J_{5}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,
 \end{aligned}
@@
                       &                                                                                    &
-    8\pi S_{1, 2, -1} & = \frac{6 J_{?}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                      &
-    8\pi S_{1, 2, -1} & = \frac{4 \sqrt{3} J_{?}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                             \\
+    8\pi S_{2, 1, -1} & = \frac{4 \sqrt{3} J_{8i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                            &
+    8\pi S_{2, 2, -1} & = \frac{8 J_8}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                        \\
 %
-    8\pi S_{2, 0,  0} & = \frac{4 (J_{2c} + 2 J_{2s})}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                        &
+    8\pi S_{2, 0,  0} & = \frac{4 (J_{2c} + 2 J_{2s})}{3\, \rmdx{\Gamma}/\rmdx{q^2}}\,,                    &
     8\pi S_{2, 1,  0} & = \frac{4 J_{2i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                     &
-    8\pi S_{2, 2,  0} & = \frac{8 (J_{2c} - J_{2s})}{3 \rmdx{\Gamma}/\rmdx{q^2}}\,,                        \\
+    8\pi S_{2, 2,  0} & = \frac{8 (J_{2c} - J_{2s})}{3\, \rmdx{\Gamma}/\rmdx{q^2}}\,,                      \\
+%
+                      &                                                                                    &
+    8\pi S_{2, 1, +1} & = \frac{4\sqrt{3} J_{4i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                             &
+    8\pi S_{2, 2, +1} & = \frac{8 J_{4}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                      \\
+%
+                      &                                                                                    &
+                      &                                                                                    &
+    8\pi S_{2, 2, +2} & = \frac{8 J_3}{\rmdx{\Gamma}/\rmdx{q^2}}                                           \\
 \end{aligned}
@@
 \begin{equation}
-    P(x|\lbrace S_k^{(j)}\rbrace)\,,\quad\text{with}\quad S_k^{(j)} = \frac{1}{8\pi}\left(\delta_{k,0} + \delta_{k,j}\right)\,,
+    \label{eq:recipe:btokstarll}
+    P(x|\lbrace S_i^{(j)}\rbrace)\,,\quad\text{with}\quad S_i^{(j)} = \frac{1}{8\pi}
+        \begin{cases}
+            \delta_{i,(0,0,0)}                  & j = (0, 0, 0)\\
+            \delta_{i,(0,0,0)}  + \delta_{i,j}  & j \neq (0, 0, 0)
+        \end{cases}
 \end{equation}
 where also $j$ is now a multi-index representing $j \sim (l_1, l_2, m)$.
+
+\danny{
+To conclude this section, we remind that the angular momentum $l_2$, associated with the angle $\theta$, is not bounded from above.
+This has to be considered if partial waves beyond the P-wave are included in the analysis, see e.g. \cite{Das:2014sra}.
+However, our choice of basis is well suited to these applications with $0 \leq l < \infty$. Note, that the
+physical range of $m$ is not affected by higher partial waves.
+}
 
@@
         S_{j,m}
-            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) A_{2}^{*(l_2)}p_{l_2}^{(m_2)}(\cos\theta)\right]\\
-            & = \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} A_{2}^{*(l_2)}\right] \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
+            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta) A_{2}^{*(l_2)}p_{l_2}^{(m_2)}(\cos\theta)\right]\\
+            & = \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{(l_1)} A_{2}^{*(l_2)}\right] \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
     \end{aligned}

### 2015-01-22 draft.tex
[draft] change notation in detector-acceptance section
o explicitly state the assumptions
o replace eps by E in most places

@@
 \newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
+\newcommand{\subd}{_{\text{d}}}
+\newcommand{\subt}{_{\text{t}}}
 \newcommand{\thvec}{\vec{\vartheta}}
@@
 \newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
+\newcommand{\xd}{x\subd}
+\newcommand{\xt}{x\subt}
+\newcommand{\Ekernel}{E(\xd|\xt)}
 
@@
 
-\subsection{Recipe for the Determination of Detector Acceptance Effects}
+\subsection{Recipe for the Determination of Detector Effects}
 \label{sec:systematics:acceptance}
@@
 \begin{equation}
-    P_\text{d}(x_\text{d}) = \int P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}}\,.
+    P_\text{d}(x_\text{d}) = \frac{1}{R} \int P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}}\,.
 \end{equation}
 Here $P_\text{t}$ is the probability distribution of the true events,
+\fred{the normalization constant $R$ is given by
+\begin{equation}
+    R \equiv \int \int P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}} \rmdx{x_\text{d}}\,,
+\end{equation}
 and the kernel $E(x_\text{d}| x_\text{t})$ parametrizes acceptance and
-resolution effects. Note that $P_\text{d}$ is \emph{not} a PDF, since
-it is not normalized,
-\begin{equation}
-    \int P_\text{d}(x) \rmdx{x} \neq 1\,.
-\end{equation}
-For the sake of clarity, we will restrict ourselves
-to pure acceptance effects and suppress resolution effects in the remainder of this section; i.e.,
-\begin{equation}
-    E(x_\text{d}, x_\text{t}) \equiv \eps(x_\text{t}) \delta(x_\text{d}, x_\text{t})\,.
-\end{equation}
-We will refer to $\eps$ as the \emph{detector acceptance} function. In what follows,
-we propose a systematic methods to unfold all effects of $\eps$ through MC simulations
-and the method of moments.\\
-
-We will now proceed with the explicit usage of a uniangular PDF with $x = \cos\theta$.\footnote{%
-    The generalization of this section to multiangular PDFs is straighforward. It can be achieved
-    by promoting $x$ to a vector, promoting the Legendre polynomials to products of independent polynomials
-    or spherical harmonics, and promoting the indices $i,j,k,m$ to multi-indices.
+resolution effects. The kernel is usually decomposed as
+\begin{equation}
+  \Ekernel = \eps(\xt) P(\xd|\xt),
+\end{equation}
+where the PDF $P(\xd|\xt)$ includes the resolution effects and the
+unnormalized density $\eps(\xt)$ is the \emph{detector acceptance}
+function. Perfect resolution corresponds to
+\begin{equation}
+  \label{eq:def-R}
+  P(\xd|\xt) = \delta(\xd - \xt) \,.
+\end{equation}
 }
-Let us define the PDF in terms of the Legendre polymials (i.e., $f_k(x) \equiv P_k(x)$),
-\begin{equation}
-    P(x) \equiv \sum_k S_k f_k(x),
-\end{equation}
-where $k = 0, 1, \dots$ denotes the total angular momentum of the observables.
-From the normalization of the PDF then follows $S_0 = 1/2$. From positivity of $P$ one
-obtains $|S_k| \leq 1/2$ for angular momentum $k > 0$. More stringent relations between the
-$S_k$ might hold, but are beyond the scope of this work. For latter use, we define
-$\vec{S}^{(m)}_k \equiv 1/2 (\delta_{k,0} + \delta_{k,m})$, and we emphasize that
-\begin{equation}
-    P^{(m)}(x) \equiv P(x | \lbrace S^{(m)}_k \rbrace)
-\end{equation}
-is a PDF. The dual basis of angular functions follows then from the normalization
+% For the sake
+% of clarity, we will restrict ourselves to pure acceptance effects and
+% suppress resolution effects in the remainder of this section; i.e.,
+% \begin{equation}
+%     E(x_\text{d}, x_\text{t}) \equiv \eps(x_\text{t}) \delta(x_\text{d}, x_\text{t})\,.
+% \end{equation}
+% We will refer to $\eps$ as the \emph{detector acceptance} function.
+In what follows, we propose a systematic method to unfold all effects
+of \fred{$\Ekernel$} through MC simulations and the method of moments
+\fred{assuming that $\Ekernel$ is independent of the angular
+  observables, and that it is possible to expand $\Ekernel$ --- at
+  least formally --- in Legendre polymials}.  For illustration, we
+proceed with the explicit example of a uniangular\footnote{%
+  The generalization of this section to multiangular PDFs is
+  straighforward. It can be achieved by promoting $x$ to a vector,
+  promoting the Legendre polynomials to products of independent
+  polynomials or spherical harmonics, and promoting the indices
+  $i,j,k,m$ to multi-indices.  } PDF with $x = \cos\theta$. Let us
+define the PDF in terms of the Legendre polymials (i.e., $f_k(x)
+\equiv P_k(x)$) \fred{and angular observables $\lbrace S_k \rbrace$ as
+\begin{equation}
+    P\subt(\xt) \equiv P\subt(\xt | \lbrace S_k \rbrace) =   \sum_k S_k f_k(\xt),
+  \end{equation}}
+where $k = 0, 1, \dots$ denotes the total angular momentum of the observables \fred{adjust ``angular momentum'' to language at the end of the section}.
+\fred{Normalization of $P\subt$ is equivalent to choosing} $S_0 = 1/2$.
+\fred{Requiring $P\subt(\xt) \ge 0 \,\forall \xt$ implies} $|S_k| \leq 1/2$ for angular momentum \fred{$k$ just an index, can we remove ``angular momentum''?} $k > 0$.
+More stringent relations between the
+$S_k$ might hold, but are beyond the scope of this work. For later use, we define
+\fred{
+  \begin{equation}
+    \label{eq:def-Sk}
+  \vec{S}^{(m)}_k \equiv
+  \begin{cases}
+    1/2 \delta_{k,0}, & m=0\\
+    1/2 (\delta_{k,0} + \delta_{k,m}), & m>0 \,,
+  \end{cases}
+\end{equation}}
+and \fred{note} that
+\begin{equation}
+    P^{(m)}(\fred{\xt}) \equiv P(\fred{\xt} | \lbrace S^{(m)}_k \rbrace)
+\end{equation}
+is a \fred{valid} PDF. The dual basis of angular functions follows then from the normalization
 and orthogonality of the Legendre polynomials, and one therefore has
@@
 \end{equation}
-
-We now define the \emph{simulated raw} moments $\lbrace Q_{i}^{(m)}\rbrace$,
-\begin{equation}
-    Q_i^{(m)} \equiv \int_{-1}^{+1} \tilde{f}_i(x) P^{(m)}(x) \eps(x) \rmdx{x} = \frac{1}{2} \int_{-1}^{+1} \tilde{f}_i(x) \big[f_0(x) + f_m(x)\big] \eps(x) \rmdx{x}\,,
+We now define the \emph{simulated raw} moments $\lbrace Q_{i}^{(m)}\rbrace$ as
+\begin{equation}
+    Q_i^{(m)} \equiv \fred{\int \int \tilde{f}_i(\xd) P^{(m)}(\xt) \Ekernel \rmdx{\xt} \rmdx{\xd},}
 \end{equation}
 which are instrumental to our recipe.
-MC estimators for these simulated moments can be constructed from specifically crafted detector events $x_\text{d}^{(n,m)}$, $n = 1, \dots, N_\text{d}^{(m)}$, where
-\begin{equation}
-    x_\text{d}^{(n,m)} \sim P_\eps^{(m)} \equiv \frac{P^{(m)} \eps}{R^{(m)}}\,.
-\end{equation}
-Here the normalization $R^{(m)}$ is chosen such that $\int P_\eps^{(m)}(x) \rmdx{x} = 1$.
-We emphasize that $R^{(m)}$ can estimated as $\est{R}^{(m)} = N_\text{d}^{(m)} / N_\text{t}$, where $N_\text{t}$ corresponds to the number of simulated true events.
-The estimators then read
+\fred{Monte Carlo} estimators of these moments can be constructed from specifically crafted detector events $x_\text{d}^{(n,m)}$, $n = 1, \dots, N_\text{d}^{(m)}$, where
+\begin{equation}
+    x_\text{d}^{(n,m)} \sim \fred{P_E^{(m)}(\xd) \equiv \frac{1}{R^{(m)}} \int P^{(m)}(\xt) \Ekernel \rmdx{\xt}}\,.
+  \end{equation}
+  \fred{In words, for each $m$ it is required to generate events from
+    a toy physical distribution in which $S_0 = S_m=1/2$ and all other
+    observables are set to zero, and to propagate those events through
+    a detector simulation.} The normalization $R^{(m)}$ is chosen such
+  that \fred{$\int P_E^{(m)}(\xd) \rmdx{\xd} = 1$}.  We emphasize that
+  $R^{(m)}$ can be estimated as $\est{R}^{(m)} = N_\text{d}^{(m)} /
+  N_\text{t}$, where $N_\text{t}$ corresponds to the number of
+  simulated true events.  The estimators then read
 \begin{equation}
@@
 
-Linearity of the integral over $x$ and convergence of the expansion of $P_\eps^{(m)}$ in terms Legendre polynomials ensures that
+Linearity of the integral over $x$ and convergence of the expansion of
+$P_E^{(m)}$ in terms of Legendre polynomials ensures that
 \begin{equation}
@@
 \end{equation}
-We call the matrix $M_{ij}$ the \emph{unfolding matrix}, which is specific to our decay at hand. Given our definition of
-$S_k^{(m)}$ it can easily be calculated as
+We call the matrix $M_{ij}$ the \emph{unfolding matrix}, which is
+specific to the decay at hand. Given our definition of $S_k^{(m)}$ in
+\fred{\refeq{def-Sk} it is easy to see that}
 \begin{equation}
@@
 \end{equation}
-Here $R \equiv \int P(x) \eps(x)$ is an a priori unknown normalization that also occurs in the determination of the branching
-ratio of the specific decay. We then obtain MC estimators of the angular observables via
+We then obtain MC estimators of the angular observables via
 \begin{equation}
@@
 \end{equation}
-The precise value of $R$ depends on the a priori unknown angular observables $\lbrace S_i\rbrace$.
-However, ratios and other suitable combinations of the estimators $\lbrace \est{S}_i\rbrace$ are independent
-of $R$. Conversely, $R$ can be extracted from the self-consistency condition\footnote{This condition
-is process dependent; see \refeq{recipe:lambdabtolambdall} and \refeq{recipe:btokstarll}.}
-$\hat{S}_0 = \frac{1}{2}$. Since $R$ is relevant in the determination of the branching ratio, it is therefore useful
-to carry out that determination and the extraction of the angular observables in a combined analysis.
+The precise value of $R$ (see \refeq{def-R}) depends on the a priori
+unknown angular observables $\lbrace S_i\rbrace$.  However, ratios and
+other suitable combinations of the estimators $\lbrace
+\est{S}_i\rbrace$ are independent of $R$. Conversely, $R$ can be
+extracted from the self-consistency condition\footnote{This condition
+  is process dependent; see \refeq{recipe:lambdabtolambdall} and
+  \refeq{recipe:btokstarll}.}  $\hat{S}_0 = \frac{1}{2}$. Since $R$ is
+relevant in the determination of the branching ratio, it is therefore
+useful to carry out that determination and the extraction of the
+angular observables in a combined analysis.
 
@@
 correspond to higher partial waves that have been suppressed in the physical model; see \refapp{btokstarll} for such a case.}
-Since $L$ depends on the construction of the particle detector at hand, it remains for
+Since $L$ depends on the \fred{setup} of the particle detector \fred{under consideration}, it remains for
 the experimental collaborations to determine the maximum order of such an expansion.
@@
 comment on the MC-induced uncertainties. As usual, one needs to find a balance between
-compute time and accuarcy. We find for a uniangular distribution and a total of $6\cdot 10^6$ MC
-samples (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$) that the error on the mean is
+compute time and accuracy. \fred{For a uniangular distribution and a total of $6\cdot 10^6$ MC
+samples (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find} that the error on the mean is
 smaller than $6\cdot 10^{-4}$. Let us conclude this section by commenting that the unfolding

### 2015-01-22 draft.tex
[draft] Rewrite abstract

@@
 \begin{abstract}
-In this letter we study how to obtain a set of angular observables
-$\{S_i\}$ that arise in a generic multi-body process without the need
-to carry out a likelihood fit of an angular distribution to the
-measured events. Instead, we present a method that only relies on
-orthogonality of angular functions, and estimation of integrals
-by means of Monte Carlo techniques. Beyond providing estimators
-for central values and uncertainties, we provide means to determine
-the correlation between all angular observables. We show that detector
-acceptance effects can be accounted for in the analysis.
+  \fred{Our goal is to obtain a complete set} of angular observables
+  arising in a generic multi-body process without the need to carry
+  out a likelihood fit of the angular distribution to the measured
+  events. Instead, we \fred{apply the method of moments} that relies
+  both on the orthogonality of angular functions and the estimation of
+  integrals by Monte Carlo techniques. \fred{The main advantage of
+    this method is that the joint distribution of all observables
+    given the data can be easily extracted, even for very few
+    events. Our main contribution is to show explicitly how systematic
+    uncertainties from detector-resolution and acceptance effects can
+    be incorporated in a general algorithm. Finally, we present the
+    necessary process-dependent formulae needed for direct
+    implementation of the method for several rare decays currently of
+    interest.}
 \end{abstract}

### 2015-01-22 draft.tex
[draft] comments on sec. III and appendix

@@
 result for $P$.  In this section, we focus on one particular class of
-mismodelling of the signal PDF: the angular momentum-cutoff in partial
+mismodelling of the signal PDF: the angular-momentum cutoff in partial
 wave expansions. This mismodelling potentially affects a large number
@@
 
-\subsection{Recipe for the Determination of Detector Effects}
+\subsection{Recipe for \fred{Including} Detector Effects}
 \label{sec:systematics:acceptance}
@@
 In order to finally extract the angular observables from data, we use the \emph{measured raw moments}. Their MC estimator
-$\lbrace \est{Q}_i\rbrace$ -- based on the \emph{detected events} $x^{(n)}$, $n=1,\dots,N$ -- reads
+$\lbrace \est{Q}_i\rbrace$ --- based on the \emph{detected events} $x^{(n)}$, $n=1,\dots,N$ --- reads
 \begin{equation}
@@
             \label{fig:errors}
+            \fred{Plots convey exactly was is said in words. I see they are useful for a talk, but do we really need them in the write-up?}
 \end{figure}
@@
 
-Let us assume that the angular decomposition has been achieved for some
-PDF $P$ for all angles except one, which we label $\theta$. We now focus on only of of the resulting
-observables, which we label $S(\theta) \equiv S(\vec{\nu},\theta)$. The dependence on the non-angular
-variables will be suppressed in the following. \danny{Fred: is this less confusing now?}
-Further, let $S$ have an expansion in terms of partial waves
-$l_1, l_2 = 0,1,2,\dots \hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
+Let us assume that the angular decomposition has been achieved for
+some PDF $P$ for all angles except for one angle $\theta$. We now
+focus on just one of the resulting observables and denote it by
+$S(\theta)$. The dependence on the non-angular variables will be
+ignored in the following. \fred{I rephrased it sligthly} Suppose $S$
+has an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots
+\hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
 \begin{equation}
@@
 \end{equation}
-Using the large-$l$ behaviour of $n_{l,m}$ one finds that with increasing $l_i$ the partial-wave amplitudes must asymptotically fall off as \fred{Let's say why.
-Unitarity?} \danny{Finiteness of observables, so yes: unitarity!}
+Using the large-$l$ behaviour of $n_{l,m}$ one finds that with
+increasing $l_i$ the partial-wave amplitudes must asymptotically fall
+off as \fred{Let's say why. Unitarity?} \danny{Finiteness of
+  observables, so yes: unitarity!} \fred{So can't we just say
+  unitarity before the first equation? That's the reason why the sum
+  need be finite, I guess.
+But if I look at (D2) again, it goes down as $1/(2l + 1)$, so If remember correctly, $A_i^{(l_i)} \propto 1/l^{\eps}$ would be enough to ensure convergence.
+So why $1/\sqrt{l_i}$?}
 \begin{equation}
@@
 
-Will will show in the following that such a cut off
+Will will show in the following that such a cutoff
 is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$. Since this expansion implies
@@
 consist of sums with infinitely many terms. It is then up to theoretical analyses to
-estimate or calculate the impact of individual contributions, with or without the cut off $L$.
+estimate or calculate the impact of individual contributions, with or without the cutoff $L$.
 For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
-We close by remarking that for any angular-momentum cut off $l < L$\fred{Do you mean $L < \infty$?}, one can find an upper limit for the squared sum of all remaining partial waves through a comparison with the inclusive decay
+We close by remarking that for any angular-momentum cutoff $l < L$\fred{Do you mean $L < \infty$?}, one can find an upper limit for the squared sum of all remaining partial waves through a comparison with the inclusive decay
 width.

### 2015-01-22 draft.tex
Changes after another discussion with Fred

@@
     necessary process-dependent formulae needed for direct
-    implementation of the method for several rare decays currently of
+    implementation of the method for several rare decays of
     interest.}
@@
 
-The initial motivation for studying what we wish to call the
+Our initial motivation for studying what we wish to call the
 \emph{method of moments} is the determination of angular observables
 in the rare decay FCNC-mediated decay $\bar{B}\to \bar{K}^*(\to
-\bar{K}\pi)\ell^+\ell^-$. However, we emphasize that the method we
-describe in this letter is general, and it applies to arbitrary decay
+\bar{K}\pi)\ell^+\ell^-$. However, note that the method we
+describe in the following is general, and it applies to arbitrary decay
 or scattering processes. We find a previous work \cite{Dighe:1998vk}
-advocates this method chiefly for the determination of angular
+that advocates this method chiefly for the determination of angular
 observables in non-leptonic $B$ decays, but also mentions the
-applicability to semileptonic decays. We improve upon this previous
-work by studying correlations \fred{really? because of higher $l$}
-between the angular observables, and by showing explicitly how to
-incorporate uncertainties due to acceptance effects. Moreover, we show
+applicability to semileptonic decays. Our aim is to improve upon this previous
+work by studying the uncertainties that are introduced by mismodelling
+of the angular distribution, and by working out a recipe to determine
+and unfold detector effects. Moreover, we show
 that the method of moments has two major advantages over the usual
@@
 We continue with basic definitions that pertain to angular observables, and our
-results in the subsequent sections. Let $\thvec = (\theta_1, \dots \theta_N)$ denote the set of all
-angles, and let $\nuvec = (\nu_1, \dots \nu_M)$ denote the set of all
+results in the subsequent sections. Let $\thvec$ denote the set of all
+angles, and let $\nuvec$ denote the set of all
 other non-angular kinematic variables needed to fully specify the
@@
 \end{align}
-Here, the dependence on the $n$ decay angles $\thvec$ has been
+Here, the dependence on the decay angles $\thvec$ has been
 explicitly factored out in terms of the angular functions
@@
     \label{eq:def-ortho-rel}
-    \int_\Omega \rmdx{^N \theta} \dual{f}_i(\thvec) f_j(\thvec)  = \delta_{ij}
+    \int_\Omega \rmdx{\vec{\theta}} \dual{f}_i(\thvec) f_j(\thvec)  = \delta_{ij}
 \end{equation}
@@
     \label{eq:def-P-decay}
-    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\rmdx{^{N+M}\Gamma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
+    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\rmdx{^{2}\Gamma}}{\rmdx{\vec\nu} \rmdx{\vec\theta}}\,,
 \end{align}
@@
     \label{eq:def-P-scattering}
-    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\rmdx{^{N+M}\sigma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
+    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\rmdx{^{2}\sigma}}{\rmdx{\vec\nu} \rmdx{\vec\theta}}\,,
 \end{align}
@@
 the angular observables $\lbrace S_i\rbrace$; thus ratios or similar suitable combinations
-of the angular observables are invariant.\\
-
-% Our method is closely related to Pearson's method of moments
-% \citeneeded{}. One draws samples from a PDF $P(x | \nuvec)$ that
-% depends on parameters $\nuvec$. Then one approximates the population
-% (central) moments $x^k$ by the sample moments
+of the angular observables are not affected by this change of normalization.\\
+
 Our method is an extension of the classical method of moments with
@@
     \label{eq:det-Pi-analytical}
-    S_i(\nuvec) = \int_{\Omega} \rmdx{^N \theta}  P(\nuvec, \thvec) \dual{f}_i(\thvec)\,.
+    S_i(\nuvec) = \int_{\Omega} \rmdx{\vec\theta}  P(\nuvec, \thvec) \dual{f}_i(\thvec)\,.
 \end{equation}
 where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular functions. In general, $\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$. This is the
-case for our selection of applications in appendices \ref{app:btokll} through \ref{app:lambdabtolambdall}.\\
+case for our selection of applications in appendices \ref{app:btokll} through \ref{app:btokstarll}.\\
 
@@
     \langle S_i\rangle
-    \equiv \int \rmdx{^M \nu} S_i(\nuvec)
-    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta} P(\nuvec,\thvec) \dual{f}_i(\thvec) \right].
+    \equiv \int \rmdx{\vec\nu} S_i(\nuvec)
+    = \int \rmdx{\vec \nu} \left[\int_{\Omega} \rmdx{\vec \theta} P(\nuvec,\thvec) \dual{f}_i(\thvec) \right].
 \end{equation}
@@
     \label{eq:mc-id}
-    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1}^K g(x^{(k)}) \,,\,    x^{(k)} \sim P
-\end{equation}
-due to the strong law of large numbers for $K \to \infty$, assuming
-that the variates $x^{(k)}$, $k = 1, \dots, K$, are distributed as
+    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{N} \sum_{n=1}^N g(x^{(n)}) \,,\,    x^{(n)} \sim P
+\end{equation}
+due to the strong law of large numbers for $N \to \infty$, assuming
+that the variates $x^{(n)}$, $n = 1, \dots, N$, are distributed as
 $P$.
@@
 \begin{equation}
-    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})\,.
+    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{N} \sum_{n=1}^{N} \dual{f}_i(x^{(n)})\,.
 \end{equation}
@@
     \langle S_i\rangle_{\vec{a},\vec{b}}
-    & \equiv \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
-    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} P(\nuvec,\thvec) \dual{f}_i(\thvec)  \right]\\
-    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta}  P(\nuvec,\thvec) \dual{f}_i(\thvec)
+    & \equiv \int_{\vec{a}}^{\vec{b}} \rmdx{\nuvec} S_i(\nuvec)\\
+    & = \int_{\vec{a}}^{\vec{b}} \rmdx{\nuvec} \left[\int_{\Omega} \rmdx{\vec\theta} P(\nuvec,\thvec) \dual{f}_i(\thvec)  \right]\\
+    & = \int \rmdx{\nuvec} \left[\int_{\Omega} \rmdx{\vec\theta}  P(\nuvec,\thvec) \dual{f}_i(\thvec)
         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
@@
     \widehat{\langle S_i\rangle_{\vec{a},\vec{b}}}
-    = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
+    = \frac{1}{N} \sum_{n=1}^{N} \dual{f}_i(x^{(n)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
 \end{equation}
 For notational simplicity, let us forget about the $\nuvec$
-integration and consider only $S_i$. In the limit $K \to \infty$, the
+integration and consider only $S_i$. In the limit $N \to \infty$, the
 central limit theorem (CLT) implies that the random vector
@@
   \label{eq:angular-obs-vec}
-  \vecest{S} \equiv (S_1, \dots, S_i\,,
+  \vecest{S} \equiv (\est{S_0}, \dots, \est{S_i}\,,
   \dots)
 \end{equation}
-follows a multivariate Gaussian distribution $\mathcal{N}( \vec{S},
+follows a multivariate Gaussian distribution $\mathcal{N}(\vec{S},
 \widehat{\Sigma})$ centered on the true value $\vec{S}$ with the
@@
 \begin{equation}
-    \cov[S_i,S_j] \to \est{\cov}[{S}_i, {S}_j]
-        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\dual{f}_i(x^{(k)}) - \est{ S_i}\big]\,\big[\dual{f}_j(x^{(k)}) - \widehat{ S_j}\big]\,.
+    \Sigma_{ij} \equiv \cov[S_i,S_j] \to \est{\Sigma_{ij}} \equiv \est{\cov}[{S}_i, {S}_j]
+        = \frac{1}{N - 1} \sum_{n=1}^{N} \Big[\dual{f}_i\big(x^{(n)}\big) - \est{S_i}\Big]\,\Big[\dual{f}_j\big(x^{(n)}\big) - \widehat{S_j}\Big]\,.
 \end{equation}
@@
 version of the CLT to hold --- finite mean and covariance of
-$\dual{f}_i$ --- are automatically satisfied.  We would like to
-emphasize that the sample covariance should \fred{``Should'' as in it
-  does in practice? Reference toy studies below} rapidly converge
-towards the true covariance matrix.  We propose to declare convergence
-\fred{I'd prefer: check that skewness and kurtosis are sufficiently
-  small} once estimators for skewness and kurtosis are sufficiently
-small,
-
-\begin{equation}
-    \est{\operatorname{Skew}}[S_i,S_j] \leq B_S\,\,\text{ and }\,\,\est{\kurt}[S_i,S_j] \leq B_K\,.
-\end{equation}
-where the limits $B_S$ and $B_K$ should be determined from process-specific dedicated toy studies.\\
+$\dual{f}_i$ --- are automatically satisfied.
+In our numerical analysis the sample covariance rapidly converges towards the true covariance
+matrix; see also \refsec{numerics}.\\
 
@@
   the likelihood is near the boundary of the physically allowed
-  region.\fred{Is there some LHCb note we could cite?} In many of the
-  decays of interest, there are only say dozens\todo{check!} of events recorded.
+  region.\fred{Is there some LHCb note we could cite?} 
+  For some of these decays of interest, there are only $\order{10}$ of events
+  per bin on record.
 \item The estimate is unbiased for any $N$. In contrast, the
@@
   the bias usually leads to an increase in variance of the sampling
-  distribution of the estimator~\cite[sec. 7.3]{James:2006zz}. From a
+  distribution of the estimator and vice versa~\cite[sec. 7.3]{James:2006zz}. From a
   Bayesian decision-theory point of view, both contribute similarly to
@@
     Descotes-Genon:2013wba,Bobeth:2013soa},
-  or for more precise predictions of optimized observables; e.g.,
+  or for more precise predictions of optimized observables; see e.g.,
   \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
@@
   in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
-  likelihood also approaches a multivariate Gaussian as $K \to
+  likelihood also approaches a multivariate Gaussian as $N \to
   \infty$, the two methods differ in their utility as input for
@@
   angular observables that are constrained to a triangular region by
-  phase-space or unitarity arguments as \fred{Could add a sketch. It
-    is supposed to resemble $A_{\text{FB}},F_L$ for $B \to K^* \ell
-    \ell$.}
+  phase-space or unitarity arguments as
   \begin{equation}
@@
   proved to be challenging due to technical reasons (data formats,
-  size etc.) and the fear that theorists misinterprete the many
+  size etc.) and the fear that theorists misinterpret the many
   nuisance parameters (from control channels, detector calibrations
   etc.) that are also part of the likelihood. This leads to the
-  undesirable situation that that only the mode and standard errors
+  undesirable situation that only the mode and standard errors
   are reported, and theorists often include the results as independent
@@
 of decays and scattering processes. For the sake of clarity we take
-the interesting class of four-body decays $B\to P_1 P_2 \ell_1
-\bar\ell_2$ \fred{How general is this? The plot implies that the
-  dimeson and the dilepton do not have a common vertex. But this
-  requires an intermediate state, e.g., $K^{*}$}as an
-example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B
+the interesting class of four-body decays $B\to P_1 P_2 \ell_1$
+as an example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B
   \to K\pi\ell^+\ell^-$, and the $V_{ub}$ suppressed decay $B\to
@@
   of $S$, $P$
-  and $D$ interference, see \cite{Das:2014sra}}.\\
+  and $D$ interference, see \cite{Das:2014sra}
+}.\\
 
@@
 with respect to the remaining angle $\theta_2$. Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
-and as defined in \refapp{partial-waves} \fred{A lot of mixing between appendices C and E}, the expansion reads
+and as defined in \refapp{partial-waves}, the expansion reads
 \begin{equation}
@@
 partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. To wit,
-ignoring further (orthogonal) terms in the PDF cannot affect the mean vector $(\dots, S_k, \dots)$ nor its variance. \fred{yes!}\\
+ignoring further (orthogonal) terms in the PDF cannot affect $\vec{S}$ nor its variance.\\
 
@@
 analyses to estimate or calculate the impact of partial waves beyond the S and P wave contributions.
-(For $B\to K\pi\ell^+\ell^-$ a first study has been carried out where contributions up to the D wave are studied \cite{Das:2014sra}).\\
+(For $B\to K\pi\ell^+\ell^-$ a first study has been carried out where contributions up to the D wave are investigated \cite{Das:2014sra}).\\
 
@@
 Here $P_\text{t}$ is the probability distribution of the true events,
-\fred{the normalization constant $R$ is given by
-\begin{equation}
-    R \equiv \int \int P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}} \rmdx{x_\text{d}}\,,
+the normalization constant $R$ is given by
+\begin{equation}
+    R \equiv \iint P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}} \rmdx{x_\text{d}}\,,
 \end{equation}
@@
 \end{equation}
-where the PDF $P(\xd|\xt)$ includes the resolution effects and the
+where the PDF $P(\xd|\xt)$ models the resolution effects and the
 unnormalized density $\eps(\xt)$ is the \emph{detector acceptance}
@@
 \end{equation}
-}
-% For the sake
-% of clarity, we will restrict ourselves to pure acceptance effects and
-% suppress resolution effects in the remainder of this section; i.e.,
-% \begin{equation}
-%     E(x_\text{d}, x_\text{t}) \equiv \eps(x_\text{t}) \delta(x_\text{d}, x_\text{t})\,.
-% \end{equation}
-% We will refer to $\eps$ as the \emph{detector acceptance} function.
+
 In what follows, we propose a systematic method to unfold all effects
-of \fred{$\Ekernel$} through MC simulations and the method of moments
-\fred{assuming that $\Ekernel$ is independent of the angular
+of $\Ekernel$ through MC simulations and the method of moments
+assuming that $\Ekernel$ is independent of the angular
 observables, and that it is possible to expand $\Ekernel$ --- at
-  least formally --- in Legendre polymials}.  For illustration, we
+least formally --- in Legendre polymials.  For illustration, we
 proceed with the explicit example of a uniangular\footnote{%
@@
 define the PDF in terms of the Legendre polymials (i.e., $f_k(x)
-\equiv P_k(x)$) \fred{and angular observables $\lbrace S_k \rbrace$ as
-\begin{equation}
-    P\subt(\xt) \equiv P\subt(\xt | \lbrace S_k \rbrace) =   \sum_k S_k f_k(\xt),
-  \end{equation}}
-where $k = 0, 1, \dots$ denotes the total angular momentum of the observables \fred{adjust ``angular momentum'' to language at the end of the section}.
-\fred{Normalization of $P\subt$ is equivalent to choosing} $S_0 = 1/2$.
-\fred{Requiring $P\subt(\xt) \ge 0 \,\forall \xt$ implies} $|S_k| \leq 1/2$ for angular momentum \fred{$k$ just an index, can we remove ``angular momentum''?} $k > 0$.
-More stringent relations between the
+\equiv P_k(x)$) and angular observables $\vec{S}$ as
+\begin{equation}
+    P\subt(\xt) \equiv P\subt(\xt | \vec{S}) = \sum_k S_k f_k(\xt),
+  \end{equation}
+where $k = 0, 1, \dots$ denotes an angular-momentum-like index associated with the observables.
+Normalization of $P\subt$ is equivalent to choosing $S_0 = 1/2$. Requiring $P\subt(\xt) \ge 0 \,\forall \xt$
+implies $|S_k| \leq 1/2$ for $k > 0$. More stringent relations between the
 $S_k$ might hold, but are beyond the scope of this work. For later use, we define
-\fred{
 \begin{equation}
   \label{eq:def-Sk}
-  \vec{S}^{(m)}_k \equiv
+  S^{(m)}_k \equiv
   \begin{cases}
@@
   \end{cases}
-\end{equation}}
-and \fred{note} that
-\begin{equation}
-    P^{(m)}(\fred{\xt}) \equiv P(\fred{\xt} | \lbrace S^{(m)}_k \rbrace)
-\end{equation}
-is a \fred{valid} PDF. The dual basis of angular functions follows then from the normalization
+\end{equation}
+and note that
+\begin{equation}
+    P^{(m)}(\xt) \equiv P(\xt | \vec{S}^{(m)})
+\end{equation}
+is a valid PDF. The dual basis of angular functions follows then from the normalization
 and orthogonality of the Legendre polynomials, and one therefore has
@@
 \end{equation}
-We now define the \emph{simulated raw} moments $\lbrace Q_{i}^{(m)}\rbrace$ as
-\begin{equation}
-    Q_i^{(m)} \equiv \fred{\int \int \tilde{f}_i(\xd) P^{(m)}(\xt) \Ekernel \rmdx{\xt} \rmdx{\xd},}
-\end{equation}
-which are instrumental to our recipe.
-\fred{Monte Carlo} estimators of these moments can be constructed from specifically crafted detector events $x_\text{d}^{(n,m)}$, $n = 1, \dots, N_\text{d}^{(m)}$, where
-\begin{equation}
-    x_\text{d}^{(n,m)} \sim \fred{P_E^{(m)}(\xd) \equiv \frac{1}{R^{(m)}} \int P^{(m)}(\xt) \Ekernel \rmdx{\xt}}\,.
-  \end{equation}
-  \fred{In words, for each $m$ it is required to generate events from
-    a toy physical distribution in which $S_0 = S_m=1/2$ and all other
-    observables are set to zero, and to propagate those events through
-    a detector simulation.} The normalization $R^{(m)}$ is chosen such
-  that \fred{$\int P_E^{(m)}(\xd) \rmdx{\xd} = 1$}.  We emphasize that
+We now define the \emph{simulated raw} moments $\vec{Q}^{(m)}$ as
+\begin{equation}
+    Q_i^{(m)} \equiv \iint \tilde{f}_i(\xd) P^{(m)}(\xt) \Ekernel \rmdx{\xt} \rmdx{\xd},
+\end{equation}
+which are instrumental to our recipe. Monte Carlo estimators of these moments can be constructed from specifically crafted detector events $x_\text{d}^{(n,m)}$, $n = 1, \dots, N_\text{d}^{(m)}$, where
+\begin{equation}
+    x_\text{d}^{(n,m)} \sim P_E^{(m)}(\xd) \equiv \frac{1}{R^{(m)}} \int P^{(m)}(\xt) \Ekernel \rmdx{\xt}\,.
+\end{equation}
+In words, for each $m$ it is required to generate events from
+a toy physical distribution $P^{(m)}$ in which $S_0 = S_m=1/2$ and all other
+observables are set to zero, and to propagate these events through
+a detector simulation. The normalization $R^{(m)}$ is chosen such
+that $\int P_E^{(m)}(\xd) \rmdx{\xd} = 1$.  We emphasize that
 $R^{(m)}$ can be estimated as $\est{R}^{(m)} = N_\text{d}^{(m)} /
@@
 \begin{equation}
-    Q_i^{(m)} = \sum_j M_{ij} S_j^{(m)}\,.
-\end{equation}
-We call the matrix $M_{ij}$ the \emph{unfolding matrix}, which is
-specific to the decay at hand. Given our definition of $S_k^{(m)}$ in
-\fred{\refeq{def-Sk} it is easy to see that}
+    \vec{Q}^{(m)} = M \vec{S}^{(m)}\,.
+\end{equation}
+We call the matrix $M$ the \emph{unfolding matrix}, which is
+specific to the decay at hand.
+Given our definition of $S_k^{(m)}$ in
+\refeq{def-Sk} it is easy to see that
 \begin{equation}
@@
 \end{equation}
-and its MC estimator $\est{M}_{ij}$  can be obtained through the replacements $Q_i^{(m)} \to \est{Q}_i^{(m)}$.\\
+and its MC estimator $\est{M}$  can be obtained through the replacements $Q_i^{(m)} \to \est{Q}_i^{(m)}$.\\
 
 In order to finally extract the angular observables from data, we use the \emph{measured raw moments}. Their MC estimator
-$\lbrace \est{Q}_i\rbrace$ --- based on the \emph{detected events} $x^{(n)}$, $n=1,\dots,N$ --- reads
+$\vecest{Q}$ --- based on the \emph{detected events} $x^{(n)}$, $n=1,\dots,N$ --- reads
 \begin{equation}
@@
     \label{eq:estS}
-    \est{S}_i \equiv \sum_{i} \left(\hat{M}^{-1}\right)_{ij} \est{Q}_j\,.
+    \vecest{S}_i \equiv \left[\est{M}^{-1}\right] \vecest{Q}\,.
 \end{equation}
 The precise value of $R$ (see \refeq{def-R}) depends on the a priori
-unknown angular observables $\lbrace S_i\rbrace$.  However, ratios and
-other suitable combinations of the estimators $\lbrace
-\est{S}_i\rbrace$ are independent of $R$. Conversely, $R$ can be
+unknown angular observables $\vec S$.  However, ratios and
+other suitable combinations of the estimators $\vecest{S}$
+are independent of $R$. Conversely, $R$ can be
 extracted from the self-consistency condition\footnote{This condition
@@
 useful to carry out that determination and the extraction of the
-angular observables in a combined analysis.
-
-\danny{
-We note that the set $\lbrace \est{S}_k\rbrace$ as determined from \refeq{estS} does not fully correspond to the
-set $\lbrace S_k\rbrace$ for an arbitrary $\eps$. Taking again the decay $B\to K\ell^+\ell^-$
+angular observables in a combined analysis.\\
+
+We note that $\vecest{S}$ as determined from \refeq{estS} does not fully correspond to $\vec{S}$
+for arbitrary $\eps$. Taking again the decay $B\to K\ell^+\ell^-$
 as an example, we have $\dim S = 3$. Assuming an expansion of the detector acceptance $\eps$
-in terms of Legendre polynomial up to order $L$, we obtain $\dim \est{Q} = \dim \est{S} = \dim S + L$.
-The MC estimators then have the following structure:
+in terms of Legendre polynomial up to order $L$, we have to calculate the raw moments up
+to $\dim \est{Q} = \dim \est{S} = \dim S + L$. The MC estimators of the corrected angular observables
+then take the following structure:
 \begin{equation}
@@
 correspond to higher partial waves that have been suppressed in the physical model; see \refapp{btokstarll} for such a case.}
-Since $L$ depends on the \fred{setup} of the particle detector \fred{under consideration}, it remains for
-the experimental collaborations to determine the maximum order of such an expansion.
-}
+Since $L$ depends on the setup of the particle detector under consideration, it remains for
+the experimental collaborations to determine the maximum order of such an expansion.\\
 
@@
 comment on the MC-induced uncertainties. As usual, one needs to find a balance between
-compute time and accuracy. \fred{For a uniangular distribution and a total of $6\cdot 10^6$ MC
-samples (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find} that the error on the mean is
-smaller than $6\cdot 10^{-4}$. Let us conclude this section by commenting that the unfolding
-matrix is universal in a sense. Specifically, it can be reused in analyses with a similar underlying decay.
-Therefore, computing resources spent on improving its accuracy are therefore not wasted.
+compute time and accuracy. For a uniangular distribution and a total of $6\cdot 10^6$ MC
+samples (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find that the error on the mean is
+smaller than $6\cdot 10^{-4}$. Let us conclude this section by commenting that parts of the unfolding
+matrix are universal in a sense. Specifically, they can be reused in analyses with a similar underlying decay.
+Therefore, computing resources spent on improving its accuracy are not wasted.
 
@@
 In order to faithfully investigate the performance of the method of moments, we repeats our
-numerical studies for several bin sizes in the kinematic range $1 \GeV^2 \leq q^2 \leq 6\GeV^2$,
-as well as $15 \GeV^2 \leq q^2 \leq q^2_\text{max}$. Here, the bin size is chosen either
-as $1\GeV^2$ or $0.5\GeV^2$. This setup is meant to ensure that a wide spectrum of possible
+numerical studies for several bin sizes in the kinematic range $1\,\GeV^2 \leq q^2 \leq 6\,\GeV^2$,
+as well as $15\,\GeV^2 \leq q^2 \leq q^2_\text{max}$. Here, the bin size is chosen either
+as $1\,\GeV^2$ or $0.5\,\GeV^2$. This setup is meant to ensure that a wide spectrum of possible
 values for the angular observables is investigated.\\
@@
         of $200$ events per study in \reffig{pulls}.
-    \item We study the absolute uncertainty $\sigma_k(K)$ with respect to the angular observable $S_k$
-        as a function of the number of simulated events $K$. As expected for a multivariate gaussian
+    \item We study the absolute uncertainty $\sigma_k(N)$ with respect to the angular observable $S_k$
+        as a function of the number of simulated events $N$. As expected for a multivariate gaussian
         distribution, we find that the absolute uncertainty is well fitted by
@@
             \label{eq:unc-on-mean}
-            \sigma_k(K) = \frac{\sigma_k(1)}{\sqrt{K}}
+            \sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}
         \end{equation}
@@
         $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
-        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $K$.}
+        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $N$.}
 \end{itemize}
 All results of our toy studies, as summarised above, show consistently that the joint distribution of the angular
-observables converges towards a multivariate Gaussian distribution. We therefore propose to describe the
+observables converges rapidly towards a multivariate Gaussian distribution. We therefore propose to describe the
 resulting distribution as a multivariate Gauss when skewness and kurtosis fall below a given threshold.
@@
 on the mean.
-Second, in the absence of acceptance effects, a determination using the method of moments is correct and unbiased
-even when not all aspects of the physical distribution are modelled. This is explicitl shown for the case of
-higher partial waveds in multibody final states.
-Third, we develop a systematic method for the dertermination of detector acceptance effects that lead to
-dilution and mixing of the angular observables. We present a way to calculate the necessary unfolding matrix,
-which is only computationally feasible when using the method of moments.\\
-Fourth, the fact that the joint distribution of the results is Gaussian allows for an easy transfer of correlation
-information to theory analyses.
-Last but not least, the resulting distribution arises without additional constraints necessary for the convergence
-of some maximum-likelihood fits. Therefore the results can be directly combined with similarly-obtained results from
-a different experiment, without the need to remove the constraints of measurements that stem from different experiments.\\
-
-In conclusion, we argue that the method of moments is a competetive alternative to maximum-likelihood fits as long
-as angular distributions are involved. We wish to raise the interesting prospect of extending this very method to
-applications with non-angular orthogonal bases for the PDF.
+Second, in the absence of detector effects, a determination using the method of moments is correct and unbiased
+even when not all aspects of the physical distribution are modelled. This is explicitly shown for the case of
+higher partial waves in multibody final states.
+Third, we develop a systematic method for the dertermination of detector effects that lead to
+dilution and mixing of the angular observables. We present an algorithm to calculate the necessary
+unfolding matrix, which is only computationally feasible when using the method of moments.
+Fourth, the fact that the joint distribution of the angular observables that results from the method of moments
+is a multivariate Gaussian distribution allows for an easy and precise transfer of correlation
+information to subsequent theoretical analyses.
+Last but not least, the resulting distribution arises without the need for additional constraints necessary
+in order to achieve convergence, such as in some maximum-likelihood fits. Therefore, the results can be
+directly combined with similarly-obtained results from different experiments, without the need to remove
+the constraints a posteriori.\\
+
+In conclusion, we argue that the method of moments is a competetive alternative to
+maximum-likelihood fits as long as angular distributions are involved. We wish to raise
+the interesting prospect of extending this method to applications that feature
+PDFs composed from non-angular orthogonal bases.
 
@@
 
-\danny{
 To conclude this section, we remind that the angular momentum $l_2$, associated with the angle $\theta$, is not bounded from above.
@@
 physical range of $m$ is not affected by higher partial waves.
-}
 
@@
 $S(\theta)$. The dependence on the non-angular variables will be
-ignored in the following. \fred{I rephrased it sligthly} Suppose $S$
+ignored in the following. Suppose $S$
 has an expansion in terms of partial waves $l_1, l_2 = 0,1,2,\dots
@@
 
-From the positivity of amplitudes, one immediately finds
+From the positivity of amplitudes and unitarity, one immediately finds
 \begin{equation}
@@
 increasing $l_i$ the partial-wave amplitudes must asymptotically fall
-off as \fred{Let's say why. Unitarity?} \danny{Finiteness of
-  observables, so yes: unitarity!} \fred{So can't we just say
-  unitarity before the first equation? That's the reason why the sum
-  need be finite, I guess.
-But if I look at (D2) again, it goes down as $1/(2l + 1)$, so If remember correctly, $A_i^{(l_i)} \propto 1/l^{\eps}$ would be enough to ensure convergence.
-So why $1/\sqrt{l_i}$?}
-\begin{equation}
-    |A_i^{(l_i)}(\cos\theta)| \Big|_{l_i \gg m_i} \sim \frac{1}{\sqrt{l_i}}\,.
+off as
+\begin{equation}
+    |A_i^{(l_i)}| \Big|_{l_i \gg m_i} \sim \frac{1}{\sqrt{l_i}}\,.
 \end{equation}
@@
 estimate or calculate the impact of individual contributions, with or without the cutoff $L$.
-For such an analysis in the decay $B\to K\pi\ell^+\ell^-$ we refer to \cite{Das:2014sra}.
 We close by remarking that for any angular-momentum cutoff $l < L$\fred{Do you mean $L < \infty$?}, one can find an upper limit for the squared sum of all remaining partial waves through a comparison with the inclusive decay

### 2015-01-22 draft.tex
Add comment on comparison of uncertainties with ML fits

@@
         for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
+        We find that the the method of moments yields uncertainties on $\vec{S}$ that are roughly
+        \danny{$10\%$} larger than those obtained from maximum-likelihood fits and with the same
+        number of events \danny{[cite!]}. However, we wish to note that said fits only produce a limited
+        subset of the angular observables, and the statistical error of the fit is expected to increase
+        with the number of fit parameters \danny{[cite?]}.
     \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of

### 2015-01-23 draft.tex
Update draft after another discussion with Fred

@@
 \begin{abstract}
-  \fred{Our goal is to obtain a complete set} of angular observables
+  Our goal is to obtain a complete set of angular observables
   arising in a generic multi-body process without the need to carry
   out a likelihood fit of the angular distribution to the measured
-  events. Instead, we \fred{apply the method of moments} that relies
+  events. Instead, we apply the method of moments that relies
   both on the orthogonality of angular functions and the estimation of
-  integrals by Monte Carlo techniques. \fred{The main advantage of
+  integrals by Monte Carlo techniques. The main advantage of
   this method is that the joint distribution of all observables
@@
   implementation of the method for several rare decays of
-    interest.}
+  interest.
 \end{abstract}
@@
     \includegraphics[width=.6\textwidth]{fig-topology.pdf}
-    \caption{Decay topology for decays $B\to P_1 P_2 \ell_1 \bar\ell_2$. \label{fig:topology}\fred{We should use the same symbol $\theta$ as in text}}
+    \caption{Decay topology for decays $B\to P_1 P_2 \ell_1 \bar\ell_2$. \label{fig:topology}}
 \end{figure}
@@
 
-\subsection{Recipe for \fred{Including} Detector Effects}
+\subsection{Recipe for Including Detector Effects}
 \label{sec:systematics:acceptance}
@@
 The accuracy of the unfolding process as outlined above critically depends on both the accuracy
-of the detector simulation, as well as the uncertainties induced by the MC estimates. While
-considerations of any detector simulation is beyond the scope of this work, we can, however,
+of the detector simulation, as well as the uncertainties induced by the MC estimates.
+For an experimental analysis, one would now turn to the determination of the distribution of $\vecest{S}$
+as a function of the detector setup. This would involve the determination of both $M$ and $\vecest{Q}$ for a number of
+detector configurations, and subsequent profiling or marginalization.
+While such considerations of any detector simulation are beyond the scope of this work, we can, however,
 comment on the MC-induced uncertainties. As usual, one needs to find a balance between
@@
             \label{fig:errors}
-            \fred{Plots convey exactly was is said in words. I see they are useful for a talk, but do we really need them in the write-up?}
 \end{figure}
@@
 \begin{equation}
-    |A_i^{(l_i)}| \Big|_{l_i \gg m_i} \sim \frac{1}{\sqrt{l_i}}\,.
+    |A_i^{(l_i)}| \Big|_{l_i \gg m_i} \sim \frac{1}{\sqrt{l_i}}\,.\todo{wrong!}
 \end{equation}
@@
 estimate or calculate the impact of individual contributions, with or without the cutoff $L$.
-We close by remarking that for any angular-momentum cutoff $l < L$\fred{Do you mean $L < \infty$?}, one can find an upper limit for the squared sum of all remaining partial waves through a comparison with the inclusive decay
+We close by remarking that for any angular-momentum cutoff $l < L < \infty$, one can find an upper limit for the squared sum of all remaining partial waves through a comparison with the inclusive decay
 width.

### 2015-01-25 draft.tex
More small changes, adjust formatting and find a proper reference to replace [2]

@@
         events, and can require reparametrizations and/or approximations
-        for a successful fit to the signal PDF, see e.g. \cite{Egede:2008uy}.
+        for a successful fit to the signal PDF, see e.g. \cite{Egede:1142152}.
         The method of moments has no such convergence problems.
     \item The results of likelihood fits suffer from systematic uncertainties
-        and systematic bias (see e.g. \cite{Egede:2008uy}), especially in but not limited
+        and systematic bias (see e.g. \cite{Egede:1142152}), especially in but not limited
         to cases in which the PDFs do not faithfully model the underlying physics. We will
@@
     \item In all studied cases we observed not a single bias in the distribution of the $\mathrm{pull}$
-        of any observables $S$,
-        \begin{equation}
-            \mathrm{pull_i} \equiv \frac{\est{S} - S}{\est{\sigma}_S}\,.
-        \end{equation}
-        Here $S$ refers to the true (input) value for the angular observables, $\est{S}$ refers to the
-        MC estimate, and $\est{\sigma} \equiv \sqrt{\est{\Sigma}}$ refers to an estimator of the
-        variance of the measurement. All pull distributions obtained in our studies can be successfully
+        of any observables $S_i$,
+        \begin{equation}
+            \mathrm{pull_i} \equiv \frac{\est{S}_i - S_i}{\est{\sigma}_{i}}\,.
+        \end{equation}
+        Here $S_i$ refers to the true (input) value for the angular observables, $\est{S}_i$ refers to the
+        mean of the pseudomeasurement via the MC estimate, and $\est{\sigma}_{i} \equiv \sqrt{\est{\Sigma_{ii}}}$
+        refers to an estimator of the standard deviation of the pseudomeasurement. All pull distributions
+        obtained in our studies can be successfully
         fitted to a gaussian distribution. Due to the large number of studied distributions, we have
@@
         $S_5 \simeq 27\%$ and $S_7 \simeq 2\%$, which are obtained from SM-like $B\to K^*\ell^+\ell^-$
-        decays, are good examples. We show their respective pull distributions for \danny{$XXX$} toy studies
+        decays, are good examples. We show their respective pull distributions for $2\cdot 10^5$ toy studies
         of $200$ events per study in \reffig{pulls}.
-    \item We study the absolute uncertainty $\sigma_k(N)$ with respect to the angular observable $S_k$
+    \item We study the MC estimate for the absolute uncertainty $\est{\sigma_i(N)}$ with respect to the angular observable $S_i$
         as a function of the number of simulated events $N$. As expected for a multivariate gaussian
@@
             \label{eq:unc-on-mean}
-            \sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}
-        \end{equation}
-        with $\sigma_k(1) = \order{1}$, regardless of the absolute size of $S_k$. The latter can best be shown
+            \est{\sigma_i(N)} = \frac{\sigma_i}{\sqrt{N}}
+        \end{equation}
+        with $\sigma_i(1) = \order{1}$, regardless of the absolute size of $S_k$. The latter can best be shown
         for the example of uncertainties of two observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
@@
         We find that the the method of moments yields uncertainties on $\vec{S}$ that are roughly
-        \danny{$10\%$} larger than those obtained from maximum-likelihood fits and with the same
+        $10\%$ larger than those obtained from maximum-likelihood fits and for the same
         number of events \danny{[cite!]}. However, we wish to note that said fits only produce a limited
         subset of the angular observables, and the statistical error of the fit is expected to increase
-        with the number of fit parameters \danny{[cite?]}.
-    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
-        $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
-        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $N$.}
+        with the number of fit parameters \danny{[cite?]}. \danny{The method of moments, on the other hand,
+        does not suffer from this problem.}
+%    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
+%        $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
+%        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $N$.}
 \end{itemize}
@@
 
-\section{Conclusion}
+\section{Summary}
 
 We have carried out a combined analytical and numerical study of the method of moments; a method for
-the extraction of angular observales from the angular distribution of a generic multi-body process.
+the extraction of angular observales from the angular distribution of a general multi-body process.
 We have studied the performance of the method of moments using pseudo data derived from the SM
@@
 First, we find no bias in the determinations of the angular observables even for a small number of events.
-However, this comes at the expense of a slight increase of the order of $10\%$\todo{check!} for the statistical uncertainty
+However, this comes at the expense of a slight increase of the order of $10\%$ for the statistical uncertainty
 on the mean.
@@
 information to subsequent theoretical analyses.
-Last but not least, the resulting distribution arises without the need for additional constraints necessary
-in order to achieve convergence, such as in some maximum-likelihood fits. Therefore, the results can be
-directly combined with similarly-obtained results from different experiments, without the need to remove
+Last but not least, the resulting distribution arises without the need for additional constraints
+in order to achieve convergence, such as e.g. in some maximum-likelihood fits. Therefore, results obtained
+using the method of moments can be directly averaged, without the need to remove
 the constraints a posteriori.\\
@@
 
+We would like to thank Ulrik Egede, Gudrun Hiller, Martin Jung and Konstantinos Petridis for insightful discussions.
 The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).
-We would like to thank Ulrik Egede and Konstantinos Petridis for insightful discussions.
-\danny{Potential people to read the manuscript: Jochen Dingfelder (Belle-II, Bonn), Ulrik Egede (LHCb, Imperial London), Christoph Langenbruch (LHCb, Warwick), Michel De Cian (LHCb, Heidelberg), Adrian Bevan (ATLAS, Queen Mary)  }
-D.v.D would like to thank Gudrun Hiller and Martin Jung for discussing the results of \cite{Das:2014sra} prior to publication.
 
@@
 
-\section{On the Partial-Wave Expansions of Angular Observables}
+\section{On the Partial-Wave Expansion of Angular Observables}
 \label{app:partial-waves}
@@
 
-From the positivity of amplitudes and unitarity, one immediately finds
-\begin{equation}
-    \int \rmdx{\cos\theta}  \, |A_i(\theta)|^2 = \sum_{l_i = 0}^\infty |A_i^{(l_i)}|^2 n_{l_i, m_i} < \infty\,,
-\end{equation}
-where we introduce $n_{l,m}$ via the scalar product of two associated Legendre polynomials,
+\danny{
+From the orthogonality of the Legendre polynomials, one immediately finds
+\begin{equation}
+    \label{eq:partial-waves:bound}
+    \int \rmdx{\cos\theta}  \, |A_i(\theta)|^2 = \sum_{l_i = 0}^\infty |A_i^{(l_i)}|^2 n_{l_i, m_i} < S_\text{incl}\,,
+\end{equation}
+where $S_\text{incl}$ is the corresponding observable in the associated inclusive decays,
+and where we introduce $n_{l,m}$ via the scalar product of two associated Legendre polynomials,
 \begin{equation}
@@
 \end{equation}
-Using the large-$l$ behaviour of $n_{l,m}$ one finds that with
-increasing $l_i$ the partial-wave amplitudes must asymptotically fall
-off as
-\begin{equation}
-    |A_i^{(l_i)}| \Big|_{l_i \gg m_i} \sim \frac{1}{\sqrt{l_i}}\,.\todo{wrong!}
-\end{equation}
-This motivates to cut off the partial-wave expansion at some arbitrary angular momentum $L$.\\
-
-Will will show in the following that such a cutoff
-is compatible with defining a basis of angular observables as coefficients of Legendre polynomials in $\cos\theta$. Since this expansion implies
-a well defined total angular momentum for each observable, one ensures that the observables can in fact be disentangled experimentally.\\
-
-We propose the decomposition of $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with total angular momentum $j$ and its third component $m=m_1 + m_2$.
+The positivity of the amplitudes in \refeq{partial-waves:bound} implies that we can estimate
+the error introduced by cutting off the expansion at some arbitrary angular momentum $L$. One
+obtains
+\begin{equation}
+    |A_i^{(l' > L)}|^2 < S_\text{incl} - \sum_{l=0}^L |A_i^{(l)}|^2\,.
+\end{equation}
+}
+
+Will will show in the following that such a cutoff is compatible with defining a basis of angular
+observables as coefficients of Legendre polynomials in $\cos\theta$. Since this expansion implies
+a well defined total angular momentum for each observable, one ensures that the observables can in
+fact be disentangled experimentally.\\
+
+We propose the decomposition of $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$,
+with total angular momentum $j$ and its third component $m=m_1 + m_2$.
 \begin{equation}
@@
 consist of sums with infinitely many terms. It is then up to theoretical analyses to
-estimate or calculate the impact of individual contributions, with or without the cutoff $L$.
-We close by remarking that for any angular-momentum cutoff $l < L < \infty$, one can find an upper limit for the squared sum of all remaining partial waves through a comparison with the inclusive decay
-width.
+estimate or calculate the impact of the neglected partial waves, e.g. as outlined above.
 

### 2015-02-16 draft.tex
Fix two typos
Incorporate some of Ulrik's comments

@@
 \newcommand{\fred}[1]{{\color{brown!85!black}#1}}
-\newcommand{\nico}[1]{{\color{green!85!black}#1}}
 \newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}
+\newcommand{\add}[1]{\textcolor{green!85!black}{#1}}
+\newcommand{\del}[1]{\textcolor{red!85!black}{#1}}
 
@@
 \begin{enumerate}
-    \item Likelihood fits have convergence problems for a small number of
+    \item \del{Likelihood fits have convergence problems for a small number of
         events, and can require reparametrizations and/or approximations
@@
         The method of moments has no such convergence problems.
+    }
+    \item \add{Likelihood fits of problems, for which the underlying
+        physical model is only partially known, may be delicate. Such cases can lead to
+        overestimating the number of physical parameters, and consequently
+        inhibit the convergence of the fits. (As an example, this type
+        of problem occured in toy studies of the decay $B\to K^*(\to K\pi)\ell^+\ell^-$
+        as reported in \cite{Egede:1142152}. It was subsequently solved
+        when a missing symmetry relation between the angular observables
+        was found and applied, thereby reducing the number of fit parameters.)
+    }
     \item The results of likelihood fits suffer from systematic uncertainties
-        and systematic bias (see e.g. \cite{Egede:1142152}), especially in but not limited
+        and systematic bias \del{(see e.g. \cite{Egede:1142152})}, especially in but not limited
         to cases in which the PDFs do not faithfully model the underlying physics. We will
@@
   the likelihood is near the boundary of the physically allowed
-  region.\fred{Is there some LHCb note we could cite?} 
-  For some of these decays of interest, there are only $\order{10}$ of events
-  per bin on record.
+  region.\fred{Is there some LHCb note we could cite?}\danny{Ulrik suggests citing some
+  statistical paper}
+  For some of these decays of interest, there are only $\order{10}$--$\order{100}$ events
+  per bin on record.\danny{What to cite? 1403.8004 only states total signal yield!}
 \item The estimate is unbiased for any $N$. In contrast, the
@@
   the expected loss associated with deciding on just one value of the
-  unknown parameter. It is therefore highly questionable to reduce
+  unknown parameter. It is therefore highly questionable \add{to outright
+  prefer the method of moments over likelihood fits, in order} to reduce
   only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
@@
 \item The approximate multivariate Gaussian distribution of $\vecest{S}$
-  allows easier and more correct transfer of the information in the
+    allows easier and more \add{precise}\del{correct} transfer of the information in the
   data to interested theorists for more accurate fits of
   standard-model and new-physics parameters \cite{Altmannshofer:2013foa,
-    Descotes-Genon:2013wba,Bobeth:2013soa},
+Descotes-Genon:2013wba,Beaujean:2013soa},
   or for more precise predictions of optimized observables; see e.g.,
@@
   nuisance parameters (from control channels, detector calibrations
-  etc.) that are also part of the likelihood. This leads to the
+  etc.) that are also part of the likelihood.
+  \danny{Ulrik: Seems an odd comment to put in a paper.}
+  This leads to the
   undesirable situation that only the mode and standard errors
@@
 of decays and scattering processes. For the sake of clarity we take
-the interesting class of four-body decays $B\to P_1 P_2 \ell_1$
+the interesting class of four-body decays $B\to P_1 P_2 \ell_1 \ell_2$
 as an example\footnote{This includes the rare $b\to s$ mediated $B$ decay $B
@@
 large total angular momentum $j$; only its third component is restricted to $j_z = -1,0,+1$.
-It is then usual to compute the angular distribution explicitly in terms of $\theta_1$ and $\theta_3$, but leave
+It is then \add{convenient}\del{usual} to compute the angular distribution explicitly in terms of $\theta_1$ and $\theta_3$, but leave
 the angular observables dependent on the remaining helicity angle $\theta_2$.
-We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(|m|)}$
-with respect to the remaining angle $\theta_2$. Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
+We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{l}^{(|m|)}$
+with respect to the remaining angle $\theta_2$. \add{Here, the angular momentum-like indices $l$ and $m$ follows from the usual
+rules for addition of the angular momenta $j$ and $\tilde{j}$ of the partial wave expansion of the underlying
+amplitude and its complex conjugate: $j - \tilde{j} \leq l \leq j + \tilde{j}$, and $m = j_z + \tilde{j}_z$.}
+Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
 and as defined in \refapp{partial-waves}, the expansion reads
 \begin{equation}
-    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{j,|m|}} S_{k,j}(\vec{\nu}) p_{j}^{(|m|)}(\cos\theta_2)\sin\theta_2\,,
-\end{equation}
-where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
+    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\sin\theta_2\,,
+\end{equation}
+where the the normalization factor $n_{l,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
 example we have (cf. also \refapp{btokstarll} and \cite{Lee:1992ih})
@@
         1\,, & k = 4,5,7,8\,,\\
-        m\,, & k = 3,9
+        2\,, & k = 3,9
     \end{cases}\,.
@@
 As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
-partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. To wit,
+partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. \del{To wit}\add{That is to say},
 ignoring further (orthogonal) terms in the PDF cannot affect $\vec{S}$ nor its variance.\\
@@
 We wish to emphasize, however, that detector acceptance effects systematically affect the expansion for any basis
-of angular functions, including the one suggested in this section. The means to cope with this problem are discussed
-in the following subsection.
+of angular functions, including the one suggested in this section.
+\add{Nevertheless, the expansion in terms of Legendre polynomials provides means to cope with these effects,
+as we discuss in the following subsection.}
+\del{The means to cope with this problem are discussed
+in the following subsection.}
 
@@
 In what follows, we propose a systematic method to unfold all effects
-of $\Ekernel$ through MC simulations and the method of moments
-assuming that $\Ekernel$ is independent of the angular
+of $\Ekernel$ through MC simulations and the method of moments.
+\add{In this process, we use that fact} that $\Ekernel$ is independent of the angular
 observables, and that it is possible to expand $\Ekernel$ --- at
@@
 for arbitrary $\eps$. Taking again the decay $B\to K\ell^+\ell^-$
-as an example, we have $\dim S = 3$. Assuming an expansion of the detector acceptance $\eps$
+as an example, \del{we have} \add{there are exactly three physical angular observables:} $\dim S = 3$.
+Assuming an expansion of the detector acceptance $\eps$
 in terms of Legendre polynomial up to order $L$, we have to calculate the raw moments up
@@
 \begin{equation}
-    \lbrace \est{S}_k \rbrace = \lbrace \underbrace{\est{S}_0, \dots, \est{S}_{\dim S}}_\text{physical}, \underbrace{\est{S}_{\dim S + 1}, \dots, \est{S}_{\dim Q}}_\text{``superfluous''}\rbrace\,.
+    \vecest{S} = ( \underbrace{\est{S}_0, \dots, \est{S}_{\dim S}}_\text{physical}, \underbrace{\est{S}_{\dim S + 1}, \dots, \est{S}_{\dim Q}}_\text{``superfluous''})\,.
 \end{equation}
@@
 Since $L$ depends on the setup of the particle detector under consideration, it remains for
-the experimental collaborations to determine the maximum order of such an expansion.\\
+the experimental collaborations to determine the maximum order of such an expansion.
+\add{We propose to do this by \dots}\\
 
@@
 distribution. We repeats theses analysis for varying sample sizes, ranging from
-$50$ to $500$ events. Our toy analysis base on SM predictions for angular observables
+$50$ to $500$ events. Our toy analyses base on SM predictions for angular observables
 in the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to K\pi)\ell^+\ell^-$, respectively.
 In order to faithfully investigate the performance of the method of moments, we repeats our
-numerical studies for several bin sizes in the kinematic range $1\,\GeV^2 \leq q^2 \leq 6\,\GeV^2$,
-as well as $15\,\GeV^2 \leq q^2 \leq q^2_\text{max}$. Here, the bin size is chosen either
+numerical studies for several bins in the kinematic range $1\,\GeV^2 \leq q^2 \leq 6\,\GeV^2$,
+as well as $15\,\GeV^2 \leq q^2 \leq q^2_\text{max}$. Here, the bin width is chosen either
 as $1\,\GeV^2$ or $0.5\,\GeV^2$. This setup is meant to ensure that a wide spectrum of possible
@@
 
-Our finding can be summarized as follows:
+Our findings can be summarized as follows:
 \begin{itemize}
@@
         Here $S_i$ refers to the true (input) value for the angular observables, $\est{S}_i$ refers to the
-        mean of the pseudomeasurement via the MC estimate, and $\est{\sigma}_{i} \equiv \sqrt{\est{\Sigma_{ii}}}$
-        refers to an estimator of the standard deviation of the pseudomeasurement. All pull distributions
+        mean of the pseudo measurement via the MC estimate, and $\est{\sigma}_{i} \equiv \est{\Sigma_{ii}}^{1/2}$
+        refers to an estimator of the standard deviation of the pseudo measurement. All pull distributions
         obtained in our studies can be successfully
@@
         We find that the the method of moments yields uncertainties on $\vec{S}$ that are roughly
-        $10\%$ larger than those obtained from maximum-likelihood fits and for the same
+        $10\%$ -- $15\%$ larger than those obtained from maximum-likelihood fits and for the same
         number of events \danny{[cite!]}. However, we wish to note that said fits only produce a limited
         subset of the angular observables, and the statistical error of the fit is expected to increase
-        with the number of fit parameters \danny{[cite?]}. \danny{The method of moments, on the other hand,
-        does not suffer from this problem.}
+        with the number of fit parameters until their errors saturate the statistical errors of the method-of-moments
+        estimators \cite[sec. 8]{Cowan:1998ji}.
 %    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
@@
 
-We would like to thank Ulrik Egede, Gudrun Hiller, Martin Jung and Konstantinos Petridis for insightful discussions.
+We would like to thank Ulrik Egede, Gudrun Hiller, Martin Jung and Konstantinos Petridis for insightful discussions,
+as well as Claus Grupen for helpful advice in searching the literatur.
 The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).
@@
 
-\danny{
 From the orthogonality of the Legendre polynomials, one immediately finds
@@
 \end{equation}
-}
 

### 2015-02-25 draft.tex
Incorporate more of Ulrik's comments

@@
 and unfold detector effects. Moreover, we show
-that the method of moments has two major advantages over the usual
+that the method of moments has \add{several} major advantages over the usual
 approach based on likelihood fits:
 \begin{enumerate}
-    \item \del{Likelihood fits have convergence problems for a small number of
+    \item Likelihood fits have convergence problems for a small number of
         events, and can require reparametrizations and/or approximations
-        for a successful fit to the signal PDF, see e.g. \cite{Egede:1142152}.
-        The method of moments has no such convergence problems.
-    }
+        for a successful fit to the signal PDF. \add{As an example,
+        see the LHCb analysis of \dots}.
+        The method of moments does not require reparametrization and approximations.
+
     \item \add{Likelihood fits of problems, for which the underlying
@@
     }
-    \item The results of likelihood fits suffer from systematic uncertainties
-        and systematic bias \del{(see e.g. \cite{Egede:1142152})}, especially in but not limited
-        to cases in which the PDFs do not faithfully model the underlying physics. We will
-        show that the method of moments does not suffer a very particular type of
-        mismodelling that arises from introducing a cutoff in a partial wave expansion.
+    \item Mismodeling the underlying physics model can result in systematic bias
+        in likelihood fits. We will
+        show that the method of moments is insensitive to a certain type of mismodeling;
+        i.e. introducing a cutoff in a partial-wave expansion of the signal PDF.
+
     \item Using the method of moments, the joint probability distribution of the
-        angular observables converges towards a multivariate Gaussian distribution.
+        angular observables rapidly converges towards a multivariate Gaussian distribution.
         This allows an easy transfer of correlation information from the experiments to
@@
   the expected loss associated with deciding on just one value of the
-  unknown parameter. It is therefore highly questionable \add{to outright
-  prefer the method of moments over likelihood fits, in order} to reduce
-  only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
+  unknown parameter. \add{One should therefore not prefer the method of moments
+  over likelihood fits just because the former reduces}
+  the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
   the results discussed below in \refsec{numerics}, the likelihood
-  fits --- if they converge --- produce uncertainties (10--15)\%
+  fits --- if they converge --- produce uncertainties \add{(10--15)\%}
   smaller than those from the method of moments.
 \item The approximate multivariate Gaussian distribution of $\vecest{S}$
-    allows easier and more \add{precise}\del{correct} transfer of the information in the
+    allows easier and more \add{precise} transfer of the information in the
   data to interested theorists for more accurate fits of
@@
   resulting likelihood as a function of $\vec{S}$ is distinctly not
-  Gaussian.  For experimentalists, communicating such a result has
-  proved to be challenging due to technical reasons (data formats,
-  size etc.) and the fear that theorists misinterpret the many
-  nuisance parameters (from control channels, detector calibrations
-  etc.) that are also part of the likelihood.
-  \danny{Ulrik: Seems an odd comment to put in a paper.}
+  Gaussian.  Communicating such a result has
+  proved to be challenging due to technical reasons (such as data formats,
+  size etc.) \add{as well as political reasons; i.e., the publication of
+  the likelihood also publishes collaboration-internal data.}
   This leads to the
@@
 As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
-partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. \del{To wit}\add{That is to say},
-ignoring further (orthogonal) terms in the PDF cannot affect $\vec{S}$ nor its variance.\\
+partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. \add{That is to say},
+ignoring further (orthogonal) terms in the PDF cannot affect $\vecest{S}$ nor its variance.\\
 
@@
 of angular functions, including the one suggested in this section.
-\add{Nevertheless, the expansion in terms of Legendre polynomials provides means to cope with these effects,
-as we discuss in the following subsection.}
-\del{The means to cope with this problem are discussed
-in the following subsection.}
+Nevertheless, the expansion in terms of Legendre polynomials as suggested above provides means to cope with these effects,
+as we discuss in the following subsection.
 
@@
 write down the full forward model from which the measured events
-arise. In practice, this would require much more CPU time than
-available, and one is therefore forced to simplify the model. The
-standard approach is to generate the \emph{true} particle events
+arise. In practice, that is not feasible, and one is
+forced to simplify the model.
+The standard approach is to generate the \emph{true} particle events
 $\lbrace x_\text{t}^{(n)}\rbrace =
@@
 \begin{equation}
+  \label{eq:def-R}
     R \equiv \iint P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}} \rmdx{x_\text{d}}\,,
@@
 \begin{equation}
-  \label{eq:def-R}
   P(\xd|\xt) = \delta(\xd - \xt) \,.
@@
 In what follows, we propose a systematic method to unfold all effects
-of $\Ekernel$ through MC simulations and the method of moments.
-\add{In this process, we use that fact} that $\Ekernel$ is independent of the angular
-observables, and that it is possible to expand $\Ekernel$ --- at
+of $\Ekernel$ through MC simulations and the method of moments,
+using that $\Ekernel$ can be expanded --- at
 least formally --- in Legendre polymials.  For illustration, we
@@
 implies $|S_k| \leq 1/2$ for $k > 0$. More stringent relations between the
-$S_k$ might hold, but are beyond the scope of this work. For later use, we define
+$S_k$ might hold, but are of no concern here. For later use, we define
 \begin{equation}
@@
 \begin{equation}
+    \label{eq:analytic-raw-moments}
     Q_i^{(m)} \equiv \iint \tilde{f}_i(\xd) P^{(m)}(\xt) \Ekernel \rmdx{\xt} \rmdx{\xd},
@@
     \label{eq:estS}
-    \vecest{S}_i \equiv \left[\est{M}^{-1}\right] \vecest{Q}\,.
-\end{equation}
-The precise value of $R$ (see \refeq{def-R}) depends on the a priori
-unknown angular observables $\vec S$.  However, ratios and
-other suitable combinations of the estimators $\vecest{S}$
-are independent of $R$. Conversely, $R$ can be
+    \vecest{S} \equiv \left[\est{M}^{-1}\right] \vecest{Q}\,.
+\end{equation}
+
+\add{Apparently we now face a circular dependence. On the one hand,
+the estimators $\vecest{Q}$, and thus also the estimator $\vecest{S}$
+are proportional to $R$, the ratio of detected events over occuring events.
+On the other hand, $R$ depends by construction (see \refeq{def-R})
+on $P_\text{t}(x_t)$, and thus on the true value of the angular observables $\vec{S}$.
+We solve this problem by observing that the MC estimators $\vecest{S}$ need to fulfill
+a self-consistency condition, which reads
+\begin{equation}
+    \est{S}_0 = \frac{1}{2}\,,\qquad\text{for a uniangular distribution}.
+\end{equation}
+(For the process-dependent conditions in the multiangular case see \refeq{recipe:lambdabtolambdall} and
+\refeq{recipe:btokstarll}.)
+This self-consistency condition is tightly related to the determination of
+the branching ratio of the underlying decay, and we therefore suggest to
+carry out a combined analysis for the determination of the branching ratio
+and the extraction of the angular observables.\\
+Moreover, in the applications to $B$ decays only ratios and similar $R$-independent combinations
+of the angular observables are of interest.
+}\\
+
+\del{The precise value of $R$ (see \refeq{def-R}) depends on the a priori
+unknown angular observables $\vec S$.  However, within ratios and
+other suitable combinations of the estimators $\vecest{S}$, the quantity
+$R$ cancels.
+Conversely, $R$ can be
 extracted from the self-consistency condition\footnote{This condition
@@
 useful to carry out that determination and the extraction of the
-angular observables in a combined analysis.\\
+angular observables in a combined analysis.}\\
 
@@
 for arbitrary $\eps$. Taking again the decay $B\to K\ell^+\ell^-$
-as an example, \del{we have} \add{there are exactly three physical angular observables:} $\dim S = 3$.
+as an example, \add{there are exactly three physical angular observables:} $\dim S = 3$.
 Assuming an expansion of the detector acceptance $\eps$
-in terms of Legendre polynomial up to order $L$, we have to calculate the raw moments up
+in terms of Legendre polynomial up to a given order $L$, we have to calculate the raw moments up
 to $\dim \est{Q} = \dim \est{S} = \dim S + L$. The MC estimators of the corrected angular observables
@@
 The method is consistent as long as the MC estimators for the ``superfluous'' observables with indices $\dim S + 1$ to $\dim Q$
-are compatible with zero. \footnote{This holds only for the physical model of uniangular decay distributions. For some decays, these superfluous observables
+are compatible with zero. \footnote{This holds only for the physical model of uniangular decay distributions. If the physical
+    model involves a partial-wave expansion with cutoff, these superfluous observables
 correspond to higher partial waves that have been suppressed in the physical model; see \refapp{btokstarll} for such a case.}
@@
 the experimental collaborations to determine the maximum order of such an expansion.
-\add{We propose to do this by \dots}\\
+\add{We suggest to carry out a dedicated study to determine a suitable choice for $L$.
+Since such a work requires in-depth understanding of the detector simulation, it remains
+beyond the scope of our possibilities.}\\
 
@@
         \end{equation}
+        \danny{Marcin, please check that this is what you used!}
         Here $S_i$ refers to the true (input) value for the angular observables, $\est{S}_i$ refers to the
@@
         of $200$ events per study in \reffig{pulls}.
+
     \item We study the MC estimate for the absolute uncertainty $\est{\sigma_i(N)}$ with respect to the angular observable $S_i$
@@
 \end{itemize}
+
+\add{We emphasize that the above results have been obtained for a flat acceptance function.
+We also study the behaviour of the unfolded angular observables. However, due to limitations of computing
+resources, we have to limit our study to the decay $B\to K\ell^+\ell^-$, with its three angular observables
+$S_1$ to $S_3$. We express the acceptance function in terms of Legendre polynomial $P_k(x)$,
+\begin{equation}
+    \eps(\cos\theta) = \frac{7}{15} P_0(\cos\theta) - \frac{4}{15} P_2(\cos\theta)\,.
+\end{equation}
+This acceptance function approximates the one used in a recent study of the angular observables in $B\to K\ell^+\ell^-$
+decays \cite{Aaij:2014tfa}. We want to focus on effects of the unfolding process itself. We therefore
+use the analytic expression for the unfolding matrix, which we compute from the raw moments as
+defined in \refeq{analytic-raw-moments}. We simulate $4000$ toy analyses with up to $300$ simulated events each.
+We find that the previous two bullet points still hold; i.e., we do not find any bias, and the distribution
+is well described by a multivariate Gaussian distribution.
+}
+
 All results of our toy studies, as summarised above, show consistently that the joint distribution of the angular
@@
 resulting distribution as a multivariate Gauss when skewness and kurtosis fall below a given threshold.
-The precise target threshold for skewness and kurtosis are subject to the details of the underlying physical analysis, and reside therefore outside the scope of this work.
+The precise target threshold for skewness and kurtosis are subject to the details of the underlying physical analysis,
+and reside therefore outside the scope of this work.
 
@@
             \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
-        \caption{Pull distribution for the angular observables $S_5$ and $S_7$, extracted from $200$ simulated events of the decay $B\to K^*\ell^+\ell^-$.
-The red curve represents a fit to a gaussian distribution.}
+        \caption{Pull distribution for the angular observables $S_5$ and $S_7$, extracted from $2\cdot 10^5$ studies of
+        $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a gaussian distribution.}
         \label{fig:pulls}
@@
             \includegraphics[width=0.45\textwidth]{figs/error-Q2_5_6_S7.png}
-            \caption{Uncertainty of the angular observables $S_5$ and $S_7$, extracted from simulated events of the decay $B\to K^*\ell^+\ell^-$ and as a function of the number of simulated events $K$.
+        \caption{Uncertainty of the angular observables $S_5$ and $S_7$, extracted from $2\cdot 10^5$ studies of 
+        simulated events for the decay $B\to K^*\ell^+\ell^-$. We show the uncertainty as a function of the number of simulated events $N$.
         The red curve represents a fit to the function given in \refeq{unc-on-mean}.}

### 2015-02-25 acceptance.py

@@ -272,6 +272,45 @@ def unfolding_matrix(_process, acceptance, components, chunks, chunk_size, ovalu
         return M
         #np.linalg.inv(M)
 
+def raw_moments(process, acceptance, R, components, chunks, chunk_size):
+        skip_index = int(chunks * chunk_size * 0.05)
+
+        sampler = Sampler(process.dim())
+        log_acceptance = lambda x: np.log(acceptance(x))
+        raw_moments = [0.0, 0.0, 0.0, 0.0, 0.0]
+        log_target = lambda x: process.log_pdf(x) + log_acceptance(x)
+        indicator = pypmc.tools.indicator.hyperrectangle([-1], [1])
+        samples = sampler.draw(log_target, start=process.start(), indicator=indicator, chunks=chunks, chunk_size=chunk_size)[skip_index:]
+        samples = samples[::20]
+        for i in range(components):
+            estimator_mean = 0
+            estimator_cov = 0
+            for x in samples:
+                estimator_mean += process.dual_component(i, x)
+
+            estimator_mean *= R / len(samples)
+
+            for x in samples:
+                estimator_cov += (process.dual_component(i, x) - estimator_mean) * (process.dual_component(i, x) - estimator_mean)
+
+            estimator_cov *= R * R / (len(samples) - 1)
+
+            raw_moments[i] = [estimator_mean, np.sqrt(estimator_cov)]
+
+        return raw_moments
+
+def raw_samples(process, acceptance, R, components, chunks, chunk_size):
+        skip_index = int(chunks * chunk_size * 0.05)
+
+        sampler = Sampler(process.dim())
+        log_acceptance = lambda x: np.log(acceptance(x))
+        log_target = lambda x: process.log_pdf(x) + log_acceptance(x)
+        indicator = pypmc.tools.indicator.hyperrectangle([-1], [1])
+        samples = sampler.draw(log_target, start=process.start(), indicator=indicator, chunks=chunks, chunk_size=chunk_size)[skip_index:]
+        samples = samples[::120]
+
+        return samples
+
 
 # Use cases
 #   I. determine unfolding matrix:
@@ -291,7 +330,7 @@ def flat_acceptance_btokll_matrix():
 
 #      b. generic acceptance "B->Kll"
 def generic_acceptance_btokll_matrix():
-    acceptance_coeffs = np.array([0.50, 0.05])
[…]

### 2015-03-08 draft.tex
added missing reference

@@
   the likelihood is near the boundary of the physically allowed
-  region.\fred{Is there some LHCb note we could cite?}\danny{Ulrik suggests citing some
-  statistical paper}
-  For some of these decays of interest, there are only $\order{10}$--$\order{100}$ events
-  per bin on record.\danny{What to cite? 1403.8004 only states total signal yield!}
+  region \cite{lehmann1998}. For some of these decays of interest, there are only $\order{100}$ events
+  per bin on record.
+
+ % \fred{Is there some LHCb note we could cite?}\danny{Ulrik suggests citing some
+ % statistical paper}
+ % For some of these decays of interest, there are only $\order{10}$--$\order{100}$ events
+ % per bin on record.\danny{What to cite? 1403.8004 only states total signal yield!}
 \item The estimate is unbiased for any $N$. In contrast, the
@@
         \centering
-            \includegraphics[width=0.45\textwidth]{figs/error-Q2_5_6_S5.png}
-            \includegraphics[width=0.45\textwidth]{figs/error-Q2_5_6_S7.png}
-        \caption{Uncertainty of the angular observables $S_5$ and $S_7$, extracted from $2\cdot 10^5$ studies of 
+            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S4.png}
+            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S8.png}
+        \caption{Uncertainty of the angular observables $S_4$ (left) and $S_8$ (right), extracted from $2\cdot 10^5$ studies of 
         simulated events for the decay $B\to K^*\ell^+\ell^-$. We show the uncertainty as a function of the number of simulated events $N$.

### 2015-03-08 draft.tex
fixed small caption of the plots

@@
             \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
-        \caption{Pull distribution for the angular observables $S_5$ and $S_7$, extracted from $2\cdot 10^5$ studies of
+        \caption{Pull distribution for the angular observables $S_5$ (left) and $S_7$ (right), extracted from $2\cdot 10^5$ studies of
         $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a gaussian distribution.}

### 2015-03-09 acceptance.py
Update acceptance.py

@@ -107,6 +107,137 @@ class BToKDilepton(Process):
         n, bins, patches = plt.hist(samples, 25 + 1, normed=1, facecolor='green', alpha=0.75)
         plt.savefig('samples-btokll-%s.pdf' % name)
 
+    def indicator(self):
+        return pypmc.tools.indicator.hyperrectangle([-1], [1])
+
+"""
+SM Case, for 3.0 GeV^2 <= q^2 <= 3.5 GeV^2
+
+Gamma =  7.9504e-21
+J1c =    4.7177e-21
+J1s =    9.6205e-21
+J2c =   -4.5659e-21
+J2s =    3.2005e-22
+J3  =   -1.9674e-23
+J4  =    6.4645e-22
+J5  =   -8.9875e-22
+J6s =    7.3982e-22
+J7  =    2.1124e-22
+J8  =   -7.3283e-23
+J9  =    1.7918e-24
+
+# B->K^*ll::J_5@LargeRecoil: form-factors=KMPW2010,model=SM
+# s_min s_max   central delta_min       delta_max       delta_min       delta_max
+3       3.5     -8.98747e-22    0       0       0       0   (-0% / +0%)
+
+"""
+class BToKstarDilepton(Process):
+    angular_momenta = [
+        (0, 0,  0),     # 1 / (8 * pi)                                              ->  0.039789
+        (0, 2,  0),     # (6 * (J1c - J1s) - 2 * (J2c - J2s)) / (24 * pi * Gamma)   -> -0.032772
+
+        (1, 0,  0),     # 2 * J6s / (8 * pi * Gamma)                                ->  0.007405
+
+        (1, 2, -1),     # 4 * sqrt(3) * J7 / (8 * pi * Gamma)                       ->  0.007324
+        (1, 2,  0),     # -2 * J6s / (8 * pi * Gamma)                               ->  0.007405
+        (1, 2, +1),     # 4 * sqrt(3) * J5 / (8 * pi * Gamma)                       -> -0.031162
+
+        (2, 0,  0),     # 4 * (J2c + 2 * J2s) / (8 * pi * Gamma)                    -> -0.078589
+
+        (2, 2, -2),     # J9 / (pi * Gamma)                                         ->  0.000072
+        (2, 2, -1),     # J8 / (pi * Gamma)                                         -> -0.002934
+        (2, 2,  0),     # (J2c - J2s) / (3 * pi * Gamma)                            -> -0.065206
[…]

### 2015-03-09 draft.tex
Update notes

@@
   uncertainties from detector-resolution and acceptance effects can
-  be incorporated in a general algorithm. Finally, we present the
+  be incorporated into a general algorithm. Finally, we present the
   necessary process-dependent formulae needed for direct
@@
 \emph{method of moments} is the determination of angular observables
-in the rare decay FCNC-mediated decay $\bar{B}\to \bar{K}^*(\to
-\bar{K}\pi)\ell^+\ell^-$. However, note that the method we
-describe in the following is general, and it applies to arbitrary decay
-or scattering processes. We find a previous work \cite{Dighe:1998vk}
-that advocates this method chiefly for the determination of angular
-observables in non-leptonic $B$ decays, but also mentions the
-applicability to semileptonic decays. Our aim is to improve upon this previous
-work by studying the uncertainties that are introduced by mismodelling
-of the angular distribution, and by working out a recipe to determine
-and unfold detector effects. Moreover, we show
-that the method of moments has \add{several} major advantages over the usual
-approach based on likelihood fits:
+in the rare FCNC-mediated decay $\bar{B}\to \bar{K}^*(\to
+\bar{K}\pi)\ell^+\ell^-$. However, the method we describe in the
+following is general and applies to arbitrary decay or scattering
+processes \fred{Not really arbitrary, it only works with orthogonal
+  basis functions}. We find a previous work \cite{Dighe:1998vk} that
+advocates this method chiefly for the determination of angular
+observables in non-leptonic $B$ decays but also mentions the
+applicability to semileptonic decays. Our aim is to improve upon this
+previous work by studying the uncertainties that are introduced by
+mismodeling of the angular distribution, and by working out a recipe
+to determine and unfold detector effects. The latter is crucial for
+the application of the method to real data. We show that
+the method of moments has several major advantages over the usual approach
+based on likelihood fits:
 \begin{enumerate}
@@
         see the LHCb analysis of \dots}.
-        The method of moments does not require reparametrization and approximations.
-
-    \item \add{Likelihood fits of problems, for which the underlying
-        physical model is only partially known, may be delicate. Such cases can lead to
+        The method of moments does not require reparametrizations or approximations.
+
+    \item \add{Likelihood fits  can be unstable in case the underlying
+        physical model is only partially known. This can lead to
         overestimating the number of physical parameters, and consequently
-        inhibit the convergence of the fits. (As an example, this type
+        inhibits the convergence of the fits. As an example, this type
         of problem occured in toy studies of the decay $B\to K^*(\to K\pi)\ell^+\ell^-$
@@
         when a missing symmetry relation between the angular observables
-        was found and applied, thereby reducing the number of fit parameters.)
+        was found and applied, thereby reducing the number of fit parameters.
     }
@@
 \end{enumerate}
+
+\fred{For us, the major advantage is that the experiment can obtain all angular observables at once, and if there are more, one doesn't need more data.
+I'm not sure this becomes clear from the text, point 1.}
 
@@
 angular observable $S_i$ as a coefficient in the probability density
-function (PDF) of the process by means of
+function (PDF), $P(\nuvec, \thvec)$, of the process by
 \begin{align}
@@
 in the basis of Legendre polynomials but the statistical properties
-are equivalent for both approaches provided that one replace $f_i \to
+are equivalent for both approaches \fred{I'm confused. What are the two approaches? Do we consider Legendre polynomials as an orthonormal basis or not?} provided that one replace $f_i \to
 \dual{f}_i$ appropriately. Using the ansatz
@@
 in the final state, we list the dual bases in a series of appendices
-\ref{app:btokll} through \ref{app:lambdabtolambdall}. Note that a
+\ref{app:btokll} through \ref{app:btokstarll}. Note that a
 similar analysis was done in~\cite{Dighe:1998vk} for the decays $B \to
@@
 effects. Numerical studies for one uni-angular and one triple-angular
-distribution are provided in section \ref{sec:numerics}. In a series
-of appendices we provide the orthonormal bases of angular functions
-relevant to several rare $b$ decays.
+distribution are provided in section \ref{sec:numerics}.
 
@@
 The orthonormality relations \refeq{def-ortho-rel} imply that a single angular observable $S_i$
-can be projected out of the full PDF $P$ by means of
+can be projected out of the full PDF $P$ as
 \begin{equation}
@@
 \end{equation}
+\fred{Why is there $\Omega$ but nothing for $\nuvec$?}
 The remainder of this section describes the method of moments, in
@@
 follows a multivariate Gaussian distribution $\mathcal{N}(\vec{S},
-\widehat{\Sigma})$ centered on the true value $\vec{S}$ with the
-covariance $\widehat{\Sigma}_{ij}$ estimated as
+\Sigma)$ centered on the true value $\vec{S}$ with the
+covariance $\Sigma_{ij}$ estimated as
 \begin{equation}
@@
   region \cite{lehmann1998}. For some of these decays of interest, there are only $\order{100}$ events
-  per bin on record.
-
- % \fred{Is there some LHCb note we could cite?}\danny{Ulrik suggests citing some
- % statistical paper}
- % For some of these decays of interest, there are only $\order{10}$--$\order{100}$ events
- % per bin on record.\danny{What to cite? 1403.8004 only states total signal yield!}
+  recorded per bin.
+
 \item The estimate is unbiased for any $N$. In contrast, the
@@
   fits --- if they converge --- produce uncertainties \add{(10--15)\%}
-  smaller than those from the method of moments.
+  smaller than those from the method of moments  \fred{Is this true, Marcin?}.
 \item The approximate multivariate Gaussian distribution of $\vecest{S}$
@@
 result for $P$.  In this section, we focus on one particular class of
-mismodelling of the signal PDF: the angular-momentum cutoff in partial
-wave expansions. This mismodelling potentially affects a large number
+mismodeling of the signal PDF: the angular-momentum cutoff in partial-wave expansions. This mismodeling potentially affects a large number
 of decays and scattering processes. For the sake of clarity we take
@@
   \pi\pi\ell^+\bar\nu_\ell$. For both examples the PDF $P$ is known in
-  the small-width approximation and when assuming a pure $P$-wave,
+  the small-width approximation and when assuming a pure $P$-wave
   resonant final state. An extension to $S-P$ interference has been
@@
 We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{l}^{(|m|)}$
-with respect to the remaining angle $\theta_2$. \add{Here, the angular momentum-like indices $l$ and $m$ follows from the usual
+with respect to the remaining angle $\theta_2$. \add{Here, the angular-momentum indices $l$ and $m$ follows from the usual
 rules for addition of the angular momenta $j$ and $\tilde{j}$ of the partial wave expansion of the underlying
 amplitude and its complex conjugate: $j - \tilde{j} \leq l \leq j + \tilde{j}$, and $m = j_z + \tilde{j}_z$.}
-Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
-and as defined in \refapp{partial-waves}, the expansion reads
-\begin{equation}
-    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\sin\theta_2\,,
-\end{equation}
-where the the normalization factor $n_{l,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
+
+For the decay at hand, we consider the partial-wave expansion for the angular observables (see \cite{Lee:1992ih} and \refapp{partial-waves})
+\begin{equation}
+    S_k(\vec{\nu}) \equiv \frac{I_k(\nuvec)}{4\pi \Gamma)}\,,\quad\text{with}\quad \Gamma = I_1(\nuvec) - \frac{I_2(\nuvec)}{3}\,,
+\end{equation}
+\fred{It not clever to use $k$ as an index and momentum variable}
+which reads
+\begin{equation}
+    \label{eq:expansion}
+    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\sin\theta_2\,.
+\end{equation}
+The normalization factor $n_{l,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
 example we have (cf. also \refapp{btokstarll} and \cite{Lee:1992ih})
@@
 \end{equation}
-The angular observables $S_{k,j}$ defined as coefficients of this expansion in Legendre polynomials
+
+The angular observables $S_{k,l}$ -- as defined in \refeq{expansion} --
 have the merit of a well defined total angular momentum, and thus are physically discriminable.
 As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
-partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. \add{That is to say},
+partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. That is to say,
 ignoring further (orthogonal) terms in the PDF cannot affect $\vecest{S}$ nor its variance.\\
+\fred{That's not true. $\vecest{S}$ is enlarged with more angular observables. But the first components are unaffected.}\\
 
@@
 
-We wish to emphasize, however, that detector acceptance effects systematically affect the expansion for any basis
+We wish to emphasize that detector acceptance effects systematically affect the expansion for any basis
 of angular functions, including the one suggested in this section.
@@
 
-The determination of a detector's performance to detect signal events
+\fred{Ascertaining} a detector's performance to detect signal events
 with accurate determination of the event's angles is generally a
 difficult task. In the ideal case, one would have an explicit
-probabilistic model of the detector acceptance effects and could thus
+probabilistic model of the detector acceptance and could thus
 write down the full forward model from which the measured events
@@
 \lbrace(\vec{\nu}^{(n)}_\text{d}, \vec\theta^{(n)}_\text{d})\rbrace$,
-$n=1,\dots,N_\text{d}$.  In general, the distribution of the detected
-events is
+$n=1,\dots,N_\text{d}$ with $N_\text{d} \le N_\text{t}$.  In general,
+the distribution of the detected events is
 \begin{equation}
@@
 \end{equation}
+\fred{In this section, all integration symbols are at the end, in ch. 2 they were right after the $\int$ sign.}
 Here $P_\text{t}$ is the probability distribution of the true events,
@@
   \label{eq:def-R}
-    R \equiv \iint P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}} \rmdx{x_\text{d}}\,,
-\end{equation}
-and the kernel $E(x_\text{d}| x_\text{t})$ parametrizes acceptance and
-resolution effects. The kernel is usually decomposed as
+    R \equiv \iint P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}} \rmdx{x_\text{d}}\,.
+\end{equation}
+The kernel $E(x_\text{d}| x_\text{t})$ is usually decomposed as
 \begin{equation}
@@
 In words, for each $m$ it is required to generate events from
-a toy physical distribution $P^{(m)}$ in which $S_0 = S_m=1/2$ and all other
-observables are set to zero, and to propagate these events through
+a toy physical distribution $P^{(m)}$, for which $S_0 = S_m=1/2$ and all other
+observables are set to zero. Next, propagate these events through
 a detector simulation. The normalization $R^{(m)}$ is chosen such
@@
 \end{equation}
-We call the matrix $M$ the \emph{unfolding matrix}, which is
+We call the matrix $M$ the \emph{unfolding matrix} \fred{actually that's the folding matrix}, which is
 specific to the decay at hand.
@@
 \add{Apparently we now face a circular dependence. On the one hand,
-the estimators $\vecest{Q}$, and thus also the estimator $\vecest{S}$
+the estimators $\vecest{Q}$ and thus also $\vecest{S}$
 are proportional to $R$, the ratio of detected events over occuring events.
@@
 We solve this problem by observing that the MC estimators $\vecest{S}$ need to fulfill
-a self-consistency condition, which reads
+the self-consistency condition
 \begin{equation}
@@
 carry out a combined analysis for the determination of the branching ratio
-and the extraction of the angular observables.\\
+and the extraction of the angular observables \fred{Marchin, Nicola: Do you do a combined analysis for Moriond?}.\\
 Moreover, in the applications to $B$ decays only ratios and similar $R$-independent combinations
@@
 \end{equation}
+\fred{Danny: Is $\est{S}_0$ physical? I guess not. So it should be
+\begin{equation}
+    \vecest{S} = ( \est{S}_0, \underbrace{\est{S}_1, \dots, \est{S}_{\dim S}}_\text{physical}, \underbrace{\est{S}_{\dim S + 1}, \dots, \est{S}_{\dim Q}}_\text{``superfluous''})\,.
+\end{equation}
+but then $\dim S$ is not right.
+}
 The method is consistent as long as the MC estimators for the ``superfluous'' observables with indices $\dim S + 1$ to $\dim Q$
@@
 compute time and accuracy. For a uniangular distribution and a total of $6\cdot 10^6$ MC
-samples (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find that the error on the mean is
-smaller than $6\cdot 10^{-4}$. Let us conclude this section by commenting that parts of the unfolding
+samples \fred{Before or after thinning?} (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find that the error on the mean
+of each matrix element is smaller than $6\cdot 10^{-4}$. \add{This suggests, that the so-induced
+systematic error can be driven below any statistical uncertainty.}
+
+Let us conclude this section by commenting that parts of the unfolding
 matrix are universal in a sense. Specifically, they can be reused in analyses with a similar underlying decay.
-Therefore, computing resources spent on improving its accuracy are not wasted.
+Therefore, computing resources spent on improving \add{the accuracy of $\est{M}$} are not wasted.
 
@@
 individual events for two separate physical processes: one uni-angular, and one tri-angular decay
-distribution. We repeats theses analysis for varying sample sizes, ranging from
-$50$ to $500$ events. Our toy analyses base on SM predictions for angular observables
-in the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to K\pi)\ell^+\ell^-$, respectively.
-In order to faithfully investigate the performance of the method of moments, we repeats our
+distribution. We repeat the analysis for varying sample sizes, ranging from
+$50$ to $500$ events. Our toy analyses are based on SM predictions for angular observables
+in the decays $B\to K\ell^+\ell^-$ and $B\to K^*(\to K\pi)\ell^+\ell^-$.
+In order to faithfully investigate the performance of the method of moments, we repeat our
 numerical studies for several bins in the kinematic range $1\,\GeV^2 \leq q^2 \leq 6\,\GeV^2$,
@@
         obtained in our studies can be successfully
-        fitted to a gaussian distribution. Due to the large number of studied distributions, we have
-        to restrict ourselved to a subset. In our opinion the pull distributions for the observables
-        $S_5 \simeq 27\%$ and $S_7 \simeq 2\%$, which are obtained from SM-like $B\to K^*\ell^+\ell^-$
-        decays, are good examples. We show their respective pull distributions for $2\cdot 10^5$ toy studies
-        of $200$ events per study in \reffig{pulls}.
-
+        fitted to a Gaussian distribution. Out of the large number  of studied distributions, we only show the pull distributions for the observables
+        $S_5 \simeq 27\%$ and $S_7 \simeq 2\%$ obtained from SM-like $B\to K^*\ell^+\ell^-$
+        decays as representative examples. We generated $2\cdot 10^5$ toy studies
+        with $200$ events per study in \reffig{pulls}.
     \item We study the MC estimate for the absolute uncertainty $\est{\sigma_i(N)}$ with respect to the angular observable $S_i$
-        as a function of the number of simulated events $N$. As expected for a multivariate gaussian
+        as a function of the number of simulated events $N$. As expected for a multivariate Gaussian
         distribution, we find that the absolute uncertainty is well fitted by
@@
 We find that the previous two bullet points still hold; i.e., we do not find any bias, and the distribution
-is well described by a multivariate Gaussian distribution.
+is well described by a multivariate Gaussian distribution. The latter only holds as long as the number of events
+per experiment exceeds $\sim 20$.
 }
@@
         \caption{Pull distribution for the angular observables $S_5$ (left) and $S_7$ (right), extracted from $2\cdot 10^5$ studies of
-        $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a gaussian distribution.}
+        $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a Gaussian distribution.}
         \label{fig:pulls}
@@
 Second, in the absence of detector effects, a determination using the method of moments is correct and unbiased
-even when not all aspects of the physical distribution are modelled. This is explicitly shown for the case of
+even when not all aspects of the physical distribution are modeled. This is explicitly shown for the case of
 higher partial waves in multibody final states.
@@
 
-We would like to thank Ulrik Egede, Gudrun Hiller, Martin Jung and Konstantinos Petridis for insightful discussions,
-as well as Claus Grupen for helpful advice in searching the literatur.
+We thank Ulrik Egede for insightful discussions and helpful comments on the
+manuscript. We are grateful to Gudrun Hiller, Martin Jung and Konstantinos Petridis for helpful discussions,
+as well as Claus Grupen for helpful advice in searching the literature.
 The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).

### 2015-03-10 draft.tex
add some comments, fix some spelling and language

@@
 amplitude and its complex conjugate: $j - \tilde{j} \leq l \leq j + \tilde{j}$, and $m = j_z + \tilde{j}_z$.}
-
-For the decay at hand, we consider the partial-wave expansion for the angular observables (see \cite{Lee:1992ih} and \refapp{partial-waves})
-\begin{equation}
-    S_k(\vec{\nu}) \equiv \frac{I_k(\nuvec)}{4\pi \Gamma)}\,,\quad\text{with}\quad \Gamma = I_1(\nuvec) - \frac{I_2(\nuvec)}{3}\,,
-\end{equation}
-\fred{It not clever to use $k$ as an index and momentum variable}
-which reads
-\begin{equation}
-    \label{eq:expansion}
-    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\sin\theta_2\,.
-\end{equation}
-The normalization factor $n_{l,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
+Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$ \fred{It not clever to use $k$ as an index and momentum variable}
+and as defined in \refapp{partial-waves}, the expansion reads
+\begin{equation}
+    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\sin\theta_2\,,
+\end{equation}
+where the the normalization factor $n_{l,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
 example we have (cf. also \refapp{btokstarll} and \cite{Lee:1992ih})
@@
 \end{equation}
-
-The angular observables $S_{k,l}$ -- as defined in \refeq{expansion} --
-have the merit of a well defined total angular momentum, and thus are physically discriminable.
-As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
-partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. That is to say,
-ignoring further (orthogonal) terms in the PDF cannot affect $\vecest{S}$ nor its variance.\\
+The angular observables $S_{k,j}$ defined as coefficients of this
+expansion in Legendre polynomials have the merit of a well defined
+total angular momentum, and thus are physically distinguishable.  As a
+consequence of the orthogonality of the Legendre polynomials, any
+mismodeling (or rather, lack of modeling of higher partial-wave
+observables) \emph{does not affect} the method of moments as discussed
+in the previous section. \add{That is to say}, ignoring further
+(orthogonal) terms in the PDF neither affects $\vecest{S}$ nor its
+variance.
 \fred{That's not true. $\vecest{S}$ is enlarged with more angular observables. But the first components are unaffected.}\\
@@
 In words, for each $m$ it is required to generate events from
-a toy physical distribution $P^{(m)}$, for which $S_0 = S_m=1/2$ and all other
-observables are set to zero. Next, propagate these events through
+a toy physical distribution $P^{(m)}$ in which $S_0 = S_m=1/2$ and all other
+observables are set to zero, and to propagate these events through
 a detector simulation. The normalization $R^{(m)}$ is chosen such
@@
 compute time and accuracy. For a uniangular distribution and a total of $6\cdot 10^6$ MC
-samples \fred{Before or after thinning?} (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find that the error on the mean
-of each matrix element is smaller than $6\cdot 10^{-4}$. \add{This suggests, that the so-induced
-systematic error can be driven below any statistical uncertainty.}
-
-Let us conclude this section by commenting that parts of the unfolding
+samples \fred{Before or after thinning?} (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find that the error on the mean is
+smaller than $6\cdot 10^{-4}$. Let us conclude this section by commenting that parts of the unfolding
 matrix are universal in a sense. Specifically, they can be reused in analyses with a similar underlying decay.
-Therefore, computing resources spent on improving \add{the accuracy of $\est{M}$} are not wasted.
+Therefore, computing resources spent on improving its accuracy are not wasted.
 
@@
 We find that the previous two bullet points still hold; i.e., we do not find any bias, and the distribution
-is well described by a multivariate Gaussian distribution. The latter only holds as long as the number of events
-per experiment exceeds $\sim 20$.
+is well described by a multivariate Gaussian distribution.
 }
@@
 
-We thank Ulrik Egede for insightful discussions and helpful comments on the
-manuscript. We are grateful to Gudrun Hiller, Martin Jung and Konstantinos Petridis for helpful discussions,
-as well as Claus Grupen for helpful advice in searching the literature.
+We would like to thank Ulrik Egede, Gudrun Hiller, Martin Jung and Konstantinos Petridis for insightful discussions,
+as well as Claus Grupen for helpful advice in searching the literatur.
 The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).

### 2015-03-10 draft.tex
Replies to Fred's comments

--- 2015-03-09 draft.tex
@@
 \bar{K}\pi)\ell^+\ell^-$. However, the method we describe in the
-following is general and applies to arbitrary decay or scattering
-processes \fred{Not really arbitrary, it only works with orthogonal
-  basis functions}. We find a previous work \cite{Dighe:1998vk} that
+following is general and applies to \add{all decay or scattering
+processes that can be formulated in terms of an orthogonal basis of angular functions.}
+\fred{Not really arbitrary, it only works with orthogonal
+basis functions.} \danny{Is this OK?}
+We find a previous work \cite{Dighe:1998vk} that
 advocates this method chiefly for the determination of angular
@@
 the angular observables $\lbrace S_i\rbrace$; thus ratios or similar suitable combinations
-of the angular observables are not affected by this change of normalization.\\
+of the angular observables are not affected by \add{a} change of normalization.\\
 
@@
 system of angular functions $\{f_i(\thvec)\}$ \emph{can} be transformed into
-an orthonormal basis. It turns out to be much more convenient to work
-in the basis of Legendre polynomials but the statistical properties
-are equivalent for both approaches \fred{I'm confused. What are the two approaches? Do we consider Legendre polynomials as an orthonormal basis or not?} provided that one replace $f_i \to
-\dual{f}_i$ appropriately. Using the ansatz
+an orthonormal basis. \add{We find it convenient to work
+in the basis of Legendre polynomials, which is not self-dual.
+However, the statistical properties of the method of moments are equivalent for both self-dual and non-self-dual
+bases, provided that one replace $f_i \to \dual{f}_i$ appropriately.}
+\fred{I'm confused. What are the two approaches? Do we consider Legendre polynomials as an orthonormal basis or not?}
+Using the ansatz
 \begin{equation}
@@
 \end{equation}
-where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular functions. In general, $\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$. This is the
+where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular functions
+\add{, and $\Omega$ represents the entire angular phase space.}. In general, $\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$. This is the
 case for our selection of applications in appendices \ref{app:btokll} through \ref{app:btokstarll}.\\
@@
 \fred{Why is there $\Omega$ but nothing for $\nuvec$?}
+\danny{a) intoduced $\Omega$ one equation earlier, b) we always need
+and integration of the \emph{entire} angular phase space; the integration
+over the non-angular phase space is irrelevant to the discussion.}
 The remainder of this section describes the method of moments, in
@@
   fits --- if they converge --- produce uncertainties \add{(10--15)\%}
-  smaller than those from the method of moments  \fred{Is this true, Marcin?}.
+      smaller than those from the method of moments  \fred{Is this true, Marcin?} \danny{Marcin already confirmed!}.
 \item The approximate multivariate Gaussian distribution of $\vecest{S}$
@@
 \fred{It not clever to use $k$ as an index and momentum variable}
+\danny{I disagree. We use the same notation as in the literature, and people
+should be able to distinguish these based on context.}
 which reads
@@
 compute time and accuracy. For a uniangular distribution and a total of $6\cdot 10^6$ MC
-samples \fred{Before or after thinning?} (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find that the error on the mean
+samples \fred{Before or after thinning?}\danny{No thinning at all!} (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find that the error on the mean
 of each matrix element is smaller than $6\cdot 10^{-4}$. \add{This suggests, that the so-induced

### 2015-03-10 draft.tex
first bunch of changes

@@
 \newcommand{\fred}[1]{{\color{brown!85!black}#1}}
+\newcommand{\marcin}[1]{{\color{cyan}#1}}
 \newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}
@@
 \bar{K}\pi)\ell^+\ell^-$. However, the method we describe in the
-following is general and applies to \add{all decay or scattering
-processes that can be formulated in terms of an orthogonal basis of angular functions.}
-\fred{Not really arbitrary, it only works with orthogonal
-basis functions.} \danny{Is this OK?}
+following is general and applies to all decay or scattering
+processes that can be formulated in terms of an orthogonal basis of angular functions.
 We find a previous work \cite{Dighe:1998vk} that
@@
 \fred{For us, the major advantage is that the experiment can obtain all angular observables at once, and if there are more, one doesn't need more data.
-I'm not sure this becomes clear from the text, point 1.}
+I'm not sure this becomes clear from the text, point 1.}\marcin{I think it is ok}
 
@@
   the expected loss associated with deciding on just one value of the
-  unknown parameter. \add{One should therefore not prefer the method of moments
-  over likelihood fits just because the former reduces}
-  the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
+  unknown parameter. One should therefore not prefer the method of moments
+  over likelihood fits just because the former reduces
+  the bias~\cite[sections 13.8,17.2]{jaynes:2003} \marcin{we said we cahnge this but after reading it again I like it and would not change}. In fact, for
   the results discussed below in \refsec{numerics}, the likelihood
-  fits --- if they converge --- produce uncertainties \add{(10--15)\%}
-      smaller than those from the method of moments  \fred{Is this true, Marcin?} \danny{Marcin already confirmed!}.
+  fits --- if they converge --- produce uncertainties (10--15)\%
+      smaller than those from the method of moments.
 \item The approximate multivariate Gaussian distribution of $\vecest{S}$
@@
   proved to be challenging due to technical reasons (such as data formats,
-  size etc.) \add{as well as political reasons; i.e., the publication of
-  the likelihood also publishes collaboration-internal data.}
+  size etc.) %\add{as well as political reasons; i.e., the publication of
+ % the likelihood also publishes collaboration-internal data.}
   This leads to the

### 2015-03-10 draft.tex
added  scatter plots

@@
 \danny{I disagree. We use the same notation as in the literature, and people
-should be able to distinguish these based on context.}
+should be able to distinguish these based on context.} \marcin{I am fine with k}
 which reads
@@
 
-\del{The precise value of $R$ (see \refeq{def-R}) depends on the a priori
-unknown angular observables $\vec S$.  However, within ratios and
-other suitable combinations of the estimators $\vecest{S}$, the quantity
-$R$ cancels.
-Conversely, $R$ can be
-extracted from the self-consistency condition\footnote{This condition
-  is process dependent; see \refeq{recipe:lambdabtolambdall} and
-\refeq{recipe:btokstarll}.}  $\hat{S}_0 = \frac{1}{2}$. Since $R$ is
-relevant in the determination of the branching ratio, it is therefore
-useful to carry out that determination and the extraction of the
-angular observables in a combined analysis.}\\
+%\del{The precise value of $R$ (see \refeq{def-R}) depends on the a priori
+%unknown angular observables $\vec S$.  However, within ratios and
+%other suitable combinations of the estimators $\vecest{S}$, the quantity
+%$R$ cancels.
+%Conversely, $R$ can be
+%extracted from the self-consistency condition\footnote{This condition
+%  is process dependent; see \refeq{recipe:lambdabtolambdall} and
+%\refeq{recipe:btokstarll}.}  $\hat{S}_0 = \frac{1}{2}$. Since $R$ is
+%relevant in the determination of the branching ratio, it is therefore
+%useful to carry out that determination and the extraction of the
+%angular observables in a combined analysis.}\\
 
@@
         \end{equation}
-        \danny{Marcin, please check that this is what you used!}
         Here $S_i$ refers to the true (input) value for the angular observables, $\est{S}_i$ refers to the
@@
 \end{itemize}
+\begin{figure}[b]
+        \centering
+            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S5_200.png}
+            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
+        \caption{Pull distribution for the angular observables $S_5$ (left) and $S_7$ (right), extracted from $2\cdot 10^5$ studies of
+        $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a Gaussian distribution.}
+        \label{fig:pulls}
+\end{figure}
 
@@
         \centering
-            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S5_200.png}
-            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
-        \caption{Pull distribution for the angular observables $S_5$ (left) and $S_7$ (right), extracted from $2\cdot 10^5$ studies of
-        $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a Gaussian distribution.}
-        \label{fig:pulls}
-\end{figure}
-
-\begin{figure}[t]
-        \centering
             \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S4.png}
@@
         \label{fig:errors}
+\end{figure}
+
+We also studied the correlation of the estimators from Method of Moments to a maximum likelihood fit.
+We performed a toy study by simulating $10^3$ toys of 200 events.
+We then use for each toy method described in~\refsec{systematics:partial-waves} and a standard maximum likelihood method.
+In \reffig{correlation} the two estimators distributions are showed.
+In conclusion the two estimators are highly correlated but different between then can be of the order of statistic uncertainty of the maximum likelihood estimator.
+
+\begin{figure}[t]
+        \centering
+            \includegraphics[width=0.45\textwidth]{figs/S3_scat.pdf}
+            \includegraphics[width=0.45\textwidth]{figs/S5_scat.pdf}
+        \caption{Correlation between Method of Moments and maximum likelihood estimators for observables $S_3$ and $S_5$. }
+        \label{fig:correlation}
 \end{figure}

### 2015-03-11 draft.tex
added  scatter plots
Update: More replies to Fred, revtex4-1, PRD style (two columns)

@@
 % vim: set sts=4 et :
-\documentclass[aps,prd,reprint,nofootinbib,preprintnumbers]{revtex4}
+\documentclass[aps,nofootinbib,preprintnumbers,prd,twocolumn]{revtex4-1}
 
@@
 \begin{equation}
-    \Sigma_{ij} \equiv \cov[S_i,S_j] \to \est{\Sigma_{ij}} \equiv \est{\cov}[{S}_i, {S}_j]
-        = \frac{1}{N - 1} \sum_{n=1}^{N} \Big[\dual{f}_i\big(x^{(n)}\big) - \est{S_i}\Big]\,\Big[\dual{f}_j\big(x^{(n)}\big) - \widehat{S_j}\Big]\,.
+\begin{aligned}
+    \Sigma_{ij}
+        & \equiv \cov[S_i,S_j]\\
+        & \to \est{\Sigma_{ij}} \equiv \est{\cov}[{S}_i, {S}_j]\\
+        & = \frac{1}{N - 1} \sum_{n=1}^{N} \Big[\dual{f}_i\big(x^{(n)}\big) - \est{S_i}\Big]\,\Big[\dual{f}_j\big(x^{(n)}\big) - \widehat{S_j}\Big]\,.
+\end{aligned}
 \end{equation}
@@
 \begin{figure}
-    \includegraphics[width=.6\textwidth]{fig-topology.pdf}
+    \includegraphics[width=.45\textwidth]{fig-topology.pdf}
     \caption{Decay topology for decays $B\to P_1 P_2 \ell_1 \bar\ell_2$. \label{fig:topology}}
@@
 which reads
-\begin{equation}
+\begin{multline}
     \label{eq:expansion}
-    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\sin\theta_2\,.
-\end{equation}
+    S_{k}(\vec{\nu},\cos\theta_2) \\
+        \equiv \sum_{j} \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\sin\theta_2\,.
+\end{multline}
 The normalization factor $n_{l,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
@@
 
-\fred{Ascertaining} a detector's performance to detect signal events
+Ascertaining a detector's performance to detect signal events
 with accurate determination of the event's angles is generally a
@@
 \begin{equation}
-    P_\text{d}(x_\text{d}) = \frac{1}{R} \int P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}}\,.
+    P_\text{d}(x_\text{d}) = \frac{1}{R} \int \rmdx{x_\text{t}} P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \,.
 \end{equation}
@@
   \label{eq:def-R}
-    R \equiv \iint P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t}) \rmdx{x_\text{t}} \rmdx{x_\text{d}}\,.
+    R \equiv \iint \rmdx{x_\text{t}} \rmdx{x_\text{d}} P_\text{t}(x_\text{t}) E(x_\text{d} | x_\text{t})\,.
 \end{equation}
@@
 and orthogonality of the Legendre polynomials, and one therefore has
-\begin{equation}
-    \tilde{f}_k(x) = \frac{2 k + 1}{2} f_k(x),\qquad \int_{-1}^{+1} \tilde{f}_k(x) f_l(x) \rmdx{x} = \delta_{k,l}\,.
-\end{equation}
+\begin{gather}
+    \tilde{f}_k(x) = \frac{2 k + 1}{2} f_k(x)\,,\\
+    \int_{-1}^{+1} \rmdx{x} \tilde{f}_k(x) f_l(x) = \delta_{k,l}\,.
+\end{gather}
 We now define the \emph{simulated raw} moments $\vec{Q}^{(m)}$ as
@@
     \label{eq:analytic-raw-moments}
-    Q_i^{(m)} \equiv \iint \tilde{f}_i(\xd) P^{(m)}(\xt) \Ekernel \rmdx{\xt} \rmdx{\xd},
+    Q_i^{(m)} \equiv \iint \rmdx{\xt} \rmdx{\xd} \tilde{f}_i(\xd) P^{(m)}(\xt) \Ekernel,
 \end{equation}
@@
 \begin{equation}
-    x_\text{d}^{(n,m)} \sim P_E^{(m)}(\xd) \equiv \frac{1}{R^{(m)}} \int P^{(m)}(\xt) \Ekernel \rmdx{\xt}\,.
+    x_\text{d}^{(n,m)} \sim P_E^{(m)}(\xd) \equiv \frac{1}{R^{(m)}} \int \rmdx{\xt} P^{(m)}(\xt) \Ekernel\,.
 \end{equation}
@@
 \end{equation}
-We call the matrix $M$ the \emph{unfolding matrix} \fred{actually that's the folding matrix}, which is
-specific to the decay at hand.
+We call the matrix \add{$M^{-1}$} the \emph{unfolding matrix},
+\fred{actually that's the folding matrix}
+\danny{switched to $M^{-1}$ instead. OK?}
+which is specific to the decay at hand.
 Given our definition of $S_k^{(m)}$ in
@@
 
-%\del{The precise value of $R$ (see \refeq{def-R}) depends on the a priori
-%unknown angular observables $\vec S$.  However, within ratios and
-%other suitable combinations of the estimators $\vecest{S}$, the quantity
-%$R$ cancels.
-%Conversely, $R$ can be
-%extracted from the self-consistency condition\footnote{This condition
-%  is process dependent; see \refeq{recipe:lambdabtolambdall} and
-%\refeq{recipe:btokstarll}.}  $\hat{S}_0 = \frac{1}{2}$. Since $R$ is
-%relevant in the determination of the branching ratio, it is therefore
-%useful to carry out that determination and the extraction of the
-%angular observables in a combined analysis.}\\
-
 We note that $\vecest{S}$ as determined from \refeq{estS} does not fully correspond to $\vec{S}$
@@
 }
+\danny{Fred: We simplfy define the label ``physical'' right here, which includes
+$S_0$. Although perhaps a better label would be ``nominal''?}
 The method is consistent as long as the MC estimators for the ``superfluous'' observables with indices $\dim S + 1$ to $\dim Q$
@@
 In conclusion the two estimators are highly correlated but different between then can be of the order of statistic uncertainty of the maximum likelihood estimator.
+We found that in some observables this can reach almost half of the statistical error.
 
@@
 \begin{equation}
+\begin{aligned}
     P(q^2, \cos\theta_1)
-        = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^2\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1}}
-        = \frac{a(q^2)}{\rmdx{\Gamma}/\rmdx{q^2}} + \frac{b(q^2)}{\rmdx{\Gamma}/\rmdx{q^2}} \cos\theta_1 + \frac{c(q^2)}{\rmdx{\Gamma}/\rmdx{q^2}} \cos^2\theta_1
-        = \sum_i S_i p_i(\cos\theta_1)\,,
+        & = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^2\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1}}\\
+        & = \frac{a(q^2)}{\rmdx{\Gamma}/\rmdx{q^2}} + \frac{b(q^2)}{\rmdx{\Gamma}/\rmdx{q^2}} \cos\theta_1\\
+        & \quad + \frac{c(q^2)}{\rmdx{\Gamma}/\rmdx{q^2}} \cos^2\theta_1\\
+        & \equiv \sum_i S_i p_i(\cos\theta_1)\,,
+\end{aligned}
 \end{equation}
@@
 \begin{equation}
-    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \sum_i S_i f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
+\begin{aligned}
+    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3)
+        & = \frac{(\rmdx{\Gamma} /\, \rmdx{q^2})^{-1} \rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}}\\
+        & = \sum_i S_i f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
+\end{aligned}
 \end{equation}
@@
 dilepton and the $N\pi$ system, respectively, and $-1 \leq m \leq 1$
-is the third component of either of the angular momenta.
-Our choice of an orthonormal basis and its dual reads
-\begin{equation}
-\label{eq:lambdab:bases}
-\begin{aligned}
-    f_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
-    & = \sqrt{\frac{(l_1 - |m|)!\,(l_2 - |m|)!}{(l_1 + |m|)!\,(l_2 + |m|)!}} p_{l_1}^{|m|}(\cos\theta_1) p_{l_2}^{|m|}(\cos\theta_2)\\
-    & \times \begin{cases}
+is the third component of either of the angular momenta.\\
+
+Our choice of an orthonormal basis reads
+\begin{multline}
+\label{eq:lambdab:bases1}
+    f_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)\\
+    = \sqrt{\frac{(l_1 - |m|)!\,(l_2 - |m|)!}{(l_1 + |m|)!\,(l_2 + |m|)!}}\\
+    \quad \times p_{l_1}^{|m|}(\cos\theta_1) p_{l_2}^{|m|}(\cos\theta_2)\\
+    \quad \times \begin{cases}
             \cos(|m|\theta_3) & m > 0\\
@@
             1                 & m = 0
-        \end{cases}\,,\\
-    \tilde{f}_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
-    & = \frac{(2l_1 + 1)(2l_2 + 1)}{8\pi}\sqrt{\frac{(l_1 - m)!\,(l_2 - m)!}{(l_1 + m)!\,(l_2 + m)!}} p_{l_1}^m(\cos\theta_1) p_{l_2}^m(\cos\theta_2)\\
-    & \times \begin{cases}
+        \end{cases}\,,
+\end{multline}
+and its dual is
+\begin{multline}
+\label{eq:lambdab:bases2}
+    \tilde{f}_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)\\
+    = \frac{(2l_1 + 1)(2l_2 + 1)}{8\pi}\sqrt{\frac{(l_1 - m)!\,(l_2 - m)!}{(l_1 + m)!\,(l_2 + m)!}}\\
+    \quad\times p_{l_1}^m(\cos\theta_1) p_{l_2}^m(\cos\theta_2)\\
+    \quad \times \begin{cases}
             2 \cos(|m|\theta_3) & m > 0\\
@@
         \end{cases}\,.\\
-\end{aligned}
-\end{equation}
+\end{multline}
+
+\begin{widetext}
 The correspondence between out choice of angular observables in the angular momentum basis, and the angular
@@
 \end{equation}
+\end{widetext}
 
 For the purpose of unfolding acceptance effects as laid down in \refsec{systematics:acceptance}, it is instrumental
-to know that $f_{0,0,0} \equiv 1$, and that $\max_{\cos\theta_1,\cos\theta_2,\phi} |f_{l_1, l_2, m}| < 1$.
-The recipe's generating PDFs are therefore
+to know that $f_{0,0,0} \equiv 1$, and that $\max_{\cos\theta_1,\cos\theta_2,\phi} |f_{l_1, l_2, m}| < 1$.\\
+
+The recipe's generating PDFs are therefore $P(x|\lbrace S_i^{(j)}\rbrace)$, with
 \begin{equation}
     \label{eq:recipe:lambdabtolambdall}
-    P(x|\lbrace S_i^{(j)}\rbrace)\,,\quad\text{with}\quad S_i^{(j)} = \frac{1}{8\pi}
+        S_i^{(j)} = \frac{1}{8\pi}
         \begin{cases}
@@
             \delta_{i,(0,0,0)}  + \delta_{i,j}  & j \neq (0, 0, 0)
-        \end{cases}
-\end{equation}
-where $j$ is now also a multi-index representing $j \equiv (\tilde l_1, \tilde l_2, \tilde m)$.
+        \end{cases}\,,
+\end{equation}
+and where $j$ is now also a multi-index representing $j \equiv (\tilde l_1, \tilde l_2, \tilde m)$.
 
@@
 \begin{equation}
-    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}}
-    = \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
+\begin{aligned}
+    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3)
+    & = \frac{(\rmdx{\Gamma}/\rmdx{q^2})^{-1}\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}}\\
+    & = \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
+\end{aligned}
 \end{equation}
@@
 is the third component of either of the angular momenta.
-We use the same bases of angular functions as given in \refeq{lambdab:bases} for the decay $\Lambda_b\to \Lambda\ell^+\ell^-$.
+We use the same bases of angular functions as given in \refeq{lambdab:bases1} and \refeq{lambdab:bases2}
+for the decay $\Lambda_b\to \Lambda\ell^+\ell^-$.
+\begin{widetext}
 In that case, the angular observables correspond to the usual choice of observables via
@@
                       &                                                                                    &
-    8\pi S_{2, 2, -2} & = \frac{8 J_9}{\rmdx{\Gamma}/\rmdx{q^2}}                                           \\
+    8\pi S_{2, 2, -2} & = \frac{8 J_9}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                        \\
 %
@@
                       &                                                                                    &
-    8\pi S_{2, 2, +2} & = \frac{8 J_3}{\rmdx{\Gamma}/\rmdx{q^2}}                                           \\
-\end{aligned}
-\end{equation}
+    8\pi S_{2, 2, +2} & = \frac{8 J_3}{\rmdx{\Gamma}/\rmdx{q^2}}\,.                                        \\
+\end{aligned}
+\end{equation}
+\end{widetext}
 
@@
 to know that $f_{0,0,0} \equiv 1$, and that $\max_{\cos\theta_1,\cos\theta_2,\phi} |f_{l_1, l_2, m}| \leq 1$.
-The recipe's generating PDFs are therefore
+The recipe's generating PDFs are therefore $P(x|\lbrace S_i^{(j)}\rbrace)$ with
 \begin{equation}
     \label{eq:recipe:btokstarll}
-    P(x|\lbrace S_i^{(j)}\rbrace)\,,\quad\text{with}\quad S_i^{(j)} = \frac{1}{8\pi}
+    S_i^{(j)} = \frac{1}{8\pi}
         \begin{cases}
@@
 
+\add{For convenience, we use this appendix to collect there necessary
+formulae needed in the partial-wave expansion.}
 Let us assume that the angular decomposition has been achieved for
@@
 \hat{=}$ S,P,D$,\dots$ of the underlying amplitudes $A_1$ and $A_2$,
+\begin{widetext}
 \begin{equation}
@@
 \end{equation}
+\end{widetext}
 where $F \in \{\text{Re},\text{Im}\}$ denotes taking either the real
@@
 \label{eq:legendre-scalar-product}
-    n_{l, m} \delta_{l, l'} \equiv \int_{-1}^1 \rmdx{\cos\theta} p_{l}^{(m)}(\cos\theta) p_{l'}^{(m)} (\cos\theta)  = \frac{2}{(2 l + 1)} \frac{(l + m)!}{(l - m)!} \delta_{l, l'}\,.
+\begin{aligned}
+    n_{l, m} \delta_{l, l'}
+    & \equiv \int_{-1}^1 \rmdx{\cos\theta} p_{l}^{(m)}(\cos\theta) p_{l'}^{(m)} (\cos\theta)\\
+    & = \frac{2}{(2 l + 1)} \frac{(l + m)!}{(l - m)!} \delta_{l, l'}\,.
+\end{aligned}
 \end{equation}
@@
 
-We propose the decomposition of $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$,
+We \add{decompose}\del{propose the decomposition of} $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$,
 with total angular momentum $j$ and its third component $m=m_1 + m_2$.
@@
 the partial-wave amplitudes,
+\begin{widetext}
 \begin{equation}
@@
 \end{equation}
-
 In the last step, we use Gaunt's formula \cite{Gaunt:1929} to integrate a triple product of associated Legendre polynomials,
@@
 \end{equation}
+\end{widetext}
 where
@@
 \begin{aligned}
-    s & = \frac{j + l_1 + l_2}{2}\,, &
-    p & = \max(0, l_2 - l_1 - m)\,, &
-    q & = \min(l_1 + l_2 - m, j - m, l_2 - m_2)\,.
+    s & \equiv \frac{j + l_1 + l_2}{2}\,, \\
+    p & \equiv \max(0, l_2 - l_1 - m)\,, \\
+    q & \equiv \min(l_1 + l_2 - m, j - m, l_2 - m_2)\,.
 \end{aligned}

### 2015-03-11 draft.tex
Update: rearrange plots, rewrite text on fit vs. mom estimators

@@
 
+\begin{figure}[b]
+        \centering
+            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S5_200.png}
+            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
+        \caption{Pull distribution for the angular observables $S_5$ (upper) and $S_7$ (lower), extracted from $2\cdot 10^5$ studies of
+        $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a Gaussian distribution.}
+        \label{fig:pulls}
+\end{figure}
+
 Our findings can be summarized as follows:
@@
         with $200$ events per study in \reffig{pulls}.
+
     \item We study the MC estimate for the absolute uncertainty $\est{\sigma_i(N)}$ with respect to the angular observable $S_i$
@@
         estimators \cite[sec. 8]{Cowan:1998ji}.
-%    \item For all toy studies, we produce plots of their skewness and their kurtosis as functions of
-%        $N$. We find in all cases that the mean skewness and kurtosis converge towards zero.
-%        \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of the number of simulated events $N$.}
+
+    \item We also compare the results as obtained by the method of moments with
+        results obtained by a conventional likelihood fit. In particular, we
+        study the correlation between the method-of-moment estimators and the
+        maximum-likelihood-fit estimators. We run $10^3$ toy analyses, with
+        $200$ simulated events per analysis. We show the joint distribution of
+        the two estimators in \reffig{correlation}. The two estimators are
+        highly correlated. The distribution of the difference of the estimators
+        exhibits now bias, which is due to the large number of simulated
+        events.  Still, we find that statistical uncertainty on the difference
+        of the two estimators is sizeable and can easily become half as large
+        as the statistical uncertainty of either estimator.
 \end{itemize}
-\begin{figure}[b]
+\begin{figure}[t]
         \centering
-            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S5_200.png}
-            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
-        \caption{Pull distribution for the angular observables $S_5$ (left) and $S_7$ (right), extracted from $2\cdot 10^5$ studies of
-        $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a Gaussian distribution.}
-        \label{fig:pulls}
+            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S4.png}
+            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S8.png}
+        \caption{Uncertainty of the angular observables $S_4$ (uppwe) and $S_8$
+            (lower), extracted from $2\cdot 10^5$ studies of simulated events
+            for the decay $B\to K^*\ell^+\ell^-$. We show the uncertainty as a
+            function of the number of simulated events $N$.  The red curve
+        represents a fit to the function given in \refeq{unc-on-mean}.}
+        \label{fig:errors}
+\end{figure}
+
+\begin{figure}[t]
+        \centering
+            \includegraphics[width=0.45\textwidth]{figs/S3_scat.pdf}
+            \includegraphics[width=0.45\textwidth]{figs/S5_scat.pdf}
+            \caption{The joint distribution of the two estimators
+                $\est{S}_i^\text{MoM}$ and $\est{S}_i^\text{Fit}$ that arise
+                from the method of moments and a maximum-likelihood fit,
+                respectively. We show the estimators for both of our benchmark
+                observables $S_3$ (upper) and $S_5$ (lower).
+                \danny{Marcin: please replace by $S_5$ (upper) and $S_7$ (lower).}
+            }
+        \label{fig:correlation}
 \end{figure}
@@
 and reside therefore outside the scope of this work.
-
-\begin{figure}[t]
-        \centering
-            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S4.png}
-            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S8.png}
-        \caption{Uncertainty of the angular observables $S_4$ (left) and $S_8$ (right), extracted from $2\cdot 10^5$ studies of
-        simulated events for the decay $B\to K^*\ell^+\ell^-$. We show the uncertainty as a function of the number of simulated events $N$.
-        The red curve represents a fit to the function given in \refeq{unc-on-mean}.}
-        \label{fig:errors}
-\end{figure}
-
-We also studied the correlation of the estimators from Method of Moments to a maximum likelihood fit.
-We performed a toy study by simulating $10^3$ toys of 200 events.
-We then use for each toy method described in~\refsec{systematics:partial-waves} and a standard maximum likelihood method.
-In \reffig{correlation} the two estimators distributions are showed.
-In conclusion the two estimators are highly correlated but different between then can be of the order of statistic uncertainty of the maximum likelihood estimator.
-We found that in some observables this can reach almost half of the statistical error.
-
-\begin{figure}[t]
-        \centering
-            \includegraphics[width=0.45\textwidth]{figs/S3_scat.pdf}
-            \includegraphics[width=0.45\textwidth]{figs/S5_scat.pdf}
-        \caption{Correlation between Method of Moments and maximum likelihood estimators for observables $S_3$ and $S_5$. }
-        \label{fig:correlation}
-\end{figure}
 

### 2015-03-12 draft.tex
added more figures

@@
         events, and can require reparametrizations and/or approximations
-        for a successful fit to the signal PDF. \add{As an example,
-        see the LHCb analysis of \dots}.
+        for a successful fit to the signal PDF.
+As an example see LHCb measurement of $\bar{B}\to \bar{K}^*(\to \bar{K}\pi)\mu^+\mu^-$\cite{Aaij:2013qta}.
 The method of moments does not require reparametrizations or approximations.
 
-    \item \add{Likelihood fits  can be unstable in case the underlying
+    \item Likelihood fits  can be unstable in case the underlying
         physical model is only partially known. This can lead to
@@
         was found and applied, thereby reducing the number of fit parameters.
-    }
     \item Mismodeling the underlying physics model can result in systematic bias
@@
 \end{equation}
-where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular functions
-\add{, and $\Omega$ represents the entire angular phase space.}. In general, $\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$. This is the
+where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular functions, and $\Omega$ represents the entire angular phase space.
+In general, $\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$.
+This is the
 case for our selection of applications in appendices \ref{app:btokll} through \ref{app:btokstarll}.\\
@@
         \centering
-            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S4.png}
-            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S8.png}
-        \caption{Uncertainty of the angular observables $S_4$ (uppwe) and $S_8$
+            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S5.pdf}
+            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S9.pdf}
+        \caption{Uncertainty of the angular observables $S_5$ (upper) and $S_9$
             (lower), extracted from $2\cdot 10^5$ studies of simulated events
@@
             function of the number of simulated events $N$.  The red curve
-        represents a fit to the function given in \refeq{unc-on-mean}.}
+        represents a fit to the function given in \refeq{unc-on-mean}. Errors correspond to $68~\%$ spread of measured uncertainties in the toys.}
         \label{fig:errors}
@@
         \centering
-            \includegraphics[width=0.45\textwidth]{figs/S3_scat.pdf}
             \includegraphics[width=0.45\textwidth]{figs/S5_scat.pdf}
+            \includegraphics[width=0.45\textwidth]{figs/S7_scat.pdf}
             \caption{The joint distribution of the two estimators

### 2015-03-12 draft.tex
Update with Fred

@@
     \item Likelihood fits have convergence problems for a small number of
-        events, and can require reparametrizations and/or approximations
-        for a successful fit to the signal PDF.
-As an example see LHCb measurement of $\bar{B}\to \bar{K}^*(\to \bar{K}\pi)\mu^+\mu^-$\cite{Aaij:2013qta}.
-The method of moments does not require reparametrizations or approximations.
+        events, and can require reparametrizations and/or approximations for a
+        successful fit to the signal PDF. As an example, see the LHCb
+        analysis of the angular distribution in $\bar{B}\to
+        \bar{K}^*\ell^+\ell^-$ decays \cite{Aaij:2013qta}.
+
+        The method of
+        moments does not require any such reparametrizations or approximations.
 
@@
         was found and applied, thereby reducing the number of fit parameters.
+
+        In contrast, we will show that the method of moments does not require
+        information on the correlations between model parameters as an input.
+        Instead, it yields the correlations as an output, at the expense of
+        somewhat larger uncertainties.
+
     \item Mismodeling the underlying physics model can result in systematic bias
-        in likelihood fits. We will
+        in likelihood fits.
+
+        We will
         show that the method of moments is insensitive to a certain type of mismodeling;
@@
 \end{enumerate}
-
-\fred{For us, the major advantage is that the experiment can obtain all angular observables at once, and if there are more, one doesn't need more data.
-I'm not sure this becomes clear from the text, point 1.}\marcin{I think it is ok}
 
@@
 the angular observables $\lbrace S_i\rbrace$; thus ratios or similar suitable combinations
-of the angular observables are not affected by \add{a} change of normalization.\\
+of the angular observables are not affected by a change of normalization.\\
 
@@
 system of angular functions $\{f_i(\thvec)\}$ \emph{can} be transformed into
-an orthonormal basis. \add{We find it convenient to work
-in the basis of Legendre polynomials, which is not self-dual.
-However, the statistical properties of the method of moments are equivalent for both self-dual and non-self-dual
-bases, provided that one replace $f_i \to \dual{f}_i$ appropriately.}
-\fred{I'm confused. What are the two approaches? Do we consider Legendre polynomials as an orthonormal basis or not?}
+an orthonormal basis. We find it convenient to work
+in the basis of Legendre polynomials that are not self-dual.
+Our approach covers the self-dual case, provided that one
+replace $\dual{f}_i \to f_i$ appropriately.
 Using the ansatz
@@
 \end{equation}
-where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular functions, and $\Omega$ represents the entire angular phase space.
-In general, $\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$.
-This is the
-case for our selection of applications in appendices \ref{app:btokll} through \ref{app:btokstarll}.\\
+where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular
+functions, and $\Omega$ represents the entire angular phase space. In general,
+$\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$. This is the
+case for our selection of applications in appendices \ref{app:btokll} through
+\ref{app:btokstarll}.\\
 
@@
 \end{equation}
-\fred{Why is there $\Omega$ but nothing for $\nuvec$?}
-\danny{a) intoduced $\Omega$ one equation earlier, b) we always need
-and integration of the \emph{entire} angular phase space; the integration
-over the non-angular phase space is irrelevant to the discussion.}
 The remainder of this section describes the method of moments, in
@@
   over likelihood fits just because the former reduces
-  the bias~\cite[sections 13.8,17.2]{jaynes:2003} \marcin{we said we cahnge this but after reading it again I like it and would not change}. In fact, for
+  the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
   the results discussed below in \refsec{numerics}, the likelihood
-  fits --- if they converge --- produce uncertainties (10--15)\%
-      smaller than those from the method of moments.
+  fits --- if they converge --- exhibit a negligible bias and
+  produce uncertainties $10\%$--$30\%$ smaller than those from the method of moments.
+
 \item The approximate multivariate Gaussian distribution of $\vecest{S}$
@@
 
-  For a likelihood fit, the constraint needs to be part of the
-  analysis performed by the experimental collaboration, and the
-  resulting likelihood as a function of $\vec{S}$ is distinctly not
-  Gaussian.  Communicating such a result has
-  proved to be challenging due to technical reasons (such as data formats,
-  size etc.) %\add{as well as political reasons; i.e., the publication of
- % the likelihood also publishes collaboration-internal data.}
-  This leads to the
-  undesirable situation that only the mode and standard errors
-  are reported, and theorists often include the results as independent
-  measurements with a Gaussian distribution and disregard the boundary
-  problem as well as correlations altogether.
-
+  For a likelihood fit, the constraint needs to be part of the analysis
+  performed by the experimental collaboration, and the resulting likelihood as
+  a function of $\vec{S}$ may be distinctly not Gaussian.  Communicating such a
+  result has proved to be challenging due to technical reasons (such as data
+  formats, size etc.) This leads to the undesirable situation that only the
+  mode and standard errors are reported, and theorists often include the
+  results as independent measurements with a Gaussian distribution and
+  disregard the boundary problem as well as correlations altogether.
 \end{enumerate}
@@
 
-For the selected class of decays, we can describe that problem as follows: The PDF $P$ has a fixed dependence on the dilepton
-helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokstarll} for details
-on the angular distribution.) However, at the level of decay amplitudes the dimeson system can have an arbitrarily
-large total angular momentum $j$; only its third component is restricted to $j_z = -1,0,+1$.
-It is then \add{convenient}\del{usual} to compute the angular distribution explicitly in terms of $\theta_1$ and $\theta_3$, but leave
-the angular observables dependent on the remaining helicity angle $\theta_2$.
-We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{l}^{(|m|)}$
-with respect to the remaining angle $\theta_2$. \add{Here, the angular-momentum indices $l$ and $m$ follows from the usual
-rules for addition of the angular momenta $j$ and $\tilde{j}$ of the partial wave expansion of the underlying
-amplitude and its complex conjugate: $j - \tilde{j} \leq l \leq j + \tilde{j}$, and $m = j_z + \tilde{j}_z$.}
+For the selected class of decays, we can describe that problem as follows: The
+PDF $P$ has a fixed dependence on the dilepton helicity angle $\theta_1$ and
+the azimuthal angle $\theta_3$. (See also \refapp{btokstarll} for details on
+the angular distribution.) However, at the level of decay amplitudes the
+dimeson system can have an arbitrarily large total angular momentum $j$; only
+its third component is restricted to $j_z = -1,0,+1$.  It is then convenient to
+compute the angular distribution explicitly in terms of $\theta_1$ and
+$\theta_3$, but leave the angular observables dependent on the remaining
+helicity angle $\theta_2$ of the dimeson:
+\begin{multline}
+    P(\cos\theta_1,\cos\theta_2,\theta_3)\\
+        \equiv \sum_k S_k(\nuvec,\cos\theta_2) f_k(\cos\theta_1,\theta_3)\,.
+\end{multline}
+We advocate here that is a sensible procedure to
+perform an expansion in terms of Legendre polynomials $p_{l}^{(|m|)}$ with
+respect to the remaining angle $\theta_2$. Here, the angular-momentum indices
+$l$ and $m$ follow from the usual rules for addition of the angular momenta $j$
+and $\tilde{j}$ of the partial-wave expansion of the underlying amplitude and
+its complex conjugate: $j - \tilde{j} \leq l \leq j + \tilde{j}$, and $m = j_z
++ \tilde{j}_z$.
 
@@
 \begin{equation}
-    S_k(\vec{\nu}) \equiv \frac{I_k(\nuvec)}{4\pi \Gamma)}\,,\quad\text{with}\quad \Gamma = I_1(\nuvec) - \frac{I_2(\nuvec)}{3}\,,
-\end{equation}
-\fred{It not clever to use $k$ as an index and momentum variable}
-\danny{I disagree. We use the same notation as in the literature, and people
-should be able to distinguish these based on context.} \marcin{I am fine with k}
+    S_k(\vec{\nu}) \equiv \frac{I_k(\nuvec)}{4\pi \Gamma}\,,\quad\text{with}\quad \Gamma = I_1(\nuvec) - \frac{I_2(\nuvec)}{3}\,,
+\end{equation}
 which reads
@@
     S_{k}(\vec{\nu},\cos\theta_2) \\
-        \equiv \sum_{j} \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\sin\theta_2\,.
+        \equiv \sum_{l=0}^\infty \frac{1}{n_{l,|m|}} S_{k,l}(\vec{\nu}) p_{l}^{(|m|)}(\cos\theta_2)\,.
 \end{multline}
@@
     |m| = \begin{cases}
-        0\,, & k = 1,2,6\,,\\
-        1\,, & k = 4,5,7,8\,,\\
+        0\,, & k = 1,2,6\\
+        1\,, & k = 4,5,7,8\\
         2\,, & k = 3,9
@@
 
-The angular observables $S_{k,l}$ -- as defined in \refeq{expansion} --
-have the merit of a well defined total angular momentum, and thus are physically discriminable.
-As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
-partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. That is to say,
-ignoring further (orthogonal) terms in the PDF cannot affect $\vecest{S}$ nor its variance.\\
-\fred{That's not true. $\vecest{S}$ is enlarged with more angular observables. But the first components are unaffected.}\\
-
-Unfortunately, this benefit on the experimental side is accompanied with a theoretical draw back. Each observable
-$S_{k,j}(\vec{\nu})$ consists of an infinite sum of bilinears of partial-wave amplitudes. It remains for theoretical
-analyses to estimate or calculate the impact of partial waves beyond the S and P wave contributions.
-(For $B\to K\pi\ell^+\ell^-$ a first study has been carried out where contributions up to the D wave are investigated \cite{Das:2014sra}).\\
-
-We wish to emphasize that detector acceptance effects systematically affect the expansion for any basis
-of angular functions, including the one suggested in this section.
-Nevertheless, the expansion in terms of Legendre polynomials as suggested above provides means to cope with these effects,
-as we discuss in the following subsection.
+The angular observables $S_{k,l}$ -- as defined in \refeq{expansion} -- have
+the merit of a well defined total angular momentum, and thus are physically
+distinguishable.  As a consequence of the orthogonality of the Legendre
+polynomials, any mismodeling (or rather, lack of modelling) of higher
+partial-wave observables \emph{does not affect} the method of moments as
+discussed in the previous section. That is to say, adding further (orthogonal) terms
+to the PDF only appends observables to $\vec{S}$, but does not change the leading
+elements. The same applies to the covariance.\\
+
+Unfortunately, this benefit on the experimental side is accompanied with a
+theoretical draw back. Each observable $S_{k,j}(\vec{\nu})$ consists of an
+infinite sum of bilinears of partial-wave amplitudes. It remains for
+theoretical analyses to estimate or calculate the impact of partial waves
+beyond the S and P wave contributions.  (For $B\to K\pi\ell^+\ell^-$ a first
+study has been carried out where contributions up to the D wave are
+investigated \cite{Das:2014sra}).\\
+
+We wish to emphasize that detector acceptance effects systematically affect the
+expansion for any basis of angular functions, including the one suggested in
+this section.  Nevertheless, the expansion in terms of Legendre polynomials as
+suggested above provides means to cope with these effects, as we discuss in the
+following subsection.
 
@@
 \end{equation}
-\fred{In this section, all integration symbols are at the end, in ch. 2 they were right after the $\int$ sign.}
 Here $P_\text{t}$ is the probability distribution of the true events,
@@
 define the PDF in terms of the Legendre polymials (i.e., $f_k(x)
-\equiv P_k(x)$) and angular observables $\vec{S}$ as
+\equiv p_k(x)$) and angular observables $\vec{S}$ as
 \begin{equation}
@@
 \end{equation}
-We call the matrix \add{$M^{-1}$} the \emph{unfolding matrix},
-\fred{actually that's the folding matrix}
-\danny{switched to $M^{-1}$ instead. OK?}
+We call the matrix $M^{-1}$ the \emph{unfolding matrix},
 which is specific to the decay at hand.
@@
 
-\add{Apparently we now face a circular dependence. On the one hand,
+Apparently we now face a circular dependence. On the one hand,
 the estimators $\vecest{Q}$ and thus also $\vecest{S}$
@@
 on $P_\text{t}(x_t)$, and thus on the true value of the angular observables $\vec{S}$.
-We solve this problem by observing that the MC estimators $\vecest{S}$ need to fulfill
+This dependence is broken by the fact that the MC estimators $\vecest{S}$ need to fulfill
 the self-consistency condition
@@
 carry out a combined analysis for the determination of the branching ratio
-and the extraction of the angular observables \fred{Marchin, Nicola: Do you do a combined analysis for Moriond?}.\\
+and the extraction of the angular observables
 Moreover, in the applications to $B$ decays only ratios and similar $R$-independent combinations
 of the angular observables are of interest.
-}\\
-
-We note that $\vecest{S}$ as determined from \refeq{estS} does not fully correspond to $\vec{S}$
-for arbitrary $\eps$. Taking again the decay $B\to K\ell^+\ell^-$
-as an example, \add{there are exactly three physical angular observables:} $\dim S = 3$.
-Assuming an expansion of the detector acceptance $\eps$
-in terms of Legendre polynomial up to a given order $L$, we have to calculate the raw moments up
-to $\dim \est{Q} = \dim \est{S} = \dim S + L$. The MC estimators of the corrected angular observables
+\\
+
+We note that $\vecest{S}$ as determined from \refeq{estS} does not fully
+correspond to $\vec{S}$ for arbitrary detector acceptance $\eps$.
+Assuming an expansion of $\eps$ in terms of Le\-gendre polynomials up to a given
+order $L$, we have to calculate the raw moments up to $\dim \est{Q} = \dim
+\est{S} = \dim S + L$. The MC estimators of the corrected angular observables
 then take the following structure:
 \begin{equation}
-    \vecest{S} = ( \underbrace{\est{S}_0, \dots, \est{S}_{\dim S}}_\text{physical}, \underbrace{\est{S}_{\dim S + 1}, \dots, \est{S}_{\dim Q}}_\text{``superfluous''})\,.
-\end{equation}
-\fred{Danny: Is $\est{S}_0$ physical? I guess not. So it should be
-\begin{equation}
-    \vecest{S} = ( \est{S}_0, \underbrace{\est{S}_1, \dots, \est{S}_{\dim S}}_\text{physical}, \underbrace{\est{S}_{\dim S + 1}, \dots, \est{S}_{\dim Q}}_\text{``superfluous''})\,.
-\end{equation}
-but then $\dim S$ is not right.
-}
-\danny{Fred: We simplfy define the label ``physical'' right here, which includes
-$S_0$. Although perhaps a better label would be ``nominal''?}
-The method is consistent as long as the MC estimators for the ``superfluous'' observables with indices $\dim S + 1$ to $\dim Q$
-are compatible with zero. \footnote{This holds only for the physical model of uniangular decay distributions. If the physical
-    model involves a partial-wave expansion with cutoff, these superfluous observables
-correspond to higher partial waves that have been suppressed in the physical model; see \refapp{btokstarll} for such a case.}
-Since $L$ depends on the setup of the particle detector under consideration, it remains for
-the experimental collaborations to determine the maximum order of such an expansion.
-\add{We suggest to carry out a dedicated study to determine a suitable choice for $L$.
-Since such a work requires in-depth understanding of the detector simulation, it remains
-beyond the scope of our possibilities.}\\
-
-The accuracy of the unfolding process as outlined above critically depends on both the accuracy
-of the detector simulation, as well as the uncertainties induced by the MC estimates.
-For an experimental analysis, one would now turn to the determination of the distribution of $\vecest{S}$
-as a function of the detector setup. This would involve the determination of both $M$ and $\vecest{Q}$ for a number of
-detector configurations, and subsequent profiling or marginalization.
-While such considerations of any detector simulation are beyond the scope of this work, we can, however,
-comment on the MC-induced uncertainties. As usual, one needs to find a balance between
-compute time and accuracy. For a uniangular distribution and a total of $6\cdot 10^6$ MC
-samples \fred{Before or after thinning?}\danny{No thinning at all!} (i.e., $2 \cdot 10^6$ MC samples per row of $M_{ij}$), we find that the error on the mean
-of each matrix element is smaller than $6\cdot 10^{-4}$. \add{This suggests, that the so-induced
-systematic error can be driven below any statistical uncertainty.}
-
-Let us conclude this section by commenting that parts of the unfolding
-matrix are universal in a sense. Specifically, they can be reused in analyses with a similar underlying decay.
-Therefore, computing resources spent on improving \add{the accuracy of $\est{M}$} are not wasted.
+    \vecest{S} = ( \underbrace{\est{S}_0, \dots, \est{S}_{\dim S - 1}}_\text{physical}, \underbrace{\est{S}_{\dim S}, \dots, \est{S}_{\dim Q - 1}}_\text{``superfluous''})\,.
+\end{equation}
+The method is consistent as long as the MC estimators for the ``superfluous''
+observables are compatible with zero. \footnote{This holds only for the
+    physical model of uniangular decay distributions. If the physical model
+    involves a partial-wave expansion with cutoff, these superfluous
+    observables correspond to higher partial waves that have been suppressed in
+the physical model; see \refapp{btokstarll} for such a case.} The value $L$ depends
+on the setup of the particle detector under consideration, and remains to
+be determined just as in studies that carry out a likelihood fit.\\
+
+The accuracy of the unfolding process as outlined above critically depends on
+both the accuracy of the detector simulation, as well as the uncertainties
+induced by the MC estimates.  For an experimental analysis, one would now turn
+to the determination of the distribution of $\vecest{S}$ as a function of the
+detector setup. This would involve the determination of both $M$ and
+$\vecest{Q}$ for a number of detector configurations, and subsequent profiling
+or marginalization.  While such considerations of any detector simulation are
+beyond the scope of this work, we can, however, comment on the MC-induced
+uncertainties. As usual, one needs to find a balance between compute time and
+accuracy. For a uniangular distribution and $\order{10^6}$ MC samples, we find
+that the error on the mean of each matrix element is $\order{10^{-4}}$.
+This suggests that the so-induced systematic error can be driven below any
+statistical uncertainty.
+
+Let us conclude this section by commenting that parts of the unfolding matrix
+are universal in a sense: They can be reused in analyses with a
+similar underlying decay.  Therefore, computing resources spent on improving
+the accuracy of $\est{M}$ are not wasted.
 
@@
         We find that the the method of moments yields uncertainties on $\vec{S}$ that are roughly
-        $10\%$ -- $15\%$ larger than those obtained from maximum-likelihood fits and for the same
-        number of events \danny{[cite!]}. However, we wish to note that said fits only produce a limited
+        $10\%$ -- $30\%$ larger than those obtained from maximum-likelihood fits and for the same
+        number of events. However, we wish to note that said fits only produce a limited
         subset of the angular observables, and the statistical error of the fit is expected to increase
@@
             function of the number of simulated events $N$.  The red curve
-        represents a fit to the function given in \refeq{unc-on-mean}. Errors correspond to $68~\%$ spread of measured uncertainties in the toys.}
+        represents a fit to the function given in \refeq{unc-on-mean}.
+        Errors correspond to $68\%$ spread of measured uncertainties in the toys.}
         \label{fig:errors}
@@
                 respectively. We show the estimators for both of our benchmark
-                observables $S_3$ (upper) and $S_5$ (lower).
-                \danny{Marcin: please replace by $S_5$ (upper) and $S_7$ (lower).}
+                observables $S_5$ (upper) and $S_7$ (lower).
             }
@@
 
-\add{We emphasize that the above results have been obtained for a flat acceptance function.
-We also study the behaviour of the unfolded angular observables. However, due to limitations of computing
-resources, we have to limit our study to the decay $B\to K\ell^+\ell^-$, with its three angular observables
-$S_1$ to $S_3$. We express the acceptance function in terms of Legendre polynomial $P_k(x)$,
-\begin{equation}
-    \eps(\cos\theta) = \frac{7}{15} P_0(\cos\theta) - \frac{4}{15} P_2(\cos\theta)\,.
-\end{equation}
-This acceptance function approximates the one used in a recent study of the angular observables in $B\to K\ell^+\ell^-$
-decays \cite{Aaij:2014tfa}. We want to focus on effects of the unfolding process itself. We therefore
-use the analytic expression for the unfolding matrix, which we compute from the raw moments as
-defined in \refeq{analytic-raw-moments}. We simulate $4000$ toy analyses with up to $300$ simulated events each.
-We find that the previous two bullet points still hold; i.e., we do not find any bias, and the distribution
-is well described by a multivariate Gaussian distribution. The latter only holds as long as the number of events
-per experiment exceeds $\sim 20$.
-}
-
-All results of our toy studies, as summarised above, show consistently that the joint distribution of the angular
-observables converges rapidly towards a multivariate Gaussian distribution. We therefore propose to describe the
-resulting distribution as a multivariate Gauss when skewness and kurtosis fall below a given threshold.
-The precise target threshold for skewness and kurtosis are subject to the details of the underlying physical analysis,
-and reside therefore outside the scope of this work.
+We emphasize that the above results have been obtained for a flat acceptance
+function.  We also study the behavior of the unfolded angular observables.
+For simplicity we limit our study to the decay $B\to K\ell^+\ell^-$, with its
+three angular observables $S_0$ to $S_2$. We express the acceptance function
+in terms of Legendre polynomials $p_k(x)$,
+\begin{equation}
+    \eps(\cos\theta) = \frac{7}{15} p_0(\cos\theta) - \frac{4}{15} p_2(\cos\theta)\,.
+\end{equation}
+This acceptance function approximates the one used in a recent study of the
+angular observables in $B\to K\ell^+\ell^-$ decays \cite{Aaij:2014tfa}.
+Focusing on effects of the unfolding process itself, we use the analytical
+expression for the unfolding matrix, which we compute from the raw moments as
+defined in \refeq{analytic-raw-moments}. Simulting $4000$ toy analyses with
+up to $300$ simulated events each, we find that the previous bullet points
+still hold; i.e., we do not find any bias, and the distribution is well
+described by a multivariate Gaussian distribution. The latter only holds as
+long as the number of events per experiment exceeds $\sim 30$.\\
+
+All of our toy studies, as summarized above, show consistently that the
+joint distribution of the angular observables converges rapidly towards a
+multivariate Gaussian distribution. We therefore propose to publish the results
+in the form of the physical components of $\vecest{S}$ and $\est{\Sigma}$.
 
@@
 
-We have carried out a combined analytical and numerical study of the method of moments; a method for
-the extraction of angular observales from the angular distribution of a general multi-body process.
-We have studied the performance of the method of moments using pseudo data derived from the SM
-predctions for one uniangular decay ($B\to K\ell^+\ell^-$) and one triangular decay ($B\to K^*\ell^+\ell^-$).
-From this, we find rapid convergence of the joint likelihood of the angular observables towards a multivariate Gaussian.
-We draw the conclusion that this method exhibits several benefits in the determination of angular observables when
-compared with a maximum-likelihood fit.\\
-
-First, we find no bias in the determinations of the angular observables even for a small number of events.
-However, this comes at the expense of a slight increase of the order of $10\%$ for the statistical uncertainty
-on the mean.
-Second, in the absence of detector effects, a determination using the method of moments is correct and unbiased
-even when not all aspects of the physical distribution are modeled. This is explicitly shown for the case of
-higher partial waves in multibody final states.
-Third, we develop a systematic method for the dertermination of detector effects that lead to
-dilution and mixing of the angular observables. We present an algorithm to calculate the necessary
-unfolding matrix, which is only computationally feasible when using the method of moments.
-Fourth, the fact that the joint distribution of the angular observables that results from the method of moments
-is a multivariate Gaussian distribution allows for an easy and precise transfer of correlation
-information to subsequent theoretical analyses.
-Last but not least, the resulting distribution arises without the need for additional constraints
-in order to achieve convergence, such as e.g. in some maximum-likelihood fits. Therefore, results obtained
-using the method of moments can be directly averaged, without the need to remove
-the constraints a posteriori.\\
+We have carried out a combined analytical and numerical study of the method of
+moments; a method for the extraction of angular observables from the angular
+distribution of a general multi-body process.  We have studied the performance
+of the method of moments using pseudo data derived from the SM predictions for
+one uniangular decay ($B\to K\ell^+\ell^-$) and one triangular decay ($B\to
+K^*\ell^+\ell^-$).  From this, we find rapid convergence of the joint
+likelihood of the angular observables towards a multivariate Gaussian.  We draw
+the conclusion that this method exhibits several benefits in the determination
+of angular observables when compared with a maximum-likelihood fit.\\
+
+First, we find no bias in the determinations of the angular observables even
+for a small number of events.  However, due to fewer model assumptions, the
+uncertainty on the mean values increases by roughly $10\%$--$30\%$ compared
+to likelihood fits.\\
+Second, in the absence of detector effects, the method of
+moments does not rely on model assumptions for the partial-wave composition
+of the PDF. This is explicitly shown for the case of higher
+partial waves in multibody final states.\\
+Third, we develop a systematic method
+for the determination of detector effects that lead to dilution and mixing of
+the angular observables. We present an algorithm to calculate the necessary
+unfolding matrix, which is only computationally feasible when using the method
+of moments.\\
+Fourth, the fact that the joint distribution of the angular
+observables that results from the method of moments is a multivariate Gaussian
+distribution allows for an easy and precise transfer of correlation information
+to subsequent theoretical analyses.\\
+Last but not least, the resulting
+distribution arises without the need for additional constraints in order to
+achieve convergence, such as e.g. in some maximum-likelihood fits. Therefore,
+results obtained using the method of moments can be directly averaged, without
+the need to remove the constraints a posteriori.\\
 
@@
 
-To conclude this section, we remind that the angular momentum $l_2$, associated with the angle $\theta$, is not bounded from above.
+To conclude this section, we remind that the angular momentum $l_2$, associated with the angle $\theta_2$, is not bounded from above.
 This has to be considered if partial waves beyond the P-wave are included in the analysis, see e.g. \cite{Das:2014sra}.
@@
 
-\add{For convenience, we use this appendix to collect there necessary
-formulae needed in the partial-wave expansion.}
+For convenience, we use this appendix to collect there necessary
+formulae needed in the partial-wave expansion.
 Let us assume that the angular decomposition has been achieved for
@@
 
-We \add{decompose}\del{propose the decomposition of} $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$,
+We decompose $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$,
 with total angular momentum $j$ and its third component $m=m_1 + m_2$.
@@
 the sum in \refeq{def-partial-wave-observable} goes to infinitely high angular momenta $l_1$ and $l_2$. As a consequence
-of this and of \refeq{angular-momentum-addition}, the angular observables $P_{j,m}$
+of this and of \refeq{angular-momentum-addition}, the angular observables $S_{j,m}$
 consist of sums with infinitely many terms. It is then up to theoretical analyses to

### 2015-03-12 draft.tex
made nice pull plots
fuckll
tiny typo fix
tiny typo fix 2
proof read up to summary

--- 2015-03-12 draft.tex
@@
         \centering
-            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S5_200.png}
-            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
+            \includegraphics[width=0.45\textwidth]{figs/Q2_5_6_S5_200.pdf}
+            \includegraphics[width=0.45\textwidth]{figs/Q2_5_6_S9_200.pdf}
         \caption{Pull distribution for the angular observables $S_5$ (upper) and $S_7$ (lower), extracted from $2\cdot 10^5$ studies of
@@
             \includegraphics[width=0.45\textwidth]{figs/S5_scat.pdf}
-            \includegraphics[width=0.45\textwidth]{figs/S7_scat.pdf}
+            \includegraphics[width=0.45\textwidth]{figs/S9_scat.pdf}
             \caption{The joint distribution of the two estimators
@@
                 observables $S_3$ (upper) and $S_5$ (lower).
-                \danny{Marcin: please replace by $S_5$ (upper) and $S_7$ (lower).}
             }
@@
 
-We have carried out a combined analytical and numerical study of the method of moments; a method for
-the extraction of angular observales from the angular distribution of a general multi-body process.
-We have studied the performance of the method of moments using pseudo data derived from the SM
-predctions for one uniangular decay ($B\to K\ell^+\ell^-$) and one triangular decay ($B\to K^*\ell^+\ell^-$).
-From this, we find rapid convergence of the joint likelihood of the angular observables towards a multivariate Gaussian.
-We draw the conclusion that this method exhibits several benefits in the determination of angular observables when
-compared with a maximum-likelihood fit.\\
-
-First, we find no bias in the determinations of the angular observables even for a small number of events.
-However, this comes at the expense of a slight increase of the order of $10\%$ for the statistical uncertainty
-on the mean.
-Second, in the absence of detector effects, a determination using the method of moments is correct and unbiased
-even when not all aspects of the physical distribution are modeled. This is explicitly shown for the case of
-higher partial waves in multibody final states.
-Third, we develop a systematic method for the dertermination of detector effects that lead to
-dilution and mixing of the angular observables. We present an algorithm to calculate the necessary
-unfolding matrix, which is only computationally feasible when using the method of moments.
-Fourth, the fact that the joint distribution of the angular observables that results from the method of moments
-is a multivariate Gaussian distribution allows for an easy and precise transfer of correlation
-information to subsequent theoretical analyses.
-Last but not least, the resulting distribution arises without the need for additional constraints
-in order to achieve convergence, such as e.g. in some maximum-likelihood fits. Therefore, results obtained
-using the method of moments can be directly averaged, without the need to remove
-the constraints a posteriori.\\
-
-In conclusion, we argue that the method of moments is a competetive alternative to
-maximum-likelihood fits as long as angular distributions are involved. We wish to raise
+We have carried out a combined analytical and numerical study of the method of
+moments; a method for the extraction of angular observables from the angular
+distribution of a general multi-body process.  We have studied the performance
+of the method of moments using pseudo data derived from the SM predictions for
+one uniangular decay ($B\to K\ell^+\ell^-$) and one triangular decay ($B\to
+K^*\ell^+\ell^-$).  From this, we find rapid convergence of the joint
+likelihood of the angular observables towards a multivariate Gaussian.  We draw
+the conclusion that this method exhibits several benefits in the determination
+of angular observables when compared with a maximum-likelihood fit.\\
+
+First, we find no bias in the determinations of the angular
+observables even for a small number of events.  However, due to fewer
+model assumptions, the uncertainty on the mean values increases by
+roughly $10\%$--$30\%$ compared
+to likelihood fits.\\
+Second, in the absence of detector effects, the method of moments does
+not rely on model assumptions for the partial-wave composition of the
+PDF. This is explicitly shown for the case of higher
+partial waves in multibody final states.\\
+Third, we develop a systematic method for the determination of
+detector effects that lead to dilution and mixing of the angular
+observables. We present an algorithm to calculate the necessary
+unfolding matrix, which is computationally feasible only when using
+the method
+of moments. The algorithm also accounts for higher partial waves.\\
+Fourth, the joint distribution of the angular observables resulting
+from the method of moments is well approximated by a multivariate
+Gaussian distribution even for small number of events $N \sim 30$ both
+for the ideal uniform acceptance and a realistic example.  This
+facilitates the precise transfer of correlation information
+to subsequent theoretical analyses.\\
+Last but not least, the resulting distribution arises without the need
+for additional model constraints. Thus more observables can be
+inferred from the same data than in a likelihood fit. In addition,
+the results from the method of moments can be more easily averaged or combined; e.g., in global fits.\\
+
+In conclusion, we argue that the method of moments is a competitive alternative to
+maximum-likelihood fits if angular distributions are involved. We wish to raise
 the interesting prospect of extending this method to applications that feature

### 2015-03-12 draft.tex
polish abstract

@@
 \begin{abstract}
-  Our goal is to obtain a complete set of angular observables
-  arising in a generic multi-body process without the need to carry
-  out a likelihood fit of the angular distribution to the measured
-  events. Instead, we apply the method of moments that relies
-  both on the orthogonality of angular functions and the estimation of
-  integrals by Monte Carlo techniques. The main advantage of
-  this method is that the joint distribution of all observables
-  given the data can be easily extracted, even for very few
-  events. Our main contribution is to show explicitly how systematic
-  uncertainties from detector-resolution and acceptance effects can
-  be incorporated into a general algorithm. Finally, we present the
-  necessary process-dependent formulae needed for direct
-  implementation of the method for several rare decays of
-  interest.
+  Our goal is to obtain a complete set of angular observables arising
+  in a generic multi-body process. We show how this can be achieved
+  without the need to carry out a likelihood fit of the angular
+  distribution to the measured events. Instead, we apply the method of
+  moments that relies both on the orthogonality of angular functions
+  and the estimation of integrals by Monte Carlo techniques. The big
+  advantage of this method is that the joint distribution of \emph{all}
+  observables can be easily extracted, even for very few events. The
+  method of moments is shown to be robust against mismodeling of the
+  angular distribution. Our main result is an explicit algorithm that
+  accounts for systematic uncertainties from detector-resolution and
+  acceptance effects. Finally, we present the necessary
+  process-dependent formulae needed for direct application of the
+  method to several rare decays of interest.
 \end{abstract}

### 2015-03-12 draft.tex
S7 plots
Revert "tiny typo fix" and fix uncertainty caption
This reverts commit 4c2db4ca257b711117ee93f473933fc1f61c92a0.

Conflicts:
	draft.tex

--- 2015-03-12 draft.tex
@@
         analysis of the angular distribution in $\bar{B}\to
-        \bar{K}^*\ell^+\ell^-$ decays \cite{Aaij:2013qta}.
+        \bar{K}^*\mu^+\mu^-$ decays \cite{Aaij:2013qta}.
 
@@
         \centering
-            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S5_200.png}
-            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
+            \includegraphics[width=0.45\textwidth]{figs/Q2_5_6_S5_200.pdf}
+            \includegraphics[width=0.45\textwidth]{figs/Q2_5_6_S7_200.pdf}
         \caption{Pull distribution for the angular observables $S_5$ (upper) and $S_7$ (lower), extracted from $2\cdot 10^5$ studies of
@@
             \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S5.pdf}
-            \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S9.pdf}
-        \caption{Uncertainty of the angular observables $S_5$ (upper) and $S_9$
-            (lower), extracted from $2\cdot 10^5$ studies of simulated events
-            for the decay $B\to K^*\ell^+\ell^-$. We show the uncertainty as a
-            function of the number of simulated events $N$.  The red curve
-        represents a fit to the function given in \refeq{unc-on-mean}.
-        Errors correspond to $68\%$ spread of measured uncertainties in the toys.}
+            % \includegraphics[width=0.45\textwidth]{figs/Q2_1_2_S7.pdf}
+            \caption{Uncertainty $\est{\sigma}_5$ of the angular
+              observable $S_5$ extracted from $2\cdot 10^5$ studies of
+              simulated events for the decay $B\to
+              K^*\ell^+\ell^-$. We show the uncertainty as a function
+              of the number of simulated events $N$.  The red curve
+              represents a fit to the function given in
+              \refeq{unc-on-mean}. The error bars correspond to the
+              $68\%$ spread of measured uncertainties in the toys. The
+              plot for $\est{\sigma}_7$ is visually indistinguishable
+              from the one shown here.}
         \label{fig:errors}
@@
 
-First, we find no bias in the determinations of the angular observables even
-for a small number of events.  However, due to fewer model assumptions, the
-uncertainty on the mean values increases by roughly $10\%$--$30\%$ compared
+First, we find no bias in the determinations of the angular
+observables even for a small number of events.  However, due to fewer
+model assumptions, the uncertainty on the mean values increases by
+roughly $10\%$--$30\%$ compared
 to likelihood fits.\\
-Second, in the absence of detector effects, the method of
-moments does not rely on model assumptions for the partial-wave composition
-of the PDF. This is explicitly shown for the case of higher
+Second, in the absence of detector effects, the method of moments does
+not rely on model assumptions for the partial-wave composition of the
+PDF. This is explicitly shown for the case of higher
 partial waves in multibody final states.\\
-Third, we develop a systematic method
-for the determination of detector effects that lead to dilution and mixing of
-the angular observables. We present an algorithm to calculate the necessary
-unfolding matrix, which is only computationally feasible when using the method
-of moments.\\
-Fourth, the fact that the joint distribution of the angular
-observables that results from the method of moments is a multivariate Gaussian
-distribution allows for an easy and precise transfer of correlation information
+Third, we develop a systematic method for the determination of
+detector effects that lead to dilution and mixing of the angular
+observables. We present an algorithm to calculate the necessary
+unfolding matrix, which is computationally feasible only when using
+the method
+of moments. The algorithm also accounts for higher partial waves.\\
+Fourth, the joint distribution of the angular observables resulting
+from the method of moments is well approximated by a multivariate
+Gaussian distribution even for small number of events $N \sim 30$ both
+for the ideal uniform acceptance and a realistic example.  This
+facilitates the precise transfer of correlation information
 to subsequent theoretical analyses.\\
-Last but not least, the resulting
-distribution arises without the need for additional constraints in order to
-achieve convergence, such as e.g. in some maximum-likelihood fits. Therefore,
-results obtained using the method of moments can be directly averaged, without
-the need to remove the constraints a posteriori.\\
-
-In conclusion, we argue that the method of moments is a competetive alternative to
-maximum-likelihood fits as long as angular distributions are involved. We wish to raise
+Last but not least, the resulting distribution arises without the need
+for additional model constraints. Thus more observables can be
+inferred from the same data than in a likelihood fit. In addition,
+the results from the method of moments can be more easily averaged or combined; e.g., in global fits.\\
+
+In conclusion, we argue that the method of moments is a competitive alternative to
+maximum-likelihood fits if angular distributions are involved. We wish to raise
 the interesting prospect of extending this method to applications that feature

### 2015-03-12 draft.tex
Disable unnecessary macros, green -> normal

@@
 \DeclareMathOperator{\cov}{Cov}
-%\DeclareMathOperator{\skew}{Skew}
-\DeclareMathOperator{\kurt}{Kurt}
 
 %% Draft Macros %%
-\newcommand{\todo}[1]{{\color{red}\bf ToDo: #1}}
-\newcommand{\danny}[1]{{\color{purple}#1}}
-\newcommand{\fred}[1]{{\color{brown!85!black}#1}}
-\newcommand{\marcin}[1]{{\color{cyan}#1}}
-\newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}
-\newcommand{\add}[1]{\textcolor{green!85!black}{#1}}
-\newcommand{\del}[1]{\textcolor{red!85!black}{#1}}
+%\newcommand{\todo}[1]{{\color{red}\bf ToDo: #1}}
+%\newcommand{\danny}[1]{{\color{purple}#1}}
+%\newcommand{\fred}[1]{{\color{brown!85!black}#1}}
+%\newcommand{\marcin}[1]{{\color{cyan}#1}}
+%\newcommand{\citeneeded}{{\color{red}\bf [cite needed]}}
+%\newcommand{\add}[1]{\textcolor{green!85!black}{#1}}
+%\newcommand{\del}[1]{\textcolor{red!85!black}{#1}}
 
@@
 \item The approximate multivariate Gaussian distribution of $\vecest{S}$
-    allows easier and more \add{precise} transfer of the information in the
+    allows easier and more precise transfer of the information in the
   data to interested theorists for more accurate fits of

### 2015-03-12 draft.tex
Fixed references (journals, publishers, names, ...)

@@
   \cite{Faller:2013dwa} for application to the decay $B\to
-  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
+  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boer:2014kda} for observables
   in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
@@
 
-The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts --- reads \cite{Boeer:2014xx}
+The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts --- reads \cite{Boer:2014kda}
 \begin{equation}
@@
 The correspondence between out choice of angular observables in the angular momentum basis, and the angular
-observables as defined in reference \cite{Boeer:2014xx} reads
+observables as defined in reference \cite{Boer:2014kda} reads
 \begin{equation}

### 2015-03-13 draft.tex
Some tweaks to the two-column formatting in the appendix

@@
 
-\begin{widetext}
 The correspondence between out choice of angular observables in the angular momentum basis, and the angular
 observables as defined in reference \cite{Boer:2014kda} reads
+\begin{widetext}
 \begin{equation}
@@
 However, our choice of basis is well suited to these applications with $0 \leq l < \infty$. Note, that the
-physical range of $m$ is not affected by higher partial waves.
+physical range of $m$ is not affected by higher partial waves.\\
 

### 2015-03-19 draft.tex
acknowledge c2pap

@@
 
-We thank Ulrik Egede for insightful discussions and helpful comments on the
-manuscript. We are grateful to Gudrun Hiller, Martin Jung and Konstantinos Petridis for helpful discussions,
-as well as Claus Grupen for helpful advice in searching the literature.
-The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung (BMBF).
+We thank Ulrik Egede for insightful discussions and helpful comments
+on the manuscript. We are grateful to Gudrun Hiller, Martin Jung, and
+Konstantinos Petridis for helpful discussions, as well as Claus Grupen
+for helpful advice in searching the literature.  The work of D.v.D has
+been supported by the Bundesministerium f\"ur Bildung und Forschung
+(BMBF). F.B. is grateful for the support by the DFG Cluster of
+Excellence "Origin and Structure of the Universe". Part of the
+numerical simulations have been carried out on the computing
+facilities of the Computational Center for Particle and Astrophysics
+(C2PAP).
 

### 2015-05-07 draft.tex
added my second affiliation
added acknowlegment
[draft] Add references on old work
* update acknowledgment
* minor updates of formulae
* add questions for less minor changes

@@
 %\newcommand{\danny}[1]{{\color{purple}#1}}
-%\newcommand{\fred}[1]{{\color{brown!85!black}#1}}
+\newcommand{\fred}[1]{{\color{brown!85!black}#1}}
 %\newcommand{\marcin}[1]{{\color{cyan}#1}}
@@
 \email{mchrzasz@cern.ch}
+\affiliation{Physik-Institut, Universit\"at Z\"urich, Z\"urich, Switzerland \\ and \\ H.Niewodniczanski Institute of Nuclear Physics, Polish Academy of Sciences, Krakow, Poland}
 \author{Nicola Serra}
@@
 in the final state, we list the dual bases in a series of appendices
-\ref{app:btokll} through \ref{app:btokstarll}. Note that a
-similar analysis was done in~\cite{Dighe:1998vk} for the decays $B \to
-J/\psi \phi$ and $B \to J/\psi K^{*}$.
+\ref{app:btokll} through \ref{app:btokstarll}. Note that a similar
+analysis was done in~\cite{Dighe:1998vk} for the decays $B \to J/\psi
+\phi$ and $B \to J/\psi K^{*}$. In~\cite[section X]{Chung:1997qd}, the
+basic ideas and formulae were already given but the latter contained a
+number of typographical errors and the presentation was not easy to
+understand. Compared to~\cite{Chung:1997qd}, we fill the gaps needed
+to apply the method in practice and explain in detail its advantages
+and disadvantages on a sound statistical basis.
 
@@
 \end{equation}
-where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular
-functions, and $\Omega$ represents the entire angular phase space. In general,
-$\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$. This is the
-case for our selection of applications in appendices \ref{app:btokll} through
-\ref{app:btokstarll}.\\
-
 It is sensible to refer to the angular observable $S_i$ as the
@@
 implies $|S_k| \leq 1/2$ for $k > 0$. More stringent relations between the
-$S_k$ might hold, but are of no concern here. For later use, we define
+$S_k$ might hold but are of no concern here. For later use, we define
 \begin{equation}
@@
 \end{equation}
-which are instrumental to our recipe. Monte Carlo estimators of these moments can be constructed from specifically crafted detector events $x_\text{d}^{(n,m)}$, $n = 1, \dots, N_\text{d}^{(m)}$, where
+which are instrumental to our recipe.
+Monte Carlo estimators of these moments can be constructed from specifically crafted detector events $x_\text{d}^{(n,m)}$, $n = 1, \dots, N_\text{d}^{(m)}$ \fred{This should be $N_\text{t}^{(m)}$, right?}, where
 \begin{equation}
@@
 a detector simulation. The normalization $R^{(m)}$ is chosen such
-that $\int P_E^{(m)}(\xd) \rmdx{\xd} = 1$.  We emphasize that
+that $\int \rmdx{\xd} P_E^{(m)}(\xd)  = 1$.  We emphasize that
 $R^{(m)}$ can be estimated as $\est{R}^{(m)} = N_\text{d}^{(m)} /
 N_\text{t}$, where $N_\text{t}$ corresponds to the number of
-simulated true events.  The estimators then read
-\begin{equation}
-    \est{Q}_i^{(m)} \equiv \est{R}^{(m)} \frac{1}{N_\text{d}} \sum_n^{N_\text{d}} \tilde{f}_i(x_\text{d}^{(n,m)})
+simulated true events.
+\fred{We should clarify: generate $N_\text{t}^{(m)}$ events and $N_\text{d}^{(m)}$ pass the simulation.
+In principle, you could generate a different number of events $N_\text{t}^{(m)}$ for each $m$.
+} The estimators then read
+\begin{equation}
+    \est{Q}_i^{(m)} \equiv \est{R}^{(m)} \frac{1}{N_\text{d}^{(m)}} \sum_n^{N_\text{d}^{(m)}} \tilde{f}_i(x_\text{d}^{(n,m)})
 \end{equation}
@@
 be determined just as in studies that carry out a likelihood fit.\\
+
+\fred{There is a maximum order of acceptance expansion that could have
+  an influence. See \cite[below (118)]{Chung:1997qd}. I think it is
+  just a consequence of Gaun'ts triple product. This is good news as
+  it relieves the experiment to play around and there is less
+  arbirariness. I suppose that was Ulrik's question. The only
+  arbitrariness comes from cutting on higher partial waves in the
+  angular expansion, that's discussed in
+  \refsec{systematics:partial-waves}
+
+  We should talk about $E$ not $\eps$ alone. In principle we just
+  expand $P$ and $E$ in the polymials and we implicitly estimate the
+  ``angular observables'' of the $E$ expansion.}
 
@@
 Konstantinos Petridis for helpful discussions, as well as Claus Grupen
-for helpful advice in searching the literature.  The work of D.v.D has
-been supported by the Bundesministerium f\"ur Bildung und Forschung
-(BMBF). F.B. is grateful for the support by the DFG Cluster of
-Excellence "Origin and Structure of the Universe". Part of the
-numerical simulations have been carried out on the computing
-facilities of the Computational Center for Particle and Astrophysics
-(C2PAP).
+for helpful advice in searching the literature.  Tobias Schlüter made
+us aware of existing ideas on our method in~\cite{Chung:1997qd} and
+his thesis~\cite[page 123]{Schlueter:2012}. The work of D.v.D has been
+supported by the Bundesministerium f\"ur Bildung und Forschung
+(BMBF). M.C. has been supported by the ''Diamond Grant'' founded by
+the Polish Ministry of Higher Education. F.B. is grateful for the
+support by the DFG Cluster of Excellence "Origin and Structure of the
+Universe". Part of the numerical simulations have been carried out on
+the computing facilities of the Computational Center for Particle and
+Astrophysics (C2PAP).
 

### 2015-05-07 draft.tex
Unpushed changed that ended up in the PRD submission

@@
 \newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
-\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
+\newcommand{\refapp}[1]{appendix~\ref{app:#1}}
 \newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
-\newcommand{\reffig}[1]{fig.~(\ref{fig:#1})}
-\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
-\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
+\newcommand{\reffig}[1]{figure~\ref{fig:#1}}
+\newcommand{\refsec}[1]{section~\ref{sec:#1}}
+\newcommand{\reftab}[1]{table~\ref{tab:#1}}
 \newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
@@
 carry out a combined analysis for the determination of the branching ratio
-and the extraction of the angular observables
+and the extraction of the angular observables.
 Moreover, in the applications to $B$ decays only ratios and similar $R$-independent combinations
@@
 This suggests that the so-induced systematic error can be driven below any
-statistical uncertainty.
+statistical uncertainty.\\
+An alternative method to unfold detector effects is weighting the data on an
+event-by-event basis, with each weight corresponding to the inverse of the detection
+efficiency.\\
 
@@
 Konstantinos Petridis for helpful discussions, as well as Claus Grupen
-for helpful advice in searching the literature.  Tobias Schlüter made
-us aware of existing ideas on our method in~\cite{Chung:1997qd} and
-his thesis~\cite[page 123]{Schlueter:2012}. The work of D.v.D has been
-supported by the Bundesministerium f\"ur Bildung und Forschung
-(BMBF). M.C. has been supported by the ''Diamond Grant'' founded by
-the Polish Ministry of Higher Education. F.B. is grateful for the
-support by the DFG Cluster of Excellence "Origin and Structure of the
-Universe". Part of the numerical simulations have been carried out on
+for helpful advice in searching the literature.
+Tobias Schlüter made us aware of existing ideas on our method in~\cite{Chung:1997qd} and
+his thesis~\cite[page 123]{Schlueter:2012}.
+F.B. is grateful for the support by the DFG Cluster of Excellence "Origin and Structure of the
+Universe".
+M.C. has been supported by the ''Diamond Grant'' founded by
+the Polish Ministry of Higher Education.
+N.S. acknowledges the support of the Swiss National Science Foundation,
+PP00P2-144674.
+The work of D.v.D has been supported by the Bundesministerium f\"ur Bildung und Forschung
+(BMBF).
+Part of the numerical simulations have been carried out on
 the computing facilities of the Computational Center for Particle and
